---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/kamino.css", "../../../z-assemblers/charts.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/header.html"
      after_body: "../../../z-assemblers/footer.html"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

library(htmltools) # needed to include html snippets
library(tidyverse)
library(viridis) # color palettes to make plots that are pretty, better represent the data, easier to read by those with colorblindness, and print well in grey scale

# needed to include bib references
library(knitcitations)
library(bibtex)

```

<div class="activity">
CHARTS
</div>

# Bar Polar Stacked
## Real-life case: Quality Control in Wine Production

> Don't call the world dirty because you forgot to clean your glasses...\
--- Aaron Hill\



***

# Load the data
## Wine quality based on physicochemical data

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
data <- read.csv("../archetypes/winequality-red.csv", header = TRUE, stringsAsFactors = TRUE)
data$quality <- as.character(data$quality)
data

```

# Prepare the data
## Prepare the dataset for labels and scaling

```{r data-prep, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Transform data in a tidy format (long format)
data <- data %>% gather(key = "observation", value="value",-c(1,2)) 
data

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
nObsType <- nlevels(as.factor(data$observation))
to_add <- data.frame( matrix(NA, empty_bar*nlevels(data$quality)*nObsType, ncol(data)) )
colnames(to_add) <- colnames(data)
to_add$group <- rep(levels(data$quality), each=empty_bar*nObsType )
data <- rbind(data, to_add)
data <- data %>% arrange(quality, Wine)
data$id <- rep( seq(1, nrow(data)/nObsType), each=nObsType)
data

# Get the name and the y position of each label
label_data <- data %>% group_by(id, Wine) %>% summarize(tot=sum(value))
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) / number_of_bar     # Substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right (1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)
label_data

# Prepare a data frame for base lines
base_data <- data %>% 
  group_by(quality) %>% 
  summarize(start=min(id), end=max(id) - empty_bar) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))
base_data

# Prepare a data frame for grid (scales)
grid_data <- base_data
grid_data$end <- grid_data$end[c(nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
grid_data <- grid_data[-1,]
grid_data

```

# Plot the chart
## Physicochemical properties in wine such as its density, alcohol or pH values

```{r draw-plot, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show', fig.width=13, fig.height=8}

p <- ggplot(data) +      
  
  # Add the stacked bar
  geom_bar(aes(x=as.factor(id), y=value, fill=observation), stat="identity", alpha=0.5) +
  scale_fill_viridis(discrete=TRUE) +
  
  # Add a val=100/75/50/25 lines. Do it at the beginning to make sure barplots are OVER it
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "grey", alpha=1, size=0.3, inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "grey", alpha=1, size=0.3, inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "grey", alpha=1, size=0.3, inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 150, xend = start, yend = 150), colour = "grey", alpha=1, size=0.3, inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 200, xend = start, yend = 200), colour = "grey", alpha=1, size=0.3, inherit.aes = FALSE ) +
  
  # Add text showing the value of each 100/75/50/25 lines
  ggplot2::annotate("text", x = rep(max(data$id),5), y = c(0, 50, 100, 150, 200), label = c("0", "50", "100", "150", "200") , color="grey", size=6, angle=0, fontface="bold", hjust=1) +
  
  ylim(-150, max(label_data$tot, na.rm=T)) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() +
  
  # Add labels on top of each bar
  geom_text(data=label_data, aes(x=id, y=tot+10, label=Wine, hjust=hjust), color="black", fontface="bold", alpha=0.6, size=5, angle=label_data$angle, inherit.aes=FALSE) +
  
  # Add base line information
  geom_segment(data=base_data, aes(x = start, y = -5, xend = end, yend = -5), colour = "black", alpha=0.8, size=0.6, inherit.aes=FALSE) +
  geom_text(data=base_data, aes(x = title, y = -18, label=group), hjust=c(1,1,0,0), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes=FALSE)

p

```

# Exercises and practice
## Knime and R practice solutions


# References
## The citations and data sources used for this case

Source: <a href="https://scialert.net/fulltext/?doi=jas.2012.598.601#924578_ja">Quality Control in Wine Production</a>

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "../archetypes/winequality-red.bib")

```


```{r mark-complete-button, message=FALSE, warning=FALSE, echo=FALSE}

# echo=FALSE will exclude block from code folding
# Include external html content for “Mark Complete” button
htmltools::includeHTML("mark-complete-button.html")

```


```{r mark-complete-click, child='mark-complete-click.Rmd'}

# JS event handler for button click

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

