---
pagetitle: "Worldwide covid19 summary"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE, class.source = 'fold-hide')
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(tidyr)
library(ggiraph)

```

ANALYTICS

# Worldwide covid19 summary 
## Descriptive



```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Nick Fewings on Unsplash"}

masthead <- "assets/nick-fewings-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Keep your face always toward the sunshine, and shadows will fall behind you...\
--- Walt Whitman\

***

Descriptive analytics or exploratory analysis is an integral part of the machine-learning process. Descriptive data analysis is the process of interpreting datasets while summarizing their various characteristics with the help of data visualization methods. We need to understand how our variables behave before we feed it into a machine learning model. 


### Ingest the data


```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read.csv("archetypes/worldometer_coronavirus_summary_data.csv")

df

```

### Understand the data
```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}
df1<-na.omit(df)
df1
```

Let's review the datatypes of the data as well as summary statistics of the data. 



```{r}
df2 <- df1 %>% select(country, continent, total_cases_per_1m_population,total_deaths_per_1m_population,total_tests_per_1m_population)
df2
```

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

str(df2) #to see datatypes 
summary(df2)

```

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 13, fig.height = 7, out.width = "100%"}

v1<-ggplot(df2, aes(x = continent, y = total_cases_per_1m_population, fill = continent)) + 
  geom_boxplot(outlier.colour = "red", outlier.shape = 1)+
  scale_fill_brewer(palette="Dark2") + 
  theme_classic()+ 
  labs(x="", y="", title="Total cases per 1m population by continent")

girafe(ggobj = v1, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 13, fig.height = 7, out.width = "100%"}

v2<-ggplot(df2, aes(x = continent, y = total_deaths_per_1m_population, fill = continent)) + 
  geom_boxplot(outlier.colour = "red", outlier.shape = 1)+
  scale_fill_brewer(palette="Dark2") + 
  theme_classic()+ 
  labs(x="", y="", title="Total deaths per 1m population by continent")

girafe(ggobj = v2, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 13, fig.height = 7, out.width = "100%"}

v3<-ggplot(df2, aes(x = continent, y = total_tests_per_1m_population, fill = continent)) + 
  geom_boxplot(outlier.colour = "red", outlier.shape = 1)+
  scale_fill_brewer(palette="Dark2") + 
  theme_classic()+ 
  labs(x="", y="", title="Total tests per 1m population by continent")

girafe(ggobj = v3, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


### References
#### citations for narrative and data sources


* Data sources: Kaggle, this file contains summary covid-19 related data for each of the 218 countries, as of 2022-01-05. [GO](https://www.kaggle.com/josephassaker/covid19-global-dataset?select=worldometer_coronavirus_summary_data.csv){target="_blank"}
