---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(rvest)
library(tidyverse)
library(reactable)
library(ggiraph)


```

<div class="activity">
INGEST  
</div>

# What are the sunniest cities in the world, by continent
## Web scraping

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Jason Wong on Unsplash"}

masthead <- "assets/jason-wong-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Just living is not enough... One must have sunshine, freedom, and a little flower...\
--- Hans Christian Andersen\

The data we need is stored in several tables on this <a href="https://en.wikipedia.org/wiki/List_of_cities_by_sunshine_duration" target="_blank" rel="noopener noreferrer">Wikipedia page - List of cities by sunshine duration</a>. 

***

### Let the scraping begin...
#### Africa

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url = 'https://en.wikipedia.org/wiki/List_of_cities_by_sunshine_duration'

africa = url %>% 
    read_html() %>%
    html_node(xpath = '//*[@id="mw-content-text"]/div[1]/table[2]') %>%
    html_table(fill = TRUE)

africa

```


#### Asia


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

asia <- url %>% 
    read_html() %>%
    html_node(xpath = '//*[@id="mw-content-text"]/div[1]/table[3]') %>%
    html_table(fill = TRUE)

asia

```


#### Europe


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

europe <- url %>% 
  read_html() %>%
  html_node(xpath = '//*[@id="mw-content-text"]/div[1]/table[4]') %>%
  html_table(fill = TRUE)

europe

```


#### North Central America


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

north_central_america <- url %>% 
  read_html() %>%
  html_node(xpath = '//*[@id="mw-content-text"]/div[1]/table[5]') %>%
  html_table(fill = TRUE)

north_central_america

```


#### South America


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

south_america <- url %>% 
  read_html() %>%
  html_node(xpath = '//*[@id="mw-content-text"]/div[1]/table[6]') %>%
  html_table(fill = TRUE)

south_america$Year = as.character(south_america$Year)
south_america

```


#### Oceania


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

oceania <- url %>% 
  read_html() %>%
  html_node(xpath = '//*[@id="mw-content-text"]/div[1]/table[7]') %>%
  html_table(fill = TRUE)

oceania

```


### Voilà, all the results


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

world <- bind_rows(africa, asia, europe, north_central_america, south_america, oceania)

tabledata <- world %>% mutate(Year = round(as.numeric(gsub(",", "", Year)),digits = 0))

tabledata

```


### Let's celebrate with a plot
#### Calculate the top 10 sunniest cities on each contient


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Preparing the data for the visual
to_add <- data.frame(
  individual=c(NA,NA,NA),
  value=c(NA,NA,NA))

top_10_africa <- africa %>%
  mutate(num_year = as.numeric(gsub(",", "", Year))) %>% arrange(desc(num_year)) %>% 
  head(10) %>% 
  select(City, num_year) %>% rename(individual = City, value = num_year)

top_10_africa <- rbind(top_10_africa, to_add)%>% mutate(group = "africa")

top_10_asia <- asia %>%
  mutate(num_year = as.numeric(gsub(",", "", Year))) %>% arrange(desc(num_year)) %>% 
  head(10) %>% 
  select(City, num_year) %>% rename(individual = City, value = num_year)

top_10_asia <- rbind(top_10_asia, to_add) %>% mutate(group = "asia")

top_10_europe <- asia %>%
  mutate(num_year = as.numeric(gsub(",", "", Year))) %>% arrange(desc(num_year)) %>% 
  head(10) %>% 
  select(City, num_year) %>% rename(individual = City, value = num_year)

top_10_europe <- rbind(top_10_europe, to_add) %>% mutate(group = "europe")

top_10_north_central_america <- north_central_america %>%
  mutate(num_year = as.numeric(gsub(",", "", Year))) %>% arrange(desc(num_year)) %>% 
  head(10) %>% 
  select(City, num_year) %>% rename(individual = City, value = num_year)

top_10_north_central_america <- rbind(top_10_north_central_america, to_add) %>% mutate(group = "north central america")

# north_central_america
top_10_south_america <- south_america %>%
  mutate(num_year = as.numeric(gsub(",", "", Year))) %>% arrange(desc(num_year)) %>% 
  head(10) %>% 
  select(City, num_year) %>% rename(individual = City, value = num_year)

top_10_south_america <- rbind(top_10_south_america, to_add) %>% mutate(group = "south america")

top_10_oceania <- oceania %>%
  mutate(num_year = as.numeric(gsub(",", "", Year))) %>% arrange(desc(num_year)) %>% 
  head(10) %>% 
  select(City, num_year) %>% rename(individual = City, value = num_year)

top_10_oceania <- rbind(top_10_oceania, to_add) %>% mutate(group = "oceania")

data <- rbind(top_10_africa, top_10_asia, top_10_europe, top_10_north_central_america, top_10_south_america, top_10_oceania)

data

```

### Plot

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

empty_bar <- 3

data <- data %>% arrange(group)
data$id <- seq(1, nrow(data))

label_data <- data
number_of_bar <- nrow(label_data)
angle <- 90 - 360 * (label_data$id-0.5) /number_of_bar     # I substract 0.5 because the letter must have the angle of the center of the bars. Not extreme right(1) or extreme left (0)
label_data$hjust <- ifelse( angle < -90, 1, 0)
label_data$angle <- ifelse(angle < -90, angle+180, angle)

# prepare a data frame for base lines
base_data <- data %>% 
  group_by(group) %>% 
  summarize(start=min(id), end=max(id) - empty_bar) %>% 
  rowwise() %>% 
  mutate(title=mean(c(start, end)))

grid_data <- base_data
grid_data$end <- grid_data$end[ c( nrow(grid_data), 1:nrow(grid_data)-1)] + 1
grid_data$start <- grid_data$start - 1
grid_data <- grid_data[-1,]

# Order data:
data = data %>% arrange(id)

v1 <- ggplot(data, aes(x=as.factor(id), y=value, fill=group)) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  
  geom_bar(aes(x=as.factor(id), y=value, fill=group), stat="identity", alpha=0.5) +
  
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
#  geom_segment(data=grid_data, aes(x = 0, y = 5000, xend = 44, yend = 5000), colour = "grey", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = 0, y = 4000, xend = 44, yend = 4000), colour = "grey", alpha=0.1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = 0, y = 3000, xend = 44, yend = 3000), colour = "grey", alpha=0.1, size=0.1 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = 0, y = 2000, xend = 44, yend = 2000), colour = "grey", alpha=0.1, size=0.1 , inherit.aes = FALSE ) +
  
  # Add text showing the value of each 100/75/50/25 lines
  annotate("text", x = rep(max(data$id),3), y = c(2000, 3000, 4000), label = c("2000 hours", "3000 hours", "4000 hours") , color="grey", size=3 , angle=0, fontface="bold", hjust=1) +
  
  geom_bar(aes(x=as.factor(id), y=value, fill=group), stat="identity", alpha=0.5) +
  ylim(-2500,5000) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() + 
  # Add labels on top of each bar
  geom_text(data=label_data, aes(x=id, y=value+100, label=paste0(individual,": ",round(value,digits=0)), hjust=hjust), color="black", fontface="bold",alpha=0.6, size=4, angle= label_data$angle, inherit.aes = FALSE ) +
  
  # Add base line information
#  geom_segment(data=base_data, aes(x = start, y = -2000, xend = end, yend = -2000), colour = "black", alpha=0.8, size=0.6 , inherit.aes = FALSE )  +
  geom_text(data=base_data, aes(x = title, y = -500, label=group), colour = "black", alpha=0.8, size=4, fontface="bold", inherit.aes = FALSE)

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```



### References
#### citations for narrative and data sources

* Narrative and Data Source: https://en.wikipedia.org/wiki/List_of_cities_by_sunshine_duration

<pre>
@misc{wikipediacontributors_2019_list,
  author = {Wikipedia Contributors},
  month = {12},
  publisher = {Wikimedia Foundation},
  title = {List of cities by sunshine duration},
  url = {https://en.wikipedia.org/wiki/List_of_cities_by_sunshine_duration},
  urldate = {2021-07-26},
  year = {2019},
  organization = {Wikipedia}
}
</pre>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "web scraping" # mostly used in wranglers and analytics
keywords <- 'cities sunshine'
commands <- 'read_html html_node html_table'
sources <- 'Wikipedia'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


