---
pagetitle: "Playfair Import Export"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(reshape2)
library(tidyverse)
library(directlabels)
library(ggiraph)

```

<div class="activity">
TEMPORALS
</div>

# Playfair Import Export
# Area Bivariate

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Clem Onojeghuo on Unsplash"}

masthead <- "assets/clem-onojeghuo-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> To be a good trader, you need to trade with your eyes open, recognize real trends and turns, and not waste time or energy on regrets and wishful thinking...\
--- Alexander Elder


***

### Load data [Ingest]

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

playfair_balance <- read.csv("archetypes/playfair-import-export/playfair-import-export.csv", header = TRUE, stringsAsFactors = TRUE)
playfair_balance

```

### Prepare data [Wrangle]

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

## create min for geom_ribbon
playfair_balance$min <- with(playfair_balance, pmin(exports, imports))
year <- playfair_balance$year

## melt data
molten_data <- melt(playfair_balance,  id.vars = c("year", "min"))
molten_data

```


### Plot [ Views / Temporals ]


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide',  fig.align='center', out.width="100%"}

theme_opts <- theme(
  title = element_text(size = 8, face = 'bold'),
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.background = element_blank(),
  plot.margin = unit(c(0, 0.25, 0, 0.25), "in")
)


v1 <- ggplot(molten_data, aes(x = year, y = value)) + 
  geom_line(aes(col = variable), size  = 1) +
  geom_ribbon(aes(ymin = min, ymax = value, fill = variable), alpha = 0.3) +
  scale_color_manual(values = c("darkred", "gold3"), guide = FALSE) + 
  scale_fill_manual(values = c("#90752d", "#BB5766"), guide = FALSE) + 
  scale_x_continuous(breaks = seq(1700, 1780, 10), expand = c(0, 0)) + 
  scale_y_continuous(breaks = seq(0, 200, 10), position = "right") +
  coord_cartesian(clip="off") +
  annotate("text", x = 1710, y = 87, label = "Line of Imports", angle = 20, size = 3) +
  annotate("text", x = 1720, y = 72,  label = "Line of Exports",  angle = 345, size = 3) +
  annotate("text", x = 1730, y = 83,  label = "italic('BALANCE AGAINST')",  angle = 0, parse = TRUE) +
  annotate("text", x = 1770, y = 110, label = "italic('BALANCE in\nFAVOUR of\nENGLAND')",  angle = 0, parse = TRUE) +
  annotate("text", x = 1770, y = 82,  label = "Imports",  angle = 20, size = 3) +
  annotate("text", x = 1760, y = 131, label = "Exports",  angle = 65, size = 3) +
  ggtitle("Exports and Imports to and from DENMARK & NORWAY from 1700 to 1780") + 
  theme_bw() + 
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.9)))

```


```{r, echo=FALSE}

ggsave(filename = "assets/playfair-import-export.svg", plot = v1, width=16, height=9)

```


### References
#### Citations and data sources

* Narrative inspiration: William Playfair's Import Export, [GO](https://www.historyofinformation.com/detail.php?entryid=2929){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


