---
pagetitle: "Global Herd Immunity"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(wbstats)
library(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Global Herd Immunity
## Dot bubble strip

```{r, out.width="60%", fig.align="center", fig.cap="Photo by the CDC on Unsplash"}

masthead <- "assets/cdc-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Receiving the vaccination at the Maternal and Child Hospital in Vientiane, Laos</div>


> We are in this together, and we will get throught this, together...\
--- UN Secretary-General António Guterres\

***

### Ingest the data
#### Covid 19 vaccination survey

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "global-herd-immunity/covid-19-vaccination-survey.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = FALSE)
df

```


### Wrangle the data
#### filter, merge, enrich, select, clean, rename... the good stuff!


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df$percent_yes <- as.numeric(str_remove(df$Yes, "[%]"))

df$iso3c <- countrycode(df$Country, 'country.name', 'iso3c')

df$region <- countrycode(df$Country, 'country.name', 'un.regionsub.name')

pop <- wb_data("SP.POP.TOTL", start_date = 2020, end_date = 2020) %>%
  select(iso3c, population = SP.POP.TOTL)

df_final <- inner_join(df, pop) %>%
  select(Country, percent_yes, population, region) %>%
  mutate(region_display = case_when(
  region == "Western Europe" ~ "Europe",
  region == "Eastern Europe" ~ "Europe",
  region == "Northern Europe" ~ "Europe",
  region == "Southern Europe" ~ "Europe",
  region == "Australia and New Zealand" ~ "Asia & Oceania",
  region == "Central Asia" ~ "Asia & Oceania",
  region == "Eastern Asia" ~ "Asia & Oceania",
  region == "Southern Asia" ~ "Asia & Oceania",
  region == "South-eastern Asia" ~ "Asia & Oceania",
  region == "Latin America and the Caribbean" ~ "Latin America & Caribbean",
  region == "Northern America" ~ "North America",
  region == "Sub-Saharan Africa" ~ "Sub-Saharan Africa",
  region == "Northern Africa" ~ "Middle East and North Africa",
  region == "Western Asia" ~ "Middle East and North Africa"
  )) %>%
  mutate(region_factor = factor(region_display, 
                                 levels=c("Europe","North America","Sub-Saharan Africa", 
                                          "Middle East and North Africa",
                                          "Latin America & Caribbean",
                                          "Asia & Oceania"
                                          ))) %>%
  group_by(region_factor) %>%
  mutate(group_min = min(percent_yes), 
         group_max = max(percent_yes),
         group_average = mean(percent_yes)) %>%
  ungroup()

```

### Plot
#### TBD

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide'}

countries_displayed <- c("Kazakhstan", "Pakistan", "India", "Myanmar", "Jamaica", "Brazil", "Mexico",
                         "Nicaragua", "Jordan", "Egypt", "Gabon", "Nigeria", "Ethiopia", "United States",
                         "Canada", "Hungary", "Russia", "France", "Germany", "Britain", "Iceland")

theme_opts <- theme(
  plot.title = element_text(size=25, face="bold", hjust = 0),
  plot.subtitle = element_text(size=20, hjust = 0),
  plot.margin = margin(.25, 1, .25, .25, "cm"),
  text = element_text(size = 25),
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  axis.text.y = element_text(hjust=0),
  panel.border = element_blank(),
  panel.background = element_blank(),
  # panel.grid.minor = element_blank(),
  # panel.grid.major = element_blank(),
  legend.position = 'none'
)

v1 <- ggplot(df_final,aes(x=region_factor, y=percent_yes)) +
  geom_point(aes(size=population), shape=21, color = "#6983AE", alpha = 5/10, fill = "#AFCDDD", stroke = 1) +
  scale_size_continuous(range = c(1, 50)) +
  geom_vline(xintercept = 1) +
  geom_vline(xintercept = 2) +
  geom_vline(xintercept = 3) +
  geom_vline(xintercept = 4) +
  geom_vline(xintercept = 5) +
  geom_vline(xintercept = 6) +
  geom_hline(yintercept = 20) +
  geom_hline(yintercept = 30) +
  geom_hline(yintercept = 40) +
  geom_hline(yintercept = 50) +
  geom_hline(yintercept = 60) +
  geom_hline(yintercept = 70) +
  geom_hline(yintercept = 80) +
  geom_hline(yintercept = 90) +
  geom_hline(yintercept = 100) +
  geom_segment(aes(x = region_factor, xend = region_factor,
                   y = group_min, yend = group_max),
               colour = "#AFCDDD", size = 3) +
  stat_summary(fun.y="mean", colour = "#B27F75", geom = "crossbar", width = 0.3, fatten = 10) +
  geom_text_repel(data = df_final[df_final$Country %in% countries_displayed,],
            aes(x=region_factor, y=percent_yes, label = Country),
            nudge_x = 0.2, size = 8) +
  annotate("text", x=3.75, y=57, label= "Regional Average", size = 8, 
           colour = "#B27F75", face = "bold") +
  scale_y_continuous(position = "right", breaks=seq(20, 100, 10)) +
  scale_x_discrete(breaks = c("Europe","North America","Sub-Saharan Africa", 
                                          "Middle East and North Africa",
                                          "Latin America & Caribbean",
                                          "Asia & Oceania"
                                          ), 
                     labels = c("Europe", "North America","Sub-Saharan \nAfrica", 
                                          "Middle East \nand North Africa",
                                          "Latin America & \nCaribbean",
                                          "Asia & Oceania"))+
  coord_flip() +
  theme_opts +
  labs(title = "Would you grab the jab?",
       subtitle = "\"If a vaccine to prevent coronavirus were available right now at no cost, would \nyou agree to be vaccinated?\", percent responded yes, Aug 2020-Feb 2021")

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = FALSE, width = 0.95))
)

```


### References
#### citations for narrative and data sources

* Narrative: The Economist, May 6th 2021, [GO](https://www.economist.com/graphic-detail/2021/05/06/global-herd-immunity-is-still-out-of-reach)
* Data Source: Gallup Survey, May 2021, https://news.gallup.com/poll/348719/billion-unwilling-covid-vaccine.aspx


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

