---
pagetitle: "Mean Streets"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Mean Streets
## Scatter plot

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Johny Goerend on Unsplash"}

#masthead <- "assets/johny-goerend-unsplash.jpg"
#knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">...</div>

> Text...\
--- Attribution\

***


### Ingest the data
#### gdp and innovation rank by country and year

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load csv data file
df_country_city <- read.csv("archetypes/mean-streets/city-homicide-unodc.csv", header = TRUE, stringsAsFactors = FALSE)
df_country_city

df_region_country <- read.csv("archetypes/mean-streets/homicide_total_rate_and_count-unodc.csv", header = TRUE, stringsAsFactors = FALSE)
df_region_country

```


### Wrangle the data
#### filter, merge, enrich, select, clean, rename, wow!


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

country_list <- c(
  "El Salvador",
  "Mexico",
  "Honduras",
  "Brazil",
  "Guatemala",
  "South Africa",
  "United States",
  "Colombia",
  "Puerto Rico",
  "Jamaica"
)

df_filtered <- df_country_city %>% filter(Country %in% country_list) %>% filter(Unit == "Count")
df_filtered

df_region_country_filtered <- df_region_country %>% filter(Year == 2018)
df_region_country_filtered

```


### Plot
#### data points with smoothing


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.grid.major = element_blank(),
    legend.position='top'
  )

# Plot
v1 <- ggplot(df_final, aes(x = GDP, y = GII)) + 
  geom_point(aes( fill = REGION, color = REGION), size = 4, shape = 21) +
  geom_smooth(method="loess", se = FALSE, linetype = 'solid', size = 2, color = '#82A0C2') + # "lm", "glm", "gam", "loess" 
  scale_x_continuous() +
  scale_y_continuous() +
  scale_y_reverse() +
  labs( title = "Ideas Factories",
        subtitle = "Global Innovation and GDP",
        caption = "Source: Cornell INSEAD WIPO",
        x = "GDP per Person Employed, constant PPP, 2020",
        y = "Global Innovation Index, 2020") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```


### Plot with annotations
#### some narrative to help tell the story


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}



  
```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "assets/mean-streets-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "assets/mean-streets-sm.svg", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative Inspiration: The Economist, Mean Streets, TBD
* Data Source: TBD


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

