---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


INGEST  


# Child labor, average working hours of children
## ingest a csv file

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Zeyn Afuang on Unsplash"}

masthead <- "assets/zeyn-afuang-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> All the problems of the world - child labor, corruption - are symptoms of a spiritual disease: lack of compassion...\
--- Bill Vaughan\

***

### Ingest
#### comma-separated-values

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}


url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "child-labor/average-working-hours-of-children.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE)

df

```


### References
#### citations for narrative and data sources

* Narrative and Data Source: Child Labor, Our World in Data,[GO](https://ourworldindata.org/child-labor){target="_blank"} 

<pre>
@misc{ortizospina_2013_child,
  author = {Ortiz-Ospina, Esteban and Roser, Max},
  title = {Child Labor},
  url = {https://ourworldindata.org/child-labor},
  urldate = {2021-02-24},
  year = {2013},
  organization = {Our World in Data}
}
</pre>