---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
INGEST  
</div>

# Child labor, average working hours of children
## ingest a csv file

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Zeyn Afuang on Unsplash"}

masthead <- "assets/zeyn-afuang-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> All the problems of the world - child labor, corruption - are symptoms of a spiritual disease: lack of compassion...\
--- Bill Vaughan\

***

### Ingest
#### comma-separated-values

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

# Load csv data file
df <- read.csv("archetypes/child-labor/average-working-hours-of-children.csv", header = TRUE, stringsAsFactors = FALSE)
df

```


### References
#### citations for narrative and data sources

* Narrative and Data Source: Child Labor, Our World in Data, https://ourworldindata.org/child-labor

<pre>
@misc{ortizospina_2013_child,
  author = {Ortiz-Ospina, Esteban and Roser, Max},
  title = {Child Labor},
  url = {https://ourworldindata.org/child-labor},
  urldate = {2021-02-24},
  year = {2013},
  organization = {Our World in Data}
}
</pre>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "CSV" # mostly used in wranglers and analytics
keywords <- 'comma separated delimited'
commands <- 'read.csv'
sources <- 'Our World in Data'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

