---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

INGEST  

# Teacher Salaries
## ingest a tab-separated file (tsv)

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Jerry Wang on Unsplash"}

masthead <- "assets/jerry-wang-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> We gotta figure out a way to pay our teachers more.\
  They're like surrogate parents away from home.\
  They have such a huge responsibility and they're underappreciated and underpaid...\
--- Justin Timberlake\

***

### Ingest
#### with tab separator

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}


url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "teacher-salaries/oecd-teacher-salaries.tsv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE)

df


```



### References
#### citations for narrative and data sources

* Data Source: OECD, Teacher Salaries, [GO](https://data.oecd.org/teachers/teachers-salaries.htm){target="_blank"}
