---
pagetitle: "Teacher Salaries"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
INGEST  
</div>

# Teacher Salaries
## ingest a tab-separated file (tsv)

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Jerry Wang on Unsplash"}

masthead <- "assets/jerry-wang-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> We gotta figure out a way to pay our teachers more.\
  They're like surrogate parents away from home.\
  They have such a huge responsibility and they're underappreciated and underpaid...\
--- Justin Timberlake\

***

### Ingest
#### with tab separator

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}


url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "teacher-salaries/oecd-teacher-salaries.tsv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE)

df


```



### References
#### citations for narrative and data sources

* Data Source: OECD, Teacher Salaries, [GO](https://data.oecd.org/teachers/teachers-salaries.htm){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

