---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

INGEST  

# World Electricity Production
## Ingest a csv file with BOM encoding

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Michael Dziedzic on Unsplash"}

masthead <- "assets/michael-dziedzic-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Every decoding is another encoding...\
--- David Lodge\

***

The first character is a magical character, invisible to the human eye, but readible by a computer. It is the byte order mark (or BOM) and it’s telling the computer that the characters that follow are encoded in Unicode. This issue will often arise when saving to a CSV file from a spreadsheet.

### Ingest
#### without considering BOM

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "world-electricity-production/world-electricity-production-bom.csv"
url <- paste0(url_root, url_file)

df_no_bom <- read.csv(url, header = TRUE)

df_no_bom

names(df_no_bom)
```


### Ingest
#### recognizing BOM encoding


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "world-electricity-production/world-electricity-production-bom.csv"
url <- paste0(url_root, url_file)

df_bom <- read.csv(url, header = TRUE, fileEncoding = 'UTF-8-BOM')

df_bom

names(df_bom)

```


### References
#### citations for narrative and data sources

* Data Source: Our World in Data, Electricity Mix, [GO](https://ourworldindata.org/electricity-mix){target="_blank"}
