---
pagetitle: "Unpaid Care And Domestic Work By Region"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# Unpaid Care And Domestic Work By Region
## Box Whisker

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Sebastian Santacruz on Unsplash"}

masthead <- "assets/sebastian-santacruz-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Everybody wants to save the earth; no one wants to help mom do the dishes...\
--- P.J. O'Rourke\

***

### Load the data
#### Have women’s and men’s unpaid care and domestic work converged in high-income countries?

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "unpaid-care-and-domestic-work-by-region/unpaid-care-and-domestic-work-by-region.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = TRUE, encoding="UTF-8")
df

```


### Wrangle
#### clean column names

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Clean column name
df_wrangle <- df %>% dplyr::rename(Country=Country, Region=SDG.Region, Ratio=Ratio..W.M.)
df_wrangle

```


### Wrangle
#### calculate and filter by regional ratios to create labels


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Calculate Max and Min ratio for each Region
regionRatio <- df_wrangle %>%
  group_by(Region) %>%
  dplyr::mutate(
    MaxByR = max(Ratio, na.rm = T),
    MinByR = min(Ratio, na.rm = T)
  ) %>%
  dplyr::arrange(Region)

regionRatio

# Filter the Max and Min value only, below countries will be our labels
country_label_max <- filter(regionRatio, MaxByR == Ratio)
country_label_min <- filter(regionRatio, MinByR == Ratio & Country != "Norway")

```


### Plot
#### region and ratio


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 11),
    axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, face = "bold"),
    panel.border = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    #panel.grid.major.y = element_blank(),
    legend.position='none'
)

region_labels <- c("Australia and\nNew Zealand",
                   "Central and\nSouthern Asia",
                   "Eastern and\nSouth-Eastern Asia",
                   "Europe and\nNorth America", 
                   "Latin America and\nthe Caribbean", 
                   "Northern Africa and\nWestern Asia", 
                   "Oceania excl.\nAustralia and\nNew Zealand",
                   "Sub-Saharan Africa"
                   )

v1 <- ggplot(df_wrangle, aes(x = Region, y = Ratio)) + 
  geom_boxplot(fill = "#ACC8ED", colour = "black") +
  geom_dotplot(binaxis='y', stackdir='center', dotsize = 0.3, fill="#A6609C", color="#A6609C") +
  scale_x_discrete(labels = region_labels) +
  scale_y_continuous(breaks = seq(0,11,1), labels = seq(0,11,1)) +
  labs( 
       title = "Ratio of female-to-male time spent",
       subtitle = "on unpaid care and domestic work by region",
       x = "", 
       y = "ratio of female-to-male") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```


### Plot
#### with country labels

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

v2 <- v1 +
  geom_text(data = country_label_max, aes(label = Country, y = (Ratio + 0.2)), vjust = 0.0, hjust = 0.5) +
  geom_text(data = country_label_min, aes(label = Country, y = (Ratio - 0.2)), vjust = 1.0, hjust = 0.5)


girafe(ggobj = v2, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```

### References
#### The citations and data sources used for this case

* Narrative and Data Source: UN Women, Progress of the Worlds Women, [GO](https://www.unwomen.org/-/media/headquarters/attachments/sections/library/publications/2019/progress-of-the-worlds-women-2019-2020-en.pdf){target="_blank"}

<pre>
@misc{unwomen_2018_making,
  author = {UN Women},
  title = {MAKING EVERY WOMAN AND GIRL COUNT 2018 ANNUAL REPORT IMPLEMENTATION PHASE},
  url = {https://data.unwomen.org/sites/default/files/documents/women%20count%202018%20annual%20report.pdf},
  urldate = {2021-06-22},
  year = {2018}
}
</pre>

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

