---
pagetitle: "Global Arms Trade"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(scales)
library(ggraph)
library(igraph)
library(graphlayouts)
library(tidygraph)
library(countrycode)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
GRAPHS
</div>

# Global Arms Trade
## graph layouts


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Taylor Wilcox on Unsplash"}

masthead <- "assets/taylor-wilcox-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


***

### Ingest
#### supplier to recipient data

```{r,message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df <- read.csv("archetypes/global-arms-trade/supplier-recipient.csv", header = TRUE, stringsAsFactors = FALSE)
head(df, n = 10)

```


### Wrangle
#### clean


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_clean <- df %>% mutate(no_ordered = as.integer(no_ordered))
df_clean$no_ordered[is.na(df_clean$no_ordered)] <- 0

df_clean <- filter(df_clean, no_ordered > 0)
df_clean

```


### Wrangle
#### filter by weapon description

<pre>
  [1] "FGA aircraft"            "Frigate"                 "Patrol craft"            "APC"                     "IFV"                     "Light aircraft"          "UAV"                     "Reconnaissance ac"      
  [9] "Tank turret"             "Diesel engine"           "Light helicopter"        "Trainer/combat ac"       "Transport aircraft"      "Trainer/combat aircraft" "Turboprop/turboshaft"    "Tank destroyer"         
 [17] "AFSV"                    "Corvette"                "OPV"                     "Submarine"               "OPV/frigate"             "Armed UAV"               "Air search radar"        "Self-propelled mortar"  
 [25] "AALS"                    "Light tank"              "Landing craft"           "Tank"                    "Air/sea search radar"    "Sea search radar"        "FAC/MCM ship"            "ASW helicopter"         
 [33] "ASW sonar"               "Transport helicopter"    "MCM ship"                "Nuclear submarine"       "Anti-ship helicopter"    "Combat helicopter"       "Armoured car"            "APC/APV"                
 [41] "Self-propelled gun"      "Anti-ship missile"       "BVRAAM"                  "Naval SAM system"        "Mortar"                  "Towed gun"               "ASM"                     "Turbofan"               
 [49] "FAC"                     "Portable SAM"            "MP aircraft radar"       "Recce satellite"         "Submarine sonar"         "Replenishment ship"      "OPV/transport ship"      "Light transport ac"     
 [57] "MP aircraft"             "AS/ASW torpedo"          "Multifunction radar"     "ABL"                     "Trainer aircraft"        "SAM system"              "AEV/ARV"                 "ARV"                    
 [65] "Turboprop"               "ASW aircraft"            "Arty locating radar"     "IFV turret"              "Anti-tank missile"       "Combat ac radar"         "Aircraft recce system"   "Air refuel system"      
 [73] "MP UAV"                  "Multifuntion radar"      "SAM"                     "AEW radar"               "APC turret"              "Naval gun"               "Supply ship"             "Helicopter"             
 [81] "Fire control radar"      "APV"                     "multi-function radar"    "EO search/fire control"  "Multi-function radar"    "Transport ship"          "Ground surv radar"       "Landing ship"           
 [89] "ASW MRL"                 "Reconnaissance AV"       "AEW helicopter"          "Mobile AD system"        "Guided bomb"             "ALV"                     "SPG chassis"             "Destroyer"              
 [97] "Tanker/transport ac"     "Anti-ship missile/SSM"   "AA gun"                  "CIWS"                    "AA gun system"           "Training ship"           "ACV/landing craft"       "Gas turbine"            
[105] "SPG turret"              "Support ship"            "SAM/ABM system"          "AEW&C aircraft"          "ISR aircraft"            "SIGINT aircraft"         "ASM/anti-tank missile"   "ABM"                    
[113] "AGS aircraft"            "ARM"                     "Guided rocket"           "Combat heli radar"       "Transport ac/helicopter" "Aircraft EO system"      "ASW torpedo"             "Guided shell"           
[121] "Self-propelled MRL"      "ABM system"              "ABM missile"            
</pre>


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_weapons <- df_clean %>%
  group_by(weapon_description) %>%
  summarise(
      total_orders = sum(no_ordered, na.rm = T),
      count = n()
  ) %>%
  arrange(-count, .by_group = TRUE)

df_weapons
  
# unique(df_clean$weapon_description)
df_filtered <- filter(df_clean, weapon_description == "Submarine")
df_filtered

```


### Wrangle 
#### transform to graph structure 


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# Convert data to graph data frame
# directed=true means it is a flow not just an association between nodes
g <- graph.data.frame(df_filtered, directed = TRUE)
g

```

### Ensuring proper attributes for Edges
#### Computing Edges Weights (as per number of students flow)

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df_graph <- g %>% 
   as_tbl_graph() %>% 
    activate(edges) %>% 
    # computes numbers between 0 and 1 according to Number of Student Number
    mutate(edge_weights = log10(no_ordered))
df_graph

```

### Ensuring proper attributes for Nodes
#### Grouping all Nodes by Continents

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df_graph <- df_graph %>% 
  activate(nodes) %>%
  mutate(group = countrycode(name, origin = 'country.name', destination = 'iso3c'))
df_graph

```


### Layout & Aesthetic Parameters
#### Choose the types of Edges you would like to display


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}


## Edge Types
# geom_edge_arc
# geom_edge_arc0
# geom_edge_arc2
# geom_edge_density
# geom_edge_diagonal
# geom_edge_diagonal0
# geom_edge_diagonal2
# geom_edge_elbow
# geom_edge_elbow0
# geom_edge_elbow2
# geom_edge_fan
# geom_edge_fan0
# geom_edge_fan2
# geom_edge_hive
# geom_edge_hive0
# geom_edge_hive2
# geom_edge_link
# geom_edge_link0
# geom_edge_link2

## Layouts can be computationally intensive
# Uncomment only for use

##################
# igraph layouts #
##################

# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'bipartite')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'circle')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'dh')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'drl')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'fr')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'gem')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'graphopt')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'grid')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'kk')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'lgl')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'mds')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'nicely')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'sphere')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'star')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'sugiyama')

## graphlayouts
layout <- create_layout(df_graph, layout = "nicely")
# layout <- create_layout(df_graph, layout = "stress")
# layout <- create_layout(df_graph, layout = "focus", focus = 1)


```


### View
#### graph


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}


theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.background = element_blank(),
)

v1 <- ggraph(layout) + 
  geom_edge_diagonal(aes(edge_width = edge_weights)) + # aes(edge_width = edge_weights)
  geom_node_point(size=2) +
  geom_node_label( aes(label=name), repel = FALSE, vjust = -0.5, hjust = 0.5, size = 4, family = "inconsolata") +
  coord_fixed(clip = 'off') + 
  theme_graph()+
  theme(legend.position = "top")

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))


```


### References
#### citations for narrative and data sources

Source: 



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


