---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggraph)
library(igraph)
library(graphlayouts)
library(tidygraph)
library(countrycode)

library(knitcitations)
library(bibtex)
```

<div class="activity">
GRAPHS
</div>

# Ethiopian Students Flow
## graph layouts


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Taylor Wilcox on Unsplash"}

masthead <- "assets/taylor-wilcox-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


***

## Load data [Ingest]

```{r,message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df_f <- read_csv("./archetypes/students-flow-ethiopia/students-flow-ethiopia.csv")
df_f


```
``

# Prepare data [Wrangle] - Part I
## Select only the fields which will be part of the flow (Nodes and Edges)

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df_f <- df_f %>% select(Source_country,Destination_country,Student_Num)
df_f

```

# Prepare data [Wrangle] - Part II 
## Format the data into a graph data frame 
## Creating two important sets: Nodes and Edges between the nodes


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# Convert data to graph data frame
# directed=true means it is a flow not just an association between nodes
g <- graph.data.frame(df_f, directed = TRUE)
g

```

# Ensuring proper attributes for Edges
## Computing Edges Weights (as per number of students flow)

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

cg <- g %>% 
   as_tbl_graph() %>% 
    activate(edges) %>% 
    # computes numbers between 0 and 1 according to Number of Student Number
    mutate(edge_weights = log10(Student_Num)/10)

cg


```

# Ensuring proper attributes for Nodes
## Grouping all Nodes by Continents

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}


cg <- cg %>% 
  activate(nodes) %>%
  mutate(group = countrycode(name, origin = 'country.name', destination = 'continent'))


cg


```


## Layout & Aesthetic Parameters
### Choose the types of Edges you would like to display

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}


## Edge Types
# geom_edge_arc
# geom_edge_arc0
# geom_edge_arc2
# geom_edge_density
# geom_edge_diagonal
# geom_edge_diagonal0
# geom_edge_diagonal2
# geom_edge_elbow
# geom_edge_elbow0
# geom_edge_elbow2
# geom_edge_fan
# geom_edge_fan0
# geom_edge_fan2
# geom_edge_hive
# geom_edge_hive0
# geom_edge_hive2
# geom_edge_link
# geom_edge_link0
# geom_edge_link2


## Layouts can be computationally intensive
# Uncomment only for use


## graphlayouts
 #nicely <- create_layout(cg, layout = "nicely")
#stress <- create_layout(cg, layout = "stress")
 radial <- create_layout(cg, layout = "focus", focus = 1)


```


## Plot with Layout


```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show', fig.width=12, fig.height=12}


theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.background = element_blank(),
)


#enter graph layout
v1 <- ggraph(radial) + 
  # enter edge type
  geom_edge_diagonal(arrow = arrow(ends = "last", angle = 30, length = unit(.5,"cm")), aes(edge_width = edge_weights, edge_colour = Student_Num)) + 
  geom_node_point(aes(color = group, size = group)) +
  geom_node_text(repel = TRUE, aes(label = name, color = group)) +
  theme_graph()+
  theme(legend.position = "top")

v1


```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/cites-wildlife-trade-database-fs.svg", plot = v1, width=720/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/cites-wildlife-trade-database-sm.svg", plot = v1, width=2.25, height=2.25)

```



### References
#### citations for narrative and data sources

Source: UNESCO, Global Flow of Tertiary-Level Students, http://uis.unesco.org/en/uis-student-flow#slideoutmenu 

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "./citations/students-flow-ethiopia.bib")

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "" # mostly used in wranglers and analytics
keywords <- 'global flow of tertiary-Level students'
commands <- 'graph_from_data_frame create_layout'
sources <- 'UNESCO'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


