---
pagetitle: "UK Government Spending"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(scales)
library(ggraph)
library(igraph)
library(graphlayouts)
library(tidygraph)
library(countrycode)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
GRAPHS
</div>

# UK Government Spending
## graph layouts


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Taylor Wilcox on Unsplash"}

masthead <- "assets/taylor-wilcox-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


***

### Ingest
#### supplier to recipient data

```{r,message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

nodes <- read.csv("archetypes/uk-government-spending/nodes.csv", header = TRUE, stringsAsFactors = FALSE)
nodes$color <- as.character(paste0("#", nodes$color))
head(nodes, n = 10)

edges <- read.csv("archetypes/uk-government-spending/edges.csv", header = TRUE, stringsAsFactors = FALSE)
edges$color <- as.character(paste0("#", edges$color))
head(edges, n = 10)

```


### Wrangle 
#### transform to graph structure 


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# Convert data to graph data frame
# directed=true means it is a flow not just an association between nodes
g <- graph.data.frame(edges, directed=TRUE, vertices=nodes)
g

```

### Ensuring proper attributes for Edges
#### Computing Edges Weights (as per number of students flow)

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df_graph <- g %>% 
   as_tbl_graph() %>% 
    activate(edges) %>% 
    # computes numbers between 0 and 1 according to Number of Student Number
    mutate(edge_weights = log10(billion_pounds)/10)
df_graph

```

### Layout & Aesthetic Parameters
#### Choose the types of Edges you would like to display


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}


## Edge Types
# geom_edge_arc
# geom_edge_arc0
# geom_edge_arc2
# geom_edge_density
# geom_edge_diagonal
# geom_edge_diagonal0
# geom_edge_diagonal2
# geom_edge_elbow
# geom_edge_elbow0
# geom_edge_elbow2
# geom_edge_fan
# geom_edge_fan0
# geom_edge_fan2
# geom_edge_hive
# geom_edge_hive0
# geom_edge_hive2
# geom_edge_link
# geom_edge_link0
# geom_edge_link2

## Layouts can be computationally intensive
# Uncomment only for use

##################
# igraph layouts #
##################

# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'bipartite')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'circle')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'dh')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'drl')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'fr')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'gem')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'graphopt')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'grid')
layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'kk')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'lgl')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'mds')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'nicely')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'sphere')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'star')
# layout <- create_layout(df_graph, layout = 'igraph', algorithm = 'sugiyama')

## graphlayouts
# layout <- create_layout(df_graph, layout = "nicely")
# layout <- create_layout(df_graph, layout = "stress")
# layout <- create_layout(df_graph, layout = "focus", focus = 1)


```


### View
#### graph


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}


theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.background = element_blank(),
)

colors <- unique(E(df_graph)$color)
color_palette <- c( colors )
color_palette

v1 <- ggraph(layout) + 
  geom_edge_elbow(aes(edge_width = edge_weights, color = color)) + # aes(edge_width = edge_weights)
  geom_node_point(aes(size=billion_pounds, color = color)) +
  geom_node_label( aes(label=name, fill = color), color = "white", repel = FALSE, vjust = -0.5, hjust = 0.5, size = 4, family = "inconsolata") +
  scale_size_continuous(range = c(1, 12)) + 
  scale_color_manual(values = color_palette) +
  coord_fixed(clip = 'off') + 
  theme_graph()+
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 14,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))


```


### References
#### citations for narrative and data sources

Source: 



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


