---
pagetitle: "Covid by European regions"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(sf)
library(scales) 
library(ggthemes) 
library(ggiraph)

```

<div class="activity">
MAPS  
</div>

# Tracking the coronavirus across Europe
## Point Spike Map

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Nick Fewings on Unsplash"}

masthead <- "assets/nick-fewings-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Bournemouth, UK</div>

> Greenhouse gases, just like viruses, do not respect national boundaries...\
--- António Guterres - Secretary-General, United Nations\

***

### Ingest
#### Data points

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read_csv("archetypes/covid-by-european-regions/covid-by-european-regions.csv")
df

```
#### Maps

```{r echo=TRUE, message=FALSE, warning=FALSE, include=FALSE, class.source = 'fold-hide'}

level0 <- st_read("archetypes/covid-by-european-regions/NUTS_RG_20M_2021_4326_LEVL_0.geojson")
level1 <- st_read("archetypes/covid-by-european-regions/NUTS_RG_20M_2021_4326_LEVL_1.geojson")
level2 <- st_read("archetypes/covid-by-european-regions/NUTS_RG_20M_2021_4326_LEVL_2.geojson")
level3 <- st_read("archetypes/covid-by-european-regions/NUTS_RG_20M_2021_4326_LEVL_3.geojson")

```

### Wrangling
#### Prepare map

```{r echo=TRUE, message=FALSE, warning=FALSE, class.source = 'fold-show'}

df_level0 <- df %>% 
  filter(LEVEL == "level0")

df_level1 <- df %>% 
  filter(LEVEL == "level1")

df_level2 <- df %>% 
  filter(LEVEL == "level2")

df_level3 <- df %>% 
  filter(LEVEL == "level3")

map0 <- inner_join(level0, df_level0, by = "NUTS_ID")
map1 <- inner_join(level1, df_level1, by = "NUTS_ID")
map2 <- inner_join(level2, df_level2, by = "NUTS_ID")
map3 <- inner_join(level3, df_level3, by = "NUTS_ID")

europe <- rbind(map0, map1, map2, map3)

# remove unnecessary objects from workspace
rm(map0, map1, map2, map3, df_level0, df_level1, df_level2, df_level3, level0, level1, level2, level3)

```


### View
#### a spike maker

This is a function to create the spike geometry so that it can be rendered using geom_sf.

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

#---------------
# story_data <- df

# DATA REQUIRES FIELD PARAMETERS:
spike_min_height <- 1
spike_max_height <- 5

# WIDTH RANGE OF SPIKE (VARIABLE)
spike_min_width <- 0.5
spike_max_width <- 1

spike_pnts <- df %>%
  # REMOVE NA & ZEROS
  filter(!is.na(COUNT)) %>%
  filter(COUNT != 0) %>% 
  # NORMALIZE VALUE RANGE
  mutate(HEIGHT = round(rescale(COUNT, 
                                to = c(spike_min_height, 
                                       spike_max_height)), 
                        digits = 3)) %>% 
  mutate(WIDTH = round(rescale(COUNT,
                                to = c(spike_min_width, spike_max_width)),
                       digits = 3)) %>%
  # GENERATE SPIKE POINTS
  mutate(x1 = LONGITUDE,
         y1 = LATITUDE,
         x2 = LONGITUDE - WIDTH,
         y2 = LATITUDE,
         x3 = LONGITUDE,
         y3 = LATITUDE + HEIGHT,
         x4 = LONGITUDE + WIDTH,
         y4 = LATITUDE,
         x5 = LONGITUDE,
         y5 = LATITUDE)


# CREATE SF POLYGON GEOMETRY
spike_dfs <- lapply(1:nrow(spike_pnts), function(x) {
  x1 <- spike_pnts[[x,"x1"]]
  x2 <- spike_pnts[[x,"x2"]]
  x3 <- spike_pnts[[x,"x3"]]
  x4 <- spike_pnts[[x,"x4"]]
  x5 <- spike_pnts[[x,"x5"]]
  
  y1 <- spike_pnts[[x,"y1"]]
  y2 <- spike_pnts[[x,"y2"]]
  y3 <- spike_pnts[[x,"y3"]]
  y4 <- spike_pnts[[x,"y4"]]
  y5 <- spike_pnts[[x,"y5"]]
  
  # polygon as closed shape
  polygon_list = list(rbind(c(x1, y1), c(x2, y2), c(x3, y3), c(x4, y4), c(x5, y5)))
  poly_sfc <- st_sfc(st_polygon(polygon_list))
    
  # line as open shape
  l_line = st_linestring(x = matrix(c(x2, x3, x4, y2, y3, y4), ncol = 2))
  line_sfc <- st_sfc(l_line)
    
  # carry over all attributes
  lnd_attrib = data.frame(spike_pnts[x,])
    
  # add polygon
  g1 <- as.data.frame(st_sf(lnd_attrib, geometry = poly_sfc ))
    
  # rename
  g1 <- g1 %>% rename( polygon = geometry )

  # add line
  g2 <- as.data.frame(st_sf(g1, geometry = line_sfc ))
    
  # rename
  g2 <- g2 %>% rename( line = geometry )

  # result
  as.data.frame(g2)

})

# Bind results
spiky_polys_df <- do.call(rbind, spike_dfs)

# Sort for proper overlap
spiky_polys_df <- spiky_polys_df[order(spiky_polys_df$LATITUDE, decreasing = TRUE),]

```

### Plot
#### with interactivity (hover over countries for additional details)

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width="100%"}

theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="#ffffff", colour="#ffffff"),
  panel.border = element_blank(),
  plot.background = element_blank(),
)

v1 <- ggplot() +
  geom_sf_interactive(data = europe, aes(tooltip = 
                                           paste0(Region,"\n",Country,"\n",
                                           "Case per 100k, last 7 days: ", COUNT,"\n",
                                           "Death per 100k, last 7 days: ",DEATH), data_id = NUTS_ID, fill = COUNT)) +   # spike poly fill
  geom_sf_interactive(data = spiky_polys_df, 
                      aes(geometry = polygon,
                          tooltip = paste0(Region,"\n",Country,"\n",
                                           "Case per 100k, last 7 days: ", COUNT,"\n",
                                           "Death per 100k, last 7 days: ",DEATH)), 
                      size = 0.5, color = NA, fill = "#CCCCCC", alpha = 1.0) +
  # spike line
  geom_sf(data = spiky_polys_df, aes(geometry = line), size = 0.5, color = "blue", fill = NA, alpha = 1.0) +
  scale_fill_gradient(low = "#F0F0F0", high = "#3EBCD2") +
  coord_sf(xlim = c(-24, 45), ylim = c(30, 73), expand = FALSE) +
  theme_map() +
	theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 16,
  options = list(
    opts_sizing(rescale = TRUE, width = 0.65) )
)

```


### References
#### citations for narrative and data sources

* Narrative sources: This is a reproduction of an article published in The Economist, Tracking the coronavirus across Europe [GO](https://www.economist.com/graphic-detail/tracking-coronavirus-across-europe){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
