---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: libs
---

```{r setup, include=FALSE}

library(tidyverse)
library(data.table)
library(knitr)
library(kableExtra)
library(knitcitations)
library(bibtex)

```

<div class="activity">
COLLECTIONS  
</div>

# Data Features
## What are they?

> It is a capital mistake to theorize before one has data...\
--- Sherlock Holmes, A Study in Scarlett (Arthur Conan Doyle)\

Features are __attributes__ that __describe__ the data object.  In tabular datasets, features are organized by fields or columns.  Think of features as the words you would use to describe something.  __Engineering__ and __selecting__ features to support a specific analysis objective is a key activity of the process.

* After ingesting a data file, most tools enable you to __inspect__ the __columns__ and __feature types__
* Use wrangler methods to profile features and assess their __influence__ in describing the object
* Use wrangler methods to __enrich__ a data set by adding new features
* Apply analytic methods to generate __measures__ and additional features
* Design views to help explore the __impact__ each feature has contributing to the __quality__ of the data

***

# Selecting Features

Feature selection is the thought process to focus on the data attributes that are __essential__ to the __analytic question__.  This includes not only the attributes identified for __enrichment__ (feature engineering) but also __omitting__ those that do not add __value__ to your solution.  The intended output of feature selection is having a data source that is "lean" and __fit for the purpose__.

```{r}

```


# Engineering Features

Feature engineering is the __addition__ of attributes to a dataset to __improve__ the quality, accuracy, description, and unique identification of data objects.  This requires a detailed assessment of feature __gaps__ that depreciate the full meaning of the data.  The concept is basically to identify new features needed to better __support__ the analytic __question__.

* A unique identifier
* A dimension
* A measure
* A classification
* A descriptor
* A reference

```{r}

```


# Evaluating Feature Impact

Feature impact identifies which attributes in a dataset have the greatest __effect__ on the outcomes.  Several methods may be used to measure which features are __meaningful__ to improving the accuracy and depth of analysis results.  Assessing which attributes are most impacting is a key input to the feature __selection__ process.

* Contribute to the uniqueness of the data
* Provide enhanced accuracy to the measured values, e.g. a specific date or location.
* Enable multi-dimensional analysis

```{r}

```


# Example : Who am I?

![](./assets/who-am-i.svg){height=300}




***


# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case



```{r generateBibliography, echo=FALSE, message=FALSE, warning=FALSE}

#cleanbib()
#options("citation_format" = "pandoc")
#read.bibtex(file = "../archetypes/average-working-hours-of-children.bib")

```




```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

