---
pagetitle: "Coral Bleaching"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(CoordinateCleaner)
library(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

### Coral Bleaching
#### Dot Map

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Pawah Reserve on Unsplash"}

masthead <- "assets/bawah-reserve-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> The most single revelatory three minutes for me was\
  the first time I put on scuba gear and dived on a coral reef...\
--- David Attenborough

***


When corals are stressed by changes in conditions such as temperature, light, or nutrients, they expel the symbiotic algae living in their tissues, causing them to turn completely white. When a coral bleaches, it is not dead. Corals can survive a bleaching event, but they are under more stress and are subject to mortality.

* Change in ocean temperature: increased ocean temperature caused by climate change is the leading cause of coral bleaching. 
* Runoff and pollution: storm generated precipitation can rapidly dilute ocean water and runoff can carry pollutants — these can bleach near-shore corals. 
* Overexposure to sunlight: when temperatures are high, high solar irradiance contributes to bleaching in shallow-water corals. 
* Extreme low tides: exposure to the air during extreme low tides can cause bleaching in shallow corals.


### Ingest
#### bleach points


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_bleach <- read.csv("archetypes/coral-bleaching/bleach-pts.csv", header = TRUE, stringsAsFactors = FALSE)
head( df_bleach, n = 10 )

```


### Wrangle
#### order by severity


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# arrange high to appear on top
severity_order <- c("Severity Unknown", "No Bleaching", "Low", "Medium", "High" )
df_bleach <- df_bleach %>% dplyr::arrange(factor(SEVERITY, levels = severity_order))

```


### Base map
#### natural earth borders, coastline, and country centroids


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

ne_world <- ne_countries(scale = "small", returnclass = "sf")
ne_coastline <- ne_coastline(scale = "small", returnclass = "sf")

centroids <- countryref %>% filter(type == "country") %>%
  select(name, centroid.lon, centroid.lat) %>%
  group_by(name) %>%
  summarise(
    longitude = mean(centroid.lon, na.rm = T),
    latitude = mean(centroid.lat, na.rm = T)
  )
  
# xlim = c(-100, -40), ylim = c(-5, 35)
centroids <- centroids %>% filter(longitude >= -100 & longitude <= -40)
centroids <- centroids %>% filter(latitude >= -5 & latitude <= 35)
head(centroids, n = 10)

```


### View
#### color by severity


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}

theme_opts <- theme(
  text = element_text(family = "inconsolata"), 
  plot.title = element_text(color = "#111111", size = 14, face = "bold", family = "inconsolata"),
  plot.subtitle = element_text(color = "#111111", size = 11, family = "inconsolata"),
  plot.caption = element_text(color = "#111111", size = 8, family = "inconsolata"),
  plot.background = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="#b5dafd", colour="#b5dafd"),
  panel.border = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  legend.position = "bottom",
  legend.title = element_blank()
)

# unique(df_bleach$SEVERITY)
# color palette from severity values
severity_types <- c(
  "High" = "#FFFFFF",
  "Medium" = "#FFD9FC",
  "Low" = "#FFA8D4",
  "No Bleaching" = "#ff7f50",
  "Severity Unknown" = "#B2DFDB"
)

v1 <- ggplot() +
  geom_sf(data = ne_coastline, fill=NA, color="#bddefe", size=10.0) +
  geom_sf(data = ne_coastline, fill=NA, color="#edf5fc", size=4.0) +
  geom_sf(data = ne_world, fill="#fdfbde", color="#797875", size=0.5) +
  geom_point( data = df_bleach, aes(x=LON, y=LAT), color = "white", size=3.5) +
  geom_point( data = df_bleach, aes(x=LON, y=LAT, fill=SEVERITY), shape = 21, color = "#ff7f50", size=2.5, alpha = 0.7) +
  geom_text_repel(data = centroids, aes(x = longitude, y = latitude, label = name), 
                  size = 4, hjust = 0.5, vjust = 0.5, family = "inconsolata", fontface = "bold",
                  seed = 42, force = 10, force_pull = 0, min.segment.length = 0, color = "black", bg.color = "white", bg.r = 0.15) +
  scale_fill_manual(values = severity_types) +
  coord_sf(xlim = c(-100, -40), ylim = c(-5, 35)) +
  labs(x=NULL,
       y=NULL,
       title = "Coral Bleaching", 
       subtitle="color by severity") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 12.5,
       options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```


### References
#### Citations and data sources


* NOAA, What is coral bleaching?, https://oceanservice.noaa.gov/facts/coral_bleach.html
* Reefbase, "Coral Bleaching Dataset," downloaded from http://www.reefbase.org on 10 August 2004.  
* Global Coral Disease Database, United Nations Environment Programme -- World Conservation Monitoring Centre, 2001.


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

