---
pagetitle: "Earthquakes"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(countrycode)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Earthquakes
## Dot Map

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by USGS Photos"}

masthead <- "assets/usgs-photos-haiti.png"
knitr::include_graphics(masthead, dpi=72)

```


> I want to remember them...\
--- Rick Santos, Haiti earthquake survivor

***


### Ingest the data
#### date, location, magnitude, and impact


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read.csv("archetypes/earthquakes/significant-earthquakes-around-the-world.csv", header = TRUE, stringsAsFactors = FALSE)
head(df, n=10)

```


### Base map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

ne_world <- ne_countries(scale = "small", returnclass = "sf")
ne_world <- filter(ne_world, iso_a3 != "ATA")

```


### Wrangle
#### enrich base map with top 10 deadliest


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_worst <- df %>% slice_max(x_of_deaths, n = 10)
df_worst$ISO3C <- countrycode(df_worst$location, origin = "country.name", destination = "iso3c")
df_worst

df_worst_merge <- df_worst %>% select(ISO3C, x_of_deaths)

ne_world_worst <- merge(ne_world, df_worst_merge, by.x = "iso_a3", by.y = "ISO3C", all = TRUE)
ne_world_worst <- ne_world_worst %>% dplyr::mutate(x_of_deaths = replace_na(x_of_deaths, 0))

```


### View
#### with country highlights, points, and annotations


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}

theme_opts <- theme(
  text = element_text(family = "inconsolata"), 
  plot.title = element_text(color = "black", size = 14, face = "bold", family = "inconsolata"),
  plot.subtitle = element_text(color = "black", size = 12, family = "inconsolata"),
  plot.caption = element_text(color = "#555555", size = 8, family = "inconsolata"),
  plot.background = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  legend.position = "none",
  legend.title = element_blank()
)

v1 <- ggplot(data = ne_world_worst) +
  geom_sf(aes(fill=x_of_deaths), color="#000000", stroke=0.5) +
  geom_point( data = df, aes(x=longitude, y=latitude, color=magnitude), size=1.5, alpha = 0.8) +
  geom_point( data = df_worst, aes(x=longitude, y=latitude, size=x_of_deaths), shape = 21, color = "black", fill = NA, stroke = 1.5, alpha = 1.0) +
  geom_label_repel(data = df_worst, aes(x = longitude, y = latitude, label = paste0(location, ", ", locality, "\n", year, ", ", magnitude,  ", ", round(x_of_deaths/1000, digits = 0), "k")), 
                  size = 4, hjust = 0.5, vjust = 0.5, nudge_y = -10, family = "inconsolata", fontface = "bold",
                  seed = 42, force = 25, force_pull = 0, box.padding = 0.75, min.segment.length = 0, direction = "both", 
                  segment.color = "black", segment.size = 1.5, segment.curvature = -0.1, segment.ncp = 3, segment.angle = 20, color = "white", fill = "#D32F2F", alpha = 0.8) +
  scale_color_gradient(low = "#FFCDD2", high = "#C62828", na.value = NA) +
  scale_fill_gradient(low = "#f0f0f0", high = "#888888", na.value = NA) +
  scale_size_continuous(range = c(4, 20), guide = "none") +
  labs(x=NULL,
       y=NULL,
       title = "Deadliest Earthquakes", 
       subtitle=NULL) +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


### References
#### Citations and data sources


* Earthquake Catalog, [GO](https://earthquake.usgs.gov/earthquakes/search/){target="_blank"}  
* NOAA Satellite and Information Service, [GO](https://www.ngdc.noaa.gov/hazel/view/hazards/earthquake/event-data?minDeaths=140000){target="_blank"} 
* Our World in Data, What were the world’s deadliest earthquakes? [GO](https://ourworldindata.org/the-worlds-deadliest-earthquakes){target="_blank"} 


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

