---
pagetitle: "Meteorite Landings"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Meteorite Landings
## Dot Map

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Tasos Mansour on Unsplash"}

masthead <- "assets/tasos-mansour-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Sometimes the meaning in life hits you like a meteorite...\
--- Curtis Tyrone Jones

***


### Ingest
#### meteorite landings


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read.csv("archetypes/meteorite-landings/meteorite-landings.csv", header = TRUE, stringsAsFactors = FALSE)
head(df, n=10)

```


### Analyze
#### simplify, group, and aggregate points

* Before: 45,716 rows
* After: 9,414 rows

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df_simplified <- df %>% dplyr::mutate(reclat = round(reclat, digits = 2), reclong = round(reclong, digits = 2)) %>%
  group_by(reclat, reclong) %>%
  summarise(mass_total = sum(mass))

df_simplified

```


### Wrangle
#### order by mass


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df_sorted <- df_simplified[order(df_simplified$mass_total),]
df_sorted <- df_sorted %>% mutate(mass_total = round(mass_total, digits = 0))

```


### Base map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

ne_world <- ne_countries(scale = "small", returnclass = "sf")

```


### View
#### using mass as a visual variable for color and alpha


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}

theme_opts <- theme(
  text = element_text(family = "inconsolata"), 
  plot.title = element_text(color = "#8D9592", size = 14, face = "bold", family = "inconsolata"),
  plot.subtitle = element_text(color = "#8D9592", size = 11, family = "inconsolata"),
  plot.caption = element_text(color = "#8D9592", size = 8, family = "inconsolata"),
  plot.background = element_rect(fill = "#0b131a", color = "#0b131a"),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="#0b131a", colour=NA),
  panel.border = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  legend.position = "bottom",
  legend.background = element_rect(fill = "#0b131a", color = "#0b131a"),
  legend.text = element_text(color = "#8D9592", size = 10, family = "inconsolata"),
  legend.key.width = unit(3, 'cm'),
  legend.title = element_blank()
)

v1 <- ggplot(data = ne_world) +
  geom_sf(fill="#081b2a", color="#09325b", stroke=0.5) +
  geom_point( data = df_sorted, aes(x=reclong, y=reclat, color=mass_total, alpha=mass_total), shape = 8, size = 1.25) +
  scale_color_gradient(low = "yellow", high = "red", na.value = NA, label = function(x) sprintf("%.0f", x)) +
  scale_alpha_continuous( range = c(0.1, 0.7), guide = "none") +
  xlim(-180, 180) +
  ylim(-90, 90) +
  labs(x=NULL,
       y=NULL,
       title = "Meteorite Landings", 
       subtitle="color and alpha by mass") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```


### References
#### Citations and data sources

* Earthquake Catalog, [GO](https://earthquake.usgs.gov/earthquakes/search/){target="_blank"}
* NOAA Satellite and Information Service, [GO](https://www.ngdc.noaa.gov/hazel/view/hazards/earthquake/event-data?minDeaths=140000){target="_blank"} 
* Our World in Data, What were the world’s deadliest earthquakes? [GO](https://ourworldindata.org/the-worlds-deadliest-earthquakes){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

