---
pagetitle: "World Language Family Map"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}


knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggrepel) 
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# World Language Family Map
## Dot Map


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Macabe5387 on Wikimedia Commons"}

masthead <- "assets/kirundi.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Burundi, main road from Bujumbura to Gitega.</br>The Kirundi text on the back of the truck warns cyclists not to hold on.</div>

> Language, any language, has a dual character:\
  it is both a means of communication and a carrier of culture...\
--- Ngugi Wa Thiong'o\

***


### Ingest
#### language, coordinates, and status


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_lang <- read.csv("archetypes/world-language-family-map/languoid-geo.csv", header = TRUE, stringsAsFactors = FALSE, fileEncoding = "utf-8")
head(df_lang, n = 10)

```


### Wrangle
#### find Kirundi a.k.a. Rundi


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df_rundi <- filter(df_lang, name == "Kirundi" | name == "Rundi")
df_rundi

```




### Base map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

ne_world <- ne_countries(scale = "small", returnclass = "sf")
ne_world <- filter(ne_world, iso_a3 != "ATA")

```


### Context maps
#### macro areas


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

africa <- st_read("archetypes/world-language-family-map/africa.geojson")
australia <- st_read("archetypes/world-language-family-map/australia.geojson")
eurasia <- st_read("archetypes/world-language-family-map/eurasia.geojson")
north_america <- st_read("archetypes/world-language-family-map/north_america.geojson")
papunesia <- st_read("archetypes/world-language-family-map/papunesia.geojson")
south_america <- st_read("archetypes/world-language-family-map/south_america.geojson")

```


### View
#### color by status


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}

theme_opts <- theme(
  text = element_text(family = "inconsolata"), 
  plot.title = element_text(color = "black", size = 14, face = "bold", family = "inconsolata"),
  plot.subtitle = element_text(color = "black", size = 12, family = "inconsolata"),
  plot.caption = element_text(color = "#555555", size = 8, family = "inconsolata"),
  plot.background = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  legend.position = "bottom",
  legend.title = element_blank()
)

# unique(df_lang$status)
status_palette <- c(
  "safe" = "#40b3ec",
  "vulnerable" = "#ec7940",
  "definitely endangered" = "#ec407a",
  "severely endangered" = "#ec407a",
  "critically endangered" = "#ec407a",
  "extinct" = "#000000"
)

v1 <- ggplot(data = ne_world) +
  geom_sf(fill="white", color="#888888", size=0.5) +
  geom_sf(data = africa, fill=NA, color="#666666", size=0.5, linetype = "dotdash") +
  geom_sf(data = australia, fill=NA, color="#666666", size=0.5, linetype = "dotdash") +
  geom_sf(data = eurasia, fill=NA, color="#666666", size=0.5, linetype = "dotdash") +
  geom_sf(data = north_america, fill=NA, color="#666666", size=0.5, linetype = "dotdash") +
  geom_sf(data = papunesia, fill=NA, color="#666666", size=0.5, linetype = "dotdash") +
  geom_sf(data = south_america, fill=NA, color="#666666", size=0.5, linetype = "dotdash") +
  geom_point( data = df_lang, aes(x=longitude, y=latitude, color=status), shape=21, size=1.5, fill = "white", alpha = 0.7) +
  geom_point( data = df_rundi, aes(x=longitude, y=latitude, fill=status), shape=21, size=8, color = "white", alpha = 0.7) +
  geom_point( data = df_rundi, aes(x=longitude, y=latitude), shape=20, size=5, color = "black", alpha = 1.0) +
  geom_text_repel(data = df_rundi, aes(x = longitude, y = latitude, label = name), 
                  size = 4, nudge_x = 25, hjust = 1.0, vjust = 0.5, family = "inconsolata", fontface = "bold",
                  seed = 42, force = 1.0, force_pull = 0, box.padding = 0.75, min.segment.length = 0, direction = "x", 
                  color = "black", bg.color = "white", bg.r = 0.15) +
  scale_color_manual(values = status_palette) +
  scale_fill_manual(values = status_palette, guide = "none") +
  labs(x=NULL,
       y=NULL,
       title = "World Languages", 
       subtitle="color by status") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 8.15,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


### References
#### citations and data sources


<pre>
Hammarström, Harald & Haspelmath, Martin & Forkel, Robert. 2017.
Glottolog 3.0. Jena: Max Planck Institute for the Science of Human History.
(Available online at http://glottolog.org, Accessed on 2017-03-23.)
</pre>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

