---
pagetitle: "Drugnet"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE, dev='svg')
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(ggraph)
library(igraph)
library(graphlayouts)
library(tidygraph)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
GRAPHS
</div>

# Drugnet
## computed layouts

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo from Wikipedia"}

masthead <- "assets/jolo-island-wikipedia.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> ...didn't pursue us...As time went on, we noticed that they never pursued us...\
--- Gracia Burnham, ASG kidnap survivor\

***

This is a dichotomous adjacency matrix of drug users in Hartford.  Ties are directed and represent acquaintanceship. The network is a result of two years of ethnographic observations of people's drug habits.

* Ethnicity codes: 2 = African American; 3 = Puerto Rican/Latino; 1, 5, 6, 7 = white or other
* Gender codes: 1 = male; 2 = female; 0 = unknown

### Ingest
#### agent × event data

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_path <- "archetypes/drugnet/drugnet.csv"
df_csv <- read.csv(df_path, header=TRUE, row.names=1, check.names=FALSE, na.strings = "")
df_csv

```


### Wrangle
#### convert matrix to graph, filter by degree


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_csv[is.na(df_csv)] <- 0
matrix <- as.matrix(df_csv) 
df_graph <- graph_from_incidence_matrix(matrix)
df_graph

# less than 3 degrees
three_degrees <- which(degree(df_graph)<3)
df_graph <- delete.vertices(df_graph, three_degrees)

# remove isolates
isolates <- which(degree(df_graph)==0)
df_graph <- delete.vertices(df_graph, isolates)


# df_graph_manual <- graph_from_data_frame( df_edges, vertices=df_nodes )


```


### Analytics
#### compute sna measures


```{r}

# Network	PK
# weights	weighted
# directionality	undirected
# connectedness	false
# no. of nodes n	246
# no. of isolated nodes ni	16
# no. of edges m	2571
# no. of components |cc|	26
# max avg. path length 〈d〉 for cc	3.034
# max shortest path length d	9
# density δ	0.085
# avg. degree 〈k	20.9
# max degree k	78
# avg. clustering coeff. 〈C〉	0.753

```


### Analytics
#### compute layout


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Layouts can be computationally intensive
# Un-comment only for use

# igraph
# layout <- create_layout(cg, layout = 'dh')
# layout <- create_layout(cg, layout = 'fr')
# layout <- create_layout(cg, layout = 'gem')
# layout <- create_layout(cg, layout = 'lgl')
# layout <- create_layout(cg, layout = 'sugiyama')
# layout <- create_layout(cg, layout = 'star')
# layout <- create_layout(cg, layout = 'kk', maxiter = 100)
# layout <- create_layout(cg, layout = 'drl')
# layout <- create_layout(cg, layout = 'linear')
# layout <- create_layout(cg, layout = 'linear' , circular = TRUE)

# ggraph
# layout <- create_layout(cg, layout = 'linear')
# layout <- create_layout(cg, layout = 'linear', circular = TRUE)
layout <- create_layout(cg, layout = 'stress')
# layout <- create_layout(cg, layout = 'sparse_stress')
# layout <- create_layout(cg, layout = 'backbone')
# layout <- create_layout(cg, layout = 'pmds')
# layout <- create_layout(cg, layout = 'eigen')
# layout <- create_layout(cg, layout = 'centrality')
# layout <- create_layout(cg, layout = 'focus')
# layout <- create_layout(cg, layout = 'dendrogram')
# layout <- create_layout(cg, layout = 'unrooted')
# layout <- create_layout(cg, layout = 'matrix')
# layout <- create_layout(cg, layout = 'hive')
# layout <- create_layout(cg, layout = 'fabric')

# graphlayouts
# layout <- create_layout(cg, layout = "nicely")
# layout <- create_layout(cg, layout = "stress")
# layout <- create_layout(cg, layout = "focus", focus = 1)

```




```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Edge Types
# geom_edge_arc
# geom_edge_arc0
# geom_edge_arc2
# geom_edge_density
# geom_edge_diagonal
# geom_edge_diagonal0
# geom_edge_diagonal2
# geom_edge_elbow
# geom_edge_elbow0
# geom_edge_elbow2
# geom_edge_fan
# geom_edge_fan0
# geom_edge_fan2
# geom_edge_hive
# geom_edge_hive0
# geom_edge_hive2
# geom_edge_link
# geom_edge_link0
# geom_edge_link2
# geom_edge_loop
# geom_edge_loop0

```



### Plot
#### nicely


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    # plot.margin = unit(c(1.5,1,1,1), "in"),
    legend.position='none'
)

v1 <- ggraph(layout) + 
  geom_edge_link() +
  geom_node_point(size = 2) +
  geom_node_label(aes(label = name), size = 4) +
  theme_graph() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 14,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)


```


### References
#### citations for narrative and data sources


* Narrative: WEEKS, M. R., CLAIR, S., BORGATTI, S. P., RADDA, K. & SCHENSUL, J. J. 2002. Social networks of drug users in high-risk sites: Finding the connections. AIDS and Behaviour, 6, 193-206.
* Data: UCINET, Covert Networks, https://sites.google.com/site/ucinetsoftware/datasets/covert-networks


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```




