---
pagetitle: "Human disease network"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE, dev='svg')
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(ggraph)
library(igraph)
library(graphlayouts)
library(tidygraph)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
GRAPHS
</div>

# Human disease network
## Node-links - Association

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Engin Akyurt on Unsplash"}

masthead <- "assets/engin-akyurt-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> One of the greatest diseases is to be nobody to anybody...\
--- Mother Teresa\

***

### Ingest
#### border graph

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_path <- "archetypes/human-disease-network/human-disease-network-edges.csv"
df <- read.csv(df_path, header = TRUE, stringsAsFactors = FALSE)

head(df)

```


### Prepare data [Wrangle]
#### Format the data into a graph data frame 


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_filter <- filter(df, DISORDER_TYPE == 'Cancer')

# Convert data to graph data frame
# directed FALSE means no flow. It's just an association
df_graph <- graph.data.frame(df, directed = FALSE)
df_graph

```




## Layout & Aesthetic Parameters
### Choose the types of Edges you would like to display


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# igraph layouts

# bipartite <- create_layout(df_graph, layout = 'igraph', algorithm = 'bipartite')
# circle <- create_layout(df_graph, layout = 'igraph', algorithm = 'circle')
# dh <- create_layout(df_graph, layout = 'igraph', algorithm = 'dh')
# drl <- create_layout(df_graph, layout = 'igraph', algorithm = 'drl')
# fr <- create_layout(df_graph, layout = 'igraph', algorithm = 'fr')
# gem <- create_layout(df_graph, layout = 'igraph', algorithm = 'gem')
# graphopt <- create_layout(df_graph, layout = 'igraph', algorithm = 'graphopt')
# grid <- create_layout(df_graph, layout = 'igraph', algorithm = 'grid')
# kk <- create_layout(df_graph, layout = 'igraph', algorithm = 'kk')
# lgl <- create_layout(df_graph, layout = 'igraph', algorithm = 'lgl')
# mds <- create_layout(df_graph, layout = 'igraph', algorithm = 'mds')
# nicely <- create_layout(df_graph, layout = 'igraph', algorithm = 'nicely')
# sphere <- create_layout(df_graph, layout = 'igraph', algorithm = 'sphere')
# star <- create_layout(df_graph, layout = 'igraph', algorithm = 'star')
# sugiyama <- create_layout(df_graph, layout = 'igraph', algorithm = 'sugiyama')

# ggraph layouts

# backbone <- create_layout(df_graph, layout = 'backbone')

# centrality_bc <- betweenness(df_graph_directed)
# centrality_cc <- closeness(df_graph_directed)
# centrality <- create_layout(df_graph_undirected, layout = 'centrality', centrality = centrality_bc)

# eigen <- create_layout(df_graph, layout = 'eigen', type = "laplacian", eigenvector = "smallest")

# fabric <- create_layout(cg, layout = 'fabric')
# focus <- create_layout(df_graph_directed, layout = 'focus', focus = 1)

# hive <- create_layout(df_graph, layout = 'hive', axis = friends, sort.by = degree)

# linear <- create_layout(df_graph, layout = 'linear')
# matrix <- create_layout(df_graph, layout = 'matrix')

# pmds_pivots <- 3
# pmds <- create_layout(df_graph, layout = 'pmds', pivots = pmds_pivots)

stress <- create_layout(df_graph, layout = 'stress')

# df_unrooted <- df_graph_undirected %>%  activate(edges) %>%  mutate(length = runif(n()))
# unrooted <- create_layout(df_graph_undirected, layout = 'unrooted' )

```


## Layout & Aesthetic Parameters
### Choose the types of Edges you would like to display


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Edge Types
# geom_edge_arc
# geom_edge_arc0
# geom_edge_arc2
# geom_edge_density
# geom_edge_diagonal
# geom_edge_diagonal0
# geom_edge_diagonal2
# geom_edge_elbow
# geom_edge_elbow0
# geom_edge_elbow2
# geom_edge_fan
# geom_edge_fan0
# geom_edge_fan2
# geom_edge_hive
# geom_edge_hive0
# geom_edge_hive2
# geom_edge_link
# geom_edge_link0
# geom_edge_link2
# geom_edge_loop
# geom_edge_loop0

```



### Plot
#### nicely

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    # plot.margin = unit(c(1.5,1,1,1), "in"),
    legend.position='top'
)

v1 <- ggraph(stress) + 
  geom_edge_diagonal(aes(colour = factor(DISORDER_TYPE)), alpha = 0.6) +
  geom_node_point(size = 1, alpha = 0.6) +
  theme_graph()+
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 1280/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)


```


### References
#### citations for narrative and data sources

* Narrative and Data: The Human Disease Network, Goh K-I, Cusick ME, Valle D, Childs B, Vidal M, Barabási A-L (2007), Proc Natl Acad Sci USA 104:8685-8690.


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


