---
pagetitle: "London Gang"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE, dev='svg')
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(ggraph)
library(igraph)
library(graphlayouts)
library(tidygraph)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
GRAPHS
</div>

# London Gang
## computed layouts

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo from Wikipedia"}

masthead <- "assets/jolo-island-wikipedia.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> ...didn't pursue us...As time went on, we noticed that they never pursued us...\
--- Gracia Burnham, ASG kidnap survivor\

***

Data is on co-offending in a London-based inner-city street gang, 2005-2009, operating from a social housing estate. Data comes from anonymised police arrest and conviction data for ‘all confirmed’ members of the gang.

Network tie values:

* 1 (hang out together)
* 2 (co-offend together)
* 3 (co-offend together, serious crime)
* 4 (co-offend together, serious crime, kin)

Attributes: 

* Age
* Birthplace (1 = West Africa, 2= Caribbean, 3= UK, 4= East Africa)
* Residence
* Arrests
* Convictions
* Prison
* Music

### Ingest
#### agent × event data

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_path <- "archetypes/london-gang/london-gang.csv"
df_csv <- read.csv(df_path, header=TRUE, row.names=1, check.names=FALSE, na.strings = "")
df_csv

```


### Wrangle
#### convert matrix to graph, filter by degree


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_csv[is.na(df_csv)] <- 0
matrix <- as.matrix(df_csv) 
df_graph <- graph_from_incidence_matrix(matrix)
df_graph

# less than 3 degrees
three_degrees <- which(degree(df_graph)<3)
df_graph <- delete.vertices(df_graph, three_degrees)

# remove isolates
isolates <- which(degree(df_graph)==0)
df_graph <- delete.vertices(df_graph, isolates)

```


### Analytics
#### compute layout


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Layouts can be computationally intensive
# Un-comment only for use

# igraph
# layout <- create_layout(cg, layout = 'dh')
# layout <- create_layout(cg, layout = 'fr')
# layout <- create_layout(cg, layout = 'gem')
# layout <- create_layout(cg, layout = 'lgl')
# layout <- create_layout(cg, layout = 'sugiyama')
# layout <- create_layout(cg, layout = 'star')
# layout <- create_layout(cg, layout = 'kk', maxiter = 100)
# layout <- create_layout(cg, layout = 'drl')
# layout <- create_layout(cg, layout = 'linear')
# layout <- create_layout(cg, layout = 'linear' , circular = TRUE)

# ggraph
# layout <- create_layout(cg, layout = 'linear')
# layout <- create_layout(cg, layout = 'linear', circular = TRUE)
layout <- create_layout(cg, layout = 'stress')
# layout <- create_layout(cg, layout = 'sparse_stress')
# layout <- create_layout(cg, layout = 'backbone')
# layout <- create_layout(cg, layout = 'pmds')
# layout <- create_layout(cg, layout = 'eigen')
# layout <- create_layout(cg, layout = 'centrality')
# layout <- create_layout(cg, layout = 'focus')
# layout <- create_layout(cg, layout = 'dendrogram')
# layout <- create_layout(cg, layout = 'unrooted')
# layout <- create_layout(cg, layout = 'matrix')
# layout <- create_layout(cg, layout = 'hive')
# layout <- create_layout(cg, layout = 'fabric')

# graphlayouts
# layout <- create_layout(cg, layout = "nicely")
# layout <- create_layout(cg, layout = "stress")
# layout <- create_layout(cg, layout = "focus", focus = 1)

```


### Plot
#### nicely


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    legend.position='none'
)

v1 <- ggraph(layout) + 
  geom_edge_link() +
  geom_node_point(size = 2) +
  geom_node_label(aes(label = name), size = 4) +
  theme_graph() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 14,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)


```


### References
#### citations for narrative and data sources


* Narrative
  * Grund, T. and Densley, J. (2015) Ethnic Homophily and Triad Closure: Mapping Internal Gang Structure Using Exponential Random Graph Models. Journal of Contemporary Criminal Justice, Vol. 31, Issue 3, pp. 354-370
  * Grund, T. and Densley, J. (2012) Ethnic Heterogeneity in the Activity and Structure of a Black Street Gang. European Journal of Criminology, Vol. 9, Issue 3, pp. 388-406.

* Data: UCINET, Covert Networks, https://sites.google.com/site/ucinetsoftware/datasets/covert-networks


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

