---
pagetitle: "Open Oil"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(tidygraph)
library(igraph)
library(ggraph)
library(ggiraph)


```

<div class="activity">
GRAPHS
</div>

## Template

Source:  template

***

### Section
#### Subsection

```{r, echo=FALSE}

df_nodes_path <- "archetypes/open-oil/open-oil-nodes.csv"
df_nodes <- read.csv(df_nodes_path, header = TRUE, stringsAsFactors = FALSE)
df_nodes

df_edges_path <- "archetypes/open-oil/open-oil-edges.csv"
df_edges <- read.csv(df_edges_path, header = TRUE, stringsAsFactors = FALSE)
df_edges <- df_edges %>% select(-id)
df_edges

```


# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_graph <- graph_from_data_frame( df_edges, vertices=df_nodes )

```


### Prepare data [Wrangle]
#### Associating different attributes for your Nodes 

Creating numerical fields for the Nodes set in order to attribute the nodes size and/or color  

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}
## Creating centrality numerical field for the Nodes

# centrality_alpha()
# centrality_authority() 
# centrality_betweenness() 
# centrality_power() 
# centrality_closeness() 
# centrality_eigen() 
# centrality_hub() 
# centrality_pagerank() 
# centrality_subgraph() 
# centrality_degree() 
# centrality_edge_betweenness() 
# centrality_manual() 
# centrality_closeness_harmonic() 
# centrality_closeness_residual() 
# centrality_closeness_generalised() 
# centrality_communicability() 
# centrality_communicability_odd() 
# centrality_communicability_even() 
# centrality_subgraph_odd() 
# centrality_subgraph_even() 
# centrality_katz() 
# centrality_betweenness_network() 
# centrality_betweenness_current() 
# centrality_betweenness_communicability() 
# centrality_betweenness_rsp_simple() 
# centrality_betweenness_rsp_net() 
# centrality_information() 
# centrality_decay() 
# centrality_random_walk() 
# centrality_expected()

cg <- df_graph %>% 
    as_tbl_graph() %>% 
    activate(nodes) %>% 
  # associating random numerical value to nodes to differentiate their colors and sizes
    mutate(centrality  = centrality_betweenness())



```


### Prepare data [Wrangle]
#### Associating different attributes for your Nodes


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

## Creating group numerical field for the Nodes

# group_components() 
# group_edge_betweenness() 
# group_fast_greedy() 
# group_infomap() 
# group_label_prop() 
# group_leading_eigen() 
# group_louvain() 
# group_optimal() 
# group_spinglass() 
# group_walktrap() 
# group_biconnected_component()

cg <- cg %>% 
  activate(nodes) %>%
  # use functions to compute numerical values to attribute the edge width and/or color
  mutate(group = group_louvain())

cg

```

### Analytics
#### compute layout


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# igraph layouts

# bipartite <- create_layout(df_graph, layout = 'igraph', algorithm = 'bipartite')
circle <- create_layout(df_graph, layout = 'igraph', algorithm = 'circle')
# dh <- create_layout(df_graph, layout = 'igraph', algorithm = 'dh')
# drl <- create_layout(df_graph, layout = 'igraph', algorithm = 'drl')
# fr <- create_layout(df_graph, layout = 'igraph', algorithm = 'fr')
# gem <- create_layout(df_graph, layout = 'igraph', algorithm = 'gem')
# graphopt <- create_layout(df_graph, layout = 'igraph', algorithm = 'graphopt')
# grid <- create_layout(df_graph, layout = 'igraph', algorithm = 'grid')
# kk <- create_layout(df_graph, layout = 'igraph', algorithm = 'kk')
# lgl <- create_layout(df_graph, layout = 'igraph', algorithm = 'lgl')
# mds <- create_layout(df_graph, layout = 'igraph', algorithm = 'mds')
# nicely <- create_layout(df_graph, layout = 'igraph', algorithm = 'nicely')
# sphere <- create_layout(df_graph, layout = 'igraph', algorithm = 'sphere')
# star <- create_layout(df_graph, layout = 'igraph', algorithm = 'star')
# sugiyama <- create_layout(df_graph, layout = 'igraph', algorithm = 'sugiyama')

# ggraph layouts

# backbone <- create_layout(df_graph_undirected, layout = 'backbone')
# centrality_bc <- betweenness(df_graph)
# centrality <- create_layout(df_graph, layout = 'centrality', centrality = centrality_bc)
# eigen <- create_layout(df_graph, layout = 'eigen', type = "laplacian", eigenvector = "smallest")
# fabric <- create_layout(df_graph, layout = 'fabric')
# focus <- create_layout(df_graph_directed, layout = 'focus', focus = 1)
# hive <- create_layout(df_graph, layout = 'hive', axis = friends, sort.by = degree)
# linear <- create_layout(df_graph, layout = 'linear')
# matrix <- create_layout(df_graph, layout = 'matrix')
# pmds_pivots <- 3
# pmds <- create_layout(df_graph, layout = 'pmds', pivots = pmds_pivots)
stress <- create_layout(df_graph, layout = 'stress')
# unrooted <- create_layout(df_graph, layout = 'unrooted' )

# stress_m <- create_layout(df_graph_manual, layout = 'stress')

```


### Plot
#### nicely


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    # plot.margin = unit(c(1.5,1,1,1), "in"),
    legend.position='none'
)

v1 <- ggraph(stress) + 
  geom_edge_link() +
  geom_node_point(size = 2) +
  # geom_node_label(aes(label = name), size = 2) +
  theme_graph() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)


```


### References
#### citations for narrative and data sources


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```




```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


