---
pagetitle: "Open Beer Database"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE, dev='svg')
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggraph)
library(igraph)
library(graphlayouts)
library(tidygraph)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
GRAPHS
</div>

# Open Beer Database
## Node-links - Association

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Marjan Blan on Unsplash"}

masthead <- "assets/marjan-blan-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> We are defined not by our borders but by our bonds...\
--- Barack Obama\

***

### Ingest
#### border graph

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_beers <- read.csv("archetypes/open-beer-db/beers.csv", header = TRUE, stringsAsFactors = FALSE, fileEncoding = "utf-8")
df_beers

df_breweries <- read.csv("archetypes/open-beer-db/breweries.csv", header = TRUE, stringsAsFactors = FALSE)
df_breweries

df_breweries_geocode <- read.csv("archetypes/open-beer-db/breweries-geocode.csv", header = TRUE, stringsAsFactors = FALSE)
df_breweries_geocode

df_categories <- read.csv("archetypes/open-beer-db/categories.csv", header = TRUE, stringsAsFactors = FALSE)
df_categories

df_styles <- read.csv("archetypes/open-beer-db/styles.csv", header = TRUE, stringsAsFactors = FALSE)
df_styles

```


### Prepare data [Wrangle]
#### Filtering only a few countries of our interest


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_beers <- df_beers %>%
  mutate(cat_id = as.integer(cat_id), style_id = as.integer(style_id), abv = as.double(abv), ibu = as.double(ibu), srm = as.double(srm), upc = as.double(upc))
df_beers
df_beers <- filter(df_beers, cat_id > 0)
df_beers <- filter(df_beers, style_id > 0)

df_beers_graph <- df_beers %>% 
  mutate(id = paste0("beer_", id), brewery_id = paste0("brewery_", brewery_id), cat_id = paste0("category_", cat_id), style_id = paste0("style_", style_id))
# df_beers_graph

# Nodes

df_beer_nodes <- df_beers %>% 
  mutate(id = paste0("beer_", id)) %>%
  select(id, name)
#df_beer_nodes

df_brewery_nodes <- df_breweries %>% 
  mutate(id = paste0("brewery_", id)) %>%
  select(id, name)
#df_brewery_nodes

df_category_nodes <- df_categories %>% 
  mutate(id = paste0("category_", id)) %>%
  select(id, cat_name)
names(df_category_nodes) <- c("id", "name")
#df_category_nodes

df_style_nodes <- df_styles %>% 
  mutate(id = paste0("style_", id)) %>%
  select(id, style_name)
names(df_style_nodes) <- c("id", "name")
#df_style_nodes

df_nodes <- rbind(df_beer_nodes, df_brewery_nodes, df_category_nodes, df_style_nodes)
df_nodes <- df_nodes[!duplicated(df_nodes), ]
rownames(df_nodes) <- c()
df_nodes

# Edges

df_beers_brewery <- df_beers_graph %>% select(id, brewery_id)
names(df_beers_brewery) <- c("from", "to")
#df_beers_brewery

df_beers_style <- df_beers_graph %>% select(id, style_id)
names(df_beers_style) <- c("from", "to")
#df_beers_style

df_styles_category <- df_beers_graph %>% select(style_id, cat_id)
names(df_styles_category) <- c("from", "to")
#df_styles_category

df_edges <- rbind(df_beers_brewery, df_beers_style, df_styles_category)
df_edges


```


### Prepare data [Wrangle]
#### Format the data into a graph data frame 


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Convert data to graph data frame
# directed FALSE means no flow. It's just an association
df_graph <- graph_from_data_frame( df_edges ) # , vertices=df_nodes

```


## Layout & Aesthetic Parameters
### Choose the types of Edges you would like to display


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Layouts can be computationally intensive
# Un-comment only for use

# igraph
# dh <- create_layout(cg, layout = 'dh')
# fr <- create_layout(cg, layout = 'fr')
# gem <- create_layout(cg, layout = 'gem')
# lgl <- create_layout(cg, layout = 'lgl')
# sugiyama <- create_layout(cg, layout = 'sugiyama')
# star <- create_layout(cg, layout = 'star')
# kk <- create_layout(cg, layout = 'kk', maxiter = 100)
# drl <- create_layout(cg, layout = 'drl')
# linear_straight <- create_layout(cg, layout = 'linear')
# linear_circular <- create_layout(cg, layout = 'linear' , circular = TRUE)

# ggraph
# arc <- create_layout(cg, layout = 'linear')
# arc_circular <- create_layout(cg, layout = 'linear', circular = TRUE)
# stress <- create_layout(cg, layout = 'stress')
# sparse_stress <- create_layout(cg, layout = 'sparse_stress')
# backbone <- create_layout(cg, layout = 'backbone')
# pmds <- create_layout(cg, layout = 'pmds')
# eigen <- create_layout(cg, layout = 'eigen')
# centrality <- create_layout(cg, layout = 'centrality')
# focus <- create_layout(cg, layout = 'focus')
# dendrogram <- create_layout(cg, layout = 'dendrogram')
# unrooted <- create_layout(cg, layout = 'unrooted')
# matrix <- create_layout(cg, layout = 'matrix')
# hive <- create_layout(cg, layout = 'hive')
# fabric <- create_layout(cg, layout = 'fabric')

# graphlayouts
nicely <- create_layout(cg, layout = "nicely")
# stress <- create_layout(cg, layout = "stress")
# radial <- create_layout(cg, layout = "focus", focus = 1)

```


## Layout & Aesthetic Parameters
### Choose the types of Edges you would like to display


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Edge Types
# geom_edge_arc
# geom_edge_arc0
# geom_edge_arc2
# geom_edge_density
# geom_edge_diagonal
# geom_edge_diagonal0
# geom_edge_diagonal2
# geom_edge_elbow
# geom_edge_elbow0
# geom_edge_elbow2
# geom_edge_fan
# geom_edge_fan0
# geom_edge_fan2
# geom_edge_hive
# geom_edge_hive0
# geom_edge_hive2
# geom_edge_link
# geom_edge_link0
# geom_edge_link2
# geom_edge_loop
# geom_edge_loop0

```



### Plot
#### nicely

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    # plot.margin = unit(c(1.5,1,1,1), "in"),
    legend.position='none'
)

v1 <- ggraph(nicely) + 
  #geom_edge_link(aes(colour = factor(km), edge_width = edge_weights)) + 
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name)) +
  theme_graph()+
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)


```



### References
#### citations for narrative and data sources

* Narrative, Visualign, Number of neighbors for world countries, https://visualign.org/2011/10/06/number-of-neighbors-for-world-countries/
* Data: https://docs.google.com/spreadsheets/d/1agWAs620UntEQGY0yXUo5_C6zZesLEjBj1TVd3tTEDc/edit#gid=0


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


