---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

library(tidyverse)
#library(rjson)
library(jsonlite)

library(knitcitations)
library(bibtex)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


INGEST  


# Managed Sanitation Services
## Ingest a JSON file

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Grant Durr on Unsplash"}

masthead <- "assets/grant-durr-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Restrooms at Welwitschia Plain outside of Swakopmund, Namibia</div>

> To her [Florence Nightingale] chiefly I owed the awakening to the fact that sanitation\
  is the supreme goal of medicine its foundation and its crown...\
--- Elizabeth Blackwell\


***

### Ingest
#### nested version

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}


url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "managed-sanitation-services/managed-sanitation-services-namibia.json"
url <- paste0(url_root, url_file)

json_nested <- fromJSON(url, flatten = FALSE)

df_nested <- as.data.frame(json_nested)
df_nested

```


### Unnest
#### and display in table friendly format


```{r, echo=TRUE, message=FALSE, warning=FALSE,class.source = 'fold-hide'}

df_nested_fact_dim <- flatten(df_nested)
df_nested_fact_dim

```


### Ingest
#### flattened version

Same result, different approach.

```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "managed-sanitation-services/managed-sanitation-services-namibia.json"
url <- paste0(url_root, url_file)

json_flat <- fromJSON(url, flatten = TRUE)

df_flat <- as.data.frame(json_flat)
df_flat

```


### References
#### citations for narrative and data sources

* Data Source:
  * World Health Organization
  * Basic and safely managed sanitation services
  * [GO](https://apps.who.int/gho/data/node.main.WSHSANITATION?lang=en){target="_blank"}
