---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
#library(rjson)
library(jsonlite)

library(knitcitations)
library(bibtex)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


<div class="activity">
INGEST  
</div>

# Managed Sanitation Services
## Ingest a JSON file

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Grant Durr on Unsplash"}

masthead <- "assets/grant-durr-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Restrooms at Welwitschia Plain outside of Swakopmund, Namibia</div>

> To her [Florence Nightingale] chiefly I owed the awakening to the fact that sanitation\
  is the supreme goal of medicine its foundation and its crown...\
--- Elizabeth Blackwell\


***

### Ingest
#### nested version

```{r, echo=TRUE, message=FALSE, warning=FALSE,class.source = 'fold-hide'}

json_nested <- fromJSON("archetypes/managed-sanitation-services/managed-sanitation-services-namibia.json", flatten = FALSE)
df_nested <- as.data.frame(json_nested)
df_nested

```


### Unnest
#### and display in table friendly format


```{r, echo=TRUE, message=FALSE, warning=FALSE,class.source = 'fold-hide'}

df_nested_fact_dim <- flatten(df_nested)
df_nested_fact_dim

```


### Ingest
#### flattened version

Same result, different approach.

```{r, echo=TRUE, message=FALSE, warning=FALSE,class.source = 'fold-hide'}

json_flat <- fromJSON("archetypes/managed-sanitation-services/managed-sanitation-services-namibia.json", flatten = TRUE)
df_flat <- as.data.frame(json_flat)
df_flat

```


### References
#### citations for narrative and data sources

* Data Source:
  * World Health Organization
  * Basic and safely managed sanitation services
  * https://apps.who.int/gho/data/node.main.WSHSANITATION?lang=en


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "JSON" # mostly used in wranglers and analytics
keywords <- 'managed sanitation services'
commands <- 'fromJSON flatten'
sources <- 'World Health Organization'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

