---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

INGEST  

# Ingest JSON file
## human-readable, machine-readable, and self-describing

```{r, out.width="40%", fig.align="center", fig.cap="Photo by Ben Davis, RO"}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "assets/json.png"
knitr::include_graphics(masthead, dpi=72)
```

JSON (JavaScript Object Notation) is an __open standard__ file format. It is a way to store information in an organized and easy-to-access format that uses __human-readable__ text. JSON is __self-describing__ and can represent __hierarchical__ structures however it must follow specific __syntax__ rules.

* A syntax for __serializing__ objects, arrays, numbers, strings, booleans, and null
* A collection of __name/value pairs__ to describe something

```
{  "region" : "Asia", "country" : "China" }
```

* An __ordered list__ of objects to describe several things

```
"world" :  [
   {  "region" : "Asia", "country" : "China" } ,
   {  "region" : "Asia", "country" : "Japan" } 
]
```

* Allows you to construct a data __hierarchy__


```
"world" :  [
   {  "region" : "Asia", "countries" : [
         country: "China",
         country: "Japan"
         ]
   }]
```
    
Because JSON files are self-describing they will often be larger than the equivalent delimited file.  But they have an advantage for storing hierarchical data. JSON is a very common and useful format for exchanging __complex__ data structures such as __trees__ and __graphs__.
