---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(knitcitations)
library(bibtex)

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
INGEST  
</div>

# Ingest JSON file
## human-readable, machine-readable, and self-describing

```{r, out.width="40%", fig.align="center", fig.cap="Photo by Ben Davis, RO"}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "assets/json.png"
knitr::include_graphics(masthead, dpi=72)
```

JSON (JavaScript Object Notation) is an __open standard__ file format. It is a way to store information in an organized and easy-to-access format that uses __human-readable__ text. JSON is __self-describing__ and can represent __hierarchical__ structures however it must follow specific __syntax__ rules.

* A syntax for __serializing__ objects, arrays, numbers, strings, booleans, and null
* A collection of __name/value pairs__ to describe something

```
{  "region" : "Asia", "country" : "China" }
```

* An __ordered list__ of objects to describe several things

```
"world" :  [
   {  "region" : "Asia", "country" : "China" } ,
   {  "region" : "Asia", "country" : "Japan" } 
]
```

* Allows you to construct a data __hierarchy__


```
"world" :  [
   {  "region" : "Asia", "countries" : [
         country: "China",
         country: "Japan"
         ]
   }]
```
    

Because JSON files are self-describing they will often be larger than the equivalent delimited file.  But they have an advantage for storing hierarchical data. JSON is a very common and useful format for exchanging __complex__ data structures such as __trees__ and __graphs__.

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "explore-json_nested-field read-json" # mostly used in wranglers and analytics
keywords <- ''
commands <- ''
sources <- ''

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```

```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

