---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    #self_contained: false
    #lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(ggplot2)
library(geofacet)

```

<div class="activity">
MAPS  
</div>

# Geographical Facets
## Case: Affordable Housing in London
## Faceting clean up and segment the visualization so you can rapidly compare patterns in different parts of the data.

***

# Load data
## Subsection

```{r}

london_afford_df <- read.csv('archetypes/london_afford.csv')
london_afford_df

# as.data.frame(get_grid_names())

```


# Plot
## Theme


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# theme parameters
theme_opts <- theme(
  legend.position = "bottom",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.background = element_blank(),
)

```

## Geo-Facet
## Question: What are the changes in the number of affordable housings in London Boroughs between 2015 and 2016.

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width=12, fig.height=6}

v1 = ggplot(london_afford_df, aes(x = year, y = starts, fill = year)) +
  geom_col(position = position_dodge()) +
  facet_geo(~ code, grid = "gb_london_boroughs_grid", label = "name") +
  labs(title = "Affordable Housing Starts in London",
    subtitle = "Each Borough, 2015-16 to 2016-17",
    caption = "Source: London Datastore", x = "", y = "")

v1

```


## Save output to file


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

ggsave(filename = "assets/affordable-housing-starts-in-london.svg", plot = v1, width=12, height=6)

```


# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case


```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

# cleanbib()
# read.bibtex(file = "./citations.bib")

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```



