---
pagetitle: "Post-War Surplus of Women"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
TEMPORALS  
</div>

# Illiteracy
## Du Bois Bar

```{r, out.width="60%", fig.align="center", fig.cap="Photo by New York Public Library on Unsplash"}

masthead <- "assets/the-new-york-public-library-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Bourscheid castle in the north of Luxembourg</div>

> To be a poor man is hard, but to be a poor race in a land of dollars is the very bottom of hardships...\
--- W E Du Bois\

***


### Ingest the data
#### the original

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

pct <- c(99, 92.1, 81.6, 67.27, 50)
df <- tibble(pct) %>%
  mutate(xend = -100,
         m_pct = - pct)

# Create vectors of plot labels
year_label <- c("(1900?)", "1890", "1880", "1870", "1860")
pct_label <- c("99%", "92.1%", "81.6%", "67.27%", "(50%?)")
df

```

### Ingest the data
#### updated with world data

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_world <- read.csv("archetypes/illiteracy/literacy-rate.csv", header = TRUE, stringsAsFactors = FALSE)
df_world <- filter(df_world, Country.Name == 'World')
df_world

```
### Wrangle
#### select by decade

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_wrangle <- df_world %>% select(X1980, X1990, X2000, X2010, X2019)
df_wrangle

```


### Plot
#### original


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.margin = margin(20, 40, 20, 40),
    plot.title = element_text(size = 24, hjust = 0.5, face = "bold", margin = margin(0,0,10,0)),
    axis.title.x = element_text(hjust = -0.1, vjust = 14),
    panel.background = element_blank(),
    panel.grid = element_blank(),
    axis.title.y = element_blank(),
    axis.ticks = element_blank()
  )

# Plot
v1 <- ggplot(df) + 
  # Vertical bars
  geom_bar(aes(x = -pct, y = pct), stat = "identity", width = 1.89, fill = "black") +
  # Horizontal black bars (the "outline")
  geom_segment(aes(x = m_pct, y = pct, xend = xend, yend = pct), 
               stat = "identity", size = 9.2, colour = "black", lineend = "square") +
  # Horizontal white bars (the "fill")
  geom_segment(aes(x = m_pct, y = pct, xend = xend, yend = pct), 
               stat = "identity", size = 9, colour = "white", lineend = "square") +
  # x axis labels
  scale_x_continuous(breaks = -pct, 
                     limits = c(-103, -45), 
                     label = pct_label,
                     expand=c(0,0),
                     name = str_wrap("PERCENT OF ILLITERACY.", 10)) +
  # y axis labels
  scale_y_continuous(breaks = c(50, 67.27, 81.6, 92.1, 99), 
                     limits = c(0, 103),
                     label = year_label,
                     expand=c(0,0)) +
  coord_cartesian(clip = 'off') +
  # Modify theme
  theme_bw() +
  theme_opts +
  # Add title
  labs(title = "ILLITERACY.")

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```

### Plot
#### world update

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

# Plot
v2 <- ggplot(df) + 
  # Vertical bars
  geom_bar(aes(x = -pct, y = pct), stat = "identity", width = 1.89, fill = "black") +
  # Horizontal black bars (the "outline")
  geom_segment(aes(x = m_pct, y = pct, xend = xend, yend = pct), 
               stat = "identity", size = 9.2, colour = "black", lineend = "square") +
  # Horizontal white bars (the "fill")
  geom_segment(aes(x = m_pct, y = pct, xend = xend, yend = pct), 
               stat = "identity", size = 9, colour = "white", lineend = "square") +
  # x axis labels
  scale_x_continuous(breaks = -pct, 
                     limits = c(-103, -45), 
                     label = pct_label,
                     expand=c(0,0),
                     name = str_wrap("PERCENT OF ILLITERACY.", 10)) +
  # y axis labels
  scale_y_continuous(breaks = c(50, 67.27, 81.6, 92.1, 99), 
                     limits = c(0, 103),
                     label = year_label,
                     expand=c(0,0)) +
  coord_cartesian(clip = 'off') +
  # Modify theme
  theme_bw() +
  theme_opts +
  # Add title
  labs(title = "ILLITERACY.")

girafe(ggobj = v2, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```


### Save plot
#### as vector or raster image


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/illiteracy-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/illiteracy-sm.svg", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative Inspiration: W E Du Bois remakes, https://rpubs.com/ejhollowood/du-bois
* Data Source: World Bank, https://data.worldbank.org/indicator/SE.ADT.LITR.ZS?end=2019&start=1970&view=chart


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "" # mostly used in wranglers and analytics
keywords <- 'dubois illiteracy'
commands <- 'geom_bar geom_segment'
sources <- 'UNESCO'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

