---
pagetitle: "Environmental impact of food"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

# Load needed libraries

library(tidyverse)
library(ggiraph)

```

<div class="activity">
CHARTS
</div>

# Environmental Impact of Food by Life Cycle Stage
## Bar Vertical Stacked

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Thought Catalog on Unsplash"}

masthead <- "assets/thought-catalog-fnztlIb52gU-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Focus on what you eat, not whether your food is local...\
--- Hannah Ritchie, Our World in Data\

***



### Load the data
#### Where do the emissions from our food come from?

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load data
df <- read_csv("archetypes/environmental-impact-of-food-by-life-cycle-stage.csv", col_names=TRUE)

# To order the group categories by stage of supply chain
df$SUPPLY_CHAIN <- factor(df$SUPPLY_CHAIN, levels=rev(c("Land use change", 
                          "Farm", 
                          "Animal Feed", 
                          "Processing", 
                          "Transport", 
                          "Retail", 
                          "Packging")))

df

# Create summary label for each stack
total_labels <- df %>%
    group_by(FOOD_PRODUCT) %>%
    summarize(TOTAL = round(sum(EMISSION), digits=1))

```

### Plot the chart
#### Focus on what you eat, not whether your food is local

```{r draw-plot, message=FALSE, warning=FALSE, echo=TRUE, fig.width=12, fig.height=9, class.source='fold-hide'}

# Theme parameters
theme_opts <- theme(
  legend.position="top",
  legend.title = element_blank(),
  text = element_text(size=14),                        # Set font size for plot text (axes labels, legend labels, plot title, etc.)
  axis.text.x = element_text(angle=90, vjust=0.5, hjust=1),
  axis.ticks = element_blank(),
  panel.grid.major.y = element_line(color="gray", size = 0.1, linetype="longdash"),
  panel.background = element_blank(),
  plot.title = element_text(size=18),                  # Increase font size of plot title text
  plot.background = element_blank(),
  plot.margin = margin(.25, .25, .25, .25, "cm")
)

# Define palette
supply_chain_palette <- c("Land use change" = "#1ea349", 
                          "Farm" = "#a3745e", 
                          "Animal Feed" = "#f36e32", 
                          "Processing" = "#417aac", 
                          "Transport" = "#f04b54", 
                          "Retail" = "#f3ca19",
                          "Packging" = "#bcb0ac")

# Group to maintain stack sort. Reorder to sort by Food Product and Emission
v1 = ggplot(data=df, aes(y=EMISSION, x=reorder(FOOD_PRODUCT,-EMISSION), fill=SUPPLY_CHAIN, group=SUPPLY_CHAIN)) +
    geom_bar(position="stack", stat="identity", width=0.8, color="#777777") +
    scale_fill_manual(values=supply_chain_palette, breaks=c("Land use change", "Farm", "Animal Feed", "Processing", "Transport", "Retail", "Packging")) +
    scale_y_continuous(expand = c(0,0), breaks=seq(0,60,5), limits=c(-5,65)) +
    coord_cartesian(clip="off") +
    labs(title = "Food: greenhouse gas emissions across the supply chain",  caption = "Source: Our World in Data") +
    theme_opts +
    guides(fill = guide_legend(nrow = 1)) +
    ylab("Greenhouse gas emissions per kilogram of food product\n(kg CO2-equivalents per kg product)") +
    xlab("") +
    geom_text(data=total_labels, aes(y=TOTAL+1, x=FOOD_PRODUCT, label=TOTAL, fill=NULL, group=NULL), size=2.5, hjust=0.5)

girafe(ggobj = v1, width_svg = 17, height_svg = 10)

```

```{r add-annotations, message=FALSE, warning=FALSE, echo=TRUE, fig.width=12, fig.height=9, class.source='fold-hide'}

# Add annotations
v2 <- v1 + 
  annotate("text", y=0, x="Nuts", 
           label = "Nuts have a negative land use change figure because nut trees are currently replacing croplands; carbon is stored in the trees. - ", 
           hjust=1.02, vjust=1, size=2.5, fontface=1, colour="darkgreen") +
  
  annotate("text", y=6, x="Cane Sugar",
           label = "  CO2 emissions from most plant-based products are as much as 10-50 times lower than most animal-based products.\n  Factors such as transport distance, retail, packaging, or specific farm methods are often small compared to importance of food type.",
           hjust="left", vjust=0.45, size=2.5, fontface=1) +
  geom_segment(aes(y=4.5, x="Cane Sugar", yend=4.5, xend="Nuts"), size=0.2) + # Draw line

  annotate("text", y=10, x="Milk",
           label = "Methane production from cows means dairy milk has significantly higher emissions than plant-based milks.",
           hjust="left", vjust=0.45, size=2.5, fontface=1) +
  geom_segment(aes(y=9, x="Milk", yend=4.5, xend="Milk"), size=0.2) +
  
  annotate("text", y=12, x="Rice", 
           label = "Flooded rice produces methane, which dominates on-farm emissions.", 
           hjust="left", vjust=0.45, size=2.5, fontface=1) +
  geom_segment(aes(y=11, x="Rice", yend=5.7, xend="Rice"), size=0.2) +
  
  annotate("text", y=16, x="Pig Meat", 
           label = "    Pigs and poultry are non-ruminant livestock so do not produce methane. They have significantly lower emissions than beef and lamb.", 
           hjust="left", vjust=0.75, size=2.5, fontface=1) +
  geom_segment(aes(y=14.5, x=9.5, yend=8.4, xend=9.5), size=0.2, hjust=5.5) + # can use the category name or the location number for the x value
  
  annotate("text", y=24, x="Beef (dairy herd)", 
           label = "Dairy co-products means beef from dairy herds has a lower carbon footprint than dedicated beef herds.", 
           hjust="left", vjust=0.75, size=2.5, fontface=1) +
  
  annotate("text", y=47, x="Beef (beef herd)", 
           label = "- Methane production from cows, and land conversion for grazing and animal feed means beef from dedicated beef herds has a very high carbon footprint.", 
           hjust=-0.03, vjust=0.45, size=2.5, fontface=1) +
  
  annotate("text", y=59, x="Beef (beef herd)", 
           label = "- Transport emissions are very small for most food products.", 
           hjust=-0.05, vjust=0.2, size=2.5, fontface=1, colour="red")

girafe(ggobj = v2, width_svg = 17, height_svg = 10)

```

### Step by step
#### Draw the base bar chart

```{r step_one, message=FALSE, warning=FALSE, echo=TRUE, fig.width=12, fig.height=9, class.source='fold-hide'}

v1 <- ggplot(data=df, aes(y=EMISSION, x=reorder(FOOD_PRODUCT,-EMISSION), fill=SUPPLY_CHAIN, group=SUPPLY_CHAIN)) +
  geom_bar(position="stack", stat="identity", width=0.8, color="#777777")

girafe(ggobj = v1, width_svg = 17, height_svg = 10)

```

#### Add bar custom colours and stack ordering, and set scales

```{r step_two, message=FALSE, warning=FALSE, echo=TRUE, fig.width=12, fig.height=9, class.source='fold-hide'}

v1 <- ggplot(data=df, aes(y=EMISSION, x=reorder(FOOD_PRODUCT,-EMISSION), fill=SUPPLY_CHAIN, group=SUPPLY_CHAIN)) +
  geom_bar(position="stack", stat="identity", width=0.8, color="#777777") +
  scale_fill_manual(values=supply_chain_palette, breaks=c("Land use change", "Farm", "Animal Feed", "Processing", "Transport", "Retail", "Packging")) +
  scale_y_continuous(expand = c(0,0), breaks=seq(0,60,5), limits=c(-5,65))

girafe(ggobj = v1, width_svg = 17, height_svg = 10)

```

#### Add data labels and theme options

```{r step_three, message=FALSE, warning=FALSE, echo=TRUE, fig.width=12, fig.height=9, class.source='fold-hide'}

v1 <- ggplot(data=df, aes(y=EMISSION, x=reorder(FOOD_PRODUCT,-EMISSION), fill=SUPPLY_CHAIN, group=SUPPLY_CHAIN)) +
  geom_bar(position="stack", stat="identity", width=0.8, color="#777777") +
  scale_fill_manual(values=supply_chain_palette, breaks=c("Land use change", "Farm", "Animal Feed", "Processing", "Transport", "Retail", "Packging")) +
  scale_y_continuous(expand = c(0,0), breaks=seq(0,60,5), limits=c(-5,65)) +
  coord_cartesian(clip="off") +
  labs(title = "Food: greenhouse gas emissions across the supply chain",  caption = "Source: Our World in Data") +
  theme_opts +
  guides(fill = guide_legend(nrow = 1)) +
  ylab("Greenhouse gas emissions per kilogram of food product\n(kg CO2-equivalents per kg product)") +
  xlab("") +
  geom_text(data=total_labels, aes(y=TOTAL+1, x=FOOD_PRODUCT, label=TOTAL, fill=NULL, group=NULL), size=2.5, hjust=0.5)

girafe(ggobj = v1, width_svg = 17, height_svg = 10)

```

#### Add annotations and line segments

```{r step_four, message=FALSE, warning=FALSE, echo=TRUE, fig.width=12, fig.height=9, class.source='fold-hide'}

v2 <- v1 + 
  annotate("text", y=0, x="Nuts", 
           label = "Nuts have a negative land use change figure because nut trees are currently replacing croplands; carbon is stored in the trees. - ", 
           hjust=1.02, vjust=1, size=2.5, fontface=1, colour="darkgreen") +
    annotate("text", y=6, x="Cane Sugar",
           label = "  CO2 emissions from most plant-based products are as much as 10-50 times lower than most animal-based products.\n  Factors such as transport distance, retail, packaging, or specific farm methods are often small compared to importance of food type.",
           hjust="left", vjust=0.45, size=2.5, fontface=1) +
  geom_segment(aes(y=4.5, x="Cane Sugar", yend=4.5, xend="Nuts"), size=0.2) +
  annotate("text", y=10, x="Milk",
           label = "Methane production from cows means dairy milk has significantly higher emissions than plant-based milks.",
           hjust="left", vjust=0.45, size=2.5, fontface=1) +
  geom_segment(aes(y=9, x="Milk", yend=4.5, xend="Milk"), size=0.2) +
  annotate("text", y=12, x="Rice", 
           label = "Flooded rice produces methane, which dominates on-farm emissions.", 
           hjust="left", vjust=0.45, size=2.5, fontface=1) +
  geom_segment(aes(y=11, x="Rice", yend=5.7, xend="Rice"), size=0.2) +
  annotate("text", y=16, x="Pig Meat", 
           label = "    Pigs and poultry are non-ruminant livestock so do not produce methane. They have significantly lower emissions than beef and lamb.", 
           hjust="left", vjust=0.75, size=2.5, fontface=1) +
  geom_segment(aes(y=14.5, x=9.5, yend=8.4, xend=9.5), size=0.2, hjust=5.5) + # can use the category name or the location number for the x value
  annotate("text", y=24, x="Beef (dairy herd)", 
           label = "Dairy co-products means beef from dairy herds has a lower carbon footprint than dedicated beef herds.", 
           hjust="left", vjust=0.75, size=2.5, fontface=1) +
  annotate("text", y=47, x="Beef (beef herd)", 
           label = "- Methane production from cows, and land conversion for grazing and animal feed means beef from dedicated beef herds has a very high carbon footprint.", 
           hjust=-0.03, vjust=0.45, size=2.5, fontface=1) +
  annotate("text", y=59, x="Beef (beef herd)", 
           label = "- Transport emissions are very small for most food products.", 
           hjust=-0.05, vjust=0.2, size=2.5, fontface=1, colour="red")

girafe(ggobj = v2, width_svg = 17, height_svg = 10)

```

### References
#### The citations and data sources used for this case

* Narrative sources: Our World in Data, _You want to reduce the carbon footprint of your food? Focus on what you eat, not whether your food is local_, [GO](https://ourworldindata.org/food-choice-vs-eating-local){target="_blank"}

<pre>
@misc{ritchie_2020_you,
  author = {Ritchie, Hannah},
  month = {01},
  title = {You want to reduce the carbon footprint of your food? Focus on what you eat, not whether your food is local},
  url = {https://ourworldindata.org/food-choice-vs-eating-local},
  urldate = {2021-02-15},
  year = {2020},
  organization = {Our World in Data}
}
</pre>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
