---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    #self_contained: false
    #lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(ggplot2)
library(ggridges)

library(knitcitations)
library(bibtex)

```

<div class="activity">
TEMPORALS
</div>

# Ridgeline Plot
## CP1919

"EIGHTY SUCCESSIVE PERIODS of the first pulsar observed, CP1919 (Cambridge pulsar at 19 hours 19 minutes right ascension), are stacked on top of one another using the average period of 1.33730 seconds in this computer-generated illustration produced at the Arecibo Radio Observatory in Puerto Rico. Although the leading edges of the radio pulses occur within a few thousandths of a second of the predicted times, the shape of the pulses is quite irregular. Some of this irregularity in radio reception is caused by the effects of transmission through the interstellar medium. The average pulse width is less than 50 thousandths of a second."



***

## Load data [Ingest]

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
cp1919_df = read.csv("archetypes/CP1919.csv", header = TRUE, stringsAsFactors = TRUE)  # read text file
cp1919_df

```

## Plot [ Views / Temporals ]

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width=12, fig.height=8, , fig.align='center', out.width="100%"}

v1 = ggplot(cp1919_df, aes(x, y, height = y, group=line )) +
  geom_ridgeline(fill = "black", colour = "white", size = 0.4) +
  theme_ridges() +
  coord_cartesian(clip = "off") +
  theme(panel.grid = element_blank(),
   panel.background = element_rect(fill = "black"),
   axis.text = element_blank(),
   axis.ticks = element_blank(),
   axis.title = element_blank())

v1

```

# Section
## Subsection

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width=12, fig.height=8, , fig.align='center', out.width="100%"}

v2 = ggplot(cp1919_df, aes(x, ymax=y, ymin=0, group=line)) +
  geom_ribbon(colour='white') +
  theme_bw() +
  theme(legend.position='none') + 
  theme(panel.grid = element_blank(),
        axis.text  = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank()) + 
  coord_fixed()

v2

```



```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Save plot to svg file
# ggsave(filename = "cp1919.svg", plot = v2, width=13.33, height=7.5)

```



# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case

<a href="https://blogs.scientificamerican.com/sa-visual/pop-culture-pulsar-origin-story-of-joy-division-s-unknown-pleasures-album-cover-video/">From "The Nature of Pulsars," by Jeremiah P. Ostriker, Scientific American, January 1971.</a>

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

# cleanbib()
# read.bibtex(file = "./citations.bib")

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```



