---
pagetitle: "Food Consumption and CO2 Emissions"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


<div class="activity">
CHARTS  
</div>

# Food Consumption and CO2 Emissions
## Heatmap


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Markus Spiske on Unsplash"}

masthead <- "assets/markus-spiske-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> The Earth started to rebel when the carbon in the atmosphere began to swell...\
--- Donna Maltz\

***

In the US, each household produces 48 tons of greenhouse gases. Food produces about 8 tons of emissions per household, or about 17% of the total. Worldwide, new reports suggest that livestock agriculture produces around half of all man-made emissions. We have to change how we produce and consume food, not just for environmental reasons, but because this is an __existential__ issue for humans.

Let's examine the situation.

### Ingest data
#### country, food category, consumption per country, co2 emissions per country


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

#Load data
url_file <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-18/food_consumption.csv"
food_consumption <- read.csv(url_file)
food_consumption

```

### Wrangle
#### group_by, summarise, select and join

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

#Select the top 10 countries by co2 emissions
country <- food_consumption %>% group_by(country)%>%summarise(total=sum(co2_emmission))%>%top_n(10)%>%select(1)

#create dataframe of top 10 countries
df <- food_consumption%>%select(1,2,4)%>% inner_join(country)
df

```


### The Heatmap
#### Food consumption (kg/person/year) and co2 emissions (kg co2/person/year)


```{r, warning=FALSE, echo=TRUE, class.source = 'fold-hide',out.width = "100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(margin = margin(b = 10), color = "#22222b",face = "bold",size = 17),
    plot.subtitle = element_text(margin = margin(b = 25),color = "#22222b", size = 12),
    plot.caption = element_text(margin = margin(t = 20),color = "#22222b", size = 10),
    axis.text.x = element_text(color = "#22222b", margin = margin(t = 15)),
    axis.text.y = element_text(color = "#22222b"),
    panel.background = element_blank(),
    panel.border = element_blank(),
    panel.grid.major = element_blank(),
    plot.background = element_rect(fill = "#e7e7e7"),
    plot.margin = unit(c(1, 2, 1, 1), "cm"),
    legend.position='none'
)



v1 <-  
  ggplot(data=df,aes(x = country, y = fct_reorder(food_category,co2_emmission))) +
  geom_tile(aes(fill = co2_emmission), color = "#2b2b2b") +
  geom_text(aes(label = co2_emmission), color = "#22292F") +
  scale_fill_gradient(low = "#20b2aa", high = "#2072b2") +
  labs(x = "",y = "",
       title = "Top 10 countries with the highest CO2 emissions",
       subtitle = "On which food category do they emit the highest level of CO2?",
       caption = "Source:Tidy Tuesday\nVisualization: JuanmaMN (Twitter @Juanma_MN)") +
  scale_x_discrete(position = "top") +
  guides(fill = NULL) +
  theme_bw() +
  theme_opts


girafe(ggobj = v1, width_svg = 16, height_svg = 9,
      options = list(opts_sizing(rescale = TRUE, width = 1.0)))



```

### References
#### Citation and data source

* Citation and data source: R for Datascience [GO](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-02-18){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
