---
pagetitle: "Greenhouse Gas (GHG) emissions by country"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


<div class="activity">
CHARTS
</div>

# Greenhouse Gas (GHG) emission by country
## Heatmap


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Shun Idota on Unsplash"}

masthead <- "assets/shun-idota-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> We should no longer measure our wealth and success in the graph that shows economic growth,
  but in the curve that shows the emissions of greenhouse gases...\
--- Greta Thunburg\

***

### Ingest data 
#### producing and consuming countries, GHG emissions, 

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

#Load data
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "ghg-emissions-by-country/ghg-emissions-by-country.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = TRUE)
df


```


### The Heatmap
#### GHG emissions (million tons CO2 per year)

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    legend.position='bottom'
)

v1 <- ggplot(df)+
      geom_tile(aes(x = Consuming.countries, y = Producing.countries, fill = GHG.emissions), color = "white", size = 1) +
      scale_x_discrete() +
      scale_y_discrete() +
      scale_fill_gradientn(colours = c("#FFEAD7", "#F49217", "#794712")) +
      labs( 
       title = "GHG emissions (million tons CO2 per year)",
       subtitle = NULL,
       x = "Consuming Countries", y = "Producing Countries") +
      theme_bw() +
      theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
      options = list(opts_sizing(rescale = TRUE, width = 1.0)))


```

### References
#### citations for narrative and data sources

* Narrative and data sources: Engage The Chain [GO](https://engagethechain.org/investor-guide-deforestation-and-climate-change){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

