---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---
```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48


# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden 
gc() #free up memory and report the memory usage.


library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```
<div class="activity">
CHARTS  
</div>

# Heatmap
## Story-Telling with Heatmap

```{r, out.height="50%", out.width="50%", fig.align="center", fig.cap="GHG emissions (million tons CO2 per year)"}
masthead <- "assets/ghg-emission-by-country.png"
knitr::include_graphics(masthead, dpi=72)
```


Heatmap is a graphical representation of data that uses a system of color-coding to represent different values. The primary purpose of Heat Maps is to better visualize the volume of locations/events within a dataset and assist in directing viewers towards areas on data visualizations that matter most. They are also a lot more visual than standard analytics reports, which can make them easier to analyze at a glance. Heat Maps are multifaceted and can also be used in more literal senses, for example, to showcase ‘hot and cold’ (density) zones on a map.

Best practices for implementing a heatmap:

* __Select an appropriate color palette__ : sequential color ramp between value and color symbolizes the lighter colors corresponding to smaller values and darker colors to larger values, or vice versa.
* __Include a Legend__ : how colors map to numeric values
* __Show values in cell__ : To add cell value annotations as a double encoding value
* __Sort level by similarity or value__ : sort categories that best helps the reader grasp patterns in the data.

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "Heatmap" # mostly used in wranglers and analytics
keywords <- ''
commands <- ''
sources <- ''

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```

```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

