---
pagetitle: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---
```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```
<div class="activity">
CHARTS  
</div>

# Heatmap
## Story-Telling with Heatmap

```{r, out.height="50%", out.width="50%", fig.align="center", fig.cap="GHG emissions (million tons CO2 per year)"}
masthead <- "assets/ghg-emission-by-country.png"
knitr::include_graphics(masthead, dpi=72)
```


Heatmap is a graphical representation of data that uses a system of color-coding to represent different values. The primary purpose of Heat Maps is to better visualize the volume of locations/events within a dataset and assist in directing viewers towards areas on data visualizations that matter most. They are also a lot more visual than standard analytics reports, which can make them easier to analyze at a glance. Heat Maps are multifaceted and can also be used in more literal senses, for example, to showcase ‘hot and cold’ (density) zones on a map.

Best practices for implementing a heatmap:

* __Select an appropriate color palette__ : sequential color ramp between value and color symbolizes the lighter colors corresponding to smaller values and darker colors to larger values, or vice versa.
* __Include a Legend__ : how colors map to numeric values
* __Show values in cell__ : To add cell value annotations as a double encoding value
* __Sort level by similarity or value__ : sort categories that best helps the reader grasp patterns in the data.
