---
pagetitle: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Bubble Facet
## Story-Telling with Bubble Facet

```{r, out.height="50%", out.width="50%", fig.align="center", fig.cap=""}
#masthead <- ""
#knitr::include_graphics(masthead, dpi=72)
```


Facet charts help to compare information with many variables. You can use various combinations of axes to have just a single row: Y, X, X or a single column: Y, Y, X. The chart is built to make category-based data exploration and visualization fast and efficient. Whereas a bubble chart is primarily used to depict and show relationships between numeric variables. Bubble facet can be beneficial when plotting the relationship among variables of interest, one of the useful ways to create visual impact is by way of using facet, which subsets data with faceted variable and creates plots for each of the subset separately. The result is a panel of subplots, with each subplot depicting the plot for same set of variables. This approach can be especially useful for panel datasets, with the panel variable acting as facet variable and each subplot depicting time series trend of variable of interest.

Types of Faceting:

* __facet_null()__ : a single plot, the default.
* __facet_wrap()__ : “wraps” a 1d ribbon of panels into 2d. This is useful if you have a single variable with many levels and want to arrange the plots in a more space efficient manner.
* __facet_grid()__ : produces a 2d grid of panels defined by variables which form the rows and columns.
