---
pagetitle: "Knife Crime"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(knitcitations)
library(bibtex)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Knife Crime
## A range plot showing trend direction

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Snehal Krishna on Unsplash"}

masthead <- "assets/ethan-wilkinson-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Remember, it is never the knife's fault...\
--- Daniel Boulud\


***

### Ingest
#### area, year, trend

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df = read.csv("archetypes/knife-crime/knife-crime.csv", header = TRUE, stringsAsFactors = TRUE)
df

```


### Wrangle
#### filter for rising and declining


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_rising <- filter(df, color == "Increase in knife crimes")
df_declining <- filter(df, color == "Decrease in knife crimes")

```


### Plot
#### Where is knife crime rising?


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="85%"}

theme_opts <- theme(
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.ticks = element_line(),
    legend.position = "none"
  )

v1 = ggplot(df_rising) + 
  geom_point(aes(x=X2017, y=factor(Area.Name)), shape=16, alpha=1.0, size=2, color="#a82e13") +
  geom_segment(aes(x=X2017, y=factor(Area.Name), xend=X2018, yend=factor(Area.Name)), 
               lineend = "round", linejoin = "round", size=1, color="#a82e13") + 
  geom_text(aes(x=X2018, y=Area.Name), label = "\u25B6", size = 12, color="#a82e13", vjust = 0.55) + 
  scale_x_continuous() +
  scale_y_discrete() +
  labs(title = "Where is knife crime rising?") +
  theme_minimal() +
  theme_opts +
  xlab(NULL) +
  ylab(NULL)

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


### Plot
#### Where is knife crime decreasing?


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="85%"}

v2 = ggplot(df_declining) + 
  geom_point(aes(x=X2017, y=factor(Area.Name)), shape=16, alpha=1.0, size=2, color="#63a0cd") +
  geom_segment(aes(x=X2017, y=factor(Area.Name), xend=X2018, yend=factor(Area.Name)), size=1, color="#63a0cd") + 
  geom_text(aes(x=X2018, y=Area.Name), label = "\u25C0", size = 12, color="#63a0cd", vjust = 0.55) + 
  scale_x_continuous() +
  scale_y_discrete() +
  labs(title = "Where is knife crime decreasing?") +
  theme_minimal() +
  theme_opts +
  xlab(NULL) +
  ylab(NULL)

girafe(ggobj = v2, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/knife-crime-fs.svg", plot = v1, width=720/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/knife-crime-sm.svg", plot = v1, width=2.25, height=2.25)

```



### References
#### citations for narrative and data sources

Inspiration: Datawrapper, Where is knife crime rising?, https://blog.datawrapper.de/weekly-chart-range-plot-the-times-ryan-watts/
Data Source: Office for National Statistics


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "range" # mostly used in wranglers and analytics
keywords <- 'knife crime'
commands <- 'geom_point geom_segment scale_y_discrete arrow'
sources <- 'Office for National Statistics'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

