---
pagetitle: "Global Trade Flows"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(scales)
library(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Global Trade Flows
## Flow Map

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Ian Taylor on Unsplash"}

masthead <- "assets/ian-taylor-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> If your personal brand were at a trade show alongside several thousand others, how would you fare? \
  Now scale that to the global economy...\
--- Ryan Lilly\

***

### Ingest
#### Flows and points

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_flows = read.csv("archetypes/global-trade-flows/global-trade-flows.csv", header = TRUE, stringsAsFactors = FALSE, as.is=T)
df_points = read.csv("archetypes/global-trade-flows/global-trade-flows-points.csv", header = TRUE, stringsAsFactors = FALSE, as.is=T)

head(df_flows)

```


### Wrangle
#### filter exporter and importer


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# change the filter to experiment with other exporters or importers
df_flows_exp <- filter( df_flows, expISO3 == "IRN" )
df_flows_exp <- filter( df_flows_exp, tot_val_usd > 0 )

df_flows_exp

df_flows_imp <- filter( df_flows, impISO3 == "IRN" )
df_flows_imp <- filter( df_flows_imp, tot_val_usd > 0 )

df_flows_imp

```



### Analyze
#### calculations for exporter and importer


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_flows_exporter <- df_flows_exp %>% 
  group_by(exporter, expISO3, slongitude, slatitude) %>% 
  summarise(Total = sum(tot_val_usd))

df_flows_exporter

df_flows_importer <- df_flows_imp %>% 
  group_by(importer, impISO3, tlongitude, tlatitude) %>% 
  summarise(Total = sum(tot_val_usd))

df_flows_importer

```


### Base map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

# PLOT NATURAL EARTH BORDERS
ne_world <- ne_countries(scale = "small", returnclass = "sf")
# class(ne_world)
# removes Antarctica
ne_world <- filter(ne_world, iso_a3 != "ATA") 

```


### Flow Map
#### exports, by total value USD


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', out.width = "100%" }

# theme parameters
theme_opts <- theme(
  text = element_text(family = "inconsolata"), 
  legend.position = "top",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_blank(),
  panel.border = element_blank(),
  plot.background = element_blank()
)


v1 <- ggplot(data = ne_world) +
  geom_sf(fill="#ffffff", color="#cccccc", size=0.75) +
  geom_point( data = df_flows_exp, aes(x=tlongitude, y=tlatitude, size=tot_val_usd, fill=tot_val_usd), shape=21, color="white", stroke=1, alpha=1.0) +
  geom_curve( data = df_flows_exp, aes( x=slongitude, y=slatitude, xend=tlongitude, yend=tlatitude, size=tot_val_usd, color=tot_val_usd, alpha=tot_val_usd ), curvature=0.2, lineend="round", linejoin="round" ) +
  geom_point( data = df_flows_exporter, aes(x=slongitude, y=slatitude), shape=21, size=14, fill='black', color="black", stroke=1, alpha=1.0) +
  geom_text( data = df_flows_exporter, aes(x=slongitude, y=slatitude, label = expISO3), color="white", alpha=1.0) +
  scale_size_continuous(range=c(1,10), guide="none") +
  scale_alpha_continuous(range=c(0.2,0.6), guide="none") +
  scale_fill_gradient(low = "#E53935", high = "#388E3C", guide="none") + 
  scale_color_gradient(low = "#E53935", high = "#388E3C", guide="none") + 
  theme_bw() +
  labs(x="",
       y="",
       title = "Global Trade Flows", 
       subtitle="Iran Exports") +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### Flow Map
#### imports, by total value USD

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', out.width="100%"}

v2 <- ggplot(data = ne_world) +
  geom_sf(fill="#ffffff", color="#cccccc", size=0.75) +
  geom_point( data = df_flows_imp, aes(x=slongitude, y=slatitude, size=tot_val_usd, fill=tot_val_usd), shape=21, color="white", stroke=1, alpha=1.0) +
  geom_text_repel( data = df_flows_imp, aes(x=slongitude, y=slatitude, label=expISO3), size=3 , color="black", alpha=1.0, family = "inconsolata") +
  geom_curve( data = df_flows_imp, aes( x=slongitude, y=slatitude, xend=tlongitude, yend=tlatitude, size=tot_val_usd, color=tot_val_usd, alpha=tot_val_usd ), curvature=0.2, lineend="round", linejoin="round" ) +
  geom_point( data = df_flows_importer, aes(x=tlongitude, y=tlatitude), shape=21, size=14, fill='black', color="black", stroke=1, alpha=1.0) +
  geom_text( data = df_flows_importer, aes(x=tlongitude, y=tlatitude, label = impISO3), color="white", alpha=1.0, family = "inconsolata") +
  scale_size_continuous(range=c(1,10), guide="none") +
  scale_alpha_continuous(range=c(0.2,0.6), guide="none") +
  scale_fill_gradient(low = "#E53935", high = "#388E3C", guide="none") + 
  scale_color_gradient(low = "#E53935", high = "#388E3C", guide="none") + 
  theme_bw() +
  labs(x="",
       y="",
       title = "Global Trade Flows", 
       subtitle="Iran Imports") +
  theme_opts

girafe(ggobj = v2, width_svg = 16, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk
ggsave(filename = "outputs/global-trade-flows-fs.svg", plot = v1, width=16, height=7)

```


### References
#### citations for narrative and data sources

* Narrative and Data sources: UN Comtrade Database, [GO](https://comtrade.un.org/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

