---
pagetitle: "Global Energy Monitor"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(countrycode)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(flextable)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Global Energy Monitor
## Flow Map

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Amir Arabshahi on Unsplash"}

masthead <- "assets/amir-arabshahi-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Another method of eating burning coals employs small balls of burned cotton in a dish of burning alcohol...\
--- Harry Houdini\

***

### Ingest
#### the flows

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_tracker <- read.csv("archetypes/global-energy-monitor/global-energy-monitor.csv", header = TRUE, stringsAsFactors = FALSE, as.is=T, fileEncoding = "utf-8")
head(df_tracker, n=10)

```


### Wrangle
#### group and aggregate flows


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_flows_count <- df_tracker %>% 
  group_by(target_iso, target_lat, target_lng, source_iso, source_lat, source_lng, source, target) %>% 
  summarise(total_dollars = sum(dollars), total_megawatts = sum(megawatts), Count = n())
head(df_flows_count, n=10)

```


### Wrangle
#### aggregate points


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_source_points <- df_tracker %>% 
  group_by(source_iso, source_lat, source_lng, source) %>% 
  summarise(total_dollars = sum(dollars), total_megawatts = sum(megawatts))
df_source_points$point_id <- paste0("source-", seq.int(nrow(df_source_points)))
# df_source_points

df_target_points <- df_tracker %>% 
  group_by(target_iso, target_lat, target_lng, target) %>% 
  summarise(total_dollars = sum(dollars), total_megawatts = sum(megawatts))
df_target_points$point_id <- paste0("target-", seq.int(nrow(df_target_points)))
# df_target_points

df_project_points <- df_tracker %>% 
  group_by(project_name, project_lat, project_lng) %>% 
  summarise(total_dollars = sum(dollars), total_megawatts = sum(megawatts))
df_project_points$point_id <- paste0("project-", seq.int(nrow(df_project_points)))
df_project_points


```


### Wrangle
#### create visual variable for choropleth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

df_sources <- as.data.frame(df_source_points$source_iso)
colnames(df_sources) <- c("iso")
# head(df_sources, n=5)

df_targets <- as.data.frame(df_target_points$target_iso)
colnames(df_targets) <- c("iso")
# head(df_targets, n=5)

df_countries <- rbind(df_sources, df_targets)
df_countries$color <- 1
df_countries$iso <- countrycode(df_countries$iso, origin = 'iso2c', destination = 'iso3c') 
df_countries <- df_countries[!duplicated(df_countries$iso), ]
head(df_countries, n=10)

```


### Base map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

# PLOT NATURAL EARTH BORDERS
ne_world <- ne_countries(scale = "small", returnclass = "sf")
# removes Antarctica
ne_world <- filter(ne_world, iso_a3 != "ATA") 

```


### World map
#### merge attributes by ISO3C


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

# combine data with map based on ISO3 codes
ne_world_df <- merge(ne_world, df_countries, by.x = "iso_a3", by.y = "iso", all = TRUE)
ne_world_df$color[is.na(ne_world_df$color)] <- 0

```


### Flow Map
#### origins, destinations, and flows


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide',  out.width = "100%"}

# theme parameters
theme_opts <- theme(
  text = element_text(family = "inconsolata"), 
  plot.title = element_text(color = "black", size = 14, face = "bold", family = "inconsolata"),
  plot.subtitle = element_text(color = "black", size = 12, family = "inconsolata"),
  plot.caption = element_text(color = "#555555", size = 8, family = "inconsolata"),
  plot.background = element_rect(fill = "#f5f5f5"),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_rect(fill = "#f5f5f5"),
  panel.border = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  legend.position = "bottom",
  legend.title = element_blank()
)

# tooltip -----
fun_tooltip <- function(dat){
  
  cols <- as.data.frame(colnames(dat))
  colnames(cols) <- "col"
  cols <- filter(cols, col != "point_id")
  
  for (row in 1:nrow(dat)) {

    tooltip <- NULL
    
    for (c in 1:nrow(cols)) {
      tooltip <- paste0(tooltip, cols[c,"col"], ": ", dat[row, cols[c,"col"]], "\n")
    }
    dat[row, "tooltip"] <- tooltip
  }
  return(dat)
}

df_source_points <- fun_tooltip(df_source_points)
df_target_points <- fun_tooltip(df_target_points)
df_project_points <- fun_tooltip(df_project_points)
# end of tooltip


v1 <- ggplot(data = ne_world_df) +
  geom_sf(fill=ifelse(ne_world_df$color == 1, "#E0E0E0", "#FFFFFF"), color="#BDBDBD", size=0.5) +
  geom_point_interactive( data = df_project_points, aes(x=project_lng, y=project_lat,
    tooltip = tooltip, data_id = point_id), shape=21, 
    size = 1.5, color="black", fill="black", stroke=1, alpha=0.5) +
  geom_curve( data = df_flows_count, 
    aes( x=source_lng, y=source_lat, xend=target_lng, yend=target_lat, alpha=total_dollars ), 
    size=0.75, color = "black", alpha = 0.2, lineend="round", linejoin="round", curvature = 0.1 ) +
  geom_point_interactive( data = df_source_points, aes(x=source_lng, y=source_lat, size=total_megawatts,
    tooltip = tooltip, data_id = point_id), 
    shape=21, color="#FF9800", fill=NA, stroke=1.5) +
  geom_point_interactive( data = df_target_points, aes(x=target_lng, y=target_lat, size=total_megawatts,
    tooltip = tooltip, data_id = point_id), 
    shape=21, color="#455A64", fill=NA, stroke=0.75) +
  scale_size_continuous(range=c(2,15), guide="none") +
  labs(x=NULL,
       y=NULL,
       title = "Global Coal Public Finance Flows", 
       subtitle=NULL,
       caption="Global Energy Monitor") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 7.15,
       options = list(
         opts_sizing(rescale = TRUE, width = 1.0),
         opts_hover(css = "stroke-width:4;")
       )
)

```


### References
#### citations for narrative and data sources

* Narrative and Data Sources: Global Energy Monitor, [GO](https://globalenergymonitor.org/projects/global-coal-public-finance-tracker/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

