---
pagetitle: "Global Energy Monitor"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(countrycode)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Global Energy Monitor
## Flow Map

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Bart Van Dijk on Unsplash"}

masthead <- "assets/bart-van-dijk-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Another method of eating burning coals employs small balls of burned cotton in a dish of burning alcohol...\
--- Harry Houdini\

***

### Ingest


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_tracker <- read.csv("archetypes/global-energy-monitor/global-energy-monitor.csv", header = TRUE, stringsAsFactors = FALSE, as.is=T)
head(df_tracker)

```


### Wrangle
#### aggregate points and flows


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_flows_count <- df_tracker %>% 
  group_by(target_iso, target_lat, target_lng, source_iso, source_lat, source_lng,source,target) %>% 
  summarise(Count = n())

df_flows_count

df_target_count <- df_tracker %>% 
  group_by(target_iso, target_lat, target_lng,target) %>% 
  summarise(Count = n())

# df_target_count

df_source_count <- df_tracker %>% 
  group_by(source_iso, source_lat, source_lng,source) %>% 
  summarise(Count = n())

# df_source_count

df_sources <- as.data.frame(df_source_count$source_iso)
colnames(df_sources) <- c("iso")
# df_sources

df_targets <- as.data.frame(df_target_count$target_iso)
colnames(df_targets) <- c("iso")
# df_targets

# Source for choropleth
df_countries <- rbind(df_sources, df_targets)
df_countries$color <- 1
df_countries$iso <- countrycode(df_countries$iso, origin = 'iso2c', destination = 'iso3c') 
df_countries <- df_countries[!duplicated(df_countries$iso), ]
# df_countries


```



### Base map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

# PLOT NATURAL EARTH BORDERS
ne_world <- ne_countries(scale = "small", returnclass = "sf")
# class(ne_world)
# removes Antarctica
ne_world <- filter(ne_world, iso_a3 != "ATA") 


```



### World map
#### merge attributes by ISO3C


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

# combine data with map based on ISO3 codes
ne_world_df <- merge(ne_world, df_countries, by.x = "iso_a3", by.y = "iso", all = TRUE)
ne_world_df$color[is.na(ne_world_df$color)] <- 0

```


### Flow Map
#### origins, destinations, and flows


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide',  out.width = "100%"}

# theme parameters
theme_opts <- theme(
  legend.position = "bottom",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_rect(fill = "#D6DADC"),
  panel.border = element_blank(),
  plot.background = element_rect(fill = "#D6DADC")
)

v1 <- ggplot(data = ne_world_df) +
  geom_sf(fill=ifelse(ne_world_df$color == 1, "#F7EBE7", "#FFFFFF"), color="#A69F9D", size=0.5) +
  geom_curve( data = df_flows_count, aes( x=source_lng, y=source_lat, xend=target_lng, yend=target_lat, size=Count, color=Count, alpha=Count  ), lineend="round", linejoin="round", curvature=0.2 ) +
  #geom_segment( data = df_flows_count, aes( x=source_lng, y=source_lat, xend=target_lng, yend=target_lat, size=Count, color=Count, alpha=Count  ), lineend="round", linejoin="round" ) +
  geom_point_interactive( data = df_source_count, aes(x=source_lng, y=source_lat, size=Count,
    tooltip = source, data_id = source_iso), shape=21, color="#d8031c", fill="#d8031c", stroke=1, alpha=0.9) +
  geom_point_interactive( data = df_target_count, aes(x=target_lng, y=target_lat, size=Count,
    tooltip = target, data_id = target_iso), shape=21, color="#6497bf", fill="#6497bf", stroke=1, alpha=0.9) +
  scale_size_continuous(range=c(1,15), guide="none") +
  scale_alpha_continuous(range=c(0.4, 0.7), guide="none") +
  scale_fill_gradient(low = "#939A99", high = "#333A41", guide="none") + 
  scale_color_gradient(low = "#939A99", high = "#333A41", guide="none") + 
  theme_bw() +
  labs(x=NULL,
       y=NULL,
       title = "Global Coal Public Finance Flows", 
       subtitle=NULL,
       caption="Global Energy Monitor") +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk
ggsave(filename = "outputs/global-energy-monitor-fs.svg", plot = v1, width=16, height=7)

```


### References
#### citations for narrative and data sources

* Narrative and Data Sources: Global Energy Monitor, [GO](https://globalenergymonitor.org/projects/global-coal-public-finance-tracker/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

