---
pagetitle: "Trans-Atlantic Slave Trade"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(geojsonio)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
# library(scales)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Trans-Atlantic Slave Trade
## Flow Map

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by the British Library on Unsplash"}

masthead <- "assets/british-library-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> The forced movement of West Africans across the Atlantic happened on an unprecedented scale of brutality and inhumanity, killings and massive abuses.\  
  Millions died without a burial, without a trace...\
--- UN Secretary-General Ban Ki-moon\

***

### Ingest
#### Flows and points

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_flows <- read.csv("archetypes/trans-atlantic-slave-trade/all-voyages.csv", header = TRUE, stringsAsFactors = FALSE, as.is=T)
df_points <- read.csv("archetypes/trans-atlantic-slave-trade/points.csv", header = TRUE, stringsAsFactors = FALSE, as.is=T)

head(df_flows)
head(df_points)

```


### Analytics
#### aggregate points and flows


```{r}

min_lat <- min(df_points$lat, na.rm=T)
#min_lat
max_lat <- max(df_points$lat, na.rm=T)
#max_lat
min_lon <- min(df_points$lon, na.rm=T)
#min_lon
max_lon <- max(df_points$lon, na.rm=T)
#max_lon

df_flows_sum <- df_flows %>% 
  group_by(dest, origin) %>% 
  summarise(Total = sum(count, na.rm = TRUE))

df_flows_sum

df_origin_sum <- df_flows %>% 
  group_by(origin) %>% 
  summarise(Total = sum(count, na.rm = TRUE))

# head(df_origin_sum)

df_dest_sum <- df_flows %>% 
  group_by(dest) %>% 
  summarise(Total = sum(count, na.rm = TRUE))

# head(df_dest_sum)

```


### Wrangle
#### enrich points (count) and flows (coordinates)


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_flows_wrangle <- filter(df_flows_sum, dest != origin)

df_flows_wrangle <- merge(df_flows_wrangle, df_points, by.x="origin", by.y="id" )
df_flows_wrangle <- df_flows_wrangle %>% rename(origin_name = name, origin_lat = lat, origin_lon = lon)

df_flows_wrangle <- merge(df_flows_wrangle, df_points, by.x="dest", by.y="id" )
df_flows_wrangle <- df_flows_wrangle %>% rename(dest_name = name, dest_lat = lat, dest_lon = lon)
# put largest on top
df_flows_wrangle <- df_flows_wrangle[order(df_flows_wrangle$Total),]
df_flows_wrangle

df_origin_wrangle <- merge(df_origin_sum, df_points, by.x="origin", by.y="id" )
# put smallest points on top so they are not obscured
df_origin_wrangle <- df_origin_wrangle[order(df_origin_wrangle$Total, decreasing=TRUE),]
# df_origin_wrangle

df_dest_wrangle <- merge(df_dest_sum, df_points, by.x="dest", by.y="id" )
# put smallest points on top so they are not obscured
df_dest_wrangle <- df_dest_wrangle[order(df_dest_wrangle$Total, decreasing=TRUE),]
# df_dest_wrangle



```


### Base map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

# PLOT NATURAL EARTH BORDERS
ne_world <- ne_countries(scale = "small", returnclass = "sf")
# class(ne_world)
# removes Antarctica
ne_world <- filter(ne_world, iso_a3 != "ATA") 

ne_coastline <- ne_coastline(scale = "small", returnclass = "sf")

```


### Flow Map
#### origins, destinations, and flows


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

# theme parameters
theme_opts <- theme(
  legend.position = "bottom",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_rect(fill = "#988373"),
  panel.border = element_blank(),
  plot.background = element_rect(fill = "#988373")
)

v1 <- ggplot() +
  geom_sf(data = ne_coastline, fill=NA, color="#8E796A", size=8) +
  geom_sf(data = ne_coastline, fill=NA, color="#837063", size=4) +
  geom_sf(data = ne_world, fill="#988373", color="#574C40", size=0.5) +
  geom_segment( data = df_flows_wrangle, aes( x=origin_lon, y=origin_lat, xend=dest_lon, yend=dest_lat, size=Total, color=Total, alpha=Total  ), lineend="round", linejoin="round" ) +
  geom_point( data = df_origin_wrangle, aes(x=lon, y=lat, size=Total), shape=21, color="white", fill="white", stroke=1, alpha=0.6) +
  geom_point( data = df_dest_wrangle, aes(x=lon, y=lat, size=Total), shape=21, color="white", fill="white", stroke=1, alpha=0.6) +
  scale_size_continuous(range=c(0.5,10), guide="none") +
  scale_alpha_continuous(range=c(0.4, 0.8), guide="none") +
  scale_fill_gradient(low = "#BF8490", high = "#FFFFFF", guide="none") + 
  scale_color_gradient(low = "#BF8490", high = "#FFFFFF", guide="none") + 
  coord_sf(xlim = c(min_lon, max_lon), ylim = c(min_lat, max_lat)) +
  theme_bw() +
  labs(x="",
       y="",
       title = "Trans-Atlantic Slave Trade", 
       subtitle=NULL) +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk
ggsave(filename = "outputs/trans-atlantic-slave-trade-fs.svg", plot = v1, width=16, height=9)

```



### References
#### citations for narrative and data sources

* Narrative sources: Trans-atlantic slave trade, [GO](https://wandabodnar.github.io/flowmap/transatlantic.html){target="_blank"}
* Data sources:
  + [Port info data](https://github.com/sctyner/slave-trade-data/blob/master/port_info.csv){target="_blank"}
  + [Voyages](https://slavevoyages.org/voyage/database){target="_blank"}
  + [RPubs](https://rpubs.com/WandaBodnar/644116){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```