---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(googlesheets4)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
INGEST  
</div>

# Kamino Project
## ingest a google sheet

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Jonathan Gallegos on Unsplash"}

masthead <- "assets/jonathan-gallegos-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Leave the road, take the trails...\
--- Pythagoras\

***

### Ingest
#### from shared link


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

# read only, authentication not needed with shared link
gs4_deauth()

path <- "https://docs.google.com/spreadsheets/d/150N38yVYhbGq6NzScBvXQkLCVr9owAmCafzOy2r3gV4/edit?usp=sharing"

```

### Plan & Process

* why
* systems
* models
* collections
* methods

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_plan <- read_sheet(path, sheet = 1)
df_plan

```

### Ingest
#### acquire data sources

* tabular
* relational
* unstructured
* pdf
* web
* social media

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_ingest <- read_sheet(path, sheet = 2)
df_ingest

```

### Wranglers
#### transform data for optimal use

* evaluate
* prepare
* reduce
* extend
* arrange
* structure
* domain
* preserve

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_wranglers <- read_sheet(path, sheet = 3)
df_wranglers

```

### Analytics
#### reveal insights

* calculate
* discover
* time-Series
* measure
* geospatial
* graph
* text-analytics

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_analytics <- read_sheet(path, sheet = 4)
df_analytics

```

### Views
#### design principles for visualization

* design
* perception
* acuity
* form
* layouts

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_views <- read_sheet(path, sheet = 5)
df_views

```

### Charts
#### design a quantitative view

* correlation
* deviation
* distribution
* magnitude
* part-to-whole
* ranking
* multiples

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_charts <- read_sheet(path, sheet = 6)
df_charts

```

### Diagrams
#### design a schematic view

* concept
* event
* logic
* structure
* system
* organization

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_diagrams <- read_sheet(path, sheet = 7)
df_diagrams

```

### Graphs
#### design a relational view

* characteristics
* operations
* link analysis
* social network analysis
* association
* flow

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_graphs <- read_sheet(path, sheet = 8)
df_graphs

```

### Maps
#### design a geospatial view

* map making
* area
* point
* abstract
* path
* space and time
* perspective


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_maps <- read_sheet(path, sheet = 9)
df_maps

```

### Semiographics
#### design a symbolic view

* meaning
* representation

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_semiographics <- read_sheet(path, sheet = 10)
df_semiographics

```

### Tables
#### design a tabular view

* chart table
* periodic table
* symbol table

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_tables <- read_sheet(path, sheet = 11)
df_tables

```

### Temporals
#### design an event view

* observables
* change
* flow
* resemblance
* finance
* chronology
* duration

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_temporals <- read_sheet(path, sheet = 12)
df_temporals

```

### Trees
#### design a hierarchical view

* space-filling
* node-link

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_trees <- read_sheet(path, sheet = 13)
df_trees

```

### Storytelling
#### design a presentation

* purpose
* design
* structure
* creation
* production

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_storytelling <- read_sheet(path, sheet = 14)
df_storytelling

```

### Summit
#### best practices and standards

* impact
* literacy
* professional standards

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_summit <- read_sheet(path, sheet = 15)
df_summit

```

### Case Studies

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_case_studies <- read_sheet(path, sheet = 16)
df_case_studies

```

### References
#### citations for narrative and data sources

* Narrative and Data Source: Kamino, https://github.com/UN-AVT/kamino-source


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "ingest google sheet" # mostly used in wranglers and analytics
keywords <- 'google sheets'
commands <- 'read_sheet sheet'
sources <- 'Kamino'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

