---
pagetitle: "Proportion of Departments by Sector"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(scales)
library(ggtern)
library(ggiraph)
library(viridis)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# Proportion of Departments by Sector
## Ternary Plot

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Hannah Reding on Unsplash"}

masthead <- "assets/hannah-reding-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Information is the reply to a question...\
--- Jacques Bertin, Sémiologie Graphique 

***

### Ingest the data
#### departments, sectors, and population

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "proportion-of-departments-by-sector/proportion-of-departments-by-sector.csv"
url <- paste0(url_root, url_file)

df_ingest <- read.csv(url, header = TRUE, stringsAsFactors = FALSE)
df_ingest

```

### Wrangle the data
#### factor department

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# not needed but for illustrative purposes
df_wrangle <- df_ingest
df_wrangle$department <- factor(df_wrangle$department)
df_wrangle

```

### Analysis
#### sum of the parts equal the whole

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_analysis <- df_wrangle %>% mutate(total_pop = i + ii + iii )
df_analysis

```


### Plot
#### position, shape, color, size


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

theme_opts <- theme(
  text = element_text(family = "inconsolata"), 
  legend.position = "none",
  legend.text = element_text(color = "black", size = 8),
  legend.title = element_blank(),
  tern.axis.title.L = element_text(hjust = 0.5),
  tern.axis.title.R = element_text(hjust = 0.5),
  panel.background = element_blank(),
  panel.border = element_blank(),
  plot.background = element_blank(),
  plot.margin = unit(c(0.25, 0.25, 0.25, 0.25), "in")
)

v1 <- ggtern(data=df_analysis, aes(x=i, y=ii, z=iii)) + 
  geom_point(aes(fill = total_pop, size = total_pop), shape = 21, color = "#ffffff", alpha = 0.7) + 
  scale_fill_viridis(option = "D") +
  scale_size("total_pop", range = c(1, 10)) +
  coord_tern() +
  theme_minimal() +
  theme_nomask() +
  theme_opts +
  labs(title = "Proportion of Departments by Sector", 
           subtitle = "by department, total_pop (color and size)") +
           xlab("Agriculture") + 
           ylab("Services") +
           zlab("Industry")

# v1

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### Wrangle
#### normalize with range scaling


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Rescale 0 to 100
df_rescale <- df_analysis
df_rescale$i <- rescale(df_rescale$i, to=c(0,100))
df_rescale$ii <- rescale(df_rescale$ii, to=c(0,100))
df_rescale$iii <- rescale(df_rescale$iii, to=c(0,100))

```


### Plot
#### with range rescaling


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}


v2 <- ggtern(data=df_rescale, aes(x=i, y=ii, z=iii)) + 
  geom_point(aes(fill = total_pop, size = total_pop), shape = 21, color = "#ffffff", alpha = 0.7) + 
  scale_fill_viridis(option = "D") +
  scale_size("total_pop", range = c(1, 10)) +
  coord_tern() +
  theme_minimal() +
  theme_nomask() +
  theme_opts +
  labs(title = "Proportion of Departments by Sector", 
           subtitle = "by department, total_pop (color and size)") +
           xlab("Agriculture") + 
           ylab("Services") +
           zlab("Industry")

girafe(ggobj = v2, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```

### References
#### citations for narrative and data sources

* Narrative and Data Source: Jacques Bertin, Sémiologie Graphique


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

