---
pagetitle: "USDA National Nutrient Database"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

library(tidyverse)
library(scales)
library(ggtern)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# USDA National Nutrient Database
## Ternary Plot

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Kelly Sikkema on Unsplash"}

masthead <- "assets/kelly-sikkema-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> The existence of broccoli does not in any way affect the taste of chocolate...\
--- John Green 

***

### Ingest the data
#### USDA National Nutrient Database

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "usda-food-data/usda-food-data-src.csv"
url <- paste0(url_root, url_file)

df_ingest <- read.csv(url, header = TRUE, stringsAsFactors = FALSE)
df_ingest



```

### Wrangle the data
#### filter on food group

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

#0: "American Indian/Alaska Native Foods"
#1: "Baby Foods"
#2: "Baked Products"
#3: "Beef Products"
#4: "Beverages"
#5: "Breakfast Cereals"
#6: "Cereal Grains and Pasta"
#7: "Dairy and Egg Products"
#8: "Fast Foods"
#9: "Fats and Oils"
#10: "Finfish and Shellfish Products"
#11: "Fruits and Fruit Juices"
#12: "Lamb, Veal, and Game Products"
#13: "Legumes and Legume Products"
#14: "Meals, Entrees, and Side Dishes"
#15: "Nut and Seed Products"
#16: "Pork Products"
#17: "Poultry Products"
#18: "Restaurant Foods"
#19: "Sausages and Luncheon Meats"
#20: "Snacks"
#21: "Soups, Sauces, and Gravies"
#22: "Spices and Herbs"
#23: "Sweets"
#24: "Vegetables and Vegetable Products"

df <- within(df_ingest, rm(ndb))
df_wrangle <- filter(df_ingest, food_group == "Vegetables and Vegetable Products")

# Reorder to avoid overlap
df_wrangle <- df_wrangle[order(df_wrangle$calories, decreasing = FALSE),]

df_wrangle

```


### Plot
#### position, shape, color, size


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

theme_opts <- theme(
  text = element_text(family = "inconsolata"), 
  legend.position = "none",
  legend.text = element_text(color = "black", size = 8),
  legend.title = element_blank(),
  tern.axis.title.L = element_text(hjust = 0.5),
  tern.axis.title.R = element_text(hjust = 0.5),
  panel.background = element_blank(),
  panel.border = element_blank(),
  plot.background = element_blank(),
  plot.margin = unit(c(0.25, 0.25, 0.25, 0.25), "in")
)

v1 <- ggtern(data=df_wrangle, aes(x=protein, y=carbohydrates, z=fat)) + 
  geom_point(aes(fill = calories, size = calories), shape = 21, color = "#ffffff", alpha = 0.7) + 
  scale_fill_gradient(low = "#DCEDC8", high = "#558B2F") +
  scale_size("calories", range = c(1, 10)) +
  coord_tern() +
  theme_minimal() +
  theme_nomask() +
  theme_opts +
  labs(title = "USDA National Nutrient Database", 
           subtitle = "by food group, calories (color and size)") +
           xlab("Protein") + 
           ylab("Carbohydrates") +
           zlab("Fat")

# v1

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### Wrangle
#### normalize with range scaling


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Rescale 0 to 100
df_rescale <- df_wrangle
df_rescale$protein <- rescale(df_rescale$protein, to=c(0,100))
df_rescale$carbohydrates <- rescale(df_rescale$carbohydrates, to=c(0,100))
df_rescale$fat <- rescale(df_rescale$fat, to=c(0,100))
df_rescale

```


### Plot
#### with range rescaling


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

v2 <- ggtern(data=df_rescale, aes(x=protein, y=carbohydrates, z=fat)) + 
  geom_point(aes(fill = calories, size = calories), shape = 21, color = "#ffffff", alpha = 0.7) + 
  scale_fill_gradient(low = "#DCEDC8", high = "#558B2F") +
  scale_size("calories", range = c(1, 10)) +
  coord_tern() +
  theme_minimal() +
  theme_nomask() +
  theme_opts +
  labs(title = "USDA National Nutrient Database", 
           subtitle = "by food group, calories (color and size)") +
           xlab("Protein") + 
           ylab("Carbohydrates") +
           zlab("Fat")

girafe(ggobj = v2, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```

### References
#### citations for narrative and data sources

* Narrative and Data Source: U.S. Department of Agriculture FoodData Central Data, [GO](https://fdc.nal.usda.gov/download-datasets.html){target="_blank"}
