---
pagetitle: "Hourly Earnings Male vs Female"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(kableExtra)
library(tidyverse)
library(magick)
library(MASS)
library(sitools)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()
```

<div class="activity">
WRANGLERS  
</div>

# Hourly Earnings Male vs Female
## Format Numbers

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Felix Koutchinski on Unsplash"}

masthead <- "assets/felix-koutchinski-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Work Place</div>


> To be a consistent winner means preparing not just one day, one month or even one year - but for a lifetime...\
--- Bill Rodgers\

***

### Load data

#### First of all, let's remove all "NA" values, do you remember how we did in __Clean__? 


```{r load raw data,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}


df <- read.csv('archetypes/hourly-earnings-male-vs-female.csv', header = TRUE, stringsAsFactors = FALSE)
df_1 <- na.omit(df)

rownames(df_1) <- NULL

```





```{r Styling Data Set, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_1%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)
df_tmp

#NOT TO BE USED AS SOLUTION 

```

### Convert double format into other formats 

#### When the number is large, such as population we can try the use of scientific format.

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 
df_2<-df_1
df_2$population<-format(df_1$population,scientific = TRUE)
 
```

```{r Styling Data Set2, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_2%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(3, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)
df_tmp
#NOT TO BE USED AS SOLUTION 

```

### Use the comma separators

```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 
df_3<-df_1
df_3$population <-format(df_1$population, big.mark=",") 


```


```{r Styling Data Set3, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_3%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(3, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)
df_tmp
#NOT TO BE USED AS SOLUTION 

```

### Long to readable
```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_8<-df_1
df_8$population_readable<-f2si(df_8$population)

```

```{r Styling Data Set8, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_8%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(6, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)

df_tmp
#NOT TO BE USED AS SOLUTION 

```  

### Currency Format
#### If there are currencies, let's add dollar sign "$" for the wage columns.

```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 
df_4<-df_1
df_4$avg_hourly_wage_men<-paste0("$ ", df_4$avg_hourly_wage_men)
df_4$avg_hourly_wage_women<-paste0("$ ", df_4$avg_hourly_wage_women)

```

```{r Styling Data Set4, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_4%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(4:5, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)
df_tmp
#NOT TO BE USED AS SOLUTION 

```
### Decimal format
#### We can round numbers to specified decimals as well, let's round __avg_hourly_wage_men__ to 1 decimal, and round __avg_hourly_wage_women__ to 3 decimals.

```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 
df_5<-df_1
df_5$avg_hourly_wage_men<-format(round(df_5$avg_hourly_wage_men,1), nsmall=1)
df_5$avg_hourly_wage_women<-format(round(df_5$avg_hourly_wage_women,3), nsmall=3)

```

```{r Styling Data Set5, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_5%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(4:5, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)

df_tmp
#NOT TO BE USED AS SOLUTION 

```

### Percentage format
#### Let's use following steps to calculate the percentage of increase/decrease for each year.

* Calculate the difference of average hourly wage between each year for men and women;
* Use the difference to divide the previous average hourly wage of that year then times 100;
* Round the result and add "%" sign in the end.


```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_6<-df_1%>%
  group_by(Entity)%>%
  mutate(avg_hourly_wage_diff_men=(avg_hourly_wage_men/lag(avg_hourly_wage_men) - 1)*100)%>%
  mutate(avg_hourly_wage_diff_women=(avg_hourly_wage_women/lag(avg_hourly_wage_women) - 1)*100)%>%
  dplyr::select(Entity,Year,avg_hourly_wage_diff_men,avg_hourly_wage_diff_women)

df_6 <- na.omit(df_6)

  df_6$avg_hourly_wage_diff_men<-format(round(df_6$avg_hourly_wage_diff_men,1), nsmall=1)
  df_6$avg_hourly_wage_diff_men<-paste0(df_6$avg_hourly_wage_diff_men," %")
  
  df_6$avg_hourly_wage_diff_women<-format(round(df_6$avg_hourly_wage_diff_women,1), nsmall=1)
  df_6$avg_hourly_wage_diff_women<-paste0(df_6$avg_hourly_wage_diff_women," %")
  

 

```


```{r Styling Data Set6, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_6%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(3:4, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)
df_tmp
#NOT TO BE USED AS SOLUTION 

```        

### Fraction format
#### If we want to calulate the ratio of average hourly wage women to men, use following steps, and display as a fraction format:

* Calculate avg_hourly_wage_women / avg_hourly_wage_men
* Decimal to fraction
* Output as character

```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_7<-df_1%>%
  mutate(avg_hourly_wage_women_men_ratio=avg_hourly_wage_women/avg_hourly_wage_men)%>%
  mutate(fraction=as.character(fractions(avg_hourly_wage_women_men_ratio)))%>%
  dplyr::select(Entity,Year,avg_hourly_wage_women_men_ratio,fraction)

```

```{r Styling Data Set7, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_7%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(4, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)
df_tmp
#NOT TO BE USED AS SOLUTION 

```  


# References
## The citations and data sources used for this case


The data source was from <a href="https://ilostat.ilo.org/" target="_blank">ILOSTAT</a>. ILOSTAT relies on multiple sources. The list of sources for each indicator, country by country, can be found in the ILOSTAT documentation under the bulk download facility, available <a href="http://www.ilo.org/ilostat/faces/oracle/webcenter/portalapp/pagehierarchy/Page30.jspx" target="_blank">here</a>

<pre>
@misc{internationallabourorganization_2018_ilostat,
  author = {International Labour Organization},
  title = {ILOSTAT},
  url = {https://ilostat.ilo.org/},
  urldate = {2021-05-28},
  year = {2018},
  organization = {ILOSTAT}
}
</pre>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```