---
pagetitle: "Hourly Earnings Male vs Female"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()
```

WRANGLERS  


# Hourly Earnings Male vs Female
## Format Numbers : Percentage Format

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Felix Koutchinski on Unsplash"}

masthead <- "assets/felix-koutchinski-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Work Place</div>


> To be a consistent winner means preparing not just one day, one month or even one year - but for a lifetime...\
--- Bill Rodgers\

***

### Ingest the data
Entity, Year, population, avg_hourly_wage_men, and avg_hourly_wage_women

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "hourly-earnings/hourly-earnings-male-vs-female.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = FALSE)
df

```

### Wrangle
First of all, let's remove all "NA" values, do you remember how we did in __Clean__? 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_1 <- na.omit(df)

rownames(df_1) <- NULL

```


Let's use following steps to calculate the percentage of increase/decrease for each year.

* Calculate the difference of average hourly wage between each year for men and women;
* Use the difference to divide the previous average hourly wage of that year then times 100;
* Round the result and add "%" sign in the end.


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'} 

df_2<-df_1%>%
  group_by(Entity)%>%
  mutate(avg_hourly_wage_diff_men=(avg_hourly_wage_men/lag(avg_hourly_wage_men) - 1)*100)%>%
  mutate(avg_hourly_wage_diff_women=(avg_hourly_wage_women/lag(avg_hourly_wage_women) - 1)*100)%>%
  dplyr::select(Entity,Year,avg_hourly_wage_diff_men,avg_hourly_wage_diff_women)

df_2 <- na.omit(df_2)

  df_2$avg_hourly_wage_diff_men<-format(round(df_2$avg_hourly_wage_diff_men,1), nsmall=1)
  df_2$avg_hourly_wage_diff_men<-paste0(df_2$avg_hourly_wage_diff_men," %")
  
  df_2$avg_hourly_wage_diff_women<-format(round(df_2$avg_hourly_wage_diff_women,1), nsmall=1)
  df_2$avg_hourly_wage_diff_women<-paste0(df_2$avg_hourly_wage_diff_women," %")
  

df_2 

```


# References
## The citations and data sources used for this case


The data source was from <a href="https://ilostat.ilo.org/" target="_blank">ILOSTAT</a>. ILOSTAT relies on multiple sources. The list of sources for each indicator, country by country, can be found in the ILOSTAT documentation under the bulk download facility, available <a href="http://www.ilo.org/ilostat/faces/oracle/webcenter/portalapp/pagehierarchy/Page30.jspx" target="_blank">here</a>

<pre>
@misc{internationallabourorganization_2018_ilostat,
  author = {International Labour Organization},
  title = {ILOSTAT},
  url = {https://ilostat.ilo.org/},
  urldate = {2021-05-28},
  year = {2018},
  organization = {ILOSTAT}
}
</pre>
