---
pagetitle: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()


```

WRANGLERS  

# Format Numbers

```{r, out.width="20%", fig.align="center"}

masthead <- "assets/noun_code formatting_2665697.svg"
knitr::include_graphics(masthead, dpi=72)

```


## Sometimes we need to format number to different types for better understanding, more readable or visual purpose. In our example, all numbers are in double class, meaning they are double-precision floating point numbers. Ways to format numbers:

* Scientific format: better for large numbers
* Comma separators format: better for large numbers
* Long to readable: better for large numbers
* Currency format: better for financial numbers
* Decimal format: better for consistence or visual purpose
* Percentage format: better for showing an increasing or decreasing trend
* Fraction format: better for comparison 
