---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/kamino.css", "../../../z-assemblers/wranglers.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/header.html"
      after_body: "../../../z-assemblers/footer.html"
    #self_contained: false
    #lib_dir: libs
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(htmltools) # needed to include html snippets
library(tidyverse)

library(knitcitations)
library(bibtex)

```

<div class="activity">
WRANGLERS  
</div>

# Storytelling
## The art and science

> One cannot achieve success with every film. Audiences can be unpredictable.\
The failure could be due to a bad script or characterisation...\
--- Amitabh Bachchan (Actor, Producer, Bollywood)\


* Cinematography
* Comics and Graphic Novels
* Creative Writing
* Data Journalism
* Documentaries
* Investigative Reporting
* Media Studies
* Animation and Stop-Motion
* Visual Communication


***

# Process
## Form Follows Function



# Story
## Elements

* Characters & Subject
* Setting & Context
* Plot & Goal
* Conflict & Problem
* Resolution & Opportunity

# Plot
## Structure

* Exposition: Introduces the character and setting
* Rising Action: Something changes; the characters meet a challenge or crisis
* Climax: The turning point and most exciting part of a story
* Falling Action: Events that follow as a result of the climax
* Resolution: The end that occurs after a conflict is resolved and a character has changed

## 

# Screenwriting
## Narrative



# Storyboarding
## Frames, Sequence, Narrative


# Visualtography
## Temp

Design
Sequential Art
Layout

# Section
## Subsection



# Section
## Subsection




# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

# cleanbib()
# read.bibtex(file = "./citations.bib")

```




```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

