---
pagetitle: "Animal Populations in Europe"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE, dev="svg"}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(dplyr) # tidy data transformation
library(colorspace)
library(sf)        # simple features GIS
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS
</div>

# Animal Populations in Europe
## point grid map

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Krzysztof Kowalik on Unsplash"}

masthead <- "assets/krzysztof-kowalik-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> He who lets the goat be laid on his shoulders is soon after forced to carry the cow...\
--- PROVERBS\

***


### Ingest
#### base and dot maps


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

# Europe Base map
nuts <- st_read("archetypes/animal-populations-in-europe/nuts.geojson", quiet = TRUE)

# Dot maps by animal
cow <- st_read("archetypes/animal-populations-in-europe/nutsdots-cow-75.geojson", quiet = TRUE)
buffalo <- st_read("archetypes/animal-populations-in-europe/nutsdots-buffalo-75.geojson", quiet = TRUE)
pig <- st_read("archetypes/animal-populations-in-europe/nutsdots-pig-75.geojson", quiet = TRUE)
sheep <- st_read("archetypes/animal-populations-in-europe/nutsdots-sheep-75.geojson", quiet = TRUE)
goat <- st_read("archetypes/animal-populations-in-europe/nutsdots-goat-75.geojson", quiet = TRUE)

```


### Plot
#### Cow


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

# draw a dot at each grid cell and scale its area
v1 <-  ggplot(data = nuts) +
  #faint land silhouettes in the back of the map
  geom_sf(fill = "grey98", color = lighten("#37474F", amount = 0.8)) +
  geom_sf(data = cow, aes(size = values), shape = 21, color = 'white', fill = "#37474F", show.legend = FALSE) +
  #geom_point(data = nutsdots, aes(x = X, y = Y, size = values), shape = 21, color = 'white', fill = '#E3D556', show.legend = FALSE) +
  #Equal area projection for Europe, and map boundaries
  coord_sf(xlim = c(2000000, 6000000), ylim =c(950000, 5000000), crs = 3035) +
  #Ensures circles are sized by area
  scale_size_area(max_size = 8) +
  theme_minimal() +
  theme(axis.text = element_blank(), panel.grid = element_line(size = 0))

girafe(ggobj = v1, width_svg = 12, height_svg = 16,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### Plot
#### Buffalo


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

# draw a dot at each grid cell and scale its area
v2 <-  ggplot(data = nuts) +
  #faint land silhouettes in the back of the map
  geom_sf(fill = "grey98", color = lighten("#5D4037", amount = 0.8)) +
  geom_sf(data = buffalo, aes(size = values), shape = 21, color = 'white', fill = "#5D4037", show.legend = FALSE) +
  #Equal area projection for Europe, and map boundaries
  coord_sf(xlim = c(2000000, 6000000), ylim =c(950000, 5000000), crs = 3035) +
  #Ensures circles are sized by area
  scale_size_area(max_size = 8) +
  theme_minimal() +
  theme(axis.text = element_blank(), panel.grid = element_line(size = 0))

girafe(ggobj = v2, width_svg = 12, height_svg = 16,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### Plot
#### Pig


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

# draw a dot at each grid cell and scale its area
v3 <-  ggplot(data = nuts) +
  #faint land silhouettes in the back of the map
  geom_sf(fill = "grey98", color = lighten("#D81B60", amount = 0.8)) +
  geom_sf(data = pig, aes(size = values), shape = 21, color = 'white', fill = "#D81B60", show.legend = FALSE) +
  #Equal area projection for Europe, and map boundaries
  coord_sf(xlim = c(2000000, 6000000), ylim =c(950000, 5000000), crs = 3035) +
  #Ensures circles are sized by area
  scale_size_area(max_size = 8) +
  theme_minimal() +
  theme(axis.text = element_blank(), panel.grid = element_line(size = 0))

girafe(ggobj = v3, width_svg = 12, height_svg = 16,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### Plot
#### Sheep


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}


# draw a dot at each grid cell and scale its area
v4 <-  ggplot(data = nuts) +
  #faint land silhouettes in the back of the map
  geom_sf(fill = "grey98", color = lighten("#D84315", amount = 0.8)) +
  geom_sf(data = sheep, aes(size = values), shape = 21, color = 'white', fill = "#D84315", show.legend = FALSE) +
  #Equal area projection for Europe, and map boundaries
  coord_sf(xlim = c(2000000, 6000000), ylim =c(950000, 5000000), crs = 3035) +
  #Ensures circles are sized by area
  scale_size_area(max_size = 8) +
  theme_minimal() +
  theme(axis.text = element_blank(), panel.grid = element_line(size = 0))

girafe(ggobj = v4, width_svg = 12, height_svg = 16,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### Plot
#### Goat


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

# draw a dot at each grid cell and scale its area
v5 <-  ggplot(data = nuts) +
  #faint land silhouettes in the back of the map
  geom_sf(fill = "grey98", color = lighten("#00695C", amount = 0.8)) +
  geom_sf(data = goat, aes(size = values), shape = 21, color = 'white', fill = "#00695C", show.legend = FALSE) +
  #Equal area projection for Europe, and map boundaries
  coord_sf(xlim = c(2000000, 6000000), ylim =c(950000, 5000000), crs = 3035) +
  #Ensures circles are sized by area
  scale_size_area(max_size = 8) +
  theme_minimal() +
  theme(axis.text = element_blank(), panel.grid = element_line(size = 0))

girafe(ggobj = v5, width_svg = 12, height_svg = 16,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/animal-populations-in-europe-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/animal-populations-in-europe-sm.svg", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative: Maarten Lambrechts, The Herds of Europe, https://www.maartenlambrechts.com/2018/07/31/beasts-of-europe.html
* Data: Eurostat, Animal populations by NUTS 2 regions, http://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=agr_r_animal&lang=en


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```




