---
pagetitle: "Global Wealth Report"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(countrycode)
library(readr)
library(ggforce)
library(ggvoronoi)
library(ggplot2)
library(treemapify)
library(SysbioTreemaps)
library(ggplotify)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
TREES  
</div>

# Global Wealth Report
## The Treemap

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1080/72, fig.height=1080/72, out.width="100%"}

# Load data
df = read.csv("./archetypes/top-100-companies/top-100-companies.csv", header = TRUE, stringsAsFactors = FALSE)  # read text file 
df

df_wrangle <- df
df_wrangle$Market.Cap..May.2021. <- parse_number(df_wrangle$Market.Cap..May.2021.)
df_wrangle

df_analysis <- df_wrangle %>% 
  group_by(Country, Sector) %>% 
  summarise(Total = sum(Market.Cap..May.2021.))

df_analysis$Region <- countrycode(df_analysis$Country, origin = 'country.name', destination = 'un.region.name') 

df_analysis <- df_analysis %>%
  arrange(Region)

df_analysis

# df_analysis$Region <- df_analysis %>% mutate(Region = ifelse( Country == 'Canada', 'Canada', as.character(df_analysis$Region)))
df_analysis$Region <- ifelse( df_analysis$Country == 'Canada', 'Canada', as.character(df_analysis$Region))
df_analysis$Region <- ifelse( df_analysis$Country == 'China', 'China', as.character(df_analysis$Region))
df_analysis$Region <- ifelse( df_analysis$Country == 'Saudi Arabia', 'Saudi Arabia', as.character(df_analysis$Region))
df_analysis

region_palette <- c(
  'Americas' = 'red',
  'Asia' = 'blue',
  'Europe' = 'green',
  'Oceania' = 'yellow'
)

tm <- voronoiTreemap(
  data = df_analysis,
  levels = c("Region", "Sector"),
  cell_size = "Total",
  shape = "circle",
  seed = 123
)

drawTreemap(tm, label_size = 2.5, label_color = "white")

library(gridSVG)

grid.export(name = "assets/treemap.svg",
            exportCoords = "none", # c("none", "inline", "file"),
            exportMappings = "none", # c("none", "inline", "file"),
            exportJS = "none", # c("none", "inline", "file"),
            res = NULL,
            prefix = "",
            addClasses = TRUE,
            indent = TRUE,
            htmlWrapper = FALSE,
            #usePaths = c("vpPaths", "gPaths", "none", "both"),
            uniqueNames = TRUE,
            annotate = TRUE,
            progress = FALSE,
            compression = 0,
            strict = TRUE,
            rootAttrs = NULL)


```



```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Marc Babin on Unsplash"}

masthead <- "assets/marc-babin-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> One of the simplest ways to get an idea of one trillion dollars is to consider the amount in terms of the passage of time.\
  One trillion seconds equals thirty-two thousand years...\
--- Geoff Davis\

***

### Ingest the data
#### trillions for what


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
df = read.csv("./archetypes/trillions/trillions.csv", header = TRUE, stringsAsFactors = FALSE)  # read text file 
df

```


### Wrangle the data
#### factor category for color mapping


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_wrangle <- df
df_wrangle$category <- factor(df_wrangle$category)
df_wrangle

```



### The Layout
#### squarified with size and fill


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

category_palette <- c(
  'helping' = '#4FC3F7',
  'hoarding' = '#00BCD4',
  'earning' = '#26A69A',
  'losing' = '#FF7043',
  'fighting' = '#F44336',
  'spending' = '#FBC02D',
  'saving' = '#8BC34A',
  'owing' = '#FF9800',
  'banking' = '#66BB6A',
  'winning' = '#5C6BC0'
)

# Layouts
# squarified" (the default), "scol", "srow" or "fixed"
# Simple
v1 <- ggplot(df_wrangle, aes(area = trillion_usd, fill = category)) +
  geom_treemap(color = "#ffffff") +
  scale_fill_manual(values = category_palette) +
  theme_minimal() +
  theme(legend.position = "bottom")

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


#### with labels


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

# Labeled
v2 <- ggplot(df_wrangle, aes(area = trillion_usd, fill = category, label = what)) +
  geom_treemap(color = "#ffffff") +
  geom_treemap_text(fontface = "italic", colour = "white", place = "centre", grow = TRUE) +
  scale_fill_manual(values = category_palette) +
  theme_minimal() +
  theme(legend.position = "bottom")

girafe(ggobj = v2, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


#### with labels and subgroups


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

# Sub-grouping
v3 <- ggplot(df_wrangle, aes(area = trillion_usd, fill = category, label = what,
                subgroup = category)) +
  geom_treemap(color = "#ffffff") +
  geom_treemap_subgroup_border(colour = "white") +
  geom_treemap_subgroup_text(place = "centre", grow = T, alpha = 0.5, colour =
                               "black", fontface = "italic", min.size = 0) +
  geom_treemap_text(colour = "white", place = "topleft", reflow = T) +
  scale_fill_manual(values = category_palette) +
  theme_minimal() +
  theme(legend.position = "bottom")

# v3

girafe(ggobj = v3, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```



### References
#### citations for narrative and data sources

* Narrative and Data Sources: 


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
