---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(patchwork)
library(grid)
library(ggtext)
library(gridtext)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
TEMPORALS  
</div>

# California Droughts
## Area Segmented Facet

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Ross Stone on Unsplash"}

masthead <- "assets/ross-stone-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> There's a 100 percent change that it gets worse before it gets better...\
--- Daniel Swain, Climate Scientist, UCLA\

***


### Ingest
#### year, month, drought level, and area percent


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df <- read.csv("archetypes/california-droughts/california-droughts.csv", header = TRUE, stringsAsFactors = TRUE)
df

```


### Wrangle
#### factor drought levels from exceptional to abnormal


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_wrangle <- df
df_wrangle$drought_lvl <- factor(df_wrangle$drought_lvl, levels = c("D4", "D3", "D2", "D1", "D0"))
df_wrangle

```



### Plot
#### facet by year

<center><mark style="background-color: #E2E6BD">D0</mark> Abnormally Dry <mark style="background-color: #E5D75E">D1</mark> Moderate Drought <mark style="background-color: #EAAF2B">D2</mark> Severe Drought <mark style="background-color: #E6863C">D3</mark> Extreme Drought <mark style="background-color: #DB595C">D4</mark> Exceptional Drought</center>  


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1920/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 10), 
    axis.text.y = element_blank(),
    legend.position='none',
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    panel.border = element_blank(),
    panel.background = element_rect(fill = "grey95", color = NA),
    panel.spacing.x = unit(1, "lines"),
    panel.spacing.y = unit(1, "lines"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.text = element_text(size = 10, face = "bold"),
    strip.background = element_blank()
)

drought_level_palette <- c(
  "D0" = "#E2E6BD",
  "D1" = "#E5D75E",
  "D2" = "#EAAF2B",
  "D3" = "#E6863C",
  "D4" = "#DB595C"
)

# Plot
v1 <- 
  ggplot(df_wrangle, aes(month, area_pct, group = drought_lvl, color = drought_lvl, fill = drought_lvl)) +
  geom_col(width = 1, size = .2 ) +
  scale_x_continuous( limits = c(0.5, 12.5), breaks = c(2, 5, 8, 11), labels = c("Feb", "May", "Aug", "Nov")) +
  scale_fill_manual(values = drought_level_palette) +
  scale_color_manual(values = drought_level_palette) +
  coord_cartesian(expand = FALSE) +
  facet_wrap( ~ year, scale = "free_y", ncol = 6) +
  labs(title = "California Droughts",
       subtitle = "by monthly drought level",
       caption = "Source: U.S. drought monitor",
       x = NULL,
       y = NULL) +
  theme_minimal() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.85))
)

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/california-droughts-fs.svg", plot = v1, width=720/72, height=1280/72)

# thumbnail version without annotations
ggsave(filename = "outputs/california-droughts-sm.svg", plot = v1, width=2.25, height=4)

```


### References
#### citations for narrative and data sources

* Narrative: TidyTuesday
* Data Source: U.S. drought monitor


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "area segmented facet" # mostly used in wranglers and analytics
keywords <- 'california droughts'
commands <- 'geom_col facet_wrap'
sources <- 'TidyTuesday U.S. drought monitor'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

