---
pagetitle: "Mapping airline routes"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE, echo=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

# Libraries
library(tidyverse)
library(rnaturalearth)
library(rnaturalearthdata)
library(geosphere)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Mapping airline routes
## Connection Map


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Wade Lambert on Unsplash"}

masthead <- "assets/wade-lambert-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> The scientific theory I like best is that the rings of Saturn are composed entirely of lost airline luggage....\
--- Mark Russell\

***

### Ingest
#### Routes and lights

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

flights_routes <- read.csv("archetypes/flight-routes/british-airways.csv", header = TRUE)
flights_routes

# use city populations to simulate lights as in original
lights = read.csv("archetypes/cities-top-10000-world.csv", header = TRUE, stringsAsFactors = FALSE)
# lights

```


### Wrangle
#### group and filter


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

flights_points <- flights_routes %>%
  group_by(group) %>%
  filter(row_number() == 1 | row_number() == n())

flights_points

```


### Base map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# PLOT NATURAL EARTH BORDERS
ne_world <- ne_countries(scale = "small", returnclass = "sf")
# removes Antarctica
ne_world <- filter(ne_world, iso_a3 != "ATA")

```


### Map Theme
#### Theme, light and dark


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

theme_opts <- theme(
      axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      legend.title = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background=element_rect(fill="#0d0e1b", colour="#0d0e1b"),
      panel.border = element_blank()
)

theme_dark <- theme(
      panel.background=element_rect(fill="#0d0e1b", colour="#0d0e1b")
)

theme_light <- theme(
      panel.background=element_rect(fill="#ffffff", colour="#ffffff")
)


```


### Connection Map
#### with dark theme


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v1 <- ggplot() +
  # Draw the natural earth map  styling to match blue marble dark lights
  geom_sf(data = ne_world, fill="#0f1227", color="#1c3153", stroke=1.0) +
  # Plot all the lights of the cities at night
  geom_point(data = lights, aes(x=lng, y=lat, alpha=Population), size=0.5, color="#ffffff" ) +
  # routes
  geom_path(data = flights_routes, aes(long, lat, group = id, color = name), alpha = 0.2, size = 0.5) + 
  # airline hubs
  geom_point(data = flights_points, aes(long, lat), alpha = 0.3, size = 1, colour = "#f9ba00") +
  # brightness by population
  scale_alpha_continuous(range=c(0.1,1), guide=FALSE) +
  # color by airline
  scale_color_manual(values = c("#f9ba00", "#075aaa", "#ff0000")) +
  theme_bw() +
  labs(x="",
       y="",
       title = "Airline Flight Routes", 
       subtitle="") +
  theme_opts +
  theme_dark

girafe(ggobj = v1, width_svg = 16, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


### Connection Map
#### with light theme


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v2 <- ggplot() +
  geom_sf(data = ne_world, fill="#f5f5f5", color="#d5d5d5", stroke=1.0) +
  # lights
  geom_point(data = lights, aes(x=lng, y=lat, alpha=Population), size=0.5, color="#777777" ) +
  # routes
  geom_path(data = flights_routes, aes(long, lat, group = id, color = name), alpha = 0.2, size = 0.5) + 
  # airline hubs
  geom_point(data = flights_points, aes(long, lat), alpha = 0.3, size = 1, colour = "#075aaa") +
  # brightness by population
  scale_alpha_continuous(range=c(0.1,1), guide=FALSE) +
  # color by airline
  scale_color_manual(values = c("#075aaa", "#f9ba00", "#ff0000")) +
  theme_bw() +
  labs(x="",
       y="",
       title = "Airline Flight Routes", 
       subtitle="") +
  theme_opts +
  theme_light

girafe(ggobj = v2, width_svg = 16, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk
ggsave(filename = "outputs/airline-flight-routes-dark-map-fs.svg", plot = v1, width=16, height=9)

```


### References
#### citations for narrative and data sources

* Narrative and Data source: Open Flights,[GO](https://openflights.org/data.html){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```



