---
pagetitle: "Where do surfers travel?"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE, echo=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

# Libraries
library(tidyverse)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Where do surfers travel?
## Connection Map


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Josh Withers on Unsplash"}

masthead <- "assets/josh-withers-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> I'm surfing the giant life wave....\
--- William Shatner\

***

### Ingest
#### tweets and lights


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
df <- read.csv("archetypes/where-do-surfers-travel/where-do-surfers-travel.csv", header = TRUE, stringsAsFactors = FALSE)
df

# use city populations to simulate lights as in original
lights = read.csv("archetypes/cities-top-10000-world.csv", header = TRUE, stringsAsFactors = FALSE)
# lights

```

### Wrangler
#### column as factor

Categorizing __homecontinent__ column as a factor. The Continents levels will be used to color the lines on the map.

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# factor for color scale
df$homecontinent=factor(df$homecontinent, levels=c("Asia", "Europe", "Australia", "Africa", "North America", "South America", "Antarctica"))
df

```


### Base map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# PLOT NATURAL EARTH BORDERS
ne_world <- ne_countries(scale = "small", returnclass = "sf")

```


### Map Theme
#### dark


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

theme_opts <- theme(
      legend.position="bottom",
      legend.title = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.border = element_blank()
)

theme_dark <- theme(
  panel.background=element_rect(fill="#05050f", colour="#000000"),
)

```


### Connection Map
#### with geom_line


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v1 <- ggplot(data = ne_world) +
  # map feature styling to match blue marble dark lights
  geom_sf(fill="#211f3c", color="#131522", stroke=0.5) +
  # lights
  geom_point( data = lights, aes(x=lng, y=lat, alpha=Population), size=0.5, color="#f9e6ba" ) +
  # brightness by population
  scale_alpha_continuous(range=c(0.1,1), guide=FALSE) +
  # connections
  geom_line(data=df, aes(x=lon, y=lat, group=group, colour=homecontinent, alpha=n), size=0.6) +
  # guides(alpha = "none") +
  scale_color_brewer(palette="Set3") +
  theme_bw() +
  labs(x="",
       y="",
       title = "Where surfers travel", 
       subtitle="10,000 #surf tweets recovered") +
  theme_opts +
  theme_dark

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk
ggsave(filename = "outputs/where-surfers-travel-fs.svg", plot = v1, width=16, height=9)

```


### References
#### citations for narrative and data sources

* Narrative and Data source: [GO](https://github.com/holtzy/About-Surfers-On-Twitter){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
