---
pagetitle: "Lone parent household"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

# Load needed libraries
library(tidyverse)
library(scales)
library(ggiraph)

```

<div class="activity">
CHARTS
</div>

# Lone-parent Households
## Bar Vertical Segmented


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Marcelo Silva on Unsplash"}

masthead <- "assets/marcelo-silva-uKxGOwwALuU-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Being a single parent is twice the work, but also twice the hugs...\
--- Unknown\

***

### Load the data
#### Lone-parent households by age and sex of parent, age of child and region, latest available year

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
df <- read_csv("archetypes/lone-parent-households/figure-2-11.csv", col_names=TRUE)

# Transpose columns
long <- gather(df, type, Percentage, "Lone father (all ages)":"Lone mother 60+ and all children 18 and over", factor_key=FALSE)

# Format x-axis labels
long$Regionwrap = str_wrap(long$Region, width = 17)

# Order by category
long$type <- factor(long$type, levels=c("Lone mother 0-17 and at least one child below 18",
                                        "Lone mother 18-24 and at least one child below 18",
                                        "Lone mother 25-34 and at least one child below 18",
                                        "Lone mother 35-59 and at least one child below 18",
                                        "Lone mother 60+ and at least one child below 18",
                                        "Lone mother 25-34 and all children 18 and over",
                                        "Lone mother 35-59 and all children 18 and over",
                                        "Lone mother 60+ and all children 18 and over",
                                        "Lone father (all ages)"))

long

```

### Plot the chart
#### One-parent households: mostly lone mothers - Figure 2.11

```{r draw-plot, message=FALSE, warning=FALSE, echo=TRUE, fig.width=10, fig.height=6, class.source = 'fold-hide'}

# Define palette
segment_palette <- c("Lone mother 0-17 and at least one child below 18" = "#6b9e7e",
                "Lone mother 18-24 and at least one child below 18" = "#88b88a",
                "Lone mother 25-34 and at least one child below 18" = "#a6609c",
                "Lone mother 35-59 and at least one child below 18" = "#692c7d",
                "Lone mother 60+ and at least one child below 18" = "#acc8ed",
                "Lone mother 25-34 and all children 18 and over" = "#678bb3",
                "Lone mother 35-59 and all children 18 and over" = "#406993",
                "Lone mother 60+ and all children 18 and over" = "#bec068",
                "Lone father (all ages)" = "#2b4662")

# Make the plot
v1<-ggplot(long, aes(y = Percentage, x = Regionwrap)) + 
  geom_col(aes(fill = type), position = "fill", width = 0.55) +
  scale_y_continuous(labels = percent_format(accuracy=1), breaks=seq(0,1,0.1)) +
  scale_fill_manual(values = segment_palette) +
  scale_x_discrete(limits=c("Sub-Saharan\nAfrica",
                            "Central and\nSouthern Asia",
                            "Northern Africa\nand Western Asia",
                            "Latin America and\nthe Caribbean",
                            "Europe and\nNorthern America",
                            "World")) +
  labs(
    title = "Figure 2.11: Lone-parent households by age and sex of parent, age of child and region, latest available year",
    caption = "Source: UN Women Progress of the World's Women 2019-2020 - Families in a Changing World") +
  theme( panel.background = element_rect(fill = "white"), 
         panel.grid.major.y = element_line(color="gray", size=0.1), 
         axis.title.x = element_blank(), 
         axis.ticks = element_blank(), 
         legend.position = "bottom", 
         legend.title = element_blank()) +
  guides(fill = guide_legend(ncol=2)) +
  geom_text(aes(fill = type, label = Percentage), position = position_fill(vjust = 0.5), check_overlap = TRUE, color="white", size = 3)
 
girafe(ggobj = v1, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```

### References
#### citations for narrative and data sources

* Narrative and Data sources: UN Women Progress of the world’s women 2019-2020 Report, [GO](https://www.unwomen.org/en/digital-library/progress-of-the-worlds-women){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```



