---
pagetitle: "Family Integration Policy by Country"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# Family Integration Policy by Country
## Bar Horizontal Ordered

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Mitchel Lensink on Unsplash"}

masthead <- "assets/mitchel-lensink-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> [t]he family is the natural and fundamental group unit of society\
  and is entitled to protection by society and the State...\
--- The Universal Declaration of Human Rights\

***

### Ingest
#### country, region, and family integration policy scores


```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "family-integration-policy-by-country/family-integration-policy-by-country.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = TRUE)
df

```

### Plot 
#### with standard alpha order

```{r draw-plot, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 11),
    plot.margin = margin(.25, 1, .25, .25, "in"),
    plot.background = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    #panel.grid.major.y = element_blank(),
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, face = "bold"),
    # axis.title.y=element_blank(),
    # axis.ticks.y=element_blank(),
    # axis.ticks.x=element_blank(),
    # axis.text.x=element_blank(),
    legend.position = "none"
)

v1 <- ggplot(df, aes(x=Country, y=Family.Integration.Policy.Average.Scores)) + 
  geom_bar(stat="identity", fill="#88b88a") +
  scale_y_continuous(breaks = seq(0, 100, 10), limits = c(0, 100)) +
  coord_cartesian(clip="off") +
  labs(title = "FAMILY INTEGRATION POLICY AVERAGE SCORES BY COUNTRY, 2014", x = NULL, y = "Family integration policy average scores") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```


### Plot
#### ordered, ascending


```{r drawa, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

v2 <- ggplot(df, aes(x=reorder(Country,Family.Integration.Policy.Average.Scores), y=Family.Integration.Policy.Average.Scores)) + 
  geom_bar(stat="identity", fill="#88b88a") +
  scale_y_continuous(breaks = seq(0, 100, 10), limits = c(0, 100)) +
  coord_cartesian(clip="off") +
  labs(title = "FAMILY INTEGRATION POLICY AVERAGE SCORES BY COUNTRY, 2014", x = NULL, y = "Family integration policy average scores") +
  theme_bw() +
  theme_opts

girafe(ggobj = v2, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```


### Plot
#### ordered, descending


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

v3 <- ggplot(df, aes(x=reorder(Country,-Family.Integration.Policy.Average.Scores), y=Family.Integration.Policy.Average.Scores)) + 
  geom_bar(stat="identity", fill="#88b88a") +
  scale_y_continuous(breaks = seq(0, 100, 10), limits = c(0, 100)) +
  coord_cartesian(clip="off") +
  labs(title = "FAMILY INTEGRATION POLICY AVERAGE SCORES BY COUNTRY, 2014", x = NULL, y = "Family integration policy average scores") +
  theme_bw() +
  theme_opts

girafe(ggobj = v3, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```

### References
#### The citations and data sources used for this case

* Narrative and Data Source, UN Women, Progress of the world’s women, [GO](https://www.unwomen.org/en/digital-library/progress-of-the-worlds-women){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

