---
pagetitle: "Alcohol Comsumption by Country"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(readxl)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


<div class="activity">
INGEST  
</div>

# Top 25 Countries in the Alcohol Comsumption Rank
## Ingest an Excel file 

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Brendan Church on Unsplash"}

masthead <- "assets/brendan-church-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> If I had a spreadsheet on my computer, it looked like I was busy...\
--- Nate Silver\

***

### Ingest
#### sheet one

```{r load-data sh1, echo=TRUE, message=FALSE, warning=FALSE,class.source = 'fold-hide'}

df1 <- read_excel('archetypes/alcohol-consumption-by-country/alcohol-consumption-by-country.xlsx', sheet=1)
df1

```


### Ingest
#### sheet two


```{r load-data sh2, echo=TRUE, message=FALSE, warning=FALSE,class.source = 'fold-hide'}

df2 <- read_excel('archetypes/alcohol-consumption-by-country/alcohol-consumption-by-country.xlsx', sheet=2)
df2

```


### References
#### citations for narrative and data sources

* Narrative and Data Source: Global Health Data Repository, World Health Organization, [GO](https://apps.who.int/gho/data/node.main-euro.A1039?lang=en&showonly=GISAH){target="_blank"}


<pre>
@misc{murray_2019_week,
  author = {Murray, Eva},
  month = {06},
  title = {Week 26: Alcohol Consumption by Country | Makeover Monday},
  url = {https://www.makeovermonday.co.uk/week-26-2019/},
  urldate = {2021-03-02},
  year = {2019},
  organization = {MakeoverMonday}
}

@misc{worldhealthorganization_2020_gho,
  author = {World Health Organization},
  month = {05},
  title = {GHO | Global Health Observatory Data Repository (European Region) | Recorded alcohol per capita consumption, from 2010 - Updated May 2020},
  url = {https://apps.who.int/gho/data/node.main-euro.A1039?lang=en&showonly=GISAH},
  urldate = {2021-03-25},
  year = {2020},
  organization = {WHO}
}
</pre>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


