---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(readxl)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

INGEST  

# Top 25 Countries in the Alcohol Comsumption Rank
## Ingest an Excel file 

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Brendan Church on Unsplash"}

masthead <- "assets/brendan-church-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> If I had a spreadsheet on my computer, it looked like I was busy...\
--- Nate Silver\

***

### Ingest
#### sheet one

```{r load-data sh1, echo=TRUE, message=FALSE, warning=FALSE,class.source = 'fold-hide'}


url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "alcohol-consumption-by-country/alcohol-consumption-by-country.xlsx"
url <- paste0(url_root, url_file)


p1f <- tempfile()
download.file(url, p1f, mode="wb")
df1<-read_excel(path = p1f, sheet = 1)

df1


```


### Ingest
#### sheet two


```{r, echo=TRUE, message=FALSE, warning=FALSE,class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "alcohol-consumption-by-country/alcohol-consumption-by-country.xlsx"
url <- paste0(url_root, url_file)


p1f <- tempfile()
download.file(url, p1f, mode="wb")
df2<-read_excel(path = p1f, sheet = 2)

df2


```


### References
#### citations for narrative and data sources

* Narrative: Global Health Data Repository, World Health Organization, [GO](https://apps.who.int/gho/data/node.main-euro.A1039?lang=en&showonly=GISAH){target="_blank"}

* Data Source: Week 26: Alcohol Consumption by Country, MakeoverMonday, [GO](https://www.makeovermonday.co.uk/week-26-2019/){target="_blank"}

<pre>
@misc{murray_2019_week,
  author = {Murray, Eva},
  month = {06},
  title = {Week 26: Alcohol Consumption by Country | Makeover Monday},
  url = {https://www.makeovermonday.co.uk/week-26-2019/},
  urldate = {2021-03-02},
  year = {2019},
  organization = {MakeoverMonday}
}

@misc{worldhealthorganization_2020_gho,
  author = {World Health Organization},
  month = {05},
  title = {GHO | Global Health Observatory Data Repository (European Region) | Recorded alcohol per capita consumption, from 2010 - Updated May 2020},
  url = {https://apps.who.int/gho/data/node.main-euro.A1039?lang=en&showonly=GISAH},
  urldate = {2021-03-25},
  year = {2020},
  organization = {WHO}
}
</pre>