---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(knitcitations)
library(bibtex)

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
INGEST  
</div>

# Ingest an excel data file
## Workbooks, worksheets, and spreadsheets

```{r, out.width="40%", fig.align="center", fig.cap="Photo by Rooty"}

# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "assets/xlsx.png"
knitr::include_graphics(masthead, dpi=72)

```

The Microsoft Excel __spreadsheet__ file format is widely used for storing tabular data.  The spreadsheet structure is based on a __grid__ of cells with __numbered rows__ and __letter-named columns__.  Although the software provides many additional features such as macros, formulas, charts, and pivot tables, the ingest solutions are focused on the use of Excel as a __data source__.  An Excel spreadsheet can be __exported__ as a __delimited data file__ as an alternative option.

* The most common file __formats__ are the binary (*.xls) and xml (.xlsx) workbook formats.
* Workbook files enable the storage of data in multiple __sheets__.
* Each sheet contains a set of data equivalent to a __table__.
* Unlike the conventions of a delimited data file, column __headers__ may not be in the first row.
* A worksheet can contain __merged columns__, __rows__, and __unstructured__ text.
* The smallest unit of stored data is a cell, the intersection of a row and column.

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "excel" # mostly used in wranglers and analytics
keywords <- 'spreadsheet excel sheet'
commands <- ''
sources <- ''

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```

```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

