---
pagetitle: "African Country's Economic Survey"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)
library(ggiraph)
library(reshape2)
library(RColorBrewer)
library(ggthemes)


library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# African's Country Economic Survey

## Looking ahead, do you expect economic conditions in this country to be better or worse in twelve months time?	

## Bar stacked divergent 

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Simon Berger  on Unsplash"}

masthead <- "assets/simon-berger-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> We have to be impatient in Moving African Forward...\
--- Akinwumi Ayodeji Adesina, AFB President\

***

### Ingest the data
#### AfroBarometer (R7 2016/2018)


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "countrys-economic-survey/AfroBarometer.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = FALSE)
df


```

### Wrangle the Data

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

colnames(df)<-c("Country", "Much worse", "Worse", "Same", "Better",  "Much better")

# We will be diving the data in half so that it centers on 0
df2 <- df %>% mutate(midLow = Same/2, midHigh = Same/2) %>% select(Country, `Much worse`, Worse, midLow, midHigh, Better, `Much better`)

#Determing the colors for the factors
colorset = c('Much worse'='#E66101','Worse'='#FDB863','Almost the Same'='#e2c0a6', 'Better' = '#B2ABD2', 'Much better' = '#5E3C99')

#GGplot works well with Long Format
df3 <- melt(df2, id="Country")
df3$value<-df3$value*100
df3$Country<-factor(df3$Country)


#This is the code for the devision, we'll be plotting two bar plots on either side of 0
highs<-na.omit(df3[(length(df3[,1])/2)+1:length(df3[,1]),])
lows<-na.omit(df3[1:(length(df3[,1])/2),])
lows <- lows[rev(rownames(lows)),]
highs <- highs[rev(rownames(highs)),]

#We convert the mid-values back to Same
levels(highs$variable)[levels(highs$variable) == "midHigh"] <- "Almost the Same" 
levels(lows$variable)[levels(lows$variable) == "midLow"] <- "Almost the Same" 

```



### Plot
#### Number of Millionaires

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Common theme for both charts
theme_opts <- theme(
    legend.position='none', 
    panel.background = element_rect(fill = "white", colour = "white"), 
    text = element_text(family = "inconsolata"), 
    plot.title = element_text(color = "black", size = 20, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 15),
    plot.caption = element_text(color = "#555555", size = 15),
    axis.text = element_text(size=15,face = "bold" ),
    panel.grid.major.x = element_line(size = 0.5, linetype = 'solid', colour = "#b0bfc8"),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank()
    )

v1 <- ggplot() + geom_bar(data=highs, aes(x = factor(Country, level = rev(levels(df3$Country))), y=value, fill=variable), position= position_stack(reverse = T), stat="identity") +
  geom_bar(data=lows, aes(x = Country, y=-value, fill=variable), position="stack", stat="identity") +
  geom_hline(yintercept = 0, color =c("#e2c0a6")) +
  scale_fill_manual(values = colorset, name = "Survey Results") +
coord_flip() +
  scale_y_continuous(breaks=seq(-100,100,25), limits=c(-100,100)) +
  labs(title="African Country’s Economic Survey", 
       subtitle = "Looking ahead, do you expect economic conditions\nin this country to be better or worse in twelve months time?",
       caption = "Afrobarometer (R7 2016/2018)",
       y="Percent",x="") +
  theme_opts

girafe(ggobj = v1, width_svg = 12, height_svg = 16,
       options = list(opts_sizing(rescale = TRUE, width = 0.6)))

```

### References
#### citations for narrative and data sources

* Inspiration and Narrative Sources: R not R, [GO](http://rnotr.com/likert/ggplot/barometer/likert-plots/){target="_blank"}
* Data Sources: AfroBarometer, [GO](https://afrobarometer.org/data){target="_blank"}
