---
pagetitle: "Average SAT Scores for NYC Public Schools"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Average SAT Scores for NYC Public Schools
## Parse Numbers
<kbd>
gsub
</kbd>

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Andre Hunter on Unsplash"}

masthead <- "assets/andre-hunter-AQ908FfdAMw-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">The Graduation</div>

> What I remember most about high school are the memories I created with my friends....\
--- J.J. Watt\

***

### Load the data

```{r Load raw data, warning=FALSE, echo=TRUE, warning=FALSE,class.source = 'fold-hide'}

df <- read.csv('./archetypes/scores.csv', header = TRUE, stringsAsFactors = FALSE)
df
```

Let's take a look at the column Street.Address. Both the Street Name and Building number are in the column. Perhaps, we'll like to sepearate them. 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

head(df$Street.Address)
```


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}
df2 <- data.frame(Building_Number = rep(1,435))
df2$Building_Number <- parse_number(df$Street.Address)
df2$Street_Name <- gsub('[[:digit:]]+', '', df$Street.Address)
df2

```

### References
#### citations for narrative and data sources
* Narrative and data sources: Average SAT Scores for NYC Public Schools, [GO](https://www.kaggle.com/nycopendata/high-schools){target="_blank"}

```{r generateBibliography, echo=FALSE, message=FALSE, warning=FALSE}

# cleanbib()
# options("citation_format" = "pandoc")
# read.bibtex(file = "./citations/UN-Member-State-admission-dates.bib")

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

