---
pagetitle: "Average SAT Scores for NYC Public Schools"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(ggiraph)
library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# Average SAT Scores for NYC Public Schools
## Parse String

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Andre Hunter on Unsplash"}

masthead <- "assets/andre-hunter-AQ908FfdAMw-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">The Graduation</div>

> What I remember most about high school are the memories I created with my friends....\
--- J.J. Watt\

***

### Load the data

```{r Load raw data, warning=FALSE, echo=TRUE, warning=FALSE,class.source = 'fold-hide'}

df <- read.csv('./archetypes/scores.csv', header = TRUE, stringsAsFactors = FALSE)
df
```
### Wrangle
<kbd> gsub </kbd>

Let's take a look at the column Street.Address. Both the Street Name and Building number are in the column. Perhaps, we'll like to separate them. 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

head(df$Street.Address)
```


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}
df2 <- data.frame(Building_Number = rep(1,435))
df2$Building_Number <- parse_number(df$Street.Address)
df2$Street_Name <- gsub('[[:digit:]]+', '', df$Street.Address)
df2

```

### References
#### citations for narrative and data sources
* Narrative and data sources: Average SAT Scores for NYC Public Schools, [GO](https://www.kaggle.com/nycopendata/high-schools){target="_blank"}
