---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/kamino.css", "../../../z-assemblers/wranglers.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/header.html"
      after_body: "../../../z-assemblers/footer.html"
    #self_contained: false
    #lib_dir: libs
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(dplyr)
library(data.tree)
library(purrr)
library(knitr)
library(kableExtra)
library(magick)

```

### Use the following methods to parse string.

#### Number as string

Recall we can use validate to check the property of each column, in our example, let's check if year is numeric. 
```{r Load raw data, echo=FALSE, message=FALSE}

df<-read.csv('../archetypes/economic-growth-does-not-guarantee-rising-happiness.csv')

```

```{r Styling Data Set, echo=FALSE}
#NOT TO BE USED AS SOLUTION

df_tmp <-df[1:10,]%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
  column_spec(7, bold = TRUE, color = "#000000", background = "#CEE3F6")
# %>%
# scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)

df_tmp 
save_kable(df_tmp,file="raw data.png")
image <- image_read("raw data.png")
svg <- image_convert(image, format="svg")

image_write(svg, "raw data.svg")

#NOT TO BE USED AS SOLUTION 

```

Recall we can use validate to check the property of each column, in our example, let's check if <span style="color: #fc7f03;font-weight:bold">year is numeric</span>. 


```{r method: find root1, echo=FALSE, message=FALSE}

is.numeric(df$year)
```

If we want to treat year rather as a string, we can parse it as string and check again.


```{r method: as string, echo=FALSE, message=FALSE}
df_1<-df
df_1$year<-as.character(df$year)
is.numeric(df_1$year)
```
#### String as number

For example, we may want to parse the logical string true or false as 1 or 0 to run some algorithms. 

```{r method: as number, echo=FALSE, message=FALSE}
df_2<-df
df_2$paradox<-as.numeric(df$paradox)


```

```{r Styling Data Set 2, echo=FALSE}
#NOT TO BE USED AS SOLUTION


df_tmp <-df_2[1:10,]%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
  column_spec(9, bold = TRUE, color = "#000000", background = "#CEE3F6")
# %>%
# scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)

df_tmp 

save_kable(df_tmp,file="as number.png")
image <- image_read("as number.png")
svg <- image_convert(image, format="svg")

image_write(svg, "as number.svg")
#NOT TO BE USED AS SOLUTION 

```



# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


