---
pagetitle: "Probly"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)
library(ggridges)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

# Probly
## Ridgeline Plot


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Ehimetalor Akhere Unuabona on Unsplash"}

masthead <- "assets/ehimetalor-akhere-unuabona-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> The most important questions of life are indeed, for the most part, really only problems of probability...\
--- Pierre-Simon Laplace\

***

What probability would you assign to the phrase “...” were asked. Answers between 0 and 100 were recorded with the distribution for each question.  The results shown in the view indicate how people perceive probability vocabulary.

### Ingest
#### text and value


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "probly/probly.csv"
url <- paste0(url_root, url_file)

probly_df <- read.csv(url, header = TRUE, stringsAsFactors = TRUE)
probly_df

```


### Wrangle
#### factor and reorder

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}


probly_df <- probly_df %>% mutate(text = fct_reorder(text, value))
probly_df

```


### Plot
#### standard

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

y_axis <- c( "Almost Certainly",
  "Highly Likely",
  "Very Good Chance",
  "Probable",
  "Likely",
  "Probably",
  "We Believe",
  "Better Than Even",
  "About Even",
  "We Doubt",
  "Improbable",
  "Unlikely",
  "Probably Not",
  "Little Chance",
  "Almost No Chance",
  "Highly Unlikely",
  "Chances Are Slight")

v1 <- ggplot(probly_df, aes(y=text, x=value,  fill=text)) +
    geom_density_ridges(scale = 2, alpha=0.6) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_discrete(labels=rev(y_axis)) +
    coord_cartesian(clip = "off") +
    theme(
      legend.position="none"
    ) +
    xlab("") +
    ylab("")

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
      options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


### Plot
#### as binlines

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

v2 <- ggplot(probly_df, aes(y=text, x=value,  fill=text)) +
    geom_density_ridges(alpha=0.6, stat="binline", bins=20) +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_discrete(labels=rev(y_axis)) +
    coord_cartesian(clip = "off") +
    theme(
      legend.position="none"
    ) +
    xlab("") +
    ylab("")

girafe(ggobj = v2, width_svg = 16, height_svg = 9,
      options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```

### References
#### citations for narrative and data sources

* Narrative and data sources: TBD
