---
pagetitle: "Arms trade database"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

# Load needed libraries
library(knitr)
library(tidyverse)
library(stringr)
library(scales)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


<div class="activity">
CHARTS  
</div>

# Arms Trade Database
## Bar radial view of weapons suppliers and recipients


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Toxic Player on Unsplash"}

masthead <- "assets/toxic-player-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> The human race has one really effective weapon, and that is laughter...\
--- Mark Twain\

***

A radial bar chart is a bar chart plotted in polar coordinates.  Because the bars are plotted on a polar axis with different radii, the lengths can not be compared as precisely as other methods.

### Ingest the data
#### series, values, and dates

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_suppliers = read.csv("archetypes/arms-trade-database/TIV-Export-Top-10-2019-suppliers.csv", header = TRUE, stringsAsFactors = FALSE)
df_suppliers

df_recipients = read.csv("archetypes/arms-trade-database/TIV-Export-Top-10-2019-recipients.csv", header = TRUE, stringsAsFactors = FALSE)
df_recipients

```


### Wrangle the data
#### Clean, arrange, tail, and factor


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_suppliers <- df_suppliers %>%
  filter(!is.na(X2019)) %>%
  arrange(X2019) %>%
  tail(6) %>%
  mutate(Supplier=factor(Supplier, Supplier))
df_suppliers

df_recipients <- df_recipients %>%
  filter(!is.na(X2019)) %>%
  arrange(X2019) %>%
  tail(6) %>%
  mutate(Recipient=factor(Recipient, Recipient))
df_recipients

```

### Plot
#### Suppliers

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 20), 
    plot.title = element_text(color = "black", size = 12, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 8),
    plot.caption = element_text(color = "#555555", size = 8),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor = element_blank(), # remove minor gridlines
    panel.grid.major.x = element_blank(), # remove x (vertical) gridlines
    legend.title = element_blank(), # remove legend title
    legend.position='none'
  )

palette <- c( "#e53935", "#FB8C00", "#039BE5", "#00ACC1", "#00897B", "#7CB342" )

v1 = ggplot(data=df_suppliers, aes(x=Supplier, y=X2019) ) +
  geom_bar(aes(fill=Supplier), stat="identity") +
  geom_text(aes( y = 0, label = paste(Supplier," ")), hjust = 1, size = 6, family = "inconsolata") +
  scale_fill_manual(values=rev(palette)) +
  xlab("") +
  ylab("") +
  coord_polar(theta = "y") +
  ylim(0,max(df_suppliers$X2019+1000)) +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 1280/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.50))
)

```

### Plot
#### Recipients

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}


v2 = ggplot(data=df_recipients, aes(x=Recipient, y=X2019) ) +
  geom_bar(aes(fill=Recipient), stat="identity") +
  geom_text(aes( y = 0, label = paste(Recipient," ")), hjust = 1, size = 6, family = "inconsolata" ) +
  scale_fill_manual(values=rev(palette)) +
  xlab("") +
  ylab("") +
  coord_polar(theta = "y") +
  ylim(0,max(df_recipients$X2019+300)) +
  theme_bw() +
  theme_opts

girafe(ggobj = v2, width_svg = 1280/72, height_svg = 1280/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.50))
)

```

### Save plot
#### as vector or raster image

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/arms-trade-database-suppliers-fs.svg", plot = v1, width=1280/72, height=1280/72)
ggsave(filename = "outputs/arms-trade-database-recipients-fs.svg", plot = v2, width=1280/72, height=1280/72)

# thumbnail version without annotations
ggsave(filename = "outputs/arms-trade-database-suppliers-sm.svg", plot = v1, width=4, height=4)
ggsave(filename = "outputs/arms-trade-database-recipients-sm.svg", plot = v2, width=4, height=4)


```


### References
#### citations for narrative and data sources

* Narrative sources: International Arms Transfers, 2019, [GO](https://reliefweb.int/sites/reliefweb.int/files/resources/fs_2003_at_2019.pdf){target="_blank"}
* Data sources: Stockholm International Peace Research Institute (SIPRI) Arms Transfers Database, [GO](https://armstrade.sipri.org/armstrade/page/toplist.php){target="_blank"}

<pre>
@misc{sipri_2005_sipri,
  author = {Sipri},
  title = {SIPRI Fact Sheet},
  url = {https://reliefweb.int/sites/reliefweb.int/files/resources/fs_2003_at_2019.pdf},
  urldate = {2021-02-19},
  year = {2005}
}
</pre>

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
