---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    #self_contained: false
    #lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggraph)
library(igraph)
library(graphlayouts)
library(tidygraph)


library(knitcitations)
library(bibtex)
```

<div class="activity">
GRAPH  
</div>

# Node-links - Association
## Case: Movies

> If you take me out of it, I find 'six degrees' to be a beautiful concept that we should try to live by.\
It's about compassion and responsibility for everyone on the planet...\
--- Kevin Bacon\


***

## Load data [Ingest]

```{r load raw data,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read.csv("./archetypes/movies/movie-edges.csv", header = TRUE, stringsAsFactors = TRUE)
df

```

```{r, echo=TRUE, class.source = 'fold-hide'}

df_f <- filter(df, SOURCE %in% c("Tom Hanks", "Kevin Bacon"))
df_f

```


# Prepare data [Wrangle]
# Format the data into a graph data frame 
## Creating two important sets: Nodes and Edges between the nodes

```{r, echo=TRUE, class.source = 'fold-hide'}

# Convert data to graph data frame
# directed FALSE means no flow. It's just an association
g <- graph.data.frame(df_f, directed = FALSE)
g

```


## Associating different attributes for your Nodes 
### Creating numercial fields for the Nodes set in order to attribute the nodes size and/or color  

```{r, echo=TRUE, class.source = 'fold-hide'}

## Creating centrality numerical field for the Nodes
# centrality_alpha()
# centrality_authority() 
# centrality_betweenness() 
# centrality_power() 
# centrality_closeness() 
# centrality_eigen() 
# centrality_hub() 
# centrality_pagerank() 
# centrality_subgraph() 
# centrality_degree() 
# centrality_edge_betweenness() 
# centrality_manual() 
# centrality_closeness_harmonic() 
# centrality_closeness_residual() 
# centrality_closeness_generalised() 
# centrality_integration() 
# centrality_communicability() 
# centrality_communicability_odd() 
# centrality_communicability_even() 
# centrality_subgraph_odd() 
# centrality_subgraph_even() 
# centrality_katz() 
# centrality_betweenness_network() 
# centrality_betweenness_current() 
# centrality_betweenness_communicability() 
# centrality_betweenness_rsp_simple() 
# centrality_betweenness_rsp_net() 
# centrality_information() 
# centrality_decay() 
# centrality_random_walk() 
# centrality_expected()

cg <- g %>% 
    as_tbl_graph() %>% 
    activate(nodes) %>% 
  # associating a numerical value to nodes to differentiate their colors and size
    mutate(centrality  = centrality_pagerank())


## Creating group numerical field for the Nodes
# group_components() 
# group_edge_betweenness() 
# group_fast_greedy() 
# group_infomap() 
# group_label_prop() 
# group_leading_eigen() 
# group_louvain() 
# group_optimal() 
# group_spinglass() 
# group_walktrap() 
# group_biconnected_component()

cg <- cg %>% 
  activate(nodes) %>%
   # use functions to compute numerical values to attribute the edge width and/or color
  mutate(group = group_louvain())

cg


```


## Associating different attributes for the Edges between Nodes 
### Creating new numerical fields (smaller values) in order to attribute the edge width and/or color  

```{r, echo=TRUE, class.source = 'fold-hide'}

cg <- cg %>% 
    activate(edges) %>% 
  # computing random number (n) which are between 0 and 1 to attribute the edge width
    mutate(edge_weights = runif(n()))

cg

```


## Layout & Aesthetic Parameters
### Choose the types of Edges you would like to display

```{r, echo=TRUE, class.source = 'fold-hide'}

# Edge Types
# geom_edge_arc
# geom_edge_arc0
# geom_edge_arc2
# geom_edge_density
# geom_edge_diagonal
# geom_edge_diagonal0
# geom_edge_diagonal2
# geom_edge_elbow
# geom_edge_elbow0
# geom_edge_elbow2
# geom_edge_fan
# geom_edge_fan0
# geom_edge_fan2
# geom_edge_hive
# geom_edge_hive0
# geom_edge_hive2
# geom_edge_link
# geom_edge_link0
# geom_edge_link2
# geom_edge_loop
# geom_edge_loop0

# Layouts can be computationally intensive
# Uncomment only for use

# igraph
# dh <- create_layout(cg, layout = 'dh')
# fr <- create_layout(cg, layout = 'fr')
# gem <- create_layout(cg, layout = 'gem')
# lgl <- create_layout(cg, layout = 'lgl')
# sugiyama <- create_layout(cg, layout = 'sugiyama')
# star <- create_layout(cg, layout = 'star')
# kk <- create_layout(cg, layout = 'kk', maxiter = 100)
# drl <- create_layout(cg, layout = 'drl')
# linear_straight <- create_layout(cg, layout = 'linear')
# linear_circular <- create_layout(cg, layout = 'linear' , circular = TRUE)

# ggraph
# arc <- create_layout(cg, layout = 'linear')
# arc_circular <- create_layout(cg, layout = 'linear', circular = TRUE)
# stress <- create_layout(cg, layout = 'stress')
# sparse_stress <- create_layout(cg, layout = 'sparse_stress')
# backbone <- create_layout(cg, layout = 'backbone')
# pmds <- create_layout(cg, layout = 'pmds')
# eigen <- create_layout(cg, layout = 'eigen')
# centrality <- create_layout(cg, layout = 'centrality')
# focus <- create_layout(cg, layout = 'focus')
# dendrogram <- create_layout(cg, layout = 'dendrogram')
# unrooted <- create_layout(cg, layout = 'unrooted')
# matrix <- create_layout(cg, layout = 'matrix')
# hive <- create_layout(cg, layout = 'hive')
# fabric <- create_layout(cg, layout = 'fabric')

# graphlayouts
# nicely <- create_layout(cg, layout = "nicely")
# stress <- create_layout(cg, layout = "stress")
radial <- create_layout(cg, layout = "focus", focus = 1)
# centrality_bc <- create_layout(cg, layout = "centrality", centrality = bc, tseq = seq(0,1,0.15))
# centrality_cc <- create_layout(cg, layout = "centrality", centrality = cc, tseq = seq(0,1,0.2))

```


## Plot with Layout


```{r, echo=TRUE, class.source = 'fold-hide'}


theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.background = element_blank(),
)

v1 <- ggraph(radial) + 
  geom_edge_link(aes(colour = factor(TYPE))) + 
  geom_node_point(aes(color = group, size = centrality)) +
  geom_node_text(aes(label = name)) +
  scale_color_gradient(low = "green", high = "blue", na.value = NA) +
  scale_size(range = c(2,6)) +
  theme_graph()+
  theme(legend.position = "none")

v1


```


# Saving the graph as .svg file

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

ggsave(filename = "./assets/movie-network.svg", plot = v1, width=12, height=6)
# ggsave(filename="template.png", plot=v1, device="png", width=12, height=6, units="in", dpi=500)

```

# References
## The citations and data sources used for this case



```{r generateBibliography, echo=FALSE, message=FALSE, warning=FALSE}

#cleanbib()
#options("citation_format" = "pandoc")
#read.bibtex(file = "./citations/.bib")

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```



