---
pagetitle: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)


```

WRANGLERS  


# Date Math
## I want to fix irregularities in my dataset

> Don't call the world dirty because you forgot to clean your glasses...\
--- Aaron Hill\

Date Math is a collection of patterns to perform mathematical operations like data/time difference, date/time shifts, date/time filtering or the creation of categorical or logical columns based on date values.

***

# Section
## Subsection

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Fold hide as this is not relevant to the task


```


# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```


# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```



# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```



# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```


# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case
