---
pagetitle: "Animal Rescues Bivariate"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(sf)
library(biscale)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Animal Rescues Bivariate
## Choropleth Facet Map

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Sara Scarpa on Unsplash"}

masthead <- "assets/sara-scarpa-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Help! I'm stuck!</div>

> Well, it may be humorous to you, but it’s a very serious matter to the squirrels...\
--- Lisa Kleypas\

***

### Ingest
#### animal group and ward_code (to match with map geometry)


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df <- read.csv("archetypes/animal-rescues/animal-rescues.csv", header = TRUE, encoding = "UTF-8")
df

```


### Wrangle & Analyze
#### summarize by spatial unit (ward) and animal group


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

animal_by_boroughs <- df %>% 
  mutate(animal_group_parent = str_to_title(animal_group_parent)) %>% 
  count(borough_code, animal_group_parent, sort = TRUE) %>% 
  filter(animal_group_parent %in% c("Horse", "Cow", "Hamster", "Squirrel", "Lamb", "Sheep", "Snake", "Lizard", "Hedgehog", "Rabbit", "Ferret", "Fish", "Goat", "Pigeon", "Bull", "Tortoise")) %>% 
  ungroup() 

as.data.frame(unique(animal_by_boroughs$animal_group_parent))

animal_by_boroughs

```



### Load maps
#### wards and regions


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

ltla_map <- st_read("archetypes/animal-rescues/local-authorities-lowertier-4-ltla-2019.geojson")
ltla_map

```


### Wrangle
#### enrich and filter map geometry, calculate centroid

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# to focus on london boroughs
# london_bk <- filter(background_map, RegionNation == "London")
london <- filter(ltla_map, RegionNation == "London")

# enrich spatial data with quantitative data for choropleth
london_animals <- london %>%
  left_join(animal_by_boroughs, by = c("Lacode" = "borough_code")) %>% 
  # by filtering out, background will show
  filter(!is.na(animal_group_parent))
head(london_animals, n = 10)

# this is used to plot an aesthetic background
center <- st_coordinates(st_centroid(london$geometry))

```


### Plot
#### color by bins, facet by animal group


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', out.width="100%"}

theme_opts <- theme(
  text = element_text(family = "inconsolata", size = 16), 
  plot.title = element_text(color = "black", size = 16, face = "bold"),
  plot.subtitle = element_text(color = "black", size = 12),
  plot.caption = element_text(color = "#555555", size = 11),
  plot.background = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  legend.position = "bottom",
  legend.title = element_blank(),
)

fill_pallete <- c("#3B454A", "#31739C", "#21B3CD", "#FFD349", "#E85E26")

v1 <- ggplot(london_animals) + 
  # bottom layer as a cirle background
  # geom_point(aes(x = center[1], y = center[2]), size = 150, shape = 21, fill = "#007EA7", stroke = 2) +
  # border outline
  geom_sf(data = london, aes(geometry = geometry), fill = "grey50", color = "white", size = 0.1) + 
  # the choropleth
  geom_sf(data = london_animals, aes(geometry = geometry, fill = n), color = "white", size = 0.1) +
  # color by bins from rescue count
  scale_fill_stepsn(colors = fill_pallete, n.breaks = 5) +
  # facet by animal group
  facet_wrap(~animal_group_parent, ncol = 4) + 
  labs(
    title = "Frequency of Rescues of Birds, Cats and Dogs in London from 2009-2021",
    subtitle = NULL,
    caption = NULL,
    x = NULL,
    y = NULL
  ) + 
  theme_minimal() + 
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 13,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk
ggsave(filename = "assets/animal-rescues-bivariate-fs.svg", plot = v1, width=1152/72, height=1152/72)

```


### References
#### citations for narrative and data sources

* Narrative sources: This is a reproduction of an original idea from @jakekaupp, [GO](https://github.com/jkaupp/tidytuesdays/tree/master/2021/week27){target="_blank"}
* Data sources: london.gov.uk, [GO](https://london.gov.uk){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

