---
pagetitle: "Tourism Density Index"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Tourism Density Index
## a range plot showing over-and-undertourism by country

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Tommaso Cantelli on Unsplash"}

masthead <- "assets/tommaso-cantelli-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> To travel is to live...\
--- Hans Christian Andersen\


***

### Ingest
#### category, country, tourists, and locals

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df = read.csv("archetypes/tourism-density-index/over-and-undertourism.csv", header = TRUE, stringsAsFactors = TRUE)
df

```


### Wrangle
#### filter for over and under


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_over <- filter(df, category == "Overtourism")
df_under <- filter(df, category == "Undertourism")

```


### Plot
#### tourism density, over / under


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="85%"}

theme_opts <- theme(
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.ticks = element_line(),
    legend.position = "none"
)

category_palette <- c(
  "Overtourism" = "#9C27B0",
  "Undertourism" = "#3F51B5"
)

v1 = ggplot(df) + 
  geom_segment(aes(x=number_of_tourists, y=country, xend=number_of_locals, yend=country, color=category), 
               lineend = "round", linejoin = "round", size=1) + 
  geom_point(aes(x=number_of_tourists, y=country), shape=21, alpha=1.0, size=2, color="#FFFFFF", fill="#9C27B0") +
  geom_point(aes(x=number_of_locals, y=country), shape=21, alpha=1.0, size=2, color="#FFFFFF", fill="#3F51B5") +
  scale_x_continuous() +
  scale_y_discrete() +
  scale_color_manual(values = category_palette) +
  labs(title = "Tourism density, over / under") +
  theme_minimal() +
  theme_opts +
  xlab(NULL) +
  ylab(NULL)

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/tourism-density-index-fs.svg", plot = v1, width=720/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/tourism-density-index-sm.svg", plot = v1, width=2.25, height=2.25)

```


### References
#### citations for narrative and data sources

Narrative: Intrepid Travel, Intrepid Adventure Index 2018
Data Source: MakeOverMonday, [GO](https://data.world/makeovermonday/2018w24-tourism-density-index){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

