---
pagetitle: "Global Energy Monitor"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(janitor)
library(geojsonio)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS
</div>

# Global Energy Monitor
## Route Map

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Alireza Khatami on Unsplash"}

masthead <- "assets/alireza-khatami-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> The grid is awesomely complex. It is the largest machine in the world...\
--- Gretchen Bakke\

***

### Ingest
#### the routes

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_pipelines <- read.csv("archetypes/global-energy-monitor/GFIT-Pipelines-December-2020.csv", header = TRUE, stringsAsFactors = FALSE, as.is=T)
head(df_pipelines, n=10)

```


### Ingest
#### the terminals

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_terminals <- read.csv("archetypes/global-energy-monitor/GFIT-LNG-Terminals-June-2021.csv", header = TRUE, stringsAsFactors = FALSE)
df_terminals <- df_terminals %>% janitor::clean_names() %>% mutate(latitude = as.numeric(latitude), longitude = as.numeric(longitude))
head(df_terminals, n=10)

```


### Wrangle
#### create routes from path data

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_pipelines_routes <- df_pipelines %>%
  janitor::clean_names() %>%
  mutate(route_id = rownames(df_pipelines)) %>%
  separate_rows(route, sep = ":", convert = TRUE) %>%
  separate(route, c("rlat", "rlon"), sep = ",", convert = TRUE) %>%
  mutate(rlat = as.numeric(rlat), rlon = as.numeric(rlon)) %>%
  select(route_id, status, fuel, rlat, rlon) %>%
  filter(nchar(rlat) > 0)

head(df_pipelines_routes, n=10)


```


### Base map
#### natural earth

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

# natural earth base map
ne_world <- ne_countries(scale = "small", returnclass = "sf")
# removes Antarctica
ne_world <- filter(ne_world, iso_a3 != "ATA") 

```


### Route map
#### with geom_path

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

theme_opts <- theme(
      legend.position="none",
      plot.background = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background=element_rect(fill="#cacdcf", colour="#cacdcf"),
      panel.border = element_blank()
)

# unique(df_ingest$status)
status_palette <- c(
  "Proposed" = "#e9b529",
  "Cancelled" = "#acd994",
  "Operating" = "#8b6f5d",
  "Construction" = "#b3351f",
  "Mothballed" = "#d4d4d4",
  "Shelved" = "#9cb9d8",
  "Retired" = "#718abe",
  "Idle" = "black"
)

v1 <- ggplot(data = ne_world) +
  geom_sf(fill="#e7e7e5", color="#e2dedd", stroke=0.5) +
  geom_path( data = df_pipelines_routes, aes(x=rlon, y=rlat, group=factor(route_id), color=status), size=0.5) +
  geom_point( data = df_terminals, aes(x=longitude, y=latitude, color=status ), size=2 ) +
  scale_color_manual(values = status_palette) +
  theme_bw() +
  labs(x="",
       y="",
       title = "Global Energy Monitor", 
       subtitle="Fossil Infrastructure Tracker") +
  theme_opts
  
girafe(ggobj = v1, width_svg = 16, height_svg = 7.5,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### References
#### citations for narrative and data sources

* Narrative and Data source: Global Fossil Infrastructure Tracker, Global Energy Monitor, December 2021


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
