---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(geojsonio)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggsci)
library(ggiraph)

library(knitcitations)
library(bibtex)

```

<div class="activity">
MAPS
</div>

# Route Map
## Submarine Cable Map

Route map of the world's major operating and planned submarine cable systems and landing stations.

***

# Load data
## The routes

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

cables = read.csv("archetypes/fusion-cables.csv", header = TRUE, stringsAsFactors = FALSE, as.is=T)
cables

```


## The landing points


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

landing_points = read.csv("archetypes/fusion-landing-points.csv", header = TRUE, stringsAsFactors = FALSE, as.is=T)
landing_points

```


## Natural Earth base map


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# PLOT NATURAL EARTH BORDERS
ne_world <- ne_countries(scale = "medium", returnclass = "sf")
# class(ne_world)

```


## Theme


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

theme_opts <- theme(
      legend.position="none",
      plot.background = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background=element_rect(fill="white", colour="white"),
      panel.border = element_blank()
)

```


## Route map


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width=12, fig.height=6, out.width = "100%"}

v1 <- ggplot(data = ne_world) +
  geom_path( data = cables, aes(x=longitude, y=latitude, group=factor(id)), color=cables$color, size=0.5) +
  geom_sf(fill="#f0f0f0", color="#888888", stroke=0.5) +
  geom_point( data = landing_points, aes(x=lon, y=lat ), shape=21, size=1, fill="#ffffff", color="#111111", stroke=0.5 ) +
  scale_color_tron() +
  scale_fill_tron() +
  ylim(-53,80) + # removes Antarctica
  theme_bw() +
  labs(x="",
       y="",
       title = "Routes Map", 
       subtitle="Submarine Cable Map") +
  theme_opts
  
girafe(ggobj = v1, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


## Save output to file


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# ggsave(filename = "assets/submarine-cable-map.svg", plot = v1, width=12, height=6)

```


# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case

Inspired by <a href="https://github.com/telegeography/www.submarinecablemap.com">Source</a>

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

# cleanbib()
# read.bibtex(file = "./citations.bib")

```




```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


