---
pagetitle: "Pangolin Trafficking Routes"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(janitor)
library(countrycode)
library(CoordinateCleaner)
library(geojsonio)
library(sf)
library(geosphere)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
#font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS
</div>

# Pangolin Trafficking Routes
## Route Map

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Peter Schad on Unsplash"}

masthead <- "assets/peter-schad-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> There would be no population explosion if people who are trying to keep the wolf from the door\
  wouldn't let the stork fly in through the window...\
--- Evan Esar\

***



### Ingest
#### tracking data from a directory of files

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read.csv("archetypes/pangolin-trafficking-routes/pangolin-trafficking-routes.csv", header = TRUE)
df
# head(df, n=10)

centroids <- read.csv("https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/lookups/country-centroids.csv", header = TRUE)
centroids <- centroids %>% select(iso3c, latitude, longitude)

```


### Wrangle
#### create coordinates for path


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_wrangled <- df %>% janitor::clean_names() %>%
             mutate(route_id = row_number(),
                    date = as.POSIXlt(date), 
                    latitude = as.numeric(latitude), 
                    longitude = as.numeric(longitude),
                    scale = as.integer(scale),
                    carcass = as.integer(carcass),
                    live = as.integer(live))

via_only <- filter(df_wrangled, nchar(via) > 0 & nchar(outbound) == 0)
via_only$via_iso3c <- countrycode(via_only$via, origin = 'country.name', destination = 'iso3c')
via_only <- merge(via_only, centroids, by.x = "via_iso3c", by.y = "iso3c")
via_only <- via_only %>% rename(from_latitude = latitude.x, from_longitude = longitude.x, via_latitude = latitude.y, via_longitude = longitude.y)
via_only <- via_only %>% select(-via_latitude, -via_longitude)
via_only

via_to <- filter(df_wrangled, nchar(via) > 0 & nchar(outbound) > 0)
via_to$via_iso3c <- countrycode(via_to$via, origin = 'country.name', destination = 'iso3c')
via_to$outbound_iso3c <- countrycode(via_to$outbound, origin = 'country.name', destination = 'iso3c')
via_to <- merge(via_to, centroids, by.x = "via_iso3c", by.y = "iso3c")
via_to <- merge(via_to, centroids, by.x = "outbound_iso3c", by.y = "iso3c")
via_to <- via_to %>% rename(from_latitude = latitude.x, from_longitude = longitude.x, via_latitude = latitude.y, via_longitude = longitude.y, to_latitude = latitude, to_longitude = longitude)
via_to

to_only <- filter(df_wrangled, nchar(via) == 0 & nchar(outbound) > 0)
to_only$via_iso3c <- countrycode(to_only$via, origin = 'country.name', destination = 'iso3c')
to_only$outbound_iso3c <- countrycode(to_only$outbound, origin = 'country.name', destination = 'iso3c')
to_only <- merge(to_only, centroids, by.x = "outbound_iso3c", by.y = "iso3c")
to_only <- to_only %>% rename(from_latitude = latitude.x, from_longitude = longitude.x, to_latitude = latitude.y, to_longitude = longitude.y)
to_only

no_dest <- filter(df_wrangled, nchar(via) == 0 & nchar(outbound) == 0)
no_dest

```


### Wrangle
#### highlight Gili


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

gili <- filter(stork_gps_year, individual_local_identifier == '2421/HH847/Gili')
head(gili, n=10)

gili_labels <- gili %>% filter(row_number() == 1 | row_number() == n())
gili_labels

stork_gps_rest <- filter(stork_gps_year, individual_local_identifier != '2421/HH847/Gili')

```


### Analyze
#### compute geospatial distance along route


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# calculate the distance from previous point
gili_dist <- gili %>%
  mutate(plocation_long = lag(location_long), plocation_lat = lag(location_lat)) %>%
  rowwise() %>%
  mutate(distance = distm( c(plocation_long, plocation_lat), c(location_long, location_lat), fun=distHaversine )) %>%
  mutate(km = distance/1000)

gili_dist <- as.data.frame(gili_dist)

# calculate cumulative sum and select samples
gili_dist <- gili_dist %>% 
  filter(distance > 0) %>% 
  mutate(cumulative_km = round(cumsum(km), digits=0)) %>%
  filter(row_number() %% 750 == 1)

gili_dist

```

### Base map, natural earth, option 1
#### continent and country select


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

africa <- ne_countries(scale = "small", continent = 'africa', returnclass = "sf")

europe <- ne_countries(scale = "small", continent = 'europe', returnclass = "sf")
europe <- filter(europe, iso_a3 != "RUS") 
europe <- filter(europe, iso_a3 != "GUF") 

middle_east <- ne_countries(scale = "small", country = c('turkey', 'syria', 'lebanon', 'jordan', 'iraq', 'israel', 'saudi arabia', 'yemen'), returnclass = "sf")

ne_region <- rbind(africa, europe, middle_east)

```


### Base map, natural earth, option 2
#### world


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

# natural earth base map
ne_world <- ne_countries(scale = "small", returnclass = "sf")
# removes Antarctica
ne_world <- filter(ne_world, iso_a3 != "ATA") 

```


### Route map
#### paths, points, and labels with coordinate limits


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

theme_opts <- theme(
  text = element_text(family = "inconsolata"), 
  plot.title = element_text(color = "black", size = 18, face = "bold", family = "inconsolata"),
  plot.subtitle = element_text(color = "black", size = 16, family = "inconsolata"),
  plot.caption = element_text(color = "#555555", size = 8, family = "inconsolata"),    
  plot.background = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="#cacdcf", colour="#cacdcf"),
  panel.border = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  legend.position="none"
)

stork_palette <- c(
  "#F44336",
  "#E91E63",
  "#9C27B0",
  "#673AB7",
  "#3F51B5",
  "#2196F3",
  "#03A9F4",
  "#00BCD4",
  "#009688",
  "#4CAF50",
  "#8BC34A",
  "#FFEB3B"
)

v1 <- ggplot(data = ne_world) +
  geom_sf_interactive(aes(tooltip = iso_a3, data_id = iso_a3), fill="#e7e7e5", color="#717c8a", stroke=0.5) +
  geom_path( data = stork_gps_rest, aes(x=location_long, y=location_lat, group=factor(tag_local_identifier)), color = "transparent", fill = 'white', size=3, alpha = 0.6) +
  geom_path( data = stork_gps_rest, aes(x=location_long, y=location_lat, group=factor(tag_local_identifier), color = individual_local_identifier), size=0.5, alpha = 0.8) +
  geom_path( data = gili, aes(x=location_long, y=location_lat, group=factor(tag_local_identifier)), size=4, color = "transparent", fill = 'white', alpha = 0.6) +
  geom_path( data = gili, aes(x=location_long, y=location_lat, group=factor(tag_local_identifier)), size=1.5, color = 'orange') +
  geom_point( data = gili_dist, aes(x=location_long, y=location_lat), shape = 21, size = 3, color = "white", fill = "black") +
  geom_label_repel( data = gili_dist, aes(x=location_long, y=location_lat, label = paste0(cumulative_km, " kilometers\n", timestamp)), 
                    xlim  = c(max(gili_dist$location_long)+10, NA),
                    force_pull = 0, segment.size = 0.5, direction = "both", min.segment.length = 0,
                    segment.curvature = -0.1, segment.ncp = 3, segment.angle = 20,
                    size = 4, label.padding = unit(0.5, "lines"), fill = "orange", color = "black", alpha = 0.8, hjust = 0.0) +
  geom_point( data = gili_labels, aes(x=location_long, y=location_lat), shape = 21, size = 4, color = "white", fill = "orange") +
  geom_label( data = gili_labels, aes(x=location_long, y=location_lat, label = paste0("Gili\n", timestamp)), 
                    nudge_x = -6, size = 4, label.padding = unit(0.5, "lines"), fill = "black", color = "white", hjust = 0.5) +
  scale_color_manual(values = stork_palette) +
  xlim(-20,60) +
  ylim(-35,60) +
  theme_bw() +
  labs(x="",
       y="",
       title = "Stork Migration Tracks", 
       subtitle="Routes Map, 2016") +
  theme_opts
  
girafe(ggobj = v1, width_svg = 12, height_svg = 16,
       options = list(opts_sizing(rescale = TRUE, width = 0.5))
)

```


### References
#### citations for narrative and data sources

* Narrative: inspired by the work of Cédric Scherer
* Original Research and Data source:

<pre>
Rotics S, Kaatz M, Turjeman S, Zurell D, Wikelski M, Sapir N, Eggers U, Fiedler W, Jeltsch F,Nathan R (2018) Early arrival at breeding grounds: causes, costs and a trade-off with over wintering latitude. Journal of Animal Ecology.
doi:10.1111/1365-2656.12898

Rotics S, Kaatz M, Turjeman S, Zurell D, Wikelski M, Sapir N, Eggers U, Fiedler W, Jeltsch F,Nathan R (2018) Data from: Early arrival at breeding grounds: causes, costs and a trade-off with over wintering latitude.
Movebank Data Repository. doi:10.5441/001/1.v8d24552
</pre>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
