---
pagetitle: "Red-backed shrike geolocator data"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE, echo=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

# Libraries
library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(wesanderson)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS
</div>

# Red-backed shrike geolocator data
## Route map

```{r, out.width="60%", fig.align="center", fig.cap="Photo from Wikipedia Commons"}

masthead <- "assets/Red-backed_shrike.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Shrikes were songbirds; he ought to know...\
--- Jodi Meadows\

***

The red-backed shrike (Lanius collurio) is a carnivorous passerine bird and member of the shrike family Laniidae. Its breeding range stretches from Western Europe east to central Russia. It is migratory and winters in the eastern areas of tropical Africa and southern Africa.

### Ingest
#### The routes

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

routes <- read.csv("archetypes/red-backed-shrike/red-backed-shrike-coords.csv", header = TRUE)
routes

```

### Ingest
#### The stopovers


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

stopovers <- read.csv("archetypes/red-backed-shrike/red-backed-shrike-main-stopovers.csv", header = TRUE)
stopovers

```


### Base map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

ne_world <- ne_countries(scale = "small", returnclass = "sf")

```


### Map labels
#### from centroids within range of limits


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

centroids = read.csv("archetypes/red-backed-shrike//country-centroids.csv", header = TRUE, stringsAsFactors = FALSE, as.is=T)
countryref <- centroids %>% select(iso3c, latitude, longitude)
countryref <- filter(countryref, latitude > -35 & latitude < 60)
countryref <- filter(countryref, longitude > -20 & longitude < 55)

countryref

```


### Route map
#### follow the shrike


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

theme_opts <- theme(
      axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      legend.title = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background=element_rect(fill="#ffffff", colour="#ffffff"),
      panel.border = element_blank()
)

# color palette for number of months
pal <- wes_palette("Zissou1", 12, type = "continuous")

v1 <- ggplot(data = ne_world) +
  geom_sf(data = ne_world, fill="#f5f5f5", color="#d5d5d5", size=1.0) +
  geom_text(data= countryref, aes(x=longitude, y=latitude, label=iso3c),
            color = "gray20", fontface = "italic", check_overlap = T, size = 2) +
  # routes
  geom_path(data = routes, aes(y, x), alpha = 0.8, size = 1.5, color = "#666666" ) + 
  geom_point(data = routes, aes(y, x), shape=21, alpha = 1.0, size = 2.0, fill = "#ffffff", color = "#666666") +
  # stopovers
  geom_point(data = stopovers, aes(Medianlon, Medianlat, size = stopover_duration, color = Main_month), alpha = 0.9) +
  # Now, for each of these points we plot the uncertainties
  # Horizontal
  geom_segment(data = stopovers, aes(y=Medianlat, x=FstQu.lon, xend=TrdQu.lon, yend=Medianlat), size = 0.5) +
  # Vertical
  geom_segment(data = stopovers, aes(y=FstQu.lat, x=Medianlon, xend=Medianlon, yend=TrdQu.lat), size = 0.5) +
  # color and size scales
  scale_color_gradientn(colours = pal) + 
  scale_size_continuous(range=c(3,12)) +
  # limit view to relevant area
  coord_sf(xlim = c(-20, 55), ylim = c(-35, 60), expand = TRUE) +
  theme_bw() +
  labs(x=NULL,
       y=NULL,
       title = "Red-Backed Shrike", 
       subtitle="Geolocation Routes") +
  theme_opts

girafe(ggobj = v1, width_svg = 9, height_svg = 12,
       options = list(opts_sizing(rescale = TRUE, width = 0.65))
)

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
ggsave(filename = "outputs/red-backed-shrike-fs.svg", plot = v1, width=9, height=12)

```


### References
#### citations for narrative and data sources

* Narrative and Data source: 
  + Pedersen, Lykke & Thorup, Kasper & Tøttrup, Anders. (2018), [GO](https://core.ac.uk/download/pdf/269314309.pdf){target="_blank"} 
  + Annual GPS tracking reveals unexpected wintering area in a long-distance migratory songbird.[GO](https://link.springer.com/article/10.1007/s10336-018-1610-8){target="_blank"} 
  + Journal of Ornithology, [GO](https://www.springer.com/journal/10336){target="_blank"} 

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
