---
pagetitle: "Submarine Cable Map"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggsci)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS
</div>

# Submarine Cable Map
## Route Map

```{r, out.width="60%", fig.align="center", fig.cap="Photo from Wikipedia Commons"}

masthead <- "assets/seekabelverlegung-wikipedia.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> No cord or cable can draw so forcibly, or bind so fast, as love can do with a single thread...\
--- Robert Burton\

***

Route map of the world's major operating and planned submarine cable systems and landing stations.

### Ingest
#### the routes

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

cables <- read.csv("archetypes/fusion-cables/fusion-cables.csv", header = TRUE, stringsAsFactors = FALSE, as.is=T)
cables

```


### Ingest
#### The landing points


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

landing_points = read.csv("archetypes/fusion-cables/fusion-landing-points.csv", header = TRUE, stringsAsFactors = FALSE, as.is=T)
landing_points

```


### Base map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

# PLOT NATURAL EARTH BORDERS
ne_world <- ne_countries(scale = "small", returnclass = "sf")
# class(ne_world)

```


### Route map
#### with path and points


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

theme_opts <- theme(
      legend.position="none",
      plot.background = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background=element_rect(fill="white", colour="white"),
      panel.border = element_blank()
)

v1 <- ggplot(data = ne_world) +
  geom_path( data = cables, aes(x=longitude, y=latitude, group=factor(id)), color=cables$color, size=0.5) +
  geom_sf(fill="#f0f0f0", color="#888888", stroke=0.5) +
  geom_point( data = landing_points, aes(x=lon, y=lat ), shape=21, size=1, fill="#ffffff", color="#111111", stroke=0.5 ) +
  scale_color_tron() +
  scale_fill_tron() +
  ylim(-53,80) + # removes Antarctica
  theme_bw() +
  labs(x="",
       y="",
       title = "Routes Map", 
       subtitle="Submarine Cable Map") +
  theme_opts
  
girafe(ggobj = v1, width_svg = 16, height_svg = 8,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk
ggsave(filename = "outputs/submarine-cable-map-fs.svg", plot = v1, width=16, height=8)

```


### References
#### citations for narrative and data sources

* Narrative and Data source: Telegeography, [GO](https://github.com/telegeography/www.submarinecablemap.com){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
