---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggiraph)
library(ggmosaic)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Mosaic
## Titanic Survivors


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Annie Spratt  on Unsplash"}

masthead <- "assets/annie-spratt-nsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Boat Beside IceBerg</div>

> I was thoroughly familiar with pretty well every type of ship afloat but it took me 14 days before I could, with confidence, find my way from one part of that ship to another...\
--- Charles Lightoller, Titanic Second Officer\

***

# Load the data
## Titanic survivors

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load csv data file
df <- read.csv("archetypes/titanic.csv", header = TRUE, stringsAsFactors = FALSE)
df


```


### Wrangle the data


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

survived <- df %>% 
  rename("Age_Sex"=Sex)%>%
  filter(Survived=="Yes") %>%
  select(-c(X, Age, Survived))

x <- survived[1:8,] %>%
  group_by(Class) %>%
  summarize(Freq = sum(Freq)) %>%
  mutate(Age_Sex = rep("Child"))%>%
  relocate(Class, Age_Sex, Freq)

survived <- rbind(survived[9:16,], x)


n_survived <- df %>% 
  rename("Age_Sex"=Sex)%>%
  filter(Survived=="No") %>%
  select(-c(X, Age, Survived))

x <- n_survived[1:8,] %>%
  group_by(Class) %>%
  summarize(Freq = sum(Freq)) %>%
  mutate(Age_Sex = rep("Child"))%>%
  relocate(Class, Age_Sex, Freq)

n_survived <- rbind(n_survived[9:16,], x)

```


### Plot
### Survivors of Titanic Wreck


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 20), 
    plot.title = element_text(color = "black",  size = 36, face = 'bold', hjust = 0.5 ),
    plot.subtitle = element_text(color = "black", size = 20, hjust = 0.5, margin=margin(0,0,40,0)),
    plot.caption = element_text(color = "#555555", size = 20),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    
    # panel.grid.minor = element_blank(),
    # panel.grid.major = element_blank(),
    legend.position='right'
  )

# Plot


v1 <-  ggplot(survived) + 
    geom_mosaic(aes(x = product(Class), fill = Age_Sex, weight = Freq),
                divider = mosaic("v")) +
    scale_fill_brewer(palette = "Set2") +
  labs(title="Survivors of Titanic Disaster") +
    theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```

### Victims of Titanic Wreck

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

v1 <-  ggplot(n_survived) + 
    geom_mosaic(aes(x = product(Class), fill = Age_Sex, weight = Freq),
                divider = mosaic("v")) +
    scale_fill_brewer(palette = "Set2") +
  labs(title="Victims of Titanic Disaster") +
    theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```


### Save plot
#### as vector or raster image


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "assets/survivors-titanic.svg", plot = v1, width=1280/72, height=720/72)

ggsave(filename = "assets/victimes-titanic.svg", plot = v1, width=1280/72, height=720/72)

```


### References
#### citations for narrative and data sources

* Narrative Inspiration: The Economist, Ideas Factories, Global innovation and GDP
* Data Source: Global Innovation Index (GII) 2021, https://www.globalinnovationindex.org/analysis-indicator


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "donut" # mostly used in wranglers and analytics
keywords <- 'country-size'
commands <- 'coor_polar'
sources <- 'UN'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

