---
pagetitle: "Aljazeera Lebanon News"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.


library(rvest)
library(tidyverse)
library(RSelenium)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()


```


<div class="activity">
INGEST  
</div>

# Aljazeera, Lebanon headlines
## ingest a news feed

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Piotr Chrobot on Unsplash"}

masthead <- "assets/piotr-chrobot-KqEYj1VHA_o-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


# Text Analytics
## Aljazeera Lebanon

First thing to check is if scraping is permitted.
* __Robots.txt__ : a way to kindly ask webbots, spiders, crawlers, wanderers and the like to access or not access certain parts of a webpage.If the output is true, it means that the bots are allowed to access this path.

```{r,message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}
library(robotstxt)
paths_allowed(
  path="/where/lebanon/",
  domain = "https://www.aljazeera.com/")
get_robotstxt(domain = "https://www.aljazeera.com/")
```
### Ingestion - Webscraping
Now we can scrape the headlines and links.

```{r,message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

rd <- rsDriver(browser = "firefox", port = 8033L)
ffd <- rd$client


ffd$navigate("https://www.aljazeera.com/where/lebanon/")
for (i in 1:6){
load_btn <- ffd$findElement(using = "css selector", "button.show-more-button.big-margin") 
load_btn$clickElement() 
Sys.sleep(2)
}
  
#button.show-more-button.big-margin
url = ffd$getPageSource()[[1]]
page = read_html(url)
headlines <- page %>%
  html_nodes("h3.gc__title") %>%
  html_text()
links <- page %>%
  html_nodes("h3.gc__title a") %>%
  html_attr("href") %>%
  paste("https://www.aljazeera.com", .,sep="")
```



### References
#### citations for narrative and data sources

* Narrative and Data Source: Aljazeera,[GO](https://www.aljazeera.com/){target="_blank"} 


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


