---
pagetitle: "CO2 emission and GDP growth"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(ggrepel)
library(ggforce) # used to add geom_link into the chart
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


# Several rich countries have decoupled GDP growth from emissions
## The dumbell chart

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Etienne Girardet on Unsplash"}

masthead <- "assets/etienne-girardet-fti002hQCCA-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> It's a collective endeavour, it's collective accountability and it may not be too late...\
--- Christine Lagarde, ex-Managing director, IMF\

***

Increasing emissions have historically gone hand-in-hand with economic growth, several rich countries are now bucking this trend. In two dozen countries, including America, Britain and France, GDP per person has increased since 2010 while carbon emissions have fallen. A dumbbell chart is helpful to highlight this relation. 

### Ingest

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "co2-emission-and-gdp-growth/co2-emissions-vs-gdp.csv"
url <- paste0(url_root, url_file)

df <- read_csv(url)
df

```

### Wrangle

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

select_country_list <- c("Australia", "United States", "Estonia", "Djibouti", "Cuba", "Barbados", "Malta", 
                         "Japan", "Germany", "United Kingdom", "Austria", "Netherlands", "Singapore", "Denmark", 
                         "France", "Sweden", "Switzerland", "Israel", "Iceland")

df_wrangle <- df %>%
  filter(Year == 2010 | Year == 2018) %>%
  filter(Entity %in% select_country_list) %>%
  mutate(total_annual_co2_megatonne = round(`Annual CO2 emissions (per capita)` * 
           `Total population (Gapminder, HYDE & UN)` / 1000000), digits = 0) %>%
  select(country = Entity, year = Year, co2_per_capita = `Annual CO2 emissions (per capita)`,
         gdp_per_capita = `GDP per capita`, total_annual_co2_megatonne)

df_wrangle

```

### Analyze
#### summarize for min and max (this data frame will be used as segment points)

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_segment <- df_wrangle %>%
  select(country, year, co2_per_capita, gdp_per_capita) %>%
  pivot_wider(names_from = year, values_from = c(co2_per_capita, gdp_per_capita))

df_segment


```

### Plot

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide'}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 30, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 25),
    plot.tag.position = c(0.8, 0.92),
    plot.tag = element_text(color = "black", size = 20),
    # axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text.x = element_text(color = "black", size = 20, vjust = 6),
    axis.text.y = element_text(color = "black", size = 20, vjust = -1),
    panel.border = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    legend.position=""
  )

v1 <- ggplot() +
  # Manually create the grid
  geom_segment(aes(x=0, y=0, xend = 0, yend = 20), color = "#cbd2d6", size = 1) +
  geom_segment(aes(x=30000, y=0, xend = 30000, yend = 20), color = "#cbd2d6", size = 1) +
  geom_segment(aes(x=60000, y=0, xend = 60000, yend = 20), color = "#cbd2d6", size = 1) +
  geom_segment(aes(x=90000, y=0, xend = 90000, yend = 20), color = "#cbd2d6", size = 1) +
  geom_hline(yintercept = 0, color = "black", size = 1) +
  geom_hline(yintercept = 5, color = "#cbd2d6", size = 1) +
  geom_hline(yintercept = 10, color = "#cbd2d6", size = 1) +
  geom_hline(yintercept = 15, color = "#cbd2d6", size = 1) +
  geom_hline(yintercept = 20, color = "#cbd2d6", size = 1) +
  # draw 2010 bubbles
  geom_point(data = df_wrangle %>% filter(year == 2010), 
             aes(x = gdp_per_capita, y = co2_per_capita, size = total_annual_co2_megatonne), 
             color = "#bed2e3") +
  # draw 2018 bubbles
  geom_point(data = df_wrangle %>% filter(year == 2018), 
             aes(x = gdp_per_capita, y = co2_per_capita, size = total_annual_co2_megatonne), 
             color = "#406ba2") +
  scale_size(range = c(2,30)) +
  # use geom_link instead of geom_segment so 
  geom_link(data = df_segment, 
               aes(x = gdp_per_capita_2010, xend = gdp_per_capita_2018, 
                   y = co2_per_capita_2010, yend = co2_per_capita_2018, 
                   color = stat(index)), 
                   size=1.0) +
  scale_colour_gradient(low = "#bed2e3", high = "#406ba2") +
  geom_text_repel(data = df_segment, 
            aes(x = gdp_per_capita_2018, y = co2_per_capita_2018, label = country),
            family = "inconsolata", size = 7, color = "#26231d") +
  scale_x_continuous(limits = c(0,100000), breaks = c(0, 30000, 60000, 90000), labels = c("0", "30,000", "60,000", "90,000")) +
  scale_y_continuous(limits = c(0,20), breaks = c(0, 5, 10, 15, 20), position = "right") +
  labs(title = "Growing apart",
       subtitle = "Selected countries, GDP growth and CO2 emmissions reductions",
       # caption = "CO2 emissions per person, tonnes"
       ) +
  xlab("GDP per person, $") +
  # Create manual legend
  geom_text(aes(x=5000, y = 19, label = "2010"),
            family = "inconsolata", size = 7, color = "#26231d") +
  geom_point(aes(x=10000, y = 19, size = 800), color = "#bed2e3") +
  geom_link(aes(x = 10000, xend = 15000,
                y = 19, yend = 19,
                color = stat(index)), 
                   size=4.0) +
  geom_point(aes(x=15000, y = 19, size = 800), color = "#406ba2") +
  geom_text(aes(x=20000, y = 19, label = "2018"),
            family = "inconsolata", size = 7, color = "#26231d") +
  geom_text(aes(x=2500, y = 17.5, label = "Total annual CO2, megatonnes"),
            family = "inconsolata", size = 7, color = "#26231d", hjust = 0) +
  geom_point(aes(x=3500, y = 16, size = 100), color = "#cccccd") +
  geom_text(aes(x=6000, y = 16, label = "100"),
            family = "inconsolata", size = 7, color = "#26231d") +
  geom_point(aes(x=10000, y = 16, size = 1000), color = "#cccccd") +
  geom_text(aes(x=14500, y = 16, label = "1000"),
            family = "inconsolata", size = 7, color = "#26231d") +
  geom_point(aes(x=21000, y = 16, size = 5000), color = "#cccccd") +
  geom_text(aes(x=27500, y = 16, label = "5000"),
            family = "inconsolata", size = 7, color = "#26231d") +
  theme_minimal() + 
  theme_opts  +
    labs(tag = "CO2 emissions per person, tonnes") +
    theme()

girafe(ggobj = v1, width_svg = 16, height_svg = 12,
       options = list(opts_sizing(rescale = TRUE, width = 0.6)))

```

### References
#### citations for narrative and data sources

* Narrative sources: The Economist, Daily chart - Several rich countries have decoupled GDP growth from emissions, [GO](https://www.economist.com/graphic-detail/2021/11/11/several-rich-countries-have-decoupled-gdp-growth-from-emissions){target="_blank"}
* Data sources: Our World in data - CO₂ emissions per capita vs GDP per capita, 2010 to 2018, [GO](https://ourworldindata.org/grapher/co2-emissions-vs-gdp?time=2010..2018){target="_blank"}

<pre>
@misc{
  author = {The Economist},
  month = {11},
  title = {Several rich countries have decoupled GDP growth from emissions},
  url = {https://www.economist.com/graphic-detail/2021/11/11/several-rich-countries-have-decoupled-gdp-growth-from-emissions},
  urldate = {2021-11-11},
  year = {2021},
  organization = {The Economist}
}
</pre>

