---
pagetitle: "Fastest Growing Brands"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# Fastest Growing Brands
## the dumbell chart

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Marvin Meyer on Unsplash"}

masthead <- "assets/marvin-meyer-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Great companies are built on great products...\
--- Elon Musk\ 

***

### Ingest
#### rank, brand, percent growth, category, etc.

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "fastest-growing-brands/fastest-growing-brands.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = FALSE) # read text file
df

```


### Wrangle
#### factor category to use for color


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_wrangle <- df
df_wrangle$Category <- as.factor(df_wrangle$Category)

head(df_wrangle)

```


### View, chart
#### segment and points 


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide'}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.title = element_text(color = "black", size = 14, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10, hjust = 0.0, vjust = 1.0),
    axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 14, face = "bold"),
    panel.border = element_blank(),
    panel.background = element_blank(),
    #panel.grid.minor = element_blank(), # remove minor gridlines
    panel.grid.major.x = element_blank(), # remove x (vertical) gridlines
    panel.grid.minor.x = element_blank(), # remove x (vertical) gridlines
    legend.title = element_blank(), # remove legend title
    legend.text = element_text(color = "black", size = 10),
    legend.position='top',
    plot.margin = unit(c(0.5, 0.25, 1.0, 0.5), "in")
  )

category_palette <- c(
                "Cars & Transportation" = "#84FF57",
                "Media & Entertainment" = "#1D74BC",
                "Consumer Goods & Retail" = "#ED297B",
                "Technology" = "#652D90",
                "Food & Beverages" = "#C3986B",
                "Retail" = "#FAEC31"
)

# create dumbbell plot
v1<-ggplot(df_wrangle) +  
  geom_segment( aes(x = Rank, xend = Rank, y = 0, yend = Brand_Value_Percent_Growth), lineend = "butt", linejoin = "round", size=1.0, color="black" ) +
  geom_point( aes(x = Rank, y = 0, size = X2020), shape = 21, fill = "white", color = "white", alpha = 1.0) +
  geom_point( aes(x = Rank, y = 0, size = X2020, fill = Category), shape = 21, color = "black", alpha = 0.6) +
  geom_text( aes(x = Rank, y = 0, label=X2020), size=6, color="black", hjust = 0.5, vjust = 0.5, family = "inconsolata", fontface = "bold" ) +
  geom_point( aes(x = Rank, y = Brand_Value_Percent_Growth, size = X2021), shape = 21, fill = "white", color = "white", alpha = 1.0) +
  geom_point( aes(x = Rank, y = Brand_Value_Percent_Growth, size = X2021, fill = Category), shape = 21, color = "black", alpha = 0.6) +
  geom_text( aes(x = Rank, y = Brand_Value_Percent_Growth, label=X2021), size=6, color="black", hjust = 0.5, vjust = 1.0, family = "inconsolata", fontface = "bold" ) + 
  geom_text( aes(x = Rank, y = Brand_Value_Percent_Growth, label=Brand), size=4, color="black", hjust = 0.5, family = "inconsolata", fontface = "bold", nudge_y = 10) + 
  scale_x_continuous(breaks = seq(1, 10, 1), labels = seq(1, 10, 1)) +
  scale_y_continuous(limits = c(0,300), breaks = c(0, 100, 200, 300), labels = c("0%", "100%", "200%", "300%")) +
  scale_size_continuous(range = c(15, 75), guide = "none") +
  scale_fill_manual(values = category_palette) +
  coord_cartesian(clip = "off") +
  labs(title = "THE FASTEST GROWING BRANDS in 2021 ",
       subtitle = "SELECTED COUNTRIES, LATEST AVAILABLE YEAR",
       caption = "Source:\nKantar BrandZ\nvia Visual Capitalist",
       x = "",
       y = "percent growth in brand value") +
  theme_minimal() + 
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


# References
## The citations and data sources used for this case

* Narrative and Data: Visual Capitalist, Ranked: The World’s Fastest Growing Brands, 2021,
[GO](https://www.visualcapitalist.com/fastest-growing-brands-2021/){target="_blank"}



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

