---
pagetitle: "Teacher Worth"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(countrycode)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

# Teacher Worth
## the dumbbell chart

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Yogendra Singh on Unsplash"}

masthead <- "assets/yogendra-singh-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> When we become a really mature, grown-up, wise society,\
  we will put teachers at the center of the community, where they belong.\
  We don't honor them enough, we don't pay them enough...\
--- Charles Kuralt\ 

***

### Ingest
#### location, indicator, measure, time, and value

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "teacher-worth/oecd-teacher-salaries.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = FALSE) # read text file
df
```


### Wrangle
#### filter, from long to wide, enrich


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_wrangle <- filter(df, TIME == 2020)
df_wrangle <- filter(df_wrangle, SUBJECT %in% c("PRY_START", "PRY15YREXP", "PRY_TOP"))
df_wrangle <- filter(df_wrangle, MEASURE == "USD")
df_wrangle <- spread(df_wrangle, SUBJECT, Value)
df_wrangle <- df_wrangle %>% select(LOCATION, PRY_START, PRY15YREXP, PRY_TOP)
df_wrangle$COUNTRY <- countrycode(df_wrangle$LOCATION, origin = 'iso3c', destination = 'country.name' )
df_wrangle$REGION <- countrycode(df_wrangle$LOCATION, origin = 'iso3c', destination = 'region' )
df_wrangle

```


### View, chart
#### segment and points


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide'}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.title = element_text(color = "black", size = 14, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10, hjust = 1.0, vjust = 1.0),
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 12, hjust = 0.5, vjust = 0.5),
    axis.text.y = element_text(size = 12, hjust = 1.0, vjust = 0.5),
    panel.border = element_blank(),
    panel.background=element_rect(fill="#ECE3CB", colour="NA"),
    panel.grid.minor = element_blank(), # remove minor gridlines
    panel.grid.major = element_line(size = 0.5, linetype = 'dotted', colour = "#BDAC81"),
    legend.title = element_blank(), # remove legend title
    legend.text = element_text(color = "black", size = 10),
    legend.position='bottom',
    plot.background = element_rect(fill="#ECE3CB", colour="NA"),
    plot.margin = unit(c(0.5, 0.5, 0.5, 0.25), "in")
  )

shape_map <- c("PRY_START" = 21, "PRY15YREXP" = 5, "PRY_TOP" = 4)

v1 <- ggplot(df_wrangle) +  
  geom_segment( aes(x = PRY_START, xend = PRY_TOP, y = COUNTRY, yend = COUNTRY), lineend = "butt", linejoin = "round", size=1.0, color="#293835" ) +
  geom_point( aes(x = PRY_START, y = COUNTRY, shape = "PRY_START" ), size = 5, fill = "#B50810", color = "#B50810", alpha = 0.9) +
  geom_point( aes(x = PRY15YREXP, y = COUNTRY, shape = "PRY15YREXP"), size = 3, color = "#293835", stroke = 1.5, alpha = 1.0) +
  geom_point( aes(x = PRY_TOP, y = COUNTRY, shape = "PRY_TOP"), size = 3, color = "#293835", stroke = 1.5, alpha = 1.0) +
  scale_x_continuous(labels=scales::dollar_format(), sec.axis = dup_axis()) +
  scale_shape_manual(values = shape_map, labels = c("START", "15YR", "TOP")) +
  coord_cartesian(clip = "off") +
  labs(title = "TEACHERS' SALARIES",
       subtitle = "Upper Secondary, starting, 15 yr, and top pay (USD)",
       caption = "Source: OECD",
       x = NULL,
       y = NULL) +
  theme_minimal() + 
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = FALSE, width = 0.95)))

```


# References
## The citations and data sources used for this case

* Narrative and Data: OECD, Teacher Salaries, [OECD](https://data.oecd.org/eduresource/teachers-salaries.html){target="_blank"}
