---
pagetitle: "Global City Populations"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Global City Populations
## Map Projection

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Steven Diaz on Unsplash"}

masthead <- "assets/steven-diaz-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Seaside Top: World Trade Center Tokyo Observation Deck, Minato Ku, Japan</div>

> Any city, however small, is in fact divided into two.\
  One the city of the poor, the other of the rich.\
  These are at war with one another...\
--- Plato\

***

### Ingest
#### world cities with coordinates and population


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

world_cities <- read.csv("archetypes/capital-cities-population/world-cities.csv", header = TRUE, encoding = "UTF-8")
world_cities <- filter(world_cities, population > 0 )
world_cities

```


### Load Map
#### Natural Earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

ne_world <- ne_countries(scale = "small", returnclass = "sf")
ne_world <- filter(ne_world, iso_a3 != "ATA") 

```


### Set crs
#### for map and data set


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

ne_world <- ne_world %>% st_as_sf() %>% st_set_crs(4326)

world_cities_sf <- world_cities %>% st_as_sf(coords = c("lng", "lat"), crs = 4326)

```


### Plot
#### showing map and data projected as Tissot


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

# theme parameters
theme_opts <- theme(
  legend.position = "bottom",
  legend.title = element_blank(),
  axis.text = element_blank(),
  #axis.line = element_blank(),
  #axis.ticks = element_blank(),
  axis.title = element_blank(),
  #panel.grid = element_blank(),
  #panel.grid.major = element_blank(),
  #panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_blank(),
  plot.background = element_blank(),
)

v1 = ggplot() +
  geom_sf(data = ne_world, color="#AAAAAA", fill="#FFFFFF", size=0.5) +
  geom_sf(data = world_cities_sf, aes(size = population, alpha = population), color="#C2185B") +
  #scale_x_continuous(name = NULL, breaks = seq(-120, 120, by = 60)) +
  #scale_y_continuous(name = NULL, breaks = seq(-60, 60, by = 30)) +
  scale_size_continuous(name = "",
                        range = c(0.5, 10), 
                        breaks = c(1000000, 5000000, 10000000, 30000000),
                        labels = c("1M", "5M", "10M", "30M")) +
  scale_alpha_continuous(range = c(0.1, 0.6), guide = "none") +
  coord_sf(crs = "+proj=tissot +lat_1=60 +lat_2=65") +
  theme_bw() +
  labs(x="", # Longitude
       y="", # Latitude
       title = "Global City Populations", 
       subtitle="Tissot Projection") +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 12,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### Plot
#### showing map and data projected as Murdoch I


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v2 = ggplot() +
  geom_sf(data = ne_world, color="#AAAAAA", fill="#FFFFFF", size=0.5) +
  geom_sf(data = world_cities_sf, aes(size = population, alpha = population), color="#C2185B") +
  #scale_x_continuous(name = NULL, breaks = seq(-120, 120, by = 60)) +
  #scale_y_continuous(name = NULL, breaks = seq(-60, 60, by = 30)) +
  scale_size_continuous(name = "",
                        range = c(0.5, 10), 
                        breaks = c(1000000, 5000000, 10000000, 30000000),
                        labels = c("1M", "5M", "10M", "30M")) +
  scale_alpha_continuous(range = c(0.1, 0.6), guide = "none") +
  coord_sf(crs = "+proj=murd1 +lat_1=30 +lat_2=50") +
  theme_bw() +
  labs(x="", # Longitude
       y="", # Latitude
       title = "Global City Populations", 
       subtitle="Murdoch I") +
  theme_opts

girafe(ggobj = v2, width_svg = 16, height_svg = 12,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk
ggsave(filename = "assets/global-city-populations-fs.svg", plot = v2, width=1280/72, height=720/72)

```


### References
#### citations for narrative and data sources

* Narrative: Proj.org, Projections, [GO](https://proj.org/operations/projections/index.html){target="_blank"}
* Data: simplemaps, [GO](https://simplemaps.com/data/world-cities){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
