---
pagetitle: "Map Projections"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Map Projections
## From sphere to plane


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Valentin Lacoste on Unsplash"}

masthead <- "assets/valentin-lacoste-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Hole, Yunnan, China</div>

> You mean to tell me that China is under us? China is under us?\
It's not. The world is flat.\
--- Shaquille O'Neal\

***

In cartography, a map projection is a way to __flatten a globe's__ surface into a plane in order to make a map. This requires a systematic transformation of the latitudes and longitudes of locations from the surface of the globe into locations on a plane. All projections of a sphere on a plane necessarily __distort__ the surface in some way and to some extent. Depending on the purpose of the map, some distortions are acceptable and others are not; therefore, different map projections exist in order to __preserve__ some properties of the sphere-like body at the expense of other properties such as angle or size.

### Load Map
#### Natural Earth

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

ne_world <- ne_countries(scale = "small", returnclass = "sf")

```


### Coordinate Reference System
#### Set crs


A coordinate reference system (CRS) refers to the way in which spatial data that represent the earth’s surface are flattened so that you can represent them on a 2-dimensional surface.

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

ne_world <- ne_world %>% st_as_sf() %>% st_set_crs(4326)

```


### Reprojected
#### Orthographic


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  #axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  #panel.grid = element_blank(),
  #panel.grid.major = element_blank(),
  #panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_blank(),
  plot.background = element_blank(),
)

v1 = ggplot() +
  geom_sf(data = ne_world, color="#AAAAAA", fill="#FFFFFF", size=0.5) +
  scale_x_continuous() +
  scale_y_continuous() +
  coord_sf(crs = "+proj=ortho") +
  theme_bw() +
  labs(x="", # Longitude
       y="", # Latitude
       title = "Natural Earth", 
       subtitle="Orthographic") +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### Reprojected
#### Robinson


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v2 = ggplot() +
  geom_sf(data = ne_world, color="#AAAAAA", fill="#FFFFFF", size=0.5) +
  scale_x_continuous() +
  scale_y_continuous() +
  coord_sf(crs = "+proj=robin") +
  theme_bw() +
  labs(x="", # Longitude
       y="", # Latitude
       title = "Natural Earth", 
       subtitle="Robinson") +
  theme_opts

girafe(ggobj = v2, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### Reprojected
#### Gall Stereographic


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v3 = ggplot() +
  geom_sf(data = ne_world, color="#AAAAAA", fill="#FFFFFF", size=0.5) +
  scale_x_continuous() +
  scale_y_continuous() +
  coord_sf(crs = "+proj=gall") +
  theme_bw() +
  labs(x="", # Longitude
       y="", # Latitude
       title = "Natural Earth", 
       subtitle="Gall Stereographic") +
  theme_opts

girafe(ggobj = v3, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### Reprojected
#### Mollweide


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v4 = ggplot() +
  geom_sf(data = ne_world, color="#AAAAAA", fill="#FFFFFF", size=0.5) +
  scale_x_continuous() +
  scale_y_continuous() +
  coord_sf(crs = "+proj=moll") +
  theme_bw() +
  labs(x="", # Longitude
       y="", # Latitude
       title = "Natural Earth", 
       subtitle="Mollweide") +
  theme_opts

girafe(ggobj = v4, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### Reprojected
#### Wagner VII


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v5 = ggplot() +
  geom_sf(data = ne_world, color="#AAAAAA", fill="#FFFFFF", size=0.5) +
  scale_x_continuous() +
  scale_y_continuous() +
  coord_sf(crs = "+proj=wag7") +
  theme_bw() +
  labs(x="", # Longitude
       y="", # Latitude
       title = "Natural Earth", 
       subtitle="Wagner VII") +
  theme_opts

girafe(ggobj = v5, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/map-projections-fs.svg", plot = v1, width=1280/72, height=720/72)

```


### References
#### citations for narrative and data sources

* Narrative and Data: Proj.org, Projections, [GO](https://proj.org/operations/projections/index.html){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
