---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/styles/content/views.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    #self_contained: false
    #lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(htmltools) # needed to include html snippets
library(tidyverse)
library(ggpubr)

library(knitcitations)
library(bibtex)

```

<div class="activity">
VIEWS  
</div>

# Texture
## I want to fix irregularities in my dataset

> Don't call the world dirty because you forgot to clean your glasses...\
--- Aaron Hill\

The process of mapping data to visual variables is called visual mapping. Choosing diff erent marks, forms, and styles for representing and expressing information can greatly infl uence the perception and understanding of the presented information. It is therefore important to know and appropriately use the characteristics of visual variables when creating any visual data representation.

***

# Section
## Subsection



# Master
## Subsection


# Section
## Subsection


# Example
## Subsection


### Result

```{r, out.width = "100%"}

# knitr::include_graphics("assets/design-considerations.svg", dpi=300)

```


# Section
## Subsection



# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

# cleanbib()
# read.bibtex(file = "./citations.bib")

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

