---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS 
</div>

# Format String
## Normalize, Convert Case, Combine, Split, Truncate, Detect, Remove non-numeric, and Remove non-alpha-numeric


```{r, out.width="20%", fig.align="center"}

masthead <- "assets/noun_code formatting_2665697.svg"
knitr::include_graphics(masthead, dpi=72)

```

Single text characters like the alphabet (__A-Z__), numeral digits (__0-9__), punctuation (__. ! ? ; :__), single/double quote marks (__' "__) form a string-type data. Therefore you will encounter many, if not most, data sources which contain string-type data. The text characters can be combined in ways that are misleading and illegible. In order to make it easier to read, write and maintain a string-type data, formatting it properly is necessary for further analysis.

* Normalize: Some Unicode characters have the same appearance but multiple representations. For example, "â" can be represented as one code point for "â", or two decomposed code points for "a" and "^". Normalize method will convert strings to __NFC, NFKC, NFD, NFKD, or NFKC_Casefold Unicode Normalization Form__ or check whether strings are normalized. Basically, Unicode normalization is the decomposition or composition of characters.
* Convert Case: convert the string into opposite case.
* Combine: connect multiple strings with separators.
* Split: break a string into multiple subsets.
* Truncate: remove characters based on its position.
* Detect: detect patterns, similar to wrangler-find methods.
* Remove non-numeric: remove digits [0-9].
* Remove non-alpha-numeric: remove alphanumeric characters [A-z0-9].



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "format-string detect-alpha combine detect-special-character lowercase normalize remove-non-alpha-numeric remove-non-numeric split format-title truncate uppercase" # mostly used in wranglers and analytics
keywords <- ''
commands <- ''
sources <- ''

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```

```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

