---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: libs

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
   dev = "svg"
)
library(tidyverse)  # metapackage with lots of helpful functions
library(data.table) # table,matrix
library(lubridate)  # date
library(gridExtra)  # ggplot functions
library(plotly)     # interactive graphs    
library(scales)     # scale axis
library(fBasics)    # for base statistics
library(reshape)    # long and wide data
library(ggrepel)    # ggplot label
library(knitr)      # for html table
library(ggfortify)  # autoplot(time series ggplot)
library(forecast)   # forecast time series 
library(ggiraph)
```

<div class="activity">
ANALYTICS
</div>

# Dynamic regression models
## I want to predict future values based on historical data plus other informations

> J'ai deux amours, mon pays et Paris...\
--- Jaséphine Baker\

To make a better prediction, it may be necessary to add external variables, which may explain some of the variations observed in the historical data.

In this section, we will focus on the following steps:

* Analyse __Historical data__
* Estimate other informations, adding __external variables__ 
* Fit __Dynamic__ Model
* Analyse __residuals__ to estimate __model__ performance
* __Forecast__


***

# Paris Air pollution - Determining its causes

We are given times series about daily pollutant levels in Paris. Here are some further information about the potential __causes__ or sources of each pollutant level 

* [EPA - O_3](https://www.epa.gov/ground-level-ozone-pollution/ground-level-ozone-basics#formation)

Tropospheric, or ground level ozone, is not emitted directly into the air, but is created by chemical reactions between oxides of nitrogen (NOx) and volatile organic compounds (VOC). This happens when pollutants __emitted by cars, power plants, industrial boilers, refineries, chemical plants__, and other sources chemically react in the __presence of sunlight__.

* [EPA - PM](https://www.epa.gov/pm-pollution/particulate-matter-pm-basics#PM)

These particles come in many sizes and shapes and can be made up of hundreds of different chemicals.

Some are emitted directly from a source, such as __construction sites, unpaved roads, fields, smokestacks or fires__.

Most particles form in the atmosphere as a result of complex reactions of chemicals such as sulfur dioxide and nitrogen oxides, which are pollutants emitted from __power plants, industries and automobiles__.

* [EPA - NO2](https://www.epa.gov/no2-pollution/basic-information-about-no2#What%20is%20NO2)

NO2 primarily gets in the air from the burning of fuel. NO2 forms from emissions from __cars, trucks and buses, power plants, and off-road equipment__.

### Loading pollutant Data

```{r, message=FALSE, warning=FALSE}
paris_pollutant <- read_csv("archetypes/paris-air-quality.csv")
paris_pollutant_1 <- paris_pollutant %>% 
  select(date, O_3 = o3, PM10 = pm10, NO_2 = no2, SO_2 = so2)

pollutant <- paris_pollutant_1 %>% 
  mutate(day = as_date(date)) %>%
  dplyr::filter(day > as.Date("2015-12-31"), day < as.Date("2016-12-01")) %>% 
  select(day, O_3, PM10, NO_2) %>%
  arrange(day)

pollutant

```

### Visualizing


```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=8}

# theme parameters
theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  #axis.text = element_blank(),
  axis.line = element_blank(),
  #axis.ticks = element_blank(),
  #axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  # panel.background = element_blank(),
  panel.background = element_rect(fill = "#ffffff"),
  panel.border = element_blank(),
  # plot.background = element_blank(),
  plot.background = element_rect(fill = "#ffffff")
)

O_3_plot <- ggplot(pollutant, aes(x=day,y=O_3)) +
  geom_line() +
  theme_opts + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))

PM10_plot <- ggplot(pollutant, aes(x=day,y=PM10)) +
  geom_line() +
  theme_opts + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))

NO_2_plot <- ggplot(pollutant, aes(x=day,y=NO_2)) +
  geom_line() +
  theme_opts + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))

v1<-grid.arrange(O_3_plot,PM10_plot,NO_2_plot,ncol=1,top="pollutant")
# girafe(ggobj = v1, width_svg = 13, height_svg = 7,
#        options = list(opts_sizing(rescale = TRUE, width = 1.0)))
```

# Adding external variables

## Is vehicle traffic a determinant to observed pollutant levels in Paris?

### Loading traffic Data


```{r}
paris_traffic <- readRDS("archetypes/paris_traffic.Rds")
head(paris_traffic)


```

### Traffic data wrangling


```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=8}

df_1 <- paris_traffic %>% 
  mutate(hour = interval / 3600) %>%
  group_by(day, hour) %>%
  summarize(mean = mean(flow)) %>% 
  count(day) %>%
  dplyr::filter(n == 24)

paris_traffic_1 <- paris_traffic %>% 
  mutate(hour = interval / 3600) %>%
  group_by(day) %>%
  summarize(mean = mean(flow)) %>%
  dplyr::filter(day %in% unique(df_1$day))

paris_traffic_1

```

### Visualize traffic Data


```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=8}

# theme parameters
theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  #axis.text = element_blank(),
  axis.line = element_blank(),
  #axis.ticks = element_blank(),
  #axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  # panel.background = element_blank(),
  panel.background = element_rect(fill = "#ffffff"),
  panel.border = element_blank(),
  # plot.background = element_blank(),
  plot.background = element_rect(fill = "#ffffff")
)

traffic_plot <- ggplot(paris_traffic_1, aes(x=day,y=mean)) +
  geom_line() +
  theme_opts + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))+
  geom_vline(xintercept = as.Date("2016-07-01"), color = "red") +
  geom_text(aes(x=as.Date("2016-07-01"), y=100, label="July 1st"), size=4, color = "red")  +
  geom_vline(xintercept = as.Date("2016-09-01"), color = "blue") +
  geom_text(aes(x=as.Date("2016-09-01"), y=90, label="Sept 1st"), size=4, color = "blue") +
  labs(y="Traffic")

girafe(ggobj = traffic_plot, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))
```


### Visualize traffic data with pollutant

```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=8}

O_3_plot <- ggplot(pollutant, aes(x=day,y=O_3)) +
  geom_line() +
  theme_opts + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))+
  geom_vline(xintercept = as.Date("2016-07-01"), color = "red") +
  geom_text(aes(x=as.Date("2016-07-01"), y=100, label="July 1st"), size=4, color = "red")  +
  geom_vline(xintercept = as.Date("2016-09-01"), color = "blue") +
  geom_text(aes(x=as.Date("2016-09-01"), y=90, label="Sept 1st"), size=4, color = "blue")

PM10_plot <- ggplot(pollutant, aes(x=day,y=PM10)) +
  geom_line() +
  theme_opts + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))+
  geom_vline(xintercept = as.Date("2016-07-01"), color = "red") +
  geom_text(aes(x=as.Date("2016-07-01"), y=100, label="July 1st"), size=4, color = "red")  +
  geom_vline(xintercept = as.Date("2016-09-01"), color = "blue") +
  geom_text(aes(x=as.Date("2016-09-01"), y=90, label="Sept 1st"), size=4, color = "blue")

NO_2_plot <- ggplot(pollutant, aes(x=day,y=NO_2)) +
  geom_line() +
  theme_opts + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))+
  geom_vline(xintercept = as.Date("2016-07-01"), color = "red") +
  geom_text(aes(x=as.Date("2016-07-01"), y=100, label="July 1st"), size=4, color = "red")  +
  geom_vline(xintercept = as.Date("2016-09-01"), color = "blue") +
  geom_text(aes(x=as.Date("2016-09-01"), y=90, label="Sept 1st"), size=4, color = "blue")

#grid.arrange(traffic_plot,O_3_plot,PM10_plot,NO_2_plot,ncol=1,top="Traffic vs pollutant")
girafe(ggobj = traffic_plot, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))
girafe(ggobj = traffic_plot, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))
girafe(ggobj = traffic_plot, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))
girafe(ggobj = traffic_plot, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))
```

## Is the weather a better determinant?

### Adding temperatures

```{r, message=FALSE, warning=FALSE, echo=TRUE}
paris_weather <- read_csv("archetypes/2627103.csv")

paris_weather_1 <- paris_weather %>%
  select(day = DATE, precipitation = PRCP, wind = SNWD, temperature = TAVG) %>%
  dplyr::filter(day > as.Date("2015-12-31"), day < as.Date("2016-12-31"))

paris_weather_1

```

```{r}

# Choose a pollutant, compute daily maximum 
#O_3 PM10, NO_2, SO_2

#paris_pollutant_1

pollutant <- paris_pollutant_1 %>% 
  mutate(day = as_date(date)) %>%
  dplyr::filter(day > as.Date("2015-12-31"), day < as.Date("2016-12-31"))

O_3_plot <- ggplot(pollutant, aes(x=day,y=O_3)) +
  geom_line() +
  theme_opts + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))+
  geom_vline(xintercept = as.Date("2016-07-01"), color = "red") +
  geom_text(aes(x=as.Date("2016-07-01"), y=100, label="July 1st"), size=4, color = "red")  +
  geom_vline(xintercept = as.Date("2016-09-01"), color = "blue") +
  geom_text(aes(x=as.Date("2016-09-01"), y=90, label="Sept 1st"), size=4, color = "blue")

PM10_plot <- ggplot(pollutant, aes(x=day,y=PM10)) +
  geom_line() +
  theme_opts + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))+
  geom_vline(xintercept = as.Date("2016-07-01"), color = "red") +
  geom_text(aes(x=as.Date("2016-07-01"), y=100, label="July 1st"), size=4, color = "red")  +
  geom_vline(xintercept = as.Date("2016-09-01"), color = "blue") +
  geom_text(aes(x=as.Date("2016-09-01"), y=90, label="Sept 1st"), size=4, color = "blue")

NO_2_plot <- ggplot(pollutant, aes(x=day,y=NO_2)) +
  geom_line() +
  theme_opts + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))+
  geom_vline(xintercept = as.Date("2016-07-01"), color = "red") +
  geom_text(aes(x=as.Date("2016-07-01"), y=100, label="July 1st"), size=4, color = "red")  +
  geom_vline(xintercept = as.Date("2016-09-01"), color = "blue") +
  geom_text(aes(x=as.Date("2016-09-01"), y=90, label="Sept 1st"), size=4, color = "blue")

girafe(ggobj = O_3_plot, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))
girafe(ggobj = PM10_plot, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))
girafe(ggobj = NO_2_plot, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))
```

### Visualize temperature data

```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=8}
weather_temp_plot <- ggplot(paris_weather_1, aes(x=day,y=temperature)) +
  geom_line() +
  theme_opts + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))+
  geom_vline(xintercept = as.Date("2016-07-01"), color = "red") +
  geom_text(aes(x=as.Date("2016-07-01"), y=100, label="July 1st"), size=4, color = "red")  +
  geom_vline(xintercept = as.Date("2016-09-01"), color = "blue") +
  geom_text(aes(x=as.Date("2016-09-01"), y=90, label="Sept 1st"), size=4, color = "blue")


girafe(ggobj = weather_temp_plot, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))
```

### Visualize temperature data with pollutant

```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=8}
#grid.arrange(weather_temp_plot,O_3_plot,PM10_plot,NO_2_plot,ncol=1,top="Temperature vs pollutant")

```

```{r, message=FALSE, warning=FALSE, echo=TRUE}
pollutant <- pollutant %>% mutate(day = as.Date(date))

df_joined <- inner_join(pollutant, paris_weather_1, by=c("day" = "day")) %>%
  dplyr::filter(!is.na(O_3))

```

# Fitting dynamic model

### Fitting first dynamic model

Using __temperature__ as additional information

```{r, message=FALSE, warning=FALSE, echo=TRUE}
fit <- auto.arima(df_joined[,"O_3"],
  xreg=as.matrix(df_joined[,"temperature"]))

fit
```

# Analyse rediduals

### Checking residuals for this model

```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=8}
checkresiduals(fit) + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))

```

### Fitting second dynamic model and checking again residuals

Using __temperature__ and __precipitation__ as additional information

```{r, message=FALSE, warning=FALSE, echo=TRUE}
xreg <- as.matrix(cbind(Temp = df_joined[,"temperature"],
              Precipitation = df_joined[,"precipitation"]))

fit_temp_prec <- auto.arima(df_joined[,"O_3"], xreg = xreg)

fit
```


```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=8}


checkresiduals(fit_temp_prec)
```

# Final forecast

```{r, message=FALSE, warning=FALSE, fig.width=16, fig.height=8}

# xreg <- as.matrix(cbind(Temp = df_joined[,"temperature"],
#               Precipitation = df_joined[,"precipitation"]))
# 
# fit_temp_prec <- auto.arima(df_joined[,"O_3"], xreg = xreg)

paris_weather_2 <- paris_weather %>%
  select(day = DATE, precipitation = PRCP, wind = SNWD, temperature = TAVG) %>%
  dplyr::filter(day > as.Date("2016-12-31"), day < as.Date("2017-03-01"))

xreg_future <- as.matrix(cbind(Temp = paris_weather_2[,"temperature"],
               Precipitation = paris_weather_2[,"precipitation"]))

fcast <- forecast(fit_temp_prec,
  xreg = xreg_future)


v1<-autoplot(fcast) + ylab("Pollutant forecast") +
  theme_opts + 
  theme(plot.title = element_text(size=25)) + 
  theme(text = element_text(size = 20))
girafe(ggobj = v1, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```

```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

