---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    #self_contained: false
    #lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggraph)
library(igraph)
library(graphlayouts)
library(tidygraph)
library(netrankr)

library(knitcitations)
library(bibtex)
```

<div class="activity">
GRAPHS
</div>

# Node-links - One-Way Inbound Flow 
## Case: UNHCR - United Nations High Commission for Refugees - Refugee Flows

***

## Load data [Ingest]

```{r,message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df <- read.csv("./archetypes/unhcr-refugee-flows/unhcr-refugee-flows-edges.csv", header = TRUE, stringsAsFactors = TRUE)


df

```

# Prepare data [Wrangle] - Part I
## Filter records where the refugees' target country is Ehtiopia (ETH based on the ISO3 code)
## Rename column value to Refugee_Num

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df_f <- filter(df, target %in% c("ETH"))

df_f <- df_f %>% rename(Refugees_Num='value')

df_f

```


# Prepare data [Wrangle] - Part II 
## Format the data into a graph data frame 
## Creating two important sets: Nodes and Edges between the nodes

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# Convert data to graph data frame
# directed=true means it is a flow not just an association between nodes
g <- graph.data.frame(df_f, directed = TRUE)
g

```
# Ensuring proper attributes for Edges
## Computing Edges Weights (as per number of refugees)

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

cg <- g %>% 
      as_tbl_graph() %>% 
      activate(edges) %>% 
      #computes a small number as per Value of refugees flow
      mutate(edge_weights = log(Refugees_Num))

cg

```


# Ensuring proper attributes for Nodes

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}
## Creating centrality numerical field for the Nodes

# centrality_power() 
# centrality_closeness() 
# centrality_eigen() 
# centrality_hub() 

cg <- cg %>% 
    activate(nodes) %>% 
  # associating random numerical value to nodes to differentiate their colors and sizes
    mutate(centrality  = centrality_power())

## Creating group numerical field for the Nodes


# group_fast_greedy() 
# group_infomap() 
# group_label_prop() 
# group_leading_eigen() 
# group_louvain() 
# group_optimal() 


cg <- cg %>% 
  activate(nodes) %>%
   # use functions to compute numerical values to attribute the edge width and/or color
  mutate(group = group_optimal())

cg

```


## Layout & Aesthetic Parameters
### Choose the types of Edges you would like to display


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# Edge Types
# geom_edge_arc
# geom_edge_arc0
# geom_edge_arc2
# geom_edge_density
# geom_edge_diagonal
# geom_edge_diagonal0
# geom_edge_diagonal2
# geom_edge_elbow
# geom_edge_elbow0
# geom_edge_elbow2
# geom_edge_fan
# geom_edge_fan0
# geom_edge_fan2
# geom_edge_hive
# geom_edge_hive0
# geom_edge_hive2
# geom_edge_link
# geom_edge_link0
# geom_edge_link2
# geom_edge_loop
# geom_edge_loop0

# Layouts can be computationally intensive
# Uncomment only for use

# igraph
# dh <- create_layout(cg, layout = 'dh')
# fr <- create_layout(cg, layout = 'fr')
# gem <- create_layout(cg, layout = 'gem')
# lgl <- create_layout(cg, layout = 'lgl')
# sugiyama <- create_layout(cg, layout = 'sugiyama')
# star <- create_layout(cg, layout = 'star')
# kk <- create_layout(cg, layout = 'kk', maxiter = 100)
# drl <- create_layout(cg, layout = 'drl')
# linear_straight <- create_layout(cg, layout = 'linear')
# linear_circular <- create_layout(cg, layout = 'linear' , circular = TRUE)

# ggraph
# arc <- create_layout(cg, layout = 'linear')
# arc_circular <- create_layout(cg, layout = 'linear', circular = TRUE)
# stress <- create_layout(cg, layout = 'stress')
# sparse_stress <- create_layout(cg, layout = 'sparse_stress')
# backbone <- create_layout(cg, layout = 'backbone')
# pmds <- create_layout(cg, layout = 'pmds')
# eigen <- create_layout(cg, layout = 'eigen')
# centrality <- create_layout(cg, layout = 'centrality')
# focus <- create_layout(cg, layout = 'focus')
# dendrogram <- create_layout(cg, layout = 'dendrogram')
# unrooted <- create_layout(cg, layout = 'unrooted')
# matrix <- create_layout(cg, layout = 'matrix')
# hive <- create_layout(cg, layout = 'hive')
# fabric <- create_layout(cg, layout = 'fabric')

# graphlayouts
# nicely <- create_layout(cg, layout = "nicely")
stress <- create_layout(cg, layout = "stress")
# radial <- create_layout(cg, layout = "focus", focus = 1)


```


## Plot with Layout


```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show', fig.width=12, fig.height=12}


theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.background = element_blank(),
)

v1 <- ggraph(stress) + 
  geom_edge_arc(arrow = arrow(ends = "last", angle = 30, length = unit(.5,"cm")), aes(color = edge_weights)) + 
  geom_node_point(aes(color = group, size = centrality)) +
  geom_node_text(repel = TRUE, aes(label = name)) +
  scale_color_gradient(low = "green", high = "blue", na.value = NA) +
  scale_size(range = c(1,6)) +
  theme_graph()+
  theme(legend.position = "top")

v1


```


## Save views

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

ggsave(filename = "./assets/unhcr-refugee-flows.svg", plot = v1, width=12, height=6)
# ggsave(filename="./assets/unhcr-refugee-flows.png", plot=v1, device="png", width=12, height=6, units="in", dpi=500)

```



# References
## The citations and data sources used for this case

Source: <a href="https://www.unhcr.org/" target="_blank"> UNHCR - United Nations High Commission for Refugees </a> 

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "./citations/unhcr-refugee-flows.bib")

```




```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


