---
pagetitle: "Corruption Perception Index"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(janitor)
library(ggtext)
library(ggdist)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


<div class="activity">
CHARTS  
</div>

# Corruption Perception Index
## Density

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Nathaniel Tetteh on Unsplash"}

masthead <- "assets/nathaniel-tetteh-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Corruption is paid by the poor...\
--- Pope Francis\

***

### Ingest
#### country, region, CPI score, standard error

```{r echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df <- read.csv("archetypes/corruption-perception-index/corruption-perception-index-2020.csv", header = TRUE, stringsAsFactors = FALSE, encoding = "UTF-8")
df

```


### Wrangle
#### clean column names and remove missing values

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_wrangle <- df %>% dplyr::select(1:4, 6) %>% janitor::clean_names()
df_wrangle <- df_wrangle %>% filter(!is.na(cpi_score_2020))
df_wrangle

```


### View / Chart
#### with stat_halfeye and stat_dotsinterval

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1280/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.title = element_text(color = "black", size = 12, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 10),
    plot.caption = element_text(color = "#555555", size = 9),
    panel.background = element_rect(fill = '#F5F5F5', color = NA),
    panel.border = element_blank(),
    plot.background = element_rect(fill = '#F5F5F5', color = NA),
    panel.grid.major.x = element_line(color = "#999999", size = 1.0, linetype = "dotted"),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "top",
    # plot.margin = unit(c(0.5, 0.5, 0.5, 0.25), "in")
    plot.margin = unit(c(0,0,0,0),"line")
)


region_scale <- c(
  'Sub-Saharan\nAfrica', 
  'Europe and\nCentral Asia', 
  'America', 
  'Asia-Pacific', 
  'Middle East and\nNorth Africa', 
  'European Union'
)


v1 <- ggplot(df_wrangle, aes(fct_reorder(region, cpi_score_2020), cpi_score_2020)) +
  stat_halfeye(side = 'left', scale = .5, alpha = 0.6, aes(fill = stat(cut_cdf_qi( cdf, .width = c(.5, .8, .95), labels = scales::percent_format() )))) +
  stat_dotsinterval(scale = 0.3, point_size = 1, fill = '#999999') +
  scale_colour_gradient(low = "#00ACC1", high = "#FDD835") +
  scale_x_discrete(labels = region_scale) +
  scale_y_continuous(breaks = seq(0, 80, 20)) +
  labs(title = "Corruption Perception Index (2020)",
       subtitle = "Index scores by region",
       caption = 'Source: Transparency International',
       x = NULL,
       y = 'CPI Score',
       fill = "Interval") +
  theme_minimal() +
  theme_opts

girafe(ggobj = v1, width_svg = 1080/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.9))
)

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; set to TRUE for production outputs

# full version
ggsave(filename = "assets/corruption-perception-index-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "assets/corruption-perception-index-sm.png", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative sources: Luis Freites, [GO](https://github.com/luisfrein/R_Tidytuesday){target="_blank"}
* Data sources: Transparency International, [GO](https://www.transparency.org/en){target="_blank"}

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

