---
pagetitle: "Energy Consumption by Fuel Type - Kuwait"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---


```{r setup, include=FALSE}


knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)

library(ggalluvial)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
TEMPORALS
</div>

# Energy Consumption by Fuel Type - Kuwait
## Alluvial Plot


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by David Clode on Unsplash"}

masthead <- "assets/david-clode-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> I'd love to fly, especially with the gas prices right now....\
--- Joel Gretsch\

***

### Ingest

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read.csv("./archetypes/owid-energy-data-long.csv", header = TRUE, stringsAsFactors = FALSE)  

df
```


### Wranglers
#### Rename column 

Rename column __variable__ as __fuel_type__

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}
df <- df %>%
  rename("fuel_type"="variable")

head(df)
```

#### Filter 

Filter only records where:

* __fuel_type__ is the same as the ones from a pre-established list
* __year__ is every two years between <mark> 2000 </mark> and <mark> 2016 </mark>
* __country__ is <mark> Kuwait </mark>

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Filter for the fields used in each view
consumption_types <- c("solar_electricity",
                  "fossil_electricity",
                  "gas_electricity"
                  )


df <- df %>% filter(fuel_type %in% consumption_types)

# Limit to every 2 years intervals
years <- c(2000, 2002, 2004,2006,2008,2010,2012,2014, 2016)
df <- df %>% filter(year %in% years)

# The specific country to generate the view
df_country <- df %>% filter(country == "Kuwait")

#df_country <- df_country %>% arrange(df_country$value)

df_country


```

### Alluvial Theme

Standard theme options to use for each view.

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Color palette for each energy type
energy_pal <- c("gas_electricity" = "#7b9095", 
                "fossil_electricity" = "#FDB813",
                "solar_electricity" = "#373A36"
                )

# Standard theme options to use for each view
theme_opts <- theme(
  legend.position = "bottom",
  legend.title = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.background = element_blank()
)

```

### Alluvial Plot
#### <kbd> geom_alluvium() </kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

# View using alluvium geom
v1 <- ggplot(data = df_country, aes(x = year, y = value, alluvium = fuel_type)) +
  geom_alluvium(aes(fill = fuel_type), size=1.5, colour = "#ffffff", alpha = 1.0, decreasing = FALSE) +
  # for set years
  scale_x_continuous(breaks = years) +
  # for aesthetics to show top-down
  scale_y_reverse() +
  # use the palette defined above
  scale_fill_manual(values = energy_pal) +
  # in case any marks fall outside panel
  coord_cartesian(clip = "off") +
  # a simple theme to modify
  theme_minimal() +
  # rotate years
  theme(axis.text.x = element_text(angle = -90, hjust = 1, vjust = 0.5)) +
  # use configured theme options
  theme_opts +
  labs(
    x="",
    y="",
    title="Country Energy Consumption by Fuel Type",
    subtitle="Kuwait"
  )

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
      options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```

### Alluvial Plot
#### <kbd> geom_flow() </kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v2 <- ggplot(data = df_country, aes(x = year, y = value, alluvium = fuel_type)) +
  geom_flow(aes(fill = fuel_type, size = value), colour = "#ffffff", alpha = 1.0, decreasing = FALSE) +
  # for set years
  scale_x_continuous(breaks = years) +
  # for aesthetics to show top-down
  scale_y_reverse() +
  # use the palette defined above
  scale_fill_manual(values = energy_pal) +
  # scale line size so smallest values still show
  scale_size_continuous(range = c(0.75,2), breaks = c(0.75,2), guide = FALSE) +
  # in case any marks fall outside panel
  coord_cartesian(clip = "off") +
  # a simple theme to modify
  theme_minimal() +
  # rotate years
  theme(axis.text.x = element_text(angle = -90, hjust = 1, vjust = 0.5)) +
  # use configured theme options
  theme_opts +
  labs(
    x="",
    y="",
    title="Country Energy Consumption by Fuel Type",
    subtitle="Kuwait"
  )

girafe(ggobj = v2, width_svg = 16, height_svg = 9,
      options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source = 'fold-hide'}

# eval = FALSE as default; set to TRUE for production outputs

# full version
ggsave(filename = "assets/energy-consumption-by-fuel-type-kuwait.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "assets/energy-consumption-by-fuel-type-kuwait.png", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative and Data sources: Energy Production and Consumption - Our World in Data, [GO](https://ourworldindata.org/energy-production-consumption){target="_blank"}



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


