---
pagetitle: "How Does Income Relate to Life Expectancy"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

library(tidyverse)
library(countrycode)
library(ggrepel)

```

<div class="activity">
CHART  
</div>

# How Does Income Relate to Life Expectancy
## Bubble Chart

This epic chart was presented by __Hans Rosling__ to illustrate that income and health go hand in hand. People live longer in richer countries. Or the other way around. Countries are richer where people live longer. There are no high income countries with a short life expectancy, and no low income countries with a long life expectancy. Still, there’s a huge difference in life expectancy between countries on the same income level, depending on how the money is distributed and how it is used.

The __y-axis__ shows a continuum from healthy to sick, the __x-axis__ from rich to poor. The bubbles are __sized__ by population and __colored__ by continent.

### Ingest the data
* Life expectancy, income and populaction of 188 nations in year 2019  


```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read_csv("archetypes/gapminder/gapminder.csv")
df

```

### Wrangle the data
* Enrich data frame with the continent name  
* Only keep required columns  

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_1 <- df %>%
  mutate(continent = countrycode(df$country_code, origin = 'iso3c', destination = 'continent')) %>%
  select(-country_code, population = pop)

df_1

```

### Scatter plot

#### Step 1 - Map x and y axis
* First, simple scatter plot of countries with 
  * x-axis: GDP  
  * y-axis: life expectancy   

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  geom_point()

```

#### Step 2 - Transform the x axis to spread points across the chart
* Use the log of x to spread the countries more evenly by GPD  

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  geom_point() +
  # Transform the scale of the x axis to "log"
  scale_x_log10(limits = range(df_1$gdp))

```

### Sizing bubbles

#### Step 1 - Map bubble size
* Use population for the size of the bubble

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  scale_x_log10(limits = range(df_1$gdp)) +
  geom_point(aes(size = population))


```

#### Step 2 - control size of bubbles
* Use a manual range to control the size the bubbles 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  scale_x_log10(limits = range(df_1$gdp)) +
  geom_point(aes(size = population)) +
  # Size mapping
  scale_size("population", range = c(2, 40))


```

### Adding colors

#### Step 1 - Map color
* color bubbles based on continent value 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  scale_x_log10(limits = range(df_1$gdp)) +
  geom_point(aes(size = population, color = continent)) +
  scale_size("population", range = c(2, 40))

```
#### Step 2 - Control colors
* Use a manual palette to control colors  

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Manual palette to match colors
continent_palette <- c("Africa" = "#A3DDF7", "Americas" = "#AAE828", "Asia" = "#DB616F", "Europe" = "#F6E71D", "Oceania" = "#DB616F")

ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  scale_x_log10(limits = range(df_1$gdp)) +
  geom_point(aes(size = population, color = continent)) +
  scale_size("population", range = c(2, 40)) +
  # Color mapping
  scale_color_manual(values = continent_palette)

```

### Adding labels

#### Step 1 - Map labels
* Add country names

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Manual palette to match colors
continent_palette <- c("Africa" = "#A3DDF7", "Americas" = "#AAE828", "Asia" = "#DB616F", "Europe" = "#F6E71D", "Oceania" = "#DB616F")

ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  scale_x_log10(limits = range(df_1$gdp)) +
  geom_point(aes(size = population, color = continent)) +
  scale_size("population", range = c(2, 40)) +
  scale_color_manual(values = continent_palette) +
  # Use geom_text to map country names
  geom_text(aes(label=country))
```

#### Step 2 - Reduce labels displayed
* Filter out "small" countries, where population is less than the mean of all countries's populations.  

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Manual palette to match colors
continent_palette <- c("Africa" = "#A3DDF7", "Americas" = "#AAE828", "Asia" = "#DB616F", "Europe" = "#F6E71D", "Oceania" = "#DB616F")

ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  scale_x_log10(limits = range(df_1$gdp)) +
  geom_point(aes(size = population, color = continent)) +
  scale_size("population", range = c(2, 40)) +
  scale_color_manual(values = continent_palette) +
  geom_text(data=filter(df_1, population > mean(population)),
                  aes(label = country, size = population / 2),
                   family = "inconsolata")

```

#### Step 3 - repel labels
* use "geom_text__repel__" to repel countries so they do not overlap (function available from package __ggrepel__)  


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Manual palette to match colors
continent_palette <- c("Africa" = "#A3DDF7", "Americas" = "#AAE828", "Asia" = "#DB616F", "Europe" = "#F6E71D", "Oceania" = "#DB616F")

ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  scale_x_log10(limits = range(df_1$gdp)) +
  geom_point(aes(size = population, color = continent)) +
  scale_size("population", range = c(2, 40)) +
  scale_color_manual(values = continent_palette) +
  geom_text_repel(data=filter(df_1, population > mean(population)),
                  aes(label = country, size = population / 2),
                  family = "inconsolata")

```

### Cleaning up, "beautifying" the graph

#### Step 1 - Labels and legends
* Turn-off scientific notation  
* Add chart title  
* Overwrite x and y axis titles  


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# turn-off scientific notation like 1e+48
options(scipen=999)  

# Manual palette to match colors
continent_palette <- c("Africa" = "#A3DDF7", "Americas" = "#AAE828", "Asia" = "#DB616F", "Europe" = "#F6E71D", "Oceania" = "#DB616F")

ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  scale_x_log10(limits = range(df_1$gdp)) +
  geom_point(aes(size = population, color = continent)) +
  scale_size("population", range = c(2, 40)) +
  scale_color_manual(values = continent_palette) +
  geom_text_repel(data=filter(df_1, population > mean(population)),
                  aes(label = country, size = population / 2), 
                  family = "inconsolata") +
  # Adding title
  ggtitle("World Health Chart 2019 by Gapminder") +
  # Overwriting x and y axis labels
  ylab("Lifespan, Life Expectancy") +
  xlab("Income, GDP per Capita") 

```

#### Step 2 - Choose a theme
* Choose white background with grid lines  

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

options(scipen=999)  # turn-off scientific notation like 1e+48

# Manual palette to match colors
continent_palette <- c("Africa" = "#A3DDF7", "Americas" = "#AAE828", "Asia" = "#DB616F", "Europe" = "#F6E71D", "Oceania" = "#DB616F")

ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  scale_x_log10(limits = range(df_1$gdp)) +
  geom_point(aes(size = population, color = continent)) +
  scale_size("population", range = c(2, 40)) +
  scale_color_manual(values = continent_palette) +
  geom_text_repel(data=filter(df_1, population > mean(population)),
                  aes(label = country, size = population / 2), 
                  family = "inconsolata") +
  ggtitle("World Health Chart 2019 by Gapminder") +
  ylab("Lifespan, Life Expectancy") +
  xlab("Income, GDP per Capita") +
  theme_bw() 

```

#### Step 3 - Further customize theme
* Control title text font, size...  
* Add line to delimit x and y axis  
* Remove borders and "minor" gridlines  
* remove legend  


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

options(scipen=999)  # turn-off scientific notation like 1e+48

# Manual palette to match colors
continent_palette <- c("Africa" = "#A3DDF7", "Americas" = "#AAE828", "Asia" = "#DB616F", "Europe" = "#F6E71D", "Oceania" = "#DB616F")

ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  scale_x_log10(limits = range(df_1$gdp)) +
  geom_point(aes(size = population, color = continent)) +
  scale_size("population", range = c(2, 40)) +
  scale_color_manual(values = continent_palette) +
  geom_text_repel(data=filter(df_1, population > mean(population)),
                  aes(label = country, size = population / 2), 
                  family = "inconsolata") +
  ggtitle("World Health Chart 2019 by Gapminder") +
  ylab("Lifespan, Life Expectancy") +
  xlab("Income, GDP per Capita") +
  theme_bw() +
  theme(
    # Control title text font, size...
    plot.title = element_text(color = "black", size = 14, face = "bold"),
    # Add line to delimit x and y axis
    axis.line.x = element_line(color="black", size = 1),
    axis.line.y = element_line(color="black", size = 1),
    # Remove borders and "minor" gridlines
    panel.border = element_blank(),
    panel.grid.minor = element_blank(),
    # remove legend
    legend.position='none'
  )

```

### Final version
* Adjust chart size from chunk properties  
* Save chart into object "v1" 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 1920/72, fig.height = 1080/72, out.width = "100%"}

options(scipen=999)  # turn-off scientific notation like 1e+48

# Manual palette to match colors
continent_palette <- c("Africa" = "#A3DDF7", "Americas" = "#AAE828", "Asia" = "#DB616F", "Europe" = "#F6E71D", "Oceania" = "#DB616F")

v1 <- ggplot(df_1, aes(x = gdp, y = life_expectancy)) +
  scale_x_log10(limits = range(df_1$gdp)) +
  geom_point(aes(size = population, color = continent)) +
  scale_size("population", range = c(2, 40)) +
  scale_color_manual(values = continent_palette) +
  geom_text_repel(data=filter(df_1, population > mean(population)),
                  aes(label = country, size = population / 2), 
                  family = "inconsolata") +
  ggtitle("World Health Chart 2019 by Gapminder") +
  ylab("Lifespan, Life Expectancy") +
  xlab("Income, GDP per Capita") +
  theme_bw() +
  theme(
    plot.title = element_text(color = "black", size = 14, face = "bold"),
    axis.line.x = element_line(color="black", size = 1),
    axis.line.y = element_line(color="black", size = 1),
    panel.border = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position='none'
  )

v1

```

### Save plot
#### as vector or raster image

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# As vector
ggsave(filename = "assets/gapminder.svg", plot = v1, width=1280/72, height=720/72)

# As raster
ggsave(filename = "assets/gapminder-sm.png", plot = v1, width=4, height=2.25)


```

