---
pagetitle: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Bubble Charts
## Story-Telling with Bubbles

```{r, fig.align="center", out.width="50%"}
masthead <- "assets/gapminder-fs.svg"
knitr::include_graphics(masthead, dpi=72)
```



A bubble chart is an extension of the scatter plot used to look at relationships between three numeric variables (x,y,z). Each dot in a bubble chart corresponds with a single data point. The first two dimensions (x, y) are visualized as coordinates on the x-axis and y-axis.The third dimension (z) is represented by size. A fourth dimension (categorical or numerical) can also be added through the color of the bubbles. The bubbles are oftentimes labelled.

Features that can be interpreted from a Bubble Chart:

* __Outliers__ : Data that doesn't fit the others in the dataset or its patterns.
* __Gaps__ : intervals that contains no data.
* __Clusters__ : isolated groups of data bubbles which follows the same characteristics.
* __Relationships__ : show relationships between three or four variables but not their exact values.

