---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48


# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden 
gc() #free up memory and report the memory usage.


library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Bubble Charts
## Story-Telling with Bubbles

```{r, fig.align="center", out.width="50%"}
masthead <- "assets/gapminder-fs.svg"
knitr::include_graphics(masthead, dpi=72)
```



A bubble chart is an extension of the scatter plot used to look at relationships between three numeric variables (x,y,z). Each dot in a bubble chart corresponds with a single data point. The first two dimensions (x, y) are visualized as coordinates on the x-axis and y-axis.The third dimension (z) is represented by size. A fourth dimension (categorical or numerical) can also be added through the color of the bubbles. The bubbles are oftentimes labelled.

Features that can be interpreted from a Bubble Chart:

* __Outliers__ : Data that doesn't fit the others in the dataset or its patterns.
* __Gaps__ : intervals that contains no data.
* __Clusters__ : isolated groups of data bubbles which follows the same characteristics.
* __Relationships__ : show relationships between three or four variables but not their exact values.


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}
# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "bubble" # mostly used in wranglers and analytics
keywords <- ''
commands <- ''
sources <- ''
# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())
# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())
```

```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

