---
pagetitle: "Transit Costs"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Transit Costs
## Bubble Chart

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Ricardo Gomez Angel on Unsplash"}

masthead <- "assets/ricardo-gomez-angel-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> It's not where you start but where you finish...\
--- April Heinrichs\

***

This example is based on the work of the __Transit Project__ using their database that spans more than 50 countries and totals more than 11,000 km of urban rail built since the late 1990s.

### Ingest data
#### country, city, line, start_year, end_year, time_comp, length, cost, etc.

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# file path parameter
df_file_path <- "archetypes/transit-costs/transit-costs.csv"
df <- read.csv(df_file_path, header = TRUE, stringsAsFactors = FALSE)
df

```

### Wrangle data
#### mutate, filter, and enrich

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_wrangle <- 
    df %>% 
    mutate(real_cost_n = as.double(real_cost),
        time_comp = as.numeric(end_year)-as.numeric(start_year)) %>% 
    filter(!is.na(city) | real_cost_n > 0) %>% 
    rename(iso2c=country)

df_wrangle <- df_wrangle %>% 
    left_join(countrycode::codelist %>% select(iso2c, country.name.en), by='iso2c') %>% 
    rename(country=country.name.en)

df_wrangle$continent <- countrycode(df_wrangle$iso2c, "iso2c", "continent")
df_wrangle <- df_wrangle %>% select(continent, country, city, line, start_year, end_year, time_comp, length, real_cost_n)

df_wrangle

```

### Bubble Chart
#### with loess smoothing (hover over points for additional details)

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 1920/72, fig.height = 1080/72, out.width = "100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.title = element_text(color = "black", size = 14, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 8),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor = element_blank(), # remove minor gridlines
    # panel.grid.major.x = element_blank(), # remove x (vertical) gridlines
    # panel.grid.major.y = element_blank(), # remove y (horizontal) gridlines
    legend.title = element_blank(), # remove legend title
    # legend.text = element_text(color = "black", size = 8),
    legend.position='none'
)

continent_palette <- c(
  "Africa" = "#0F894A",
  "Americas" = "#3499CC",
  "Asia" = "#F15A63",
  "Europe" = "#173552",
  "Oceania" = "#FFC53E",
  "NA" = "#999999"
)

v1 <- ggplot(data = df_wrangle, aes(y = real_cost_n, x = length)) +
    geom_smooth(method = 'loess', formula = 'y ~ x', color='#F0F0F0', fill="#F0F0F0") +  
    geom_point_interactive(aes(size = time_comp, fill = continent, 
                           tooltip = paste0("Continent: ", continent, "\n", 
                                            "Country: ", country, "\n", 
                                            "City: ", city, "\n", 
                                            "Line: ", line, "\n", 
                                            "Start year: ", start_year, "\n", 
                                            "End year: ", end_year, "\n", 
                                            "Time Comp: ", time_comp, "\n", 
                                            "Length: ", length, "\n",
                                            "Real cost: ", real_cost_n), data_id = row.names(df_wrangle)), 
                           shape = 21, color = "#FFFFFF", stroke = 1.0, alpha = 0.6) +
    scale_x_continuous(labels = scales::unit_format(suffix = 'km')) +
    scale_y_log10(labels = scales::dollar) +
    scale_fill_manual(values = continent_palette) +
    annotation_logticks(sides = 'l') +
    scale_size_area(max_size = 10) +
    labs(title = "Transit Costs",
        subtitle = "color by continent, size by time to complete",
        x = 'Length',
        y = 'Real Cost in Millions of USD',
        caption = "Source:Transit Costs Project")+
    theme_minimal() +
    theme_opts


girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "assets/transit-costs-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "assets/transit-costs-sm.png", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative sources: John Mutiso, TidyTuesday, [GO](https://github.com/johnmutiso/-TidyTuesday/tree/master/2021/week%202){target="_blank"}
* Data sources: Transit Costs Project, [GO]( https://transitcosts.com/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
