---
pagetitle: "Commonwealth War Dead"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dev = "svg" )
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(stringr)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()
 
```

<div class="activity">
WRANGLERS  
</div>

# Commonwealth War Dead
## Separate a column

```{r, out.width="50%", fig.align="center",out.height="50%", fig.cap="Photo by Razi Purjafarian on Unsplash"}

masthead <- "assets/razi-purjafarian-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Never think that war, no matter how necessary, nor how justified, is not a crime.\
--- Ernest Hemingway\

***

### Ingest the data
Surname, forename, DateOfDeath

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "commonwealth-war-dead/casualty-search.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = FALSE)
df

```


### Wrangle
Separate a column into multiple columns using <kbd>separate()</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

#Selecting only certain columns
df1 <- df %>% select(Surname,Forename,DateOfDeath)

#splitting dateofdeath column into day,month, and year columns
df2 <- df1%>%separate(DateOfDeath, c('day','month','year'),"/")
df2

```

Another useful function to split a column into separate columns is <kbd>str_split_fixed()</kbd> in <kbd>stringr</kbd> package

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

#splitting Forename into First name and middle name
df4 <- df2
new_df <- as.data.frame(str_split_fixed(df4$Forename," ",2))
colnames(new_df) <- c("First Name","Middle Name")
df4 <- cbind(df4,new_df)
df4 <- df4[,c("Surname","First Name","Middle Name")]
df4

```

### References
#### Citations and data sources

* Narration and data: Walk Free, [GO](https://www.cwgc.org/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```







