---
pagetitle: "Drone Privacy Laws"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


<div class="activity">
WRANGLERS 
</div>

# Drone privacy laws
## Combine columns


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Jason Blackeye on Unsplash"}

masthead <- "assets/jason-blackeye-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> There are drones flying over the air randomly that are recording everything that's happening on what we consider our private  property. That type of technology has to stimulate us to think about what is it that we cherish in privacy, and how far we want to protect it and from whom...\
--- Sonia Sotomayor\

***

### Ingest
country, continent, legal status

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

#Load data
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "drone-privacy-laws/drone-privacy-laws.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = FALSE)
df

```


### Wrangle
Combine columns country and continent using <kbd>unite()</kbd> function from <kbd>tidyr</kbd> package

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

#renaming first column
names(df)[1] <- "Country"

#combining columns
df1 <- df %>% unite('country_region',Country,Continent, sep = "_", remove = TRUE, na.rm = FALSE )
df1

```


Combine using <kbd>paste()</kbd> function from base <kbd>R</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

#combining columns
df2 <- df
df2$country_region <- paste(df$Country, df$Continent, sep="_")
df2

```


### References
#### citations for narrative and data sources

* Narrative and Data Source: Visual Capitalist, Mapped: Drone Privacy Laws Around the World, [GO](https://www.visualcapitalist.com/mapped-drone-privacy-laws-around-the-world/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```




