---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

library(tidyverse)


library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


<div class="activity">
WRANGLERS 
</div>

# Greenhouse Gas (GHG) emission by country
## Rename a column


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Marcin Jozwiak on Unsplash"}

masthead <- "assets/marcin-jozwiak-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Climate change is no longer some far-off problem; it is happening here,
it is happening now...\
--- Barack Obama\

***

### Ingest data 
producing and consuming countries, GHG emissions, 

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

#Load data
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "ghg-emissions-by-country/ghg-emissions-by-country.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = TRUE)
df


```

### Wrangle
Rename column using <kbd>Column Name</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df1 <- df

#remove "." from the column names
names(df1)[names(df1) == 'Producing.countries'] <- "Producing countries"
names(df1)[names(df1) == 'Consuming.countries'] <- "Consuming countries"
names(df1)[names(df1) == 'GHG.emissions'] <- "GHG emissions"
df1


```

Using <kbd>Column index</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df2 <- df

#rename the first column
names(df2)[1] <- "Producing Countries"
df2


```


### References
#### citations for narrative and data sources

* Narrative and data sources: Engage The Chain [GO](https://engagethechain.org/investor-guide-deforestation-and-climate-change){target="_blank"}
