---
pagetitle: "Global Slavery Index"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, dev = "svg" )
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()
 
```

WRANGLERS  

# Global Slavery Index
## Rename column

```{r, out.width="30%", fig.align="center",out.height="30%", fig.cap="Photo by Hermes Rivera on Unsplash"}

masthead <- "assets/hermes-rivera-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Those who deny freedom to others, deserve it not for themselves.\
--- Abraham Lincoln\

***

### Ingest the data
country, gdp per capita based on PPP, and government response score

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "global-slavery-index/data.csv"
url <- paste0(url_root, url_file)

df_slavery <- read.csv(url, header = TRUE, stringsAsFactors = FALSE)
df_slavery

```


### Wrangle
Rename all columns using <kbd>gsub()</kbd> and <kbd>regex</kbd>


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

#Renaming column names
df1 <- df_slavery
colnames(df1) <- gsub("\\.|\\_", " ",colnames(df1))
df1


```

Another approach
\
Convert all columns using <kbd>rename_with()</kbd> and <kbd>gsub()</kbd>


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df2 <- df_slavery

#rename_with() renames columns using a function
df2 <- df2 %>%  rename_with(~ gsub('[[:punct:]]',' ',.x))
df2

```


### References
#### Citations and data sources

* Narration and data: Walk Free, [GO](https://www.globalslaveryindex.org/){target="_blank"}
