---
pagetitle: "Life Satisfaction vs GDP"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)
library(data.table)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# Life Satisfaction vs GDP
## Rename multiple columns

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Peter Conlan on Unsplash"}

masthead <- "assets/peter-conlan-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Happiness is a journey, not a desitnation...\
--- Buddha\

***

GDP is an important indicator as higher economic output is usually associated with higher household income. Higher income mean families can spend more on the things they value. Meanwhile, it means governments have a greater capacity to provide public services. As a result, higher GDP per capita is often associated with positive outcomes in wide range of areas such as better health, more education, and even greater life satisfaction. 


### Ingest the data
life satisfaction, gdp, and population by country and year

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load csv data file
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "life-satisfaction-vs-gdp/life-satisfaction-vs-gdp.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = FALSE)
df

```


### Wrangle
Rename multiple columns using <kbd>Column index</kbd> 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df1 <- df

#rename columns with "_"
names(df1)[4:5] <- c("Life Satisfaction","GDP per Capita PPP")
df1

```
Another approach
\
Rename columns using <kbd>rename()</kbd> 


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df2 <- df

#rename first 3 columns to uppercase
df2 <- df2 %>% rename(ENTITY = Entity, CODE = Code, YEAR = Year)
df2


```

Using <kbd>setnames</kbd> from <kbd>data.table</kbd> package

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df3 <- df

#change all the columns to upper case and remove "_"
setnames(df3, old = c("Entity","Code","Year","Life_Satisfaction","GDP_per_Capita_PPP","Population"), new = c("ENTITY","CODE","YEAR","LIFE SATISFACTION","GDP PER CAPITA PPP","POPULATION"))
df3


```


### References
#### citations for narrative and data sources

* Narrative and Data Source: Our World in Data, Self-reported Life Satisfaction vs GDP per capita, 2020, [GO](https://ourworldindata.org/happiness-and-life-satisfaction){target="_blank"}
