---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS   
</div>

# Manage Column
## Rename, add, unite, separate, and populate

```{r, out.width="20%", fig.align="center"}

masthead <- "assets/noun_column_2658409.svg"
knitr::include_graphics(masthead, dpi=72)

```


The column characteristics and structure of a data set provide the basis for accessing specific features. There are often cases when columns needed to be manipulated to accomplish a specific analytic or visualization objective. For example, columns can be combined to form a unique identifier or serve as a label in a visualization.

These are the key solutions that comprise the column task:

* __constant value__: create and populate a column with a set value
* __rename__: rename one, some, or all fields to simplify or standardize
* __separate__: pulls apart one column into multiple columns, by splitting wherever a separator character appears
* __unite__: combines multiple columns into a single column with a specified delimiter


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "column add-constant combine rename rename-all rename-replace select seperate" # mostly used in wranglers and analytics
keywords <- ''
commands <- ''
sources <- ''

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```

```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

