---
pagetitle: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS   

# Manage Column
## Rename, add, unite, separate, and populate

```{r, out.width="20%", fig.align="center"}

masthead <- "assets/noun_column_2658409.svg"
knitr::include_graphics(masthead, dpi=72)

```


The column characteristics and structure of a data set provide the basis for accessing specific features. There are often cases when columns needed to be manipulated to accomplish a specific analytic or visualization objective. For example, columns can be combined to form a unique identifier or serve as a label in a visualization.

These are the key solutions that comprise the column task:

* __constant value__: create and populate a column with a set value
* __rename__: rename one, some, or all fields to simplify or standardize
* __separate__: pulls apart one column into multiple columns, by splitting wherever a separator character appears
* __unite__: combines multiple columns into a single column with a specified delimiter
