---
pagetitle: "Percentage of Females Married by 18"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)
library(data.table)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  


# Percentage of females married by 18
## Constant value column

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Ben Waardenburg on Unsplash"}

masthead <- "assets/ben-waardenburg-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> We should be respectful but we must also have the courage to stop harmful practices that impoverish girls, women and their communities...\
--- Graca Machel (Women and children's right activist)\

***

### Ingest
country, females married by 18, males married by 18

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "child-marriage-bar-dot/Child_Marriage.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url)
df

```

### Wrangle
Add a constant value column using <kbd>add_column</kbd> 


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df1 <- add_column(df,new_col=("Let kids be kids"))
df1

```

Using <kbd>mutate()</kbd> from <kbd>dplyr</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df2 <- df %>%  mutate(new_col = "Let kids be kids")
df2

```
  
  
### References
#### citations for narrative and data sources

* Narrative sources: Visualize Gender Equality - Help us end child marriage, [GO](https://media.data.world/1o2xvmj7TLCDfJPErISo_Child%20Marriage%20Dasbboard.png){target="_blank"}
