---
pagetitle: "Percentage of Females Married by 18"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(data.table)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()


```

<div class="activity">
WRANGLERS  
</div>


# Percentage of females married by 18
## Constant value column

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Ben Waardenburg on Unsplash"}

masthead <- "assets/ben-waardenburg-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> We should be respectful but we must also have the courage to stop harmful practices that impoverish girls, women and their communities...\
--- Graca Machel (Women and children's right activist)\

***

### Ingest
country, females married by 18, males married by 18

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "child-marriage-bar-dot/Child_Marriage.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url)
df

```

### Wrangle
Add a constant value column using <kbd>add_column</kbd> 


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df1 <- add_column(df,new_col=("Let kids be kids"))
df1

```

Using <kbd>mutate()</kbd> from <kbd>dplyr</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df2 <- df %>%  mutate(new_col = "Let kids be kids")
df2

```
  
  
### References
#### citations for narrative and data sources

* Narrative sources: Visualize Gender Equality - Help us end child marriage, [GO](https://media.data.world/1o2xvmj7TLCDfJPErISo_Child%20Marriage%20Dasbboard.png){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


