---
pagetitle: "Baboon Mating"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE, dev='svg')
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(ggraph)
library(igraph)
library(graphlayouts)
library(tidygraph)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
GRAPHS
</div>

# Baboon mating
## Node-links - Association

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Igal Ness on Unsplash"}

masthead <- "assets/igal-ness-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Baboons have the exact physiology as humans do...\
--- Robert Sapolsky\

***

### Ingest
#### border graph

This dataset contains over 12,000 observations of the following variables:

* female_id: three letter "short name" ID for the female in a potentially consorting pair; each female has a unique ID
* male_id: three letter "short name" ID for the male in a potentially consorting pair; each male has a unique ID
* consort: whether the female-male pair consorted (1) or not (0), given the opportunity to do so
* conceptive: whether the estrus cycle resulted in a conception (1) or not (0)


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_path <- "archetypes/baboon-mating/baboon-mating.csv"
df <- read.csv(df_path, header = TRUE, stringsAsFactors = FALSE)
df

```


### Prepare data [Wrangle]
#### Filtering only a few countries of our interest

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_wrangle <- df %>% select(female_id, male_id, consort, conceptive)
df_wrangle <- filter(df_wrangle, consort == 1)
df_wrangle

```



```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_wrangle <- df_wrangle %>% rename(from='female_id', to='male_id')
df_wrangle

```


### Prepare data [Wrangle]
#### Format the data into a graph data frame 


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Convert data to graph data frame
# directed FALSE means no flow. It's just an association
g <- graph.data.frame(df_wrangle, directed = FALSE)
g

```


### Prepare data [Wrangle]
#### Associating different attributes for your Nodes 

Creating numerical fields for the Nodes set in order to attribute the nodes size and/or color  

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}
## Creating centrality numerical field for the Nodes

# centrality_alpha()
# centrality_authority() 
# centrality_betweenness() 
# centrality_power() 
# centrality_closeness() 
# centrality_eigen() 
# centrality_hub() 
# centrality_pagerank() 
# centrality_subgraph() 
# centrality_degree() 
# centrality_edge_betweenness() 
# centrality_manual() 
# centrality_closeness_harmonic() 
# centrality_closeness_residual() 
# centrality_closeness_generalised() 
# centrality_communicability() 
# centrality_communicability_odd() 
# centrality_communicability_even() 
# centrality_subgraph_odd() 
# centrality_subgraph_even() 
# centrality_katz() 
# centrality_betweenness_network() 
# centrality_betweenness_current() 
# centrality_betweenness_communicability() 
# centrality_betweenness_rsp_simple() 
# centrality_betweenness_rsp_net() 
# centrality_information() 
# centrality_decay() 
# centrality_random_walk() 
# centrality_expected()

df_graph <- g %>% 
    as_tbl_graph() %>% 
    activate(nodes) %>% 
  # associating random numerical value to nodes to differentiate their colors and sizes
    mutate(centrality  = centrality_betweenness())



```


### Prepare data [Wrangle]
#### Associating different attributes for your Nodes


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

## Creating group numerical field for the Nodes

# group_components() 
# group_edge_betweenness() 
# group_fast_greedy() 
# group_infomap() 
# group_label_prop() 
# group_leading_eigen() 
# group_louvain() 
# group_optimal() 
# group_spinglass() 
# group_walktrap() 
# group_biconnected_component()

df_graph <- df_graph %>% 
  activate(nodes) %>%
  # use functions to compute numerical values to attribute the edge width and/or color
  mutate(group = group_louvain())

df_graph

```


## Associating different attributes for the Edges between Nodes 
### Creating new numerical fields (smaller values) in order to attribute the edge width and/or color  


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_graph <- df_graph %>% 
    activate(edges) %>% 
  # computing random number (n) which are between 0 and 1 to attribute the edge width and/or color
    #mutate(edge_weights = runif(n()))
  ## computes numbers between 0 and 1 according to distance in km
  mutate(edge_weights = conceptive)

df_graph


```


## Layout & Aesthetic Parameters
### Choose the types of Edges you would like to display


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# igraph layouts

# bipartite <- create_layout(df_graph, layout = 'igraph', algorithm = 'bipartite')
# circle <- create_layout(df_graph, layout = 'igraph', algorithm = 'circle')
# dh <- create_layout(df_graph, layout = 'igraph', algorithm = 'dh')
# drl <- create_layout(df_graph, layout = 'igraph', algorithm = 'drl')
# fr <- create_layout(df_graph, layout = 'igraph', algorithm = 'fr')
# gem <- create_layout(df_graph, layout = 'igraph', algorithm = 'gem')
# graphopt <- create_layout(df_graph, layout = 'igraph', algorithm = 'graphopt')
# grid <- create_layout(df_graph, layout = 'igraph', algorithm = 'grid')
# kk <- create_layout(df_graph, layout = 'igraph', algorithm = 'kk')
# lgl <- create_layout(df_graph, layout = 'igraph', algorithm = 'lgl')
# mds <- create_layout(df_graph, layout = 'igraph', algorithm = 'mds')
# nicely <- create_layout(df_graph, layout = 'igraph', algorithm = 'nicely')
# sphere <- create_layout(df_graph, layout = 'igraph', algorithm = 'sphere')
# star <- create_layout(df_graph, layout = 'igraph', algorithm = 'star')
# sugiyama <- create_layout(df_graph, layout = 'igraph', algorithm = 'sugiyama')

# ggraph layouts

# backbone <- create_layout(df_graph_undirected, layout = 'backbone')

# centrality_bc <- betweenness(df_graph_directed)
# centrality_cc <- closeness(df_graph_directed)
# centrality <- create_layout(df_graph_undirected, layout = 'centrality', centrality = centrality_bc)

# circlepack <- create_layout(df_graph_directed, layout = 'circlepack')
# dendrogram <- create_layout(df_graph_directed, layout = 'dendrogram')
# eigen <- create_layout(df_graph, layout = 'eigen', type = "laplacian", eigenvector = "smallest")

# fabric <- create_layout(cg, layout = 'fabric')
# focus <- create_layout(df_graph_directed, layout = 'focus', focus = 1)

# hive <- create_layout(df_graph, layout = 'hive', axis = friends, sort.by = degree)

# linear <- create_layout(df_graph, layout = 'linear')
# matrix <- create_layout(df_graph, layout = 'matrix')
# partition <- create_layout(df_graph_directed, layout = 'partition')

# pmds_pivots <- 3
# pmds <- create_layout(df_graph, layout = 'pmds', pivots = pmds_pivots)

stress <- create_layout(df_graph, layout = 'stress')
# sunburst <- create_layout(df_graph_directed, layout = 'partition', circular = TRUE)
# treemap <- create_layout(df_graph_directed, layout = 'treemap')

# df_unrooted <- df_graph_undirected %>%  activate(edges) %>%  mutate(length = runif(n()))
# unrooted <- create_layout(df_graph_undirected, layout = 'unrooted' )

```


## Layout & Aesthetic Parameters
### Choose the types of Edges you would like to display


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Edge Types
# geom_edge_arc
# geom_edge_arc0
# geom_edge_arc2
# geom_edge_density
# geom_edge_diagonal
# geom_edge_diagonal0
# geom_edge_diagonal2
# geom_edge_elbow
# geom_edge_elbow0
# geom_edge_elbow2
# geom_edge_fan
# geom_edge_fan0
# geom_edge_fan2
# geom_edge_hive
# geom_edge_hive0
# geom_edge_hive2
# geom_edge_link
# geom_edge_link0
# geom_edge_link2
# geom_edge_loop
# geom_edge_loop0

```



### Plot
#### nicely

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    # plot.margin = unit(c(1.5,1,1,1), "in"),
    legend.position='none'
)

v1 <- ggraph(stress) + 
  geom_edge_link(aes(colour = factor(conceptive))) +
  geom_node_point(aes(color = group, size = centrality)) +
  geom_node_text(aes(label = name)) +
  scale_color_gradient(low = "green", high = "blue", na.value = NA) +
  scale_size(range = c(1,6)) +
  theme_graph()+
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)


```


### References
#### citations for narrative and data sources

* Narrative and Data: Kaggle, Baboon Mating and Conception Probability by Age, https://www.kaggle.com/kinguistics/baboon-mating-and-conception-probability-by-age/data

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


