---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: libs

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE,
   dev = "svg")
options(scipen=999)  # turn-off scientific notation like 1e+48

library(htmltools) # needed to include html snippets
library(knitcitations)
library(bibtex)
library(changepoint)
library(ggiraph)

```

<div class="activity">
ANALYTICS 
</div>

# Change

Detect a single change point or multiple change points in time series data sets where trends break or abrupt shifts occur. 

## Library: changepoint

## Further self-study resources:

* https://cran.r-project.org/web/packages/changepoint/changepoint.pdf
* https://www.youtube.com/watch?v=WelmlZK5G2Y&ab_channel=NHSRCommunityNHSRCommunity
* https://www.coursera.org/learn/machine-learning

## Methods:

* At Most One Change (AMOC)
* Binary Segmentation (BinSeg)
* Segment Neighborhood (SegNeigh)
* Pruned Exact Linear Time (PELT)

## r functions:

* Mean

```{r echo=TRUE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, class.source='fold-hide'}

set.seed(1)
data = c(rnorm(100,0,1), rnorm(100,5,1))
m = cpt.mean(data)
plot(m)
cpts(m)

param.est(m)

```


* Variance

```{r echo=TRUE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, class.source='fold-hide'}

set.seed(1)
data = c(rnorm(100,0,1), rnorm(100,0,3), rnorm(100,0,10))
v = cpt.var(data, method = 'PELT')
plot(v)
cpts(v)

param.est(v)

```

* Mean and Variance

```{r echo=TRUE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, class.source='fold-hide'}

set.seed(1)
data = c(rnorm(100,5,1), rnorm(100,5,10), rnorm(100,2,3))
mv=cpt.meanvar(data, method = 'BinSeg')
plot(mv)
cpts(mv)

param.est(mv)

```

***

# Case(s)

* US Border Crossing Entry




```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

