---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: libs

---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE,
   dev = "svg")
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(knitcitations)
library(bibtex)
library(changepoint)
library(tidyverse)
library(rvest)
library(ggplot2)
library(dplyr)
library(tabulizer)
library(pdftools)
library(ggiraph)

```

<div class="activity">
ANALYTICS 
</div>

# Change
# Case: Houston Monthly Minimum Temperature 

## Anomaly detection is a process in Data Science that deals with identifying data points that deviate from a dataset’s usual behavior. Anomalous data can indicate critical incidents, such as financial fraud, a software issue, or potential opportunities, like a change in end-user buying patterns. 

***

# Load the data
## For this case, we extract the data from a pdf file, so extra steps maybe required.

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}


df <- extract_tables("./archetypes/houston temp.pdf",
             output = "data.frame", guess = FALSE
             )

df <- reduce(df, bind_rows)
df <- df[-c(1,56:62,118:124, 129:134),]

df1 <- df[1:54,1:6]
df2 <- df[55:113,1:13]

foo <- data.frame(do.call('rbind', strsplit(as.character(df1$X.2),' ',fixed=TRUE)))
df1 <- cbind(df1, foo)
df1 <- df1 %>% select(-c(X.2,X.3,X.4),X.3, X.4)
names(df1) <- df1[1,]
df1 <- df1[-1,]
names(df2) <- names(df1)


df <- rbind(df1,df2)
head(df)

```

# Wrangle the data
## Our dataframe is in a wide form. We will need to pivot it to a long form.

```{r message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

temp <- df

temp <- temp %>% pivot_longer(!Year, names_to = 'Month', values_to='Temperature')
temp <- temp[1:1338,]

temp$Month <- match(temp$Month, month.abb)
temp <- within(temp, Date <- sprintf("%s-%02d-01", Year, Month))


temp <- temp %>% select(Date, Temperature)
temp$Date <- as.Date(temp$Date)
temp$Temperature <- as.numeric(temp$Temperature)
head(temp)
```

# Year 2000 - 2021
## We will subset the data and plot it to have a clearer picture first.


```{r message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show', fig.height=6, fig.width=12}

temp00 <- temp[1081:1338,]

p1 <- ggplot(temp00, aes(x=Date, y=Temperature)) +
  geom_line() + 
  xlab("")
girafe(ggobj = p1, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


# Anomaly Detection.
## This Anomaly package was created by Twitter to find anomalies in timeseries.

* alpha: is a parameter that is used to control the size of the bands. If we decrease alpha, it increases the bands making it more difficult to be an outlier.

* max_anoms: is a parameter used to control the maximum percentage of data that can be an anomaly.

```{r echo=TRUE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, class.source='fold-show'}

library(AnomalyDetection) #install.packages("devtools")  # devtools::install_github("twitter/AnomalyDetection")

ano <- AnomalyDetectionVec(temp00$Temperature, period = 12, max_anoms=0.1, alpha=0.05,  direction = 'both', plot = T)
ano$anoms
y <- ano$anoms[,1]


for(i in y){
  print(paste0('Anomaly Dates and Temperature :' , temp00$Date[i], '   ', temp00$Temperature[i]))
}

ano$plot
```




# We will use another Anomaly Detection Package which analyzes the timeseries in more details 

```{r echo=TRUE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, class.source='fold-show'}
temp0 <- as_tibble(temp00)

library(anomalize)

df_anomalized <- temp0 %>%
    time_decompose(Temperature, merge = TRUE) %>%
    anomalize(remainder, alpha = 0.05, max_anoms = 0.2) %>%
    time_recompose() %>%
    plot_anomalies(time_recomposed = TRUE) +
    ggtitle("Minimum Temperature of Houston")

girafe(ggobj = df_anomalized, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


## The package has a decomposition feature for further analysis.

```{r echo=TRUE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, class.source='fold-hide'}

temp0 %>%
    time_decompose(Temperature, merge = TRUE) %>%
    anomalize(remainder, alpha = 0.05, max_anoms = 0.2) %>%
    time_recompose() %>%
    plot_anomaly_decomposition() +
    ggtitle("Decomposition into Trend, Season, Residual")
temp0
```



# Year 1910 - 2021

## We now move on to the entire dataset. Let's Plot the Data first to understand it better.

## Notice that it gets harder to visually eye-ball the time series. 

```{r message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.height=6, fig.width=12}


p2 <- ggplot(temp, aes(x=Date, y=Temperature)) +
  geom_line() + 
  xlab("")
girafe(ggobj = p2, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


# library(AnomalyDetection)

```{r echo=TRUE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, class.source='fold-hide'}



ano <- AnomalyDetectionVec(temp$Temperature, period = 12, max_anoms=0.4,  direction = 'both', plot = T)
x <- ano$anoms[,1]

for(i in x){
  print(paste0('Anomaly Dates :' , temp$Date[i], temp$Temperature[i]))
}

ano$plot
```


# library(anomalize)

```{r echo=TRUE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, class.source='fold-hide'}

df3 <- as_tibble(temp)



df_anomalized <- df3 %>%
    time_decompose(Temperature, merge = TRUE) %>%
    anomalize(remainder) %>%
    time_recompose()


df_anomalized %>% plot_anomalies(ncol = 3, alpha_dots = 0.75)

p3 <- df_anomalized %>%
    plot_anomaly_decomposition() +
    ggtitle("Freq/Trend = 'auto'")
girafe(ggobj = p3, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```

# Extracting the Anomalous Data Points

```{r echo=TRUE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, class.source='fold-hide'}
df3 %>% 
  time_decompose(Temperature) %>%
  anomalize(remainder) %>%
  time_recompose() %>%
  filter(anomaly == 'Yes')


```





# References
## The data source is from [National Weather Service Forecast](https://w2.weather.gov/climate/xmacis.php?wfo=hgx)




```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
