---
title: "Economic Value of Peace"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(textreadr)
library(readr)

library(tidytext)
library(ggtext)
library(pdftools)


library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
INGEST  
</div>

# Economic value of peace, 2021
## ingest a pdf document

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Kyle Glenn on Unsplash"}

masthead <- "assets/kyle-glenn-nXt5HtLmlgE-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


>The first lesson of economics is scarcity: there is never enough of anything to fully satisfy all those who want it. The first lesson of politics is to disregard the first lesson of economics.\
---Thomas Sowell\


***

### Ingest a pdf

Ingest for all pages (click right hand arrow to see text)


```{r load-data, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}


url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "economic-value-of-peace/economic-value-of-peace-2021.pdf"
url <- paste0(url_root, url_file)

pdf_file <- url

readpdf <- 	read_pdf(url)
readpdf


```

now let's skip the first 10 lines
```{r , echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}


readpdf10 <- 	read_pdf(url, skip =10)

readpdf10

```

### References
#### citations for narrative and data sources

* Narrative and Data Source: Institute for Economics and Peace (IEP) |    [GO](https://reliefweb.int/report/world/economic-value-peace-2021-measuring-global-economic-impact-violence-and-conflict){target="_blank"}



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```

```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
