---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

INGEST  


# Ingest a text file
## Workbooks, worksheets, and spreadsheets

```{r, out.width="40%", fig.align="center", fig.cap="Photo by JunGSa, ID"}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "assets/pdf.png"
knitr::include_graphics(masthead, dpi=72)
```

> If I had a spreadsheet on my computer, it looked like I was busy...\
--- Nate Silver\

This task refers to the ingest of __unstructured text__, meaning text in a file that does not have a delimiter or discernible data structure.  A common form would be __narrative__ text such as documents, messages, and other forms of written language.

To illustrate the methods, this case contains several text files for Ghana's state of the nation addresses. The state of the nation address is an annual address to parliament given by the president. It typically summarizes the government's agenda and the progress made in the past year as seen by the administration in power.

The case provides various methods to ingest the files and make them available for subsequent processing.

***

# Case(s)

* ...
