---
pagetitle: "Pandas in Zoos"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Pandas in Zoos
## Clean Data


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Michael Payne on Unsplash"}

masthead <- "assets/michael-payne-jkBvXKwr4MY-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">It's time for lunch</div>

> Never give up on your dreams... Keep Sleeping!...\
--- Probably a Panda\

***

### Load the data

```{r load-data, echo=TRUE, message=FALSE, warning=FALSE,class.source = 'fold-hide'}
# Load data
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "panda-list/panda-list.csv"
url <- paste0(url_root, url_file)

df <- read_csv(url, col_names=TRUE)
df

```

### Wrangle
#### Replace the missing value using <kbd>is.na()</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

#Replace the missing record (NA) from Loan_Expire_Date with a value
df_1 <- df
df_1[is.na(df_1$Loan_Expire_Date),]$Loan_Expire_Date <- "01/01/2030" 
df_1

```

### References
#### citations for narrative and data sources

* Narrative and Data sources: Giant Panda Global website, [GO](https://www.giantpandaglobal.com/){target="_blank"}

<!-- or -->

<pre>
@misc{jeroen_2000_giantpandaglobalcom,
  author = {Jeroen, Jacobs},
  month = {10},
  title = {GiantPandaGlobal.com},
  url = {https://www.giantpandaglobal.com/},
  year = {2000},
  organization = {GiantPandaGlobal.com}
}
</pre>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


