---
pagetitle: "Road deaths by country"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS 
</div>

# Road deaths by country
## Clean Data

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Yannis H on Unsplash"}

masthead <- "assets/yannis-h-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Some car accidents are caused by the ignorance or disbelief of the fact\
  that a driver’s eyes and mind can be thousands of kilometres apart...\
--- Mokokoma Mokhonoana\

***


### Ingest the data
#### Load GDP Dataset 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

#Load
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"

url_file1 <- "road-deaths-by-country/gdp.csv"
url1 <- paste0(url_root, url_file1)

df_gdp <- read.csv(url1, header = TRUE, stringsAsFactors = FALSE, encoding = "UTF-8")
df_gdp

```
### Wrangle the data
#### Replace value "NA" with "Not Applicable" using <kbd>is.na()</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

#Replacing one value with another 
df_gdp[is.na(df_gdp)] = "Not Applicable"
df_gdp


```
### References
#### citations for narrative and data sources

* Data Source: World Health Organization, [GO](https://apps.who.int/gho/data/node.main.A997){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

