---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS 

# Where does your medicine come from?
## Remove missing value

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Benjamin Lehman on Unsplash"}

masthead <- "assets/benjamin-lehman-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Always laugh when you can. It is cheap medicine....\
--- Lord Byron\

***


### Ingest

exporter, year, usd value

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

#Load
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "where-does-your-medicine-come-from/data/drug_medicine_exports.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE)
df

```

### Wrangle

Remove records which contain missing values within a particular field/column using <kbd>is.na()</kbd> 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Remove missing record using is.na(), function returns the value of true for each data point that is NA.
df_1 <- df[!is.na(df$exports_usd),]
df_1 

```
Remove records which contain missing values within any field/column of the data set using <kbd>na.omit()</kbd> 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Remove missing record using na.omit(), function simply removes the rows of data containing the NA value
df_2 <- na.omit(df)
df_2 

```

### References
#### citations for narrative and data sources

* Narrative sources: Makeover Monday, [GO](https://data.world/makeovermonday/2018w8-where-does-your-medicine-come-from){target="_blank"}
* Data sources: ITC, TradeMap, [GO](https://www.trademap.org/Country_SelProduct_TS.aspx?nvpm=1%7c%7c%7c%7c%7cTOTAL%7c%7c%7c2%7c1%7c1%7c2%7c2%7c1%7c2%7c1%7c%7c1){target="_blank"}
