---
pagetitle: "Sunniest cities in the world"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

# Load needed libraries
library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS
</div>

# Sunniest cities in the world
## Replace duplicates

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Donald Giannatti D on Unsplash"}

masthead <- "assets/donald-giannatti-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Yuma, Arizona</div>


>  You are my Sunshine...\
--- Johnny Cash\

***

### Load the data

Where are the sunniest cities in the world?

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load data
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "sunniest-cities/sunniest_cities.csv"
url <- paste0(url_root, url_file)

df <- read_csv(url, col_names=TRUE)
df


```
### Wrangle

Identify the position of duplicate value using <kbd>duplicated()</kbd> 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# To locate the position of duplicate elements 
df1 <- duplicated(df)
df1

```
Replace the duplicate value using <kbd>replace()</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Replace duplicate records with another value
f_replace <- function(df_replace,value1,value2) {
  replace(df_replace, df_replace==value1, value2 )
}

# Call the function with your values to the parameters
f1 <- f_replace(df,"america","USA") 
f1
```
### References
#### citations for narrative and data sources

* Data sources: Wikipedia page - List of cities by sunshine duration, [GO](https://en.wikipedia.org/wiki/List_of_cities_by_sunshine_duration){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
