---
pagetitle: "Global Education Expenditure"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)

library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Global Education Expenditure
## Compare

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Annie Spratt on Unsplash"}

masthead <- "assets/annie-spratt-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Books and Education</div>


> Education is not preparation for life; education is life itself....\
--- John Dewey\


***

### Load the data

Real-life case: Global education expenditure.

```{r Load raw data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'} 

df <- read.csv('./archetypes/share-edu-spending-gdp-vs-share-edu-total-spending.csv', header = TRUE, stringsAsFactors = FALSE)
df

```

### The Side Set 

The following <span style="color: #01DFD7"> __Continent list__</span>  will be used to compare with the above data file records.


```{r reference list, echo=FALSE, message=FALSE}

list<-c('Africa','Asia','Europe')

list%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = c("striped", "hover"))%>%
column_spec(1, bold = TRUE, color = "#000000", background = "#A9F5F2")

```


### Intersect

This method helps you view the relevant information of education expenditure of only those countries from the same <span style="color: #F78181;font-weight:bold">Continents</span> as the <span style="color: #01DFD7;font-weight:bold">Continents</span> listed in the side set.


```{r Method: intersect, echo=TRUE, message=FALSE}

df_1 <-df[df$Continent %in% list,]
row.names(df_1)<-NULL

```

<!-- FOR DISPLAY ONLY -->

```{r Styling Data Set 1, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_1
names(df_tmp)[3] <- cell_spec(names(df_tmp)[3], color = "#F78181")

df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(3, bold = TRUE, color = "#000000", background = "#F5ECCE")%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)

```


### Difference

Whereas this method helps you view the opposite scenario: only the relevant information of education expenditure of those countries that are not located in the <span style="color: #01DFD7;font-weight:bold">Continents</span> listed in the side set.


```{r Method: difference, echo=TRUE, message=FALSE}
df_2 <-subset(df, !(Continent %in% list))
row.names(df_2)<-NULL

```

<!-- FOR DISPLAY ONLY -->

```{r Styling Data Set 2, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <-df_2
names(df_tmp)[3] <- cell_spec(names(df_tmp)[3], color = "#F78181")

df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(3, bold = TRUE, color = "#000000", background = "#F5ECCE")%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)
```


### References
#### citations for narrative and data sources 

* Narrative and Data sources: The data source used by this wrangler task is one of the baseline data used by the "Our World in Data" article called Financing Education, [GO](https://ourworldindata.org/financing-education){target="_blank"} 

<!-- or -->

<pre>
@misc{roser_2013_financing,
  author = {Roser, Max and Ortiz-Ospina, Esteban},
  title = {Financing Education},
  url = {https://ourworldindata.org/financing-education},
  urldate = {2021-03-04},
  year = {2013},
  organization = {Our World in Data}
}
</pre>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

