---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Compare
## Intersect, Difference

```{r, out.width="60%", fig.align="center", fig.cap="Photo by "}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
#masthead <- "assets/asses_name.png"
#knitr::include_graphics(masthead, dpi=72)

```

Comparing records is an easy way to filter in or filter out specific information against your data source. Before applying this task, you should ensure the following steps are taken:
  
  * Have a __side set__ of records (e.g. list, data file) to be compared with your data
* Ensure the __side set__ has the same data type as the data to be compared with

The methods __Intersect__ and __Difference__ help you achieve the __Compare__ task as follows:
  
  * __Intersect__ : Returns rows not contained in reference to compared. The resulting collection contains only the rows from the 1st collection that don't appear in the 2nd collection. This is essentially subtracting the rows from the 2nd collection from the 1st and creating a new collection with the remaining rows.
* __Difference__ : Returns rows contained in both compared.  The resulting collection contains the intersection of rows from the two input collections. These are only the rows that appear in both collections.


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "compare difference intersect" # mostly used in wranglers and analytics
keywords <- ''
commands <- ''
sources <- ''

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

