---
pagetitle: "Decline of the Landline"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(geofacet)
library(cowplot)
library(ggimage)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Decline of the Landline
## Tile Grid

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Sanjoy Saha on Unsplash"}

masthead <- "assets/sanjoy-saha-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Mr. Watson—Come here—I want to see you...\
--- Alexander Graham Bell, first words spoken on a telephone\

***

### Ingest
#### landline subscriptions

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

landline <- read.csv("archetypes/phone-subscriptions/landline-usage.csv", header = TRUE)
landline

```


### Ingest
#### mobile subscriptions


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

mobile <- read.csv("archetypes/phone-subscriptions/mobile-phone-usage.csv", header = TRUE)
mobile

```


### Wrangle
#### join, group, and summarize by decade


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

phones <- landline %>% 
  select(entity, year, landline_subs) %>% 
  left_join(mobile) %>% 
  mutate(decade = year %/% 10 * 10) %>% 
  group_by(entity, decade) %>% 
  mutate(
    median_landline_subs = median(landline_subs, na.rm = TRUE),
    median_mobile_subs = median(mobile_subs, na.rm = TRUE)
    ) %>% 
  ungroup() %>% 
  distinct(entity, code, decade, median_landline_subs, median_mobile_subs) %>% 
  group_by(entity) %>% 
  fill(code) %>% 
  ungroup() %>% 
  group_by(entity, decade) %>% 
  mutate(
    most = if_else(median_landline_subs > median_mobile_subs, "landline", "smartphone"),
    img = if_else(!is.na(most), paste0("archetypes/phone-subscriptions/", most, ".png"), NULL)
    ) %>% 
  ungroup() %>% 
  left_join(world_countries_grid1, by = c("entity" = "name"))

phones

```


### View
#### tiles with symbols by year


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.title = element_text(color = "black", size = 14, face = "bold", family = "inconsolata"),
    plot.subtitle = element_text(color = "black", size = 12, family = "inconsolata"),
    plot.caption = element_text(color = "#555555", size = 8, family = "inconsolata"),    
    plot.margin = margin(10, 10, 10, 10),
    plot.background = element_rect(fill = "grey97", color = NA)
)

v1 <- ggplot(phones) +
  geom_image(aes(col, -row - decade * 2.5, image = img), size = 0.014, asp = 0.8) +
  geom_text(aes(-8, -10 - decade * 2.5, label = paste0("'", str_sub(decade, -2, -1), "s")), size = 10, stat = "unique", family = "inconsolata", color = "black", alpha = 0.8) +
  labs(
    title = toupper("The fall of landline"),
    subtitle = "Indicating majority share of phone subscriptions (landline or mobile)\nas median values by country and decade"
    ) +
  coord_cartesian(clip = "off") +
  xlim(-14, 34) +
  theme_void() +
  theme_opts

girafe(ggobj = v1, width_svg = 12, height_svg = 16,
       options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```



### References
#### citations for narrative and data sources

* Data: OurWorldInData.org
* View: Georgios Karamanis


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
