---
pagetitle: "State of Global Air: PM 2.5"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(countrycode)
library(geofacet)
library(ggtext)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# State of Global Air: PM 2.5
## World Tile Grid


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Yaroslav Boshnakov on Unsplash"}

masthead <- "assets/yaroslav-boshnakov-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Environmental pollution is an incurable disease. It can only be prevented...\
--- Barry Commoner\


***

### Ingest
#### average PM 2.5 levels by country


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_soga <- read.csv("archetypes/state-of-global-air/soga-pm2.5-rank-0.csv", header = TRUE)
df_soga

```


### Wrangle
#### enrich with iso3c codes


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_soga_countries <- df_soga %>% select(Location, Average)

df_soga_countries$iso3c <- countrycode(df_soga_countries$Location, origin = "country.name", destination = "iso3c")

df_soga_countries

```


### Wrangle
#### enrich with grid coordinates


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

worldtilegrid <- read.csv("archetypes/world-tile-grid.csv", header = TRUE)
worldtilegrid <- worldtilegrid %>% select(alpha.3, x, y)

df_grid <- merge(df_soga_countries, worldtilegrid, by.x = "iso3c", by.y = "alpha.3")
df_grid

```


### View
#### sized tiles with conditional label colors


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.title = element_text(color = "black", size = 14, face = "bold", family = "inconsolata", hjust = 0.5),
    plot.subtitle = element_text(color = "black", size = 12, family = "inconsolata", hjust = 0.5),
    plot.caption = element_text(color = "#555555", size = 8, family = "inconsolata"),    
    plot.margin = margin(10, 10, 10, 10),
    plot.background = element_rect(fill = "#f5f5f5", color = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background=element_rect(fill="#f5f5f5", colour="#f5f5f5"),
    panel.border = element_blank(),
    axis.text = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    legend.position = "none"
)

df_grid_view <- df_grid %>% mutate(color = ifelse(Average < mean(Average), "black", "white"))

v1 <- ggplot(df_grid_view, aes(x = x, y = y)) +
    geom_point(aes( fill = Average, size = Average), shape = 21, color = "white", stroke = 1.5) +
    geom_text(aes(label = iso3c, color = color), size = 3, vjust = 0.5, hjust = 0.5, family = "inconsolata", fontface = "bold" ) +
    scale_size( range = c(4, 16), guide = F ) +
    scale_y_reverse() +
    scale_fill_gradient(low = "#ffffff", high = "#111111", na.value = NA) +
    scale_color_identity() +
    coord_cartesian(clip = "off") +
    labs(
      title = "Global State of Air",
      subtitle = "PM 2.5 Levels",
      caption = NULL, x = NULL, y = NULL) +
    theme_bw() +
    theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 14,
       options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```


### References
#### citations for narrative and data sources

* Data: Health Effects Institute, State of Global Air / 2020

<pre>
Health Effects Institute. 2020. State of Global Air 2020. Special Report.
Boston, MA:Health Effects Institute.
</pre>

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
