---
pagetitle: "Life Satisfaction vs GDP"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Life Satisfaction vs GDP
## Scatter plot

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Larm Rmah on Unsplash"}

masthead <- "assets/larm-rmah-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Happiness is a warm puppy...\
--- Charles M. Schulz\

***

Based on the reporting of Our World in Data, if we compare life satisfaction reports from around the world at any given point in time, we immediately see that countries with higher average national incomes tend to have higher average life satisfaction scores. In other words: People in richer countries tend to report higher life satisfaction than people in poorer countries. 


### Ingest the data
#### life satisfaction, gdp, and population by country and year

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load csv data file
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "life-satisfaction-vs-gdp/life-satisfaction-vs-gdp.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = FALSE)
df

```


### Wrangle the data
#### filter and remove incomplete cases


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_wrangle <- df %>% filter(Year == 2020)
df_wrangle <- df_wrangle[complete.cases(df_wrangle), ]
df_wrangle

```


### Analyze the data
#### apply a clustering method


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

set.seed(20)
clusters <- kmeans(df_wrangle[,c(4,5)], centers=3)
clusters

df_clustered <- df_wrangle
df_clustered$Clusters <- as.factor(clusters$cluster)
df_clustered

```


### Plot
#### color by cluster


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide'}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.grid.major = element_blank(),
    legend.position='none'
  )

# 1 - least
# 2 - better
# 3 - rosy
cluster_palette <- c("1" = "#F48FB1", "2" = "#81C784", "3" = "#00ACC1")

# Plot
v1 <- ggplot(df_clustered, aes(x = Life_Satisfaction, y = GDP_per_Capita_PPP, color = Clusters)) + 
  geom_point(size = 4, shape = 21, fill = "#FFFFFF", stroke = 2) +
  scale_x_continuous(breaks = seq(3.0, 8.0, 0.5), labels = seq(3.0, 8.0, 0.5), limits = c(3.0, 8.0)) +
  scale_y_continuous(breaks = seq(0, 100000, 20000), labels = scales::dollar, limits = c(0, 100000)) +
  scale_color_manual(values = cluster_palette) +
  labs( title = "Self-reported Life Satisfaction vs GDP per capita, 2020",
        subtitle = "Showing national average of the self-reported life satisfaction vs. GDP per capita adjusted for inflation and cross-country price differences.",
        caption = "Source: Our World in Data",
        x = "Happiness", y = "GDP") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```

### References
#### citations for narrative and data sources

* Narrative and Data Source: Our World in Data, Self-reported Life Satisfaction vs GDP per capita, 2020, [GO](https://ourworldindata.org/happiness-and-life-satisfaction){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

