---
pagetitle: "Public Support for Free Speech"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)
library(countrycode)
library(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Public Support for Free Speech
## Scatter plot

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Marie S on Unsplash"}

masthead <- "assets/marie-s-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> What is freedom of expression? Without the freedom to offend, it ceases to exist...\
--- Salman Rushdie\

***


### Ingest the data
#### life satisfaction, gdp, and population by country and year

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load csv data file
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"

url_file1 <- "public-support-for-free-speech/vdem-v2x_freexp.csv"
url1 <- paste0(url_root, url_file1)

df_vdem <- read.csv(url1, header = TRUE, stringsAsFactors = FALSE)
df_vdem

url_file2 <- "public-support-for-free-speech/justitia-free-speech-index.csv"
url2 <- paste0(url_root, url_file2)

df_justitia <- read.csv(url2, header = TRUE, stringsAsFactors = FALSE)
df_justitia


```


### Wrangle the data
#### country codes and join


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_justitia$ISO3 <- countrycode(df_justitia$COUNTRY_DATA, origin='country.name', destination='iso3c')
# df_justitia

df_combined <- merge(df_justitia, df_vdem, by.x='ISO3', by.y='country_text_id')
df_combined$Region <- countrycode(df_combined$ISO3, origin='iso3c', destination='un.region.name')
# df_combined

df_final <- df_combined %>% select(c(ISO3, country_name, v2x_freexp, Free_Speech_Index, Region))
df_final

```


### Plot
#### data points with smoothing


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide'}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.grid.major = element_blank(),
    legend.position='none'
  )

# Plot
v1 <- ggplot(df_final, aes(x = Free_Speech_Index, y = v2x_freexp)) + 
  geom_point(size = 4, shape = 21, fill = '#95A7C8', color = '#95A7C8' ) +
  geom_smooth(method="lm", se = FALSE, linetype = 'dashed', size = 2, color = '#82A0C2') + # "lm", "glm", "gam", "loess" 
  scale_x_continuous(breaks=seq(35,90, 5)) +
  scale_y_continuous(breaks=seq(0, 1, 0.2)) +
  labs( title = "You can't always get what you want",
        subtitle = "Desired v actual freedom of speech",
        # caption = "Source: V-Dem Institute, Justitia",
        x = "Less <- Public support for speech, 2020 -> More",
        y = "Amount of permitted free speech, 2020") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.8))
)

```


### Plot with annotations
#### some narrative to help tell the story


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

v2 <- v1 +
  geom_text_repel(aes(label = country_name), direction = "y", min.segment.length = 0.0, nudge_y = 0.02, point.padding = 0.2, family = "inconsolata")

girafe(ggobj = v2, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.8)))

  
```


### References
#### citations for narrative and data sources

* Narrative Inspiration: The Economist, In some countries, people think they have too much freedom of speech.
* Data Source: Justitia, Who Cares about Free Speech?, [GO](http://justitia-int.org/en/report-who-cares-about-free-speech-findings-from-a-global-survey-of-free-speech/){target="_blank"}
* Data Source: V-Dem Institute, Varieties of Democracy Project, [GO](https://www.v-dem.net/en/data/data/v-dem-dataset-v111/){target="_blank"}
