---
pagetitle: "Public Support for Free Speech"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Public Support for Free Speech
## Scatter plot

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Kristina Flour on Unsplash"}

masthead <- "assets/kristina-flour-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> What is freedom of expression? Without the freedom to offend, it ceases to exist...\
--- Salman Rushdie\

***


### Ingest the data
#### life satisfaction, gdp, and population by country and year

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load csv data file
df_vdem <- read.csv("archetypes/public-support-for-free-speech/vdem-v2x_freexp.csv", header = TRUE, stringsAsFactors = FALSE)
df_vdem

df_justitia <- read.csv("archetypes/public-support-for-free-speech/justitia-free-speech-index.csv", header = TRUE, stringsAsFactors = FALSE)
df_justitia

```


### Wrangle the data
#### country codes and join


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_justitia$ISO3 <- countrycode(df_justitia$COUNTRY_DATA, origin='country.name', destination='iso3c')
df_justitia

df_combined <- merge(df_justitia, df_vdem, by.x='ISO3', by.y='country_text_id')
df_combined
df_combined$Region <- countrycode(df_combined$ISO3, origin='iso3c', destination='un.region.name')

df_final <- df_combined %>% select(c(ISO3, country_name, v2x_freexp, Free_Speech_Index, Region))
df_final

```


### Plot
#### data points with smoothing


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.grid.major = element_blank(),
    legend.position='none'
  )

# Plot
v1 <- ggplot(df_final, aes(x = Free_Speech_Index, y = v2x_freexp)) + 
  geom_point(size = 4, shape = 21, fill = '#95A7C8', color = '#95A7C8' ) +
  geom_smooth(method="lm", se = FALSE, linetype = 'dashed', size = 2, color = '#82A0C2') + # "lm", "glm", "gam", "loess" 
  scale_x_continuous(breaks=seq(35,90, 5)) +
  scale_y_continuous(breaks=seq(0, 1, 0.2)) +
  labs( title = "You can't always get what you want",
        subtitle = "Desired v actual freedom of speech",
        caption = "Source: V-Dem Institute, Justitia",
        x = "Less <- Public support for speech, 2020 -> More",
        y = "Amount of permitted free speech, 2020") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```


### Plot with annotations
#### some narrative to help tell the story


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}



  
```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/public-support-for-free-speech-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/public-support-for-free-speech-sm.svg", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative Inspiration: The Economist, In some countries, people think they have too much freedom of speech.
* Data Source: Justitia, Who Cares about Free Speech?, [GO](http://justitia-int.org/en/report-who-cares-about-free-speech-findings-from-a-global-survey-of-free-speech/){target="_blank"}
* Data Source: V-Dem Institute, Varieties of Democracy Project, [GO](https://www.v-dem.net/en/data/data/v-dem-dataset-v111/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

