---
pagetitle: "Road deaths by country"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(stringr)
library(countrycode)
library(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Road deaths by country
## Scatter plot

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Yannis H on Unsplash"}

masthead <- "assets/yannis-h-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Some car accidents are caused by the ignorance or disbelief of the fact\ that a driver’s eyes and mind can be thousands of kilometres apart...\
--- Mokokoma Mokhonoana\

***


### Ingest the data
#### gdp and road traffic accidents

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load csv data file
df_gdp <- read.csv("archetypes/road-deaths-by-country/gdp.csv", header = TRUE, stringsAsFactors = FALSE, encoding = "UTF-8")
df_gdp

df_rd <- read.csv("archetypes/road-deaths-by-country/road-deaths.csv", header = TRUE, stringsAsFactors = FALSE, encoding = "UTF-8")
df_rd


```


### Wrangle the data
#### bracket removal and more


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_rd_wrangle <- df_rd %>% mutate(road_deaths = as.integer(str_replace(est_road_traffic_death_rate_per_100k_population_both_sexes, "\\[.+?\\]", "")))
df_rd_wrangle <- df_rd_wrangle %>% filter(year == 2017)
df_rd_wrangle <- df_rd_wrangle %>% select(c(country, road_deaths))
df_rd_wrangle$iso3 <- countrycode(df_rd_wrangle$country, origin='country.name', destination='iso3c')
# df_rd_wrangle

df_combined <- merge(df_rd_wrangle, df_gdp, by.x='iso3', by.y='Country_Code')
df_combined$region <- countrycode(df_combined$iso3, origin='iso3c', destination='un.region.name')
df_combined <- df_combined %>% select(c(iso3, country, road_deaths, X2017, region))
df_combined <- df_combined[complete.cases(df_combined), ]
# df_combined

df_final <- df_combined %>% rename(gdp = X2017)
df_final <- df_final %>% rename_with(toupper)
df_final <- df_final %>% filter(ROAD_DEATHS > 0)
df_final

```


### Plot
#### data points with smoothing


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.grid.major = element_blank(),
    legend.position='top'
  )

# Plot
v1 <- ggplot(df_final, aes(x = GDP, y = ROAD_DEATHS)) + 
  geom_point(aes( fill = REGION, color = REGION), size = 4, shape = 21) +
  geom_smooth(method="loess", se = FALSE, linetype = 'solid', size = 2, color = '#82A0C2') + # "lm", "glm", "gam", "loess" 
  geom_text_repel(aes(label = COUNTRY)) + 
  scale_x_log10() +
  scale_y_continuous() +
  labs( title = "Driving lessons",
        subtitle = NULL,
        caption = "Source: World Bank, IHME",
        x = "GDP per capita, PPP (constant 2017 international $)",
        y = "Est road traffic death rate per 100k population both sexes, 2017") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```


### Plot with annotations
#### some narrative to help tell the story


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}



  
```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/road-deaths-by-country-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/road-deaths-by-country-sm.svg", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative Inspiration: The Economist, Driving lession
* Data Source: World Health Organization, [GO](https://apps.who.int/gho/data/node.main.A997){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

