---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggraph)
library(igraph)
library(tidygraph)
library(graphlayouts)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
 GRAPHS  
</div>

# Al Cardinal
## Link analysis 

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Guillaume Bourdages on Unsplash"}

masthead <- "assets/guillaume-bourdages-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> It's clear that there's a lot of human wood out there for this coronavirus forest fire to burn...\
--- Michael Thomas Osterholm\

***



### Ingest
#### the tree of mutations


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Tree data
df_edges_path <- "archetypes/al-cardinal/the-sentry-al-cardinal.csv"
df_edges <- read.csv(df_edges_path, header = TRUE, stringsAsFactors = FALSE)
df_edges

```


### Wrangle
#### create graph structure


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# transform to graph data structure
df_graph <- graph_from_data_frame( df_edges, directed = TRUE )
#df_graph_directed <- graph_from_data_frame( df_tree, directed = TRUE )
#df_graph_undirected <- graph_from_data_frame( df_tree, directed = FALSE )

# to view results as data frame
df_graph_view <-  get.data.frame(df_graph, what= "both" ) # as.data.frame(get.edgelist(df_graph))
# df_graph_view

```


### Analytics
#### compute layouts


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}


# igraph layouts

# bipartite <- create_layout(df_graph, layout = 'igraph', algorithm = 'bipartite')
circle <- create_layout(df_graph, layout = 'igraph', algorithm = 'circle')
dh <- create_layout(df_graph, layout = 'igraph', algorithm = 'dh')
drl <- create_layout(df_graph, layout = 'igraph', algorithm = 'drl')
fr <- create_layout(df_graph, layout = 'igraph', algorithm = 'fr')
gem <- create_layout(df_graph, layout = 'igraph', algorithm = 'gem')
graphopt <- create_layout(df_graph, layout = 'igraph', algorithm = 'graphopt')
grid <- create_layout(df_graph, layout = 'igraph', algorithm = 'grid')
kk <- create_layout(df_graph, layout = 'igraph', algorithm = 'kk')
lgl <- create_layout(df_graph, layout = 'igraph', algorithm = 'lgl')
mds <- create_layout(df_graph, layout = 'igraph', algorithm = 'mds')
nicely <- create_layout(df_graph, layout = 'igraph', algorithm = 'nicely')
sphere <- create_layout(df_graph, layout = 'igraph', algorithm = 'sphere')
star <- create_layout(df_graph, layout = 'igraph', algorithm = 'star')
sugiyama <- create_layout(df_graph, layout = 'igraph', algorithm = 'sugiyama')

# ggraph layouts

#backbone <- create_layout(df_graph_undirected, layout = 'backbone')

#centrality_bc <- betweenness(df_graph_directed)
#centrality_cc <- closeness(df_graph_directed)
#centrality <- create_layout(df_graph_undirected, layout = 'centrality', centrality = centrality_bc)

#circlepack <- create_layout(df_graph_directed, layout = 'circlepack')
# dendrogram <- create_layout(df_graph, layout = 'dendrogram')
# eigen <- create_layout(df_graph, layout = 'eigen', type = "laplacian", eigenvector = "smallest")

focus <- create_layout(df_graph, layout = 'focus', focus = 1)

# hive <- create_layout(df_graph, layout = 'hive', axis = friends, sort.by = degree)

#linear <- create_layout(df_graph, layout = 'linear')
#matrix <- create_layout(df_graph, layout = 'matrix')
#partition <- create_layout(df_graph_directed, layout = 'partition')

pmds_pivots <- 4
pmds <- create_layout(df_graph, layout = 'pmds', pivots = pmds_pivots)

stress <- create_layout(df_graph, layout = 'stress')
#sunburst <- create_layout(df_graph_directed, layout = 'partition', circular = TRUE)
#treemap <- create_layout(df_graph_directed, layout = 'treemap')

# df_unrooted <- df_graph_undirected %>%  activate(edges) %>%  mutate(length = runif(n()))
#unrooted <- create_layout(df_graph_undirected, layout = 'unrooted' )

```


### Plot
#### dendrogram


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.margin = unit(c(1,1,1,1), "in"),
    legend.position='none'
  )

v1 <- ggraph(dh) + 
  geom_edge_link() + 
  geom_node_point(size=2) +
  geom_node_label( aes(label=name), repel = FALSE, vjust = -0.5, hjust = 0.5, size = 4, family = "inconsolata") +
  coord_fixed(clip = 'off') + 
  theme_void() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

# pg <- ggplot_build(v1)
# pg$data[[2]]
# pg$data[[3]]

```




```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/covid-19-mutations-fs.svg", plot = v1, width=720/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/covid-19-mutations-sm.svg", plot = v1, width=2.25, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative: Economist, It's a family affair, https://www.economist.com/graphic-detail/2021/02/27/the-same-covid-19-mutations-are-appearing-in-different-places  
* Narrative: Nextstrain, Genomic epidemiology of novel coronavirus, https://nextstrain.org/ncov/gisaid/global
* Data sources: Nextstrain, SARS-CoV-2 data, https://github.com/nextstrain/ncov

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "" # mostly used in wranglers and analytics
keywords <- 'covid mutations epidemiology sars'
commands <- 'graph_from_data_frame create_layout'
sources <- 'Economist Nextstrain'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

