---
pagetitle: "Coffee Flavors"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(sunburstR)
library(ggraph)
library(igraph)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
 TREES  
</div>

# Coffee Flavors
## Sunburst Chart 

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo of Nemonte Nenquimo"}

masthead <- "assets/nemonte-nenquimo.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> And now, as a woman, as a mother, as a water protector and a forest defender,\
  I want you to join us in our fight to defend our way of life, our forests and our planet...\
--- Nemonte Nenquimo\

***

### Ingest
#### name, category, country, role


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_file_path <- "archetypes/top-100-influential-women/top-100-influential-women.csv"
df = read.csv(df_file_path, header = TRUE, stringsAsFactors = FALSE, encoding = "UTF-8")
df

```


### Wrangle
#### enrich with continent to create hierarchy


```{r echo=TRUE, message=FALSE, warning=FALSE, class.source = 'fold-hide'}


```


### Wrangle, part II
#### create graph hierarchy


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}



```


### Plot
#### graph version

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}



```


### References
#### citations for narrative and data sources

* Narrative and data sources: BBC's Top 100 Influential Women, https://www.bbc.com/news/world-55042935  


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```