---
pagetitle: "Top 100 GHG Emitters"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(sunburstR)
library(ggraph)
library(igraph)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
 TREES  
</div>

# Top 100 GHG Emitters
## Sunburst Chart 

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo of Nemonte Nenquimo"}

masthead <- "assets/nemonte-nenquimo.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> And now, as a woman, as a mother, as a water protector and a forest defender,\
  I want you to join us in our fight to defend our way of life, our forests and our planet...\
--- Nemonte Nenquimo\

***


### Ingest
#### name, category, country, role


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_file_path <- "archetypes/top-10-ghg-emitters/top-10-ghg-emitters.csv"
df <- read.csv(df_file_path, header = TRUE, stringsAsFactors = FALSE, encoding = "UTF-8")
df

```


### Wrangle
#### enrich with continent to create hierarchy


```{r echo=TRUE, message=FALSE, warning=FALSE, class.source = 'fold-hide'}

df_wrangle <- df

# select only the needed columns
df_wrangle <- df_wrangle %>% select(name, category, country, role)

# enrich with UN region name
df_wrangle$region <- countrycode(df_wrangle$country, origin='country.name', destination='un.region.name')

# for non-matches, replace with a generic "World" entry
# df_wrangle <- df_wrangle %>% replace_na(list(region = "World"))
# or, replace with country entries
df_wrangle$region <- ifelse(is.na(df_wrangle$region), df_wrangle$country, df_wrangle$region)

# we'll add a constant size variable for the aggregation
df_wrangle <- df_wrangle %>% mutate(ID = row_number(), SIZE = 1)
# we need to create unique ids to avoid duplicate vertices
df_wrangle <- df_wrangle %>% mutate(country = paste0(country, "_", ID))
df_wrangle

```


### Wrangle, part II
#### create graph hierarchy

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

df_filtered <- filter(df_wrangle, category != 'Top 100')

# unique edges
df_edges_0 <- aggregate(x = df_filtered$SIZE,
          by = list(df_filtered$category),
          FUN = sum)

# standard edge table structure
colnames(df_edges_0) <- c("TO", "SIZE")
df_edges_0$FROM <- "Top 100"

df_edges_1 <- aggregate(x = df_filtered$SIZE,
          by = list(df_filtered$category, df_filtered$country),
          FUN = sum)

# standard edge table structure
colnames(df_edges_1) <- c("FROM","TO", "SIZE")

df_edges_2 <- aggregate(x = df_filtered$SIZE,
          by = list(df_filtered$country, df_filtered$name),
          FUN = sum)

# standard edge table structure
colnames(df_edges_2) <- c("FROM","TO", "SIZE")

# combine
df_edges <- rbind(df_edges_0, df_edges_1, df_edges_2)
df_edges <- df_edges[c("FROM", "TO", "SIZE")]
df_edges

# consolidate to have nodes list; used for validation if needed
df_node_list <- as.data.frame(c(df_edges$FROM, df_edges$TO))
colnames(df_node_list) <- c("NODE")
#df_node_list

# root nodes
df_nodes_1 <- aggregate(x = df_wrangle$SIZE,
          by = list(df_wrangle$category),
          FUN = sum)

colnames(df_nodes_1) <- c("NODE","SIZE")
df_nodes_1$COLOR <- df_nodes_1$NODE

# leaf nodes
df_nodes_2 <- aggregate(x = df_filtered$SIZE,
          by = list(df_filtered$country, df_filtered$category),
          FUN = sum)

colnames(df_nodes_2) <- c("NODE", "COLOR", "SIZE")

# leaf nodes
# df_nodes_3 <- df_filtered %>% select(name, category, SIZE)
df_nodes_3 <- aggregate(x = df_filtered$SIZE,
          by = list(df_filtered$name, df_filtered$category),
          FUN = sum)
colnames(df_nodes_3) <- c("NODE", "COLOR", "SIZE")

# combine
df_nodes <- rbind(df_nodes_1, df_nodes_2, df_nodes_3)
df_nodes

# a check, when needed, to find missing node entries
test_1 <- anti_join(df_nodes, df_node_list, by = "NODE" )
#test_1
test_2 <- anti_join(df_node_list, df_nodes, by = "NODE" )
#test_2


# transform to graph data structure
df_graph <- graph_from_data_frame( df_edges, vertices = df_nodes )

```


### Plot
#### graph version

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.margin = unit(c(1.5,1,1,1), "in"),
    legend.position='none'
  )

category_palette <- c("Top 100" = "#FFFFFF", "LEAF" = "#FFFFFF", "Creativity" = "#E8F5E9", "Identity" = "#E3F2FD", "Knowledge" = "#F3E5F5","Leadership" = "#FCE4EC")

v1 <- ggraph(df_graph, layout = 'partition', circular = TRUE, weight = SIZE) + 
  geom_node_arc_bar(aes(fill = ifelse(leaf, 'LEAF', COLOR)), color='#ffffff') + 
  scale_fill_manual(values = category_palette) +
  geom_node_label( aes(label=name, filter=depth<2), size = 6, label.size = NA, family = "inconsolata") +
  geom_node_text( aes(filter = leaf, angle = node_angle(x, y), label = name), hjust = 0, size = 3, family = "inconsolata" ) +
  coord_fixed(clip = 'off') + 
  theme_void() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

# pg <- ggplot_build(v1)
# pg$data[[2]]
# pg$data[[3]]

```


### References
#### citations for narrative and data sources

* Narrative and data sources: 


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```