---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: libs

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(htmltools) # needed to include html snippets
library(tidyverse)
library(classInt)
library(knitcitations)
library(bibtex)

```

<div class="activity">
ANALYTICS
</div>

# Discretize
## I want to reduce a continuous variable to bins of similar values

> Don't call the world dirty because you forgot to clean your glasses...\
--- Aaron Hill\

Discretizing is a method to smooth a sorted data value by consulting its neighborhood of values around it. The sorted values are distributed into a number of neighborhood bins. This method enables you to reduce a continuous variable to a fixed number of discrete observations.

These are the methods that can be applied, each with their own pros and cons depending on the profile of the data:

* __Equal-width__ : divides the range into 𝑁 intervals of equal size.
* __Equal-frequency__ : divides the range into 𝑁 intervals, each containing approximately the same number of samples
  
***

# Discretize
## Case:  SDG INDICATOR 1.1.1 - Share of the population living in extreme poverty, by country

## Load Data

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read.csv("archetypes/share-of-the-population-living-in-extreme-poverty.csv")

df


```




## Clean Data

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df1 <- df  %>% rename("Ratio" = "Poverty.headcount.ratio.at..1.90.a.day..2011.PPP.....of.population.")%>% filter(Code != "")%>% filter(Entity!= "World")
df1

df2 <- df1 %>% filter(Year == '2015') 
df2
```


## Equal Width



```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

equal_width <- classIntervals(df2$Ratio, 10, style = 'equal')
equal_width
```


## Equal frequency



```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

equal_fre <- classIntervals(df1$Year, 3, style = 'quantile')
equal_fre

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


