---
pagetitle: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)


```

ANALYTICS

# Indicators
## I want to fix irregularities in my dataset

> Don't call the world dirty because you forgot to clean your glasses...\
--- Aaron Hill\

Average Gain: ...
Moving Average Convergence Divergence (MACD): ...
Momentum: ...
On-Balance Volume (OBV): ...
Rate of Change (ROC): ...
Relative Strength Index (RSI): ...
Volume-Price Trend (VPT): ...

***

# Section
## Subsection

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Fold hide as this is not relevant to the task


```


# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```


# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```



# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```



# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```


# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case
