---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/kamino.css", "../../../z-assemblers/temporals.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/header.html"
      after_body: "../../../z-assemblers/footer.html"
    #self_contained: false
    #lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(ggTimeSeries)

library(htmltools) # needed to include html snippets
library(knitcitations)
library(bibtex)

```

<div class="activity">
TEMPORALS
</div>

# Streamgraph
## Europes Dark Clouds

***

# Section
## Subsection

```{r, echo=FALSE}

df <- read.csv("../archetypes/europes-dark-clouds-summary.csv", header = TRUE, stringsAsFactors = TRUE)
df

df_country <- read.csv("../archetypes/europes-dark-clouds-country.csv", header = TRUE, stringsAsFactors = FALSE)
df_country

```

# Section
## Subsection


```{r, echo=FALSE, fig.width=12, fig.height=6}

theme_opts <- theme(
  legend.position = "bottom",
  legend.title = element_blank(),
  axis.text.y = element_blank(),
  axis.line.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank(),
  # panel.grid = element_blank(),
  # panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.background = element_blank(),
)

code_pal <- c("CO" = "#526381", 
              "NMVOC" = "#bcb8b5",
              "NH3" = "#a56f85",
              "NOx" = "#95989a",
              "TSP" = "#6b6280",
              "Other.pollutants" = "#00BCD4",
              "PM10" = "#ce767e",
              "PM2.5" = "#ce767e",
              "SOx" = "#b4bbc0")

v1 <- ggplot(df, aes(x = Year, y = Emissions, group = Pollutant_name, fill = Pollutant_name)) +
  stat_steamgraph() +
  scale_x_continuous(breaks = c(1990, 1995, 2000, 2005, 2010, 2015, 2018)) +
  scale_fill_manual(values = code_pal ) +
  #coord_fixed( 0.2 * diff(range(df$Year)) / diff(range(df$N))) +
  theme_bw() +
  theme_opts +
  xlab(NULL) +
  ylab(NULL)

v1

```

# Section
## Subsection

```{r, echo=FALSE, fig.width=12, fig.height=6}

v2 <- v1 + 
  coord_cartesian(clip="off") +
  annotate("text", x = 2011, y = max(df$Emissions), 
           label = "Extreme levels of particulate matter (PM 10 &\n2.5) caused by the eruption of Grímsvötn in\n2011, Iceland's most active volcano", hjust = "center", size = 3, fontface = 2)

v2

```

# Section
## Subsection

```{r, echo=FALSE, fig.width=12, fig.height=2}

is_subset <- c("IS") 
df_is <- filter(df_country, Country_Code %in% is_subset )
# df_is

v3 <- ggplot(df_is, aes(x = Year, y = Emissions, group = Pollutant_name, fill = Pollutant_name)) +
  stat_steamgraph() +
  scale_x_continuous(breaks = c(1990, 1995, 2000, 2005, 2010, 2015, 2018)) +
  scale_y_continuous() +
  scale_fill_manual(values = code_pal ) +
  theme_bw() +
  theme_opts +
  theme(legend.position = "none") +
  xlab(NULL) +
  ylab(NULL)

v3

```

# Section
## Subsection

```{r, echo=FALSE, fig.width=12, fig.height=4}

gb_subset <- c("GB") 
df_gb <- filter(df_country, Country_Code %in% gb_subset )
# df_gb

v4 <- ggplot(df_gb, aes(x = Year, y = Emissions, group = Pollutant_name, fill = Pollutant_name)) +
  stat_steamgraph() +
  scale_x_continuous(breaks = c(1990, 1995, 2000, 2005, 2010, 2015, 2018)) +
  scale_y_continuous() +
  scale_fill_manual(values = code_pal ) +
  theme_bw() +
  theme_opts +
  xlab(NULL) +
  ylab(NULL)

v4

```

# Section
## Subsection


```{r, echo=FALSE}

# ggsave(filename = "stream-europes-dark-clouds-summary.svg", plot = v1, width=12, height=6)
# ggsave(filename="stream-nuclear-weapon-tests.png", plot=v1, device="png", height=6, width=12, units="in", dpi=500)

# ggsave(filename = "stream-europes-dark-clouds-annotation.svg", plot = v2, width=12, height=6)
# ggsave(filename = "stream-europes-dark-clouds-country.png", plot = v2, device = "png", height = 6, width = 12, units = "in", dpi = 500)

# ggsave(filename = "stream-europes-dark-clouds-is.svg", plot = v3, width=12, height=2)
# ggsave(filename = "stream-europes-dark-clouds-gb.svg", plot = v4, width=12, height=4)

```



# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case

Source:  <a href="https://www.eea.europa.eu/data-and-maps/data/national-emissions-reported-to-the-convention-on-long-range-transboundary-air-pollution-lrtap-convention-14">National emissions reported to the Convention on Long-range Transboundary Air Pollution (LRTAP Convention)</a>

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

# cleanbib()
# read.bibtex(file = "./citations.bib")

```


```{r, message=FALSE, warning=FALSE, echo=FALSE}

# echo=FALSE will exclude block from code folding
# Example for including external html content when needed
htmltools::includeHTML("mark-complete-button.html")

```



```{r, child='mark-complete-click.Rmd'}

# JS event handler for button click

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

