---
pagetitle: "More Money More Time"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggthemes)
library(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# More Money More Time
## Scatter Quadrant


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Annie Spratt on Unsplash"}

masthead <- "assets/annie-spratt-2-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> I am issuing a call to action for countries, companies and institutions globally\
  to step-up and become champions for paid parental leave...\
--- UN Women Goodwill Ambassador Anne Hathaway\

***

Investing in __family friendly policies__ is good for families, businesses and economies. But for too many parents around the world, policies, such as __paid parental leave__, breastfeeding breaks, childcare and child grants, are not a reality. Family-friendly policies matter because they help children to get a better start in life and help parents to find the right balance between their commitments at work and at home. Yet even some of the world’s richest countries fail to offer comprehensive solutions to all families.

Let's take a closer look at the situation.

### Ingest the source
#### maternity leave, payment rate


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df = read.csv("archetypes/more-money-more-time/more-money-more-time.csv", header = TRUE, stringsAsFactors = FALSE)
df

```


### Wrangle
#### select, clean, and factor


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Select only the needed
df_complete <- select(df, c("Country", "Paid_maternity_leave_avg_payment_rate_percent", "Paid_maternity_leave_in_months", "difference_from_OECD_average"))

# Make sure we don't factor empty strings
df_complete <- filter(df_complete, nchar(Country) > 0)
# Factor the string fields
df_complete$Country <- as.factor(df_complete$Country)

# Remove incomplete cases
df_complete <- df_complete[complete.cases(df_complete), ]

df_complete

```


### Base Scatter Plot
#### position, shape, labels


```{r, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

# theme parameters
theme_opts <- theme(
  text = element_text(family = "inconsolata"), 
  legend.position = "none",
  legend.title = element_blank(),
  #axis.text = element_blank(),
  #axis.line = element_blank(),
  #axis.ticks = element_blank(),
  #axis.title = element_blank(),
  #panel.grid = element_blank(),
  panel.grid.major = element_line(linetype = "dotted"),
  panel.grid.minor = element_blank(),
  panel.background = element_rect(fill="white", colour="white"),
  #panel.border = element_blank(),
  plot.background = element_rect(fill="white", colour="white"),
  plot.title = element_text(vjust = 5.0),
  plot.subtitle = element_text(vjust = 5.0),
  plot.margin = unit(c(0.5,0.5,0.5,0.5), "in")
)

rate_average <- mean(df_complete$Paid_maternity_leave_avg_payment_rate_percent)
leave_average <- mean(df_complete$Paid_maternity_leave_in_months)

v1 <- ggplot(df_complete) +
      annotate("rect", xmin = 0, xmax = leave_average, ymin = rate_average, ymax = 110, fill = "#f5f2d2", alpha = 0.8) +
      annotate("rect", xmin = leave_average, xmax = 14.5, ymin = rate_average, ymax = 110, fill = "#e4edcc", alpha = 0.8) +
      annotate("rect", xmin = 0, xmax = leave_average, ymin = 0, ymax = rate_average, fill = "#eeddc2", alpha = 0.8) +
      annotate("rect", xmin = leave_average, xmax = 14.5, ymin = 0, ymax = rate_average, fill = "#f5f2d2", alpha = 0.8) +
      geom_point_interactive(aes(x = Paid_maternity_leave_in_months, 
                 y = Paid_maternity_leave_avg_payment_rate_percent, 
                 tooltip = paste0("Country: ", Country, "\n", 
                                  "Paid_maternity_leave_avg_payment_rate_percent: ", Paid_maternity_leave_avg_payment_rate_percent, "%\n", 
                                  "Payment_Rate: ", Paid_maternity_leave_in_months, "\n", 
                                  "difference_from_OECD_average: ", difference_from_OECD_average),
                 data_id = row.names(df_complete)), 
                 color='#111111', size = 3.0, alpha = 1.0 ) +
      geom_text_repel(aes(x = Paid_maternity_leave_in_months, 
                 y = Paid_maternity_leave_avg_payment_rate_percent, 
                 label = Country), family = 'inconsolata', size = 4, force = 0.5, nudge_x = 0.25, segment.size  = 0.2, segment.color = "grey50", direction = "y", hjust = 0) +
      scale_x_continuous(limits = c(0, 15), breaks = seq(0, 15, 2), labels = seq(0, 15, 2), expand = c(0,0)) +
      scale_y_continuous(limits = c(0, 110), breaks = seq(0, 110, 20), labels = seq(0, 110, 20), expand = c(0,0)) +
      coord_cartesian(clip = 'off') +
      labs(x="Paid Maternity Leave in Months",
         y="Payment Rate",
         title = "Maternity Leave & Pay",
         caption = "source: OECD, DataWrapper") +
      theme_minimal(base_family = "inconsolata", base_size = 16) +
      theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 12,
       options = list(
         opts_sizing(rescale = TRUE, width = 1.0), 
         opts_hover_inv(css = "opacity:0.2;"), 
         opts_hover(css = "fill:black;")
         )
      )

```


### The Quadrant
#### with annotations...


```{r, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v2 <- v1 + geom_hline(yintercept = rate_average, linetype = "dashed", color = "#bbbbbb") +
  geom_vline(xintercept = leave_average, linetype = "dashed", color = "#bbbbbb") +
  annotate("text", x = leave_average, y = 110, 
           label = "OECD Leave Avg", 
           hjust = 0.5, vjust = -1.0, size = 5, color = "#aaaaaa", family = "inconsolata", fontface = 1) +
  annotate("text", x = 14.6, y = rate_average, 
           label = "OECD\nRate\nAvg", 
           hjust = 0, vjust = 1.2, size = 5, color = "#aaaaaa", family = "inconsolata", fontface = 1) +
  annotate("text", x = 2, y = 20, 
           label = "less money\n& less time", 
           hjust = 0.5, vjust = 0, size = 5, color = "#c67e63", family = "inconsolata", fontface = 1) +
  annotate("text", x = 9, y = 20, 
           label = "less money\nbut more time", 
           hjust = 0.5, vjust = 0, size = 5, color = "#c1a04f", family = "inconsolata", fontface = 1) +
  annotate("text", x = 2, y = 90, 
           label = "more money\nbut less time", 
           hjust = 0.5, vjust = 0, size = 5, color = "#c1a04f", family = "inconsolata", fontface = 1) +
  annotate("text", x = 9, y = 90, 
           label = "more money\nand more time", 
           hjust = 0.5, vjust = 0, size = 5, color = "#5b7e47", family = "inconsolata", fontface = 1)

girafe(ggobj = v2, width_svg = 16, height_svg = 12,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source = 'fold-hide'}

# full version
ggsave(filename = "assets/more-money-more-time-fs.svg", plot = v2, width=1280/72, height=720/72)

# without annotations
ggsave(filename = "assets/more-money-more-time-sm.svg", plot = v1, width=4, height=2.25)

```


### References
#### Citations and data sources

* Inspiration: DataWrapper, [GO](https://blog.datawrapper.de/weekly37/){target="_blank"}
* Data source: OECD, Parental Leave Systems, [GO](https://www.oecd.org/els/soc/PF2_1_Parental_leave_systems.pdf){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```




```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

