---
pagetitle: "Most Generous Nations"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(ggthemes)
library(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Most Generous Nations
## Scatter Quadrant


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Matt Collamer on Unsplash"}

masthead <- "assets/matt-collamer-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Generosity is the most natural outward expression of an inner attitude of compassion and loving-kindness...\
--- The Dalai Lama XIV\

***

We have a natural instinct to help others. Wealth doesn’t come into it. Citizens of relatively poor countries such as Myanmar and Indonesia are some of the most generous. They __help__ strangers. They __donate__ money. They __volunteer__ time. The top 20 includes countries that have suffered massive instability. Haiti. Liberia. Sierra Leone. Shared human values, shining through.

Let's take a closer look at the situation.

### Ingest the source
#### giving score, GDP, population


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "worlds-most-generous/worlds-most-generous.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE, stringsAsFactors = FALSE)
df

```


### Wrangle
#### select, clean, and cast data types


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Select only the needed
df_complete <- select(df, c("Country", "Overall_CAF_Giving_Index_Score_Percent", "GDP_per_capita_current_USD", "population"))

# Make sure all visual variables are proper data types
df_complete$Overall_CAF_Giving_Index_Score_Percent <- parse_number(df_complete$Overall_CAF_Giving_Index_Score_Percent)
df_complete$GDP_per_capita_current_USD <- parse_number(df_complete$GDP_per_capita_current_USD)
df_complete$population <- parse_number(df_complete$population)

# Make sure we don't factor empty strings
df_complete <- filter(df_complete, nchar(Country) > 0)
# Factor the string fields
df_complete$Country <- as.factor(df_complete$Country)

# Remove incomplete cases
df_complete <- df_complete[complete.cases(df_complete), ]

df_complete

```


### Quadrant Measures
#### min, max, mean, and conditional logic

```{r, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# measures to use for quadrant placement
gdp_average <- mean(df_complete$GDP_per_capita_current_USD)
gdp_min <- min(df_complete$GDP_per_capita_current_USD)
gdp_max <- max(df_complete$GDP_per_capita_current_USD)

generosity_average <- mean(df_complete$Overall_CAF_Giving_Index_Score_Percent)
generosity_min <- min(df_complete$Overall_CAF_Giving_Index_Score_Percent)
generosity_max <- max(df_complete$Overall_CAF_Giving_Index_Score_Percent)

# Create a color variable for a manual scale
df_complete <- df_complete %>% mutate(color = ifelse( GDP_per_capita_current_USD < gdp_average & Overall_CAF_Giving_Index_Score_Percent > generosity_average, 'R', 'B'))
df_complete

```



### Base Scatter Plot
#### position, shape, color, and labels


```{r, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# theme parameters
theme_opts <- theme(
  text = element_text(family = "inconsolata"), 
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  #axis.title = element_blank(),
  panel.grid = element_blank(),
  # panel.grid.major = element_line(linetype = "dotted"),
  # panel.grid.minor = element_blank(),
  panel.background = element_rect(fill="#B3E5FC", colour="#B3E5FC"),
  panel.border = element_blank(),
  plot.background = element_rect(fill="#B3E5FC", colour="white"),
  plot.title = element_text(vjust = 3.0),
  plot.subtitle = element_text(vjust = 3.0),
  plot.margin = unit(c(0.5,0.5,0.5,0.5), "in")
)

color_palette <- c("B" = "#111111", "R" = "#f15a24")

v1 <- ggplot(df_complete) +
      geom_point_interactive(aes(x = GDP_per_capita_current_USD, 
                 y = Overall_CAF_Giving_Index_Score_Percent, 
                 size = population,
                 color = color,
                 tooltip = paste0("Country: ", Country, "\n", 
                                  "Overall_CAF_Giving_Index_Score_Percent: ", Overall_CAF_Giving_Index_Score_Percent, "%\n", 
                                  "GDP_per_capita_current_USD: ", GDP_per_capita_current_USD, "\n", 
                                  "population: ", population),
                 data_id = row.names(df_complete)), 
                 shape = 21, fill = "#E1F5FE", alpha = 1.0 ) + # or fill = "NA"
      geom_text_repel(data=filter(df_complete, population>mean(population)),
                      aes(x = GDP_per_capita_current_USD, y = Overall_CAF_Giving_Index_Score_Percent, label = Country, color = color),
                      family = 'inconsolata', size = 4, force = 0.5, nudge_x = 0.25, segment.size  = 0.2, segment.color = "grey50", direction = "both", hjust = 0) +
      scale_x_continuous(trans = "log2") +
      scale_y_continuous() +
      scale_size("population", range = c(2, 40)) +
      scale_color_manual(guide = FALSE, values = color_palette) +
      coord_cartesian(clip = 'off') +
      labs(x="GDP",
         y="Generosity",
         title = "Some of the World's Poorest Nations\nare also the Most Generous",
         caption = "source: Charities Aid Foundation, Information is Beautiful") +
      theme_minimal(base_family = "inconsolata", base_size = 16) +
      theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 12,
       options = list(
         opts_sizing(rescale = TRUE, width = .80), 
         opts_hover(css = "fill:#81D4FA;")
         )
      )

```


### The Quadrant
#### with annotations...


```{r, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

v2 <- v1 + geom_hline(yintercept = generosity_average, linetype = "dashed", color = "#f15a24") +
  geom_vline(xintercept = gdp_average, linetype = "dashed", color = "#f15a24") +
  annotate("text", x = gdp_min, y = generosity_max, 
           label = "poor & generous countries", 
           hjust = 0.3, vjust = 0.5, size = 5, color = "#f15a24", family = "inconsolata", fontface = 2) +
  annotate("text", x = gdp_max, y = generosity_max, 
           label = "rich & generous", 
           hjust = 0.55, vjust = 0.5, size = 5, color = "#111111", family = "inconsolata", fontface = 2) +
  annotate("text", x = gdp_min, y = generosity_min, 
           label = "poor & less generous", 
           hjust = 0.3, vjust = 0, size = 5, color = "#111111", family = "inconsolata", fontface = 2) +
  annotate("text", x = gdp_max, y = generosity_min, 
           label = "rich & less generous", 
           hjust = 0.7, vjust = 0, size = 5, color = "#111111", family = "inconsolata", fontface = 2) +
  annotate("text", x = gdp_average, y = generosity_max, 
           label = "HIGH GENEROSITY", 
           hjust = 0.5, vjust = -4.0, size = 5, color = "#f15a24", family = "inconsolata", fontface = 1) +
  annotate("text", x = gdp_average, y = generosity_min, 
           label = "LOW GENEROSITY", 
           hjust = 0.5, vjust = 5.0, size = 5, color = "#f15a24", family = "inconsolata", fontface = 1) +
  annotate("text", x = gdp_min, y = generosity_average, 
           label = "LOW WEALTH", 
           hjust = 0.8, vjust = 1.5, size = 5, color = "#f15a24", family = "inconsolata", fontface = 1) +
  annotate("text", x = gdp_max, y = generosity_average, 
           label = "HIGH WEALTH", 
           hjust = 0.3, vjust = 1.5, size = 5, color = "#f15a24", family = "inconsolata", fontface = 1)

girafe(ggobj = v2, width_svg = 16, height_svg = 12,
       options = list(
         opts_sizing(rescale = TRUE, width = .80), 
         opts_hover(css = "fill:#81D4FA;")
         )
      )

```


### References
#### Citations and data sources

* Inspiration and data: Information is Beautiful, [GO](https://informationisbeautiful.net/beautifulnews/1025-generous-countries/){target="_blank"}
