---
pagetitle: "Electric Cars"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(ggiraph)
library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# Electric Cars
## Parse Numbers

```{r, out.width="60%", fig.align="center", fig.cap="Photo by CHUTTERSNAP on Unsplash"}

masthead <- "assets/chuttersnap-xfaYAsMV1p8-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Electric Cars</div>

> The time is right for electric cars - in fact the time is critical...\
--- Carlos Ghosn\

***

### Load the data

```{r Load raw data, warning=FALSE, echo=TRUE, warning=FALSE,class.source = 'fold-hide'}

df <- read.csv('./archetypes/Cheapestelectriccars-EVDatabase.csv', header = TRUE, stringsAsFactors = FALSE)
df
```

Let's take a look at the datatypes we have on our dataset. 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

str(df)

```
### Wrangle 

Most of our data are in Character formats where it should be numerical. Having numerical data-points will allow us to do computations as well as plot the data efficiently. It's imperative that we get rid of the strings in the data point and convert it to numerical. 

We'll use the help of the function parse_number from library(readr)

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}


df$Acceleration <- readr::parse_number(df$Acceleration)
df$TopSpeed <- parse_number(df$TopSpeed)
df$Range <- parse_number(df$Range)
df$Efficiency <- parse_number(df$Efficiency)

```


Now we can observe the columns that've been parsed and converted to numerical 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

str(df)

```


### References
#### citations for narrative and data sources
* Narrative sources: Cheapest Electric Cars, [GO](https://www.kaggle.com/kkhandekar/cheapest-electric-cars){target="_blank"}
* Data sources: Electric Vehicle Database, [GO](https://ev-database.org/){target="_blank"}
