---
pagetitle: "Climate Classification"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(colorspace)
library(sf)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Climate Classification
## Contour map

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Visit Greenland on Unsplash"}

masthead <- "assets/visit-greenland-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Aasiaat, Greenland during winter</div>

> How do you find America? Turn left at Greenland...\
--- Ringo Starr, media question to Beatles during first U.S. tour 1964\

***

### Ingest
#### map attributes with climate zones


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df <- read.csv("archetypes/climate-classification/world-climates-koppen-geiger.csv", header = TRUE, stringsAsFactors = FALSE)
head(df, n=10)

unique(df$climates_f)

```


### Base Map
#### Köppen-Geiger Climate Zones


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

climate_zone_map <- st_read("archetypes/climate-classification/world-climates-koppen-geiger.geojson")

```


### Wrangle
#### enrich climate zone labels


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

climate_zone_map_enriched <-
  climate_zone_map %>% 
  mutate(
    main = case_when(
      str_detect(climates_f, "^A") ~ "Equatorial climates",
      str_detect(climates_f, "^B") ~ "Arid climates",
      str_detect(climates_f, "^C") ~ "Warm temperate climates",
      str_detect(climates_f, "^D") ~ "Snow climates",
      str_detect(climates_f, "^E") ~ "Polar climates",
      TRUE ~ NA_character_
    ),
    type = case_when(
      str_detect(climates_f, "^Af") ~ "Equatorial rainforest, fully humid",
      str_detect(climates_f, "^Am") ~ "Equatorial monsoon",
      str_detect(climates_f, "^As") ~ "Equatorial savannah with dry summer",
      str_detect(climates_f, "^AW") ~ "Equatorial savannah with dry winter",
      str_detect(climates_f, "^BS") ~ "Arid steppe climate",
      str_detect(climates_f, "^Bs") ~ "Arid steppe climate",
      str_detect(climates_f, "^BW") ~ "Arid desert climate",
      str_detect(climates_f, "^Bw") ~ "Arid desert climate",
      str_detect(climates_f, "^CS") ~ "Warm temperate climate with dry summer",
      str_detect(climates_f, "^Cs") ~ "Warm temperate climate with dry summer",
      str_detect(climates_f, "^Cw") ~ "Warm temperate climate with dry winter",
      str_detect(climates_f, "^Cf") ~ "Warm temperate climate, fully humid",
      str_detect(climates_f, "^Ds") ~ "Snow climate with dry summer",
      str_detect(climates_f, "^Dw") ~ "Snow climate with dry winter",
      str_detect(climates_f, "^Df") ~ "Snow climate, fully humid",
      str_detect(climates_f, "ET") ~ "Polar tundra climate",
      str_detect(climates_f, "EF") ~ "Polar frost climate",
      TRUE ~ NA_character_
    ),
    type = factor(type, levels = c(
      "Equatorial rainforest, fully humid",
      "Equatorial monsoon",
      "Equatorial savannah with dry summer",
      "Equatorial savannah with dry winter",
      "Arid steppe climate",
      "Arid desert climate",
      "Warm temperate climate with dry summer",
      "Warm temperate climate with dry winter",
      "Warm temperate climate, fully humid",
      "Snow climate with dry summer",
      "Snow climate with dry winter",
      "Snow climate, fully humid",
      "Polar tundra climate",
      "Polar frost climate",
      TRUE ~ NA_character_
    ))
  ) %>% 
  filter(!is.na(type))

climate_zone_map_enriched

```


### Plot
#### contour


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

theme_opts <- theme(
  text = element_text(family = "inconsolata", size = 12), 
  plot.title = element_text(color = "black", size = 16, face = "bold"),
  plot.subtitle = element_text(color = "black", size = 12),
  plot.caption = element_text(color = "#555555", size = 11),
  plot.background = element_rect(fill = "#f0f0f0", color = NA),
  plot.margin = margin(.25, .25, .25, .25, "cm"),
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  axis.text.x = element_blank(),
  axis.text.y = element_blank(),
  panel.border = element_blank(),
  panel.background = element_rect(fill = "#f0f0f0", color = NA),
  # panel.grid.minor = element_blank(),
  # panel.grid.major = element_blank(),
  legend.position = 'bottom',
  legend.title = element_blank(), #change legend title font size
  legend.text = element_text(size=10)
)

fill_palette <- c(
  "#4f3314",
  "#784e1e",
  "#a16928",
  "#ca8432",
  "#ca9273",
  "#d8af98",
  "#e7daae",
  "#dbd787",
  "#cbcf60",
  "#b6ccca",
  "#98b7b4",
  "#7aa29e",
  "#36b9cd",
  "#2890a0"
)

color_palette <- darken(fill_palette, 0.1)

v1 = ggplot(data = climate_zone_map_enriched) + 
  geom_sf(aes(fill=type, color=type), stroke=0.5) +
  scale_fill_manual( values = fill_palette ) +
  scale_color_manual( values = color_palette ) +
  coord_sf() +
  ggtitle( "Köppen-Geiger Climate Zones" ) +
  theme_void() +
  theme_opts

girafe( ggobj = v1, width_svg = 16, height_svg = 9,
  options = list( opts_sizing(rescale = TRUE, width = 1.0) )
)

```




```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
ggsave(filename = "assets/climate-classification-fs.svg", plot = v1, width=16, height=7.5)

```


### References
#### citations for narrative and data sources

* Narrative: inspired by visualization created by Cédric Scherer
* Map Source: Kottek et al. 2006 (DOI: 10.1127/0941-2948/2006/0130)

<pre>
Based on raster file from:
Kottek, M., J. Grieser, C. Beck, B. Rudolf, and F. Rubel, 
2006: World Map of the Koppen-Geiger climate classification updated. 
Meteorol. Z., 15, 259-263. 
DOI: 10.1127/0941-2948/2006/0130.
</pre>

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


