---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(pdftools)
library(tidyverse)
library(tidytext)
library(syuzhet)
library(vader)
library(ggExtra)
library(ggiraph)
library(purrr)
library(kableExtra)
library(knitcitations)
library(bibtex)

```

TEXT ANALYSIS  

# Ingest table from pdf
## Extracting data for analysis

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Mathias P.R. Reding on Unsplash"}

masthead <- "assets/mathias-p-r-reding-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> When the power of love overcomes the love of power the world will know peace...\
--- Jimi Hendrix\

The role of diamonds in fueling conflict: breaking the link between the illicit transaction of rough diamonds and armed conflict as a contribution to prevention and settlement of conflicts.

***

### Ingest pdf

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "un-resolutions/A_55_PV.79-EN.pdf"
url <- paste0(url_root, url_file)

pdf_file <- url

#pdf_file <- "./archetypes/un-resolutions/A_55_PV.79-EN.pdf"

# Extract the text for all pages
speech_text <- pdf_text(pdf_file) %>% strsplit(split = "\r\n")

speech_text[[1]]
#speech_text

```


### References
#### The citations and data sources used for this case

