---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(pdftools)
library(tidyverse)
library(tidytext)

library(syuzhet)
library(vader)

library(ggExtra)
library(ggiraph)

library(purrr)
library(kableExtra)

library(knitcitations)
library(bibtex)

```


<div class="activity">
TEXT ANALYSIS  
</div>

# Ingest table from pdf
## Extracting data for analysis

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Mathias P.R. Reding on Unsplash"}

masthead <- "assets/mathias-p-r-reding-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> When the power of love overcomes the love of power the world will know peace...\
--- Jimi Hendrix\

The role of diamonds in fueling conflict: breaking the link between the illicit transaction of rough diamonds and armed conflict as a contribution to prevention and settlement of conflicts.

***

### Ingest pdf

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "un-resolutions/A_55_PV.79-EN.pdf"
url <- paste0(url_root, url_file)

pdf_file <- url

#pdf_file <- "./archetypes/un-resolutions/A_55_PV.79-EN.pdf"

# Extract the text for all pages
speech_text <- pdf_text(pdf_file) %>% strsplit(split = "\r\n")

speech_text[[1]]
#speech_text

```


### References
#### The citations and data sources used for this case


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}


# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

