---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(wesanderson)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
TEMPORALS  
</div>

# Global sea levels
## vertical bar chart

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Saad Chaudhry on Unsplash"}

masthead <- "assets/saad-chaudhry-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Sea level rise and destruction of water resources as glaciers melt alone may have horrendous human consequences...\
--- Noam Chomsky\

***


### Ingest the data
#### global sea level by year

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df <- read.csv("archetypes/global-sea-levels/global-sea-levels.csv", header = TRUE, stringsAsFactors = FALSE)
df

```


### Plot
#### standard baseline (0)


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.title = element_text(color = "black", size = 12, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 8),
    plot.caption = element_text(color = "#555555", size = 8),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor = element_blank(), # remove minor gridlines
    panel.grid.major = element_blank(), # remove x (vertical) gridlines
    legend.title = element_blank(), # remove legend title
    legend.text = element_text(color = "black", size = 8),
    legend.position='none'
)

pal <- wes_palette("Zissou1", 21, type = "continuous")

# Plot
v1 <- ggplot(df) + 
  # Vertical bars
  geom_bar(aes(x = year, y = global_sea_level_mm, fill = global_sea_level_mm), stat = "identity", width = 1.89) +
  scale_fill_gradientn(colours = pal) + 
  # ylim(-200, 250) +
  scale_y_continuous(breaks=seq(min(df$global_sea_level_mm), max(df$global_sea_level_mm), length=5), limits=c(min(df$global_sea_level_mm), max(df$global_sea_level_mm))) +
  coord_cartesian(clip = 'off') +
  # Modify theme
  theme_bw() +
  theme_opts +
  # Add title
  labs(title = "Global Sea Levels")

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```

### Plot
#### rescale negative values

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

df_trans <- df
m <- min(df_trans$global_sea_level_mm) # find min
df_trans$global_sea_level_mm <- df_trans$global_sea_level_mm - m

v2 <- ggplot(df_trans) + 
  geom_bar(aes(x = year, y = global_sea_level_mm, fill = global_sea_level_mm), stat = "identity", width = 1.89) +
  scale_fill_gradientn(colours = pal) + 
  # ylim(-200, 250) +
  scale_y_continuous(breaks=seq(min(df_trans$global_sea_level_mm), max(df_trans$global_sea_level_mm), length=5), 
                     limits=c(min(df_trans$global_sea_level_mm), max(df_trans$global_sea_level_mm)), 
                     labels=as.character(round(seq(m, max(df_trans$global_sea_level_mm+m), length=5),2))) +
  coord_cartesian(clip = 'off') +
  theme_bw() +
  theme_opts +
  labs(title = "Global Sea Levels")

girafe(ggobj = v2, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```


### Plot
#### with annotations

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

city_label <- 'Abidjan, Accra, Alexandria, Bangkok, Dakka,\nFuzhou, Guangzhou, Hai Phong, Hong Kong, Jakarta, Karachi,\nKalkota, Lagos, Lomé, London, Manila, Miami,\nNYC, Ningbo, Rangoon, Shanghai, Singapore, Zhanjiang'

v3 <- v2 + 
    geom_hline(yintercept = -m, linetype="dashed", color = "red") +
    geom_vline(xintercept=1860, linetype="dashed", color = "black") +
    annotate("text", x = 1700, y = 170, 
             label = city_label, 
             hjust = 0.0, vjust = 0.0, color = "#333333", size = 3, fontface = 1, family = "inconsolata") +
    annotate("text", x = 1865, y = 0, 
             label = "Rise trend starts", 
             hjust = 0.0, vjust = 1.75, color = "#333333", size = 6, fontface = 2, family = "inconsolata")

girafe(ggobj = v3, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk
# full version
ggsave(filename = "outputs/global-sea-levels-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/global-sea-levels-sm.svg", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative: Observable, Day 19 of 30DayChartChallenge, https://observablehq.com/@terezaif/annual-global-sea-levels
* Data: World Meteorological Organization, Climate Explorer, https://climexp.knmi.nl/getindices.cgi?WMO=PSMSLData/gsl_ann&STATION=global_sea_level&TYPE=i&id=someone@somewhere&NPERYEAR=1

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "" # mostly used in wranglers and analytics
keywords <- 'sea levels'
commands <- 'wes_palette geom_bar'
sources <- 'Observable World-Meteorological-Organization WMO'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

