---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/kamino.css", "../../../z-assemblers/analytics.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/header.html"
      after_body: "../../../z-assemblers/footer.html"
    #self_contained: false
    #lib_dir: libs
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(htmltools) # needed to include html snippets
library(tidyverse)

library(knitcitations)
library(bibtex)

```

<div class="activity">
ANALYTICS
</div>

# DISPERSION
## I want to fix irregularities in my dataset

> Don't call the world dirty because you forgot to clean your glasses...\
--- Aaron Hill\

There are two common metrics to quantify spread.

* __Range__ : The range is the difference between the maximum value and the minimum value of the attribute. The range is simple to calculate and articulate but has shortcomings as it is severely impacted by the presence of outliers and fails to consider the distribution of all other data points in the attributes.
* __Deviation__ : The variance and standard deviation measures the spread, by considering all the values of the attribute. Deviation is simply measured as the difference between any given value (xi) and the mean of the sample (μ). The variance is the sum of the squared deviations of all data points divided by the number of data points.

Interquartile range can be used to identify outliers and to show interval of likely values. The z-score of individual values show how far that observation deviates from typical values. The visual representation of dispersion is a box plot where points within the box are withing interquartile range and points on the whiskers are outside.

***

# Section
## Subsection

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Fold hide as this is not relevant to the task


```


# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```


# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```



# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```



# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```


# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

# cleanbib()
# read.bibtex(file = "./citations.bib")

```


```{r, message=FALSE, warning=FALSE, echo=FALSE}

# echo=FALSE will exclude block from code folding
# Example for including external html content when needed
htmltools::includeHTML("mark-complete-button.html")

```



```{r, child='mark-complete-click.Rmd'}

# JS event handler for button click

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

