---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Ideas Factories
## Scatter plot

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Johny Goerend on Unsplash"}

masthead <- "assets/johny-goerend-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Bourscheid castle in the north of Luxembourg</div>

> A pile of rocks ceases to be a rock pile when somebody contemplates it with the idea of a cathedral in mind...\
--- Antoine Saint-Exupéry\

***


### Ingest the data
#### gdp and innovation rank by country and year

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load csv data file
df_gdp <- read.csv("archetypes/ideas-factories/gdp-per-person-employed-constant-ppp.csv", header = TRUE, stringsAsFactors = FALSE)
df_gdp

df_gii <- read.csv("archetypes/ideas-factories/global-innovation-index.csv", header = TRUE, stringsAsFactors = FALSE)
df_gii

```


### Wrangle the data
#### filter, merge, enrich, select, clean, rename, wow!


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_gdp_filtered <- df_gdp %>% filter(Year == 2020)

df_gii_filtered <- df_gii %>% filter(Indicator == 'Global Innovation Index')
df_gii_filtered <- df_gii_filtered %>% filter(Subindicator.Type == 'Rank')
df_gii_filtered <- df_gii_filtered %>% select(c(Country.ISO3, Country.Name, X2020))

df_combined <- merge(df_gdp_filtered, df_gii_filtered, by.x='Code', by.y='Country.ISO3')

df_combined$REGION <- countrycode(df_combined$Code, origin='iso3c', destination='un.region.name')

df_combined <- df_combined %>% select(c(Code, Entity, GDP.per.person.employed..constant.2017.PPP..., X2020, REGION))

df_combined <- df_combined[complete.cases(df_combined), ]

df_final <- df_combined %>%
  rename(ISO3 = Code,
         COUNTRY = Entity,
         GDP = GDP.per.person.employed..constant.2017.PPP...,
         GII = X2020)

df_final <- df_final %>% rename_with(toupper)
df_final


```


### Plot
#### data points with smoothing


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.grid.major = element_blank(),
    legend.position='top'
  )

# Plot
v1 <- ggplot(df_final, aes(x = GDP, y = GII)) + 
  geom_point(aes( fill = REGION, color = REGION), size = 4, shape = 21) +
  geom_smooth(method="loess", se = FALSE, linetype = 'solid', size = 2, color = '#82A0C2') + # "lm", "glm", "gam", "loess" 
  scale_x_continuous() +
  scale_y_continuous() +
  scale_y_reverse() +
  labs( title = "Ideas Factories",
        subtitle = "Global Innovation and GDP",
        caption = "Source: Cornell INSEAD WIPO",
        x = "GDP per Person Employed, constant PPP, 2020",
        y = "Global Innovation Index, 2020") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```


### Plot with annotations
#### some narrative to help tell the story


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}



  
```


### Save plot
#### as vector or raster image


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/ideas-factories-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/ideas-factories-sm.svg", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative Inspiration: The Economist, Ideas Factories, Global innovation and GDP
* Data Source: Global Innovation Index (GII) 2021, https://www.globalinnovationindex.org/analysis-indicator


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "" # mostly used in wranglers and analytics
keywords <- 'innovation GII'
commands <- 'countrycode geom_smooth scale_y_reverse'
sources <- 'Economist Cornell INSEAD WIPO'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

