---
pagetitle: "Environmental impact of food"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

# Load needed libraries
library(tidyverse)
library(ggiraph)

```

<div class="activity">
CHARTS
</div>

# The carbon footprint of your food
## Bar Vertical Grouped

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Thought Catalog on Unsplash"}

masthead <- "assets/thought-catalog-fnztlIb52gU-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Focus on what you eat, not whether your food is local...\
--- Hannah Ritchie, Our World in Data\

***

### Load the data
#### Where do the emissions from our food come from?

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
df <- read_csv("archetypes/environmental-impact-of-food-by-life-cycle-stage.csv", col_names=TRUE)

# To order the group categories (for chart display) by stage of supply chain
df$SUPPLY_CHAIN <- factor(df$SUPPLY_CHAIN, levels=c("Land use change", 
                          "Farm", 
                          "Animal Feed", 
                          "Processing", 
                          "Transport", 
                          "Retail", 
                          "Packging"))

df

# Determine max emission value
max_val <- max(df$EMISSION)
#max_val

```

### Plot the chart
#### Focus on what you eat, not whether your food is local

```{r draw-plot, message=FALSE, warning=FALSE, echo=TRUE, fig.width=12, fig.height=9, class.source = 'fold-hide'}

# Theme parameters
theme_opts <- theme(
  legend.position="top",
  legend.title = element_blank(),
  text = element_text(size=14),                        # Set font size for plot text (axes labels, legend labels, plot title, etc.)
  axis.ticks = element_blank(),
  panel.grid.major.y = element_line(color="gray", size = 0.1, linetype="longdash"),
  panel.background = element_blank(),
  plot.title = element_text(size=18),                  # Increase font size of plot title text
  plot.background = element_blank(),
  plot.margin = margin(.25, .25, .25, .25, "cm")
)

# Define palette
supply_chain_palette <- c("Land use change" = "#1ea349", 
                          "Farm" = "#a3745e", 
                          "Animal Feed" = "#f36e32", 
                          "Processing" = "#417aac", 
                          "Transport" = "#f04b54", 
                          "Retail" = "#f3ca19", 
                          "Packging" = "#bcb0ac")

# Reorder to sort by Food Product and Emission
v1 <- ggplot(data=df, aes(y=EMISSION, x=reorder(FOOD_PRODUCT,EMISSION), fill=SUPPLY_CHAIN)) + 
  geom_col(position="dodge", stat="identity") +
  scale_fill_manual(values=supply_chain_palette,
                    breaks=c("Land use change", "Farm", "Animal Feed", "Processing", "Transport", "Retail", "Packging")) +
  scale_y_continuous(expand = c(0,0), breaks=seq(0,max_val,5), limits=c(0,max_val+5)) + 
  scale_x_discrete(limits=c("Beef (beef herd)", "Lamb & Mutton", "Cheese", "Beef (dairy herd)", "Dark Chocolate", "Coffee", "Shrimps (farmed)")) + # limit the food products to the top 7
  geom_text(aes(label=EMISSION),
            angle=90,
            hjust=0,
            vjust=ifelse(df$SUPPLY_CHAIN == "Land use change", -4.7, 
                         ifelse(df$SUPPLY_CHAIN == "Farm", -3,
                                ifelse(df$SUPPLY_CHAIN == "Animal Feed", -1.4,
                                       ifelse(df$SUPPLY_CHAIN == "Processing", 0.3,
                                              ifelse(df$SUPPLY_CHAIN == "Transport", 2,
                                                     ifelse(df$SUPPLY_CHAIN == "Retail", 3.7,
                                                            5.4))))))) + 
  coord_cartesian(clip="off") + 
  labs(title = "Food: greenhouse gas emissions across the supply chain", caption = "Source: Our World in Data") +
  theme_opts +
  guides(fill = guide_legend(nrow = 1)) +
  xlab("") + 
  ylab("Greenhouse gas emissions per kilogram of food product\n(kg CO2-equivalents per kg product)")

girafe(ggobj = v1, width_svg = 17, height_svg = 10)

```

### Step by step
#### Draw the base bar chart

```{r step_one, message=FALSE, warning=FALSE, echo=TRUE, fig.width=12, fig.height=9, class.source = 'fold-hide'}

v1 <- ggplot(data=df, aes(y=EMISSION, x=reorder(FOOD_PRODUCT,EMISSION), fill=SUPPLY_CHAIN)) +
  geom_col(position="dodge", stat="identity")

girafe(ggobj = v1, width_svg = 17, height_svg = 10)


```

#### Add bar custom colours and order and limit discrete values

```{r step_two, message=FALSE, warning=FALSE, echo=TRUE, fig.width=12, fig.height=9, class.source = 'fold-hide'}

v1 <- ggplot(data=df, aes(y=EMISSION, x=reorder(FOOD_PRODUCT,EMISSION), fill=SUPPLY_CHAIN)) +
  geom_col(position="dodge", stat="identity") +
  scale_fill_manual(values=supply_chain_palette,
                    breaks=c("Land use change", "Farm", "Animal Feed", "Processing", "Transport", "Retail", "Packging")) +
  scale_y_continuous(expand = c(0,0), breaks=seq(0,max_val,5), limits=c(0,max_val+5)) +
  scale_x_discrete(limits=c("Beef (beef herd)", "Lamb & Mutton", "Cheese", "Beef (dairy herd)", "Dark Chocolate", "Coffee", "Shrimps (farmed)"))

girafe(ggobj = v1, width_svg = 17, height_svg = 10)


```

#### Add data labels

```{r step_three, message=FALSE, warning=FALSE, echo=TRUE, fig.width=12, fig.height=9, class.source = 'fold-hide'}

v1 <- ggplot(data=df, aes(y=EMISSION, x=reorder(FOOD_PRODUCT,EMISSION), fill=SUPPLY_CHAIN)) +
  geom_col(position="dodge", stat="identity") +
  scale_fill_manual(values=supply_chain_palette,
                    breaks=c("Land use change", "Farm", "Animal Feed", "Processing", "Transport", "Retail", "Packging")) +
  scale_y_continuous(expand = c(0,0), breaks=seq(0,max_val,5), limits=c(0,max_val+5)) +
  scale_x_discrete(limits=c("Beef (beef herd)", "Lamb & Mutton", "Cheese", "Beef (dairy herd)", "Dark Chocolate", "Coffee", "Shrimps (farmed)")) +
  geom_text(aes(label=EMISSION),
            angle=90,
            hjust=0,
            vjust=ifelse(df$SUPPLY_CHAIN == "Land use change", -4.7,
                         ifelse(df$SUPPLY_CHAIN == "Farm", -3,
                                ifelse(df$SUPPLY_CHAIN == "Animal Feed", -1.4,
                                       ifelse(df$SUPPLY_CHAIN == "Processing", 0.3,
                                              ifelse(df$SUPPLY_CHAIN == "Transport", 2,
                                                     ifelse(df$SUPPLY_CHAIN == "Retail", 3.7,
                                                            5.4))))))) +
  coord_cartesian(clip="off")

girafe(ggobj = v1, width_svg = 17, height_svg = 10)


```

#### Beautify by adding theme options

```{r step_four, message=FALSE, warning=FALSE, echo=TRUE, fig.width=12, fig.height=9, class.source = 'fold-hide'}

v1 <- ggplot(data=df, aes(y=EMISSION, x=reorder(FOOD_PRODUCT,EMISSION), fill=SUPPLY_CHAIN)) +
  geom_col(position="dodge", stat="identity") +
  scale_fill_manual(values=supply_chain_palette,
                    breaks=c("Land use change", "Farm", "Animal Feed", "Processing", "Transport", "Retail", "Packging")) +
  scale_y_continuous(expand = c(0,0), breaks=seq(0,max_val,5), limits=c(0,max_val+5)) +
  scale_x_discrete(limits=c("Beef (beef herd)", "Lamb & Mutton", "Cheese", "Beef (dairy herd)", "Dark Chocolate", "Coffee", "Shrimps (farmed)")) +
  geom_text(aes(label=EMISSION),
            angle=90,
            hjust=0,
            vjust=ifelse(df$SUPPLY_CHAIN == "Land use change", -4.7,
                         ifelse(df$SUPPLY_CHAIN == "Farm", -3,
                                ifelse(df$SUPPLY_CHAIN == "Animal Feed", -1.4,
                                       ifelse(df$SUPPLY_CHAIN == "Processing", 0.3,
                                              ifelse(df$SUPPLY_CHAIN == "Transport", 2,
                                                     ifelse(df$SUPPLY_CHAIN == "Retail", 3.7,
                                                            5.4))))))) +
  coord_cartesian(clip="off") +
  labs(title = "Food: greenhouse gas emissions across the supply chain", caption = "Source: Our World in Data") +
  theme_opts +
  guides(fill = guide_legend(nrow = 1)) +
  xlab("") +
  ylab("Greenhouse gas emissions per kilogram of food product\n(kg CO2-equivalents per kg product)")

girafe(ggobj = v1, width_svg = 17, height_svg = 10)


```

### References
#### The citations and data sources used for this case

* Narrative sources: Our World in Data, _You want to reduce the carbon footprint of your food? Focus on what you eat, not whether your food is local_, [GO](https://ourworldindata.org/food-choice-vs-eating-local){target="_blank"}

<pre>
@misc{ritchie_2020_you,
  author = {Ritchie, Hannah},
  month = {01},
  title = {You want to reduce the carbon footprint of your food? Focus on what you eat, not whether your food is local},
  url = {https://ourworldindata.org/food-choice-vs-eating-local},
  urldate = {2021-02-15},
  year = {2020},
  organization = {Our World in Data}
}
</pre>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
