---
pagetitle: "How far can you go with 1 gallon of gas?"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(ggimage)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
# font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
SEMIOGRAPHIC  
</div>

# How far can you go with 1 gallon of gas?
# isotypes

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Jeremy Bezanger on Unsplash"}

masthead <- "assets/jeremy-bezanger-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> quote...\
--- attribution\

***


### Ingest
#### number of aircraft carriers in operation worldwide as of December 2019


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_ingest <- read.csv("archetypes/mpg-by-car/mpg-by-car.csv", header = TRUE)
df_ingest

```



```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_cars_top <- 
  df_ingest %>%
  pivot_longer(cols = c("city08", "cityA08"), 
               names_to = "fuel",
               values_to = "mpg") %>%
  filter(mpg > 0) %>%
  group_by(make) %>%
  summarize(median = median(mpg)) %>%
  ungroup()  %>% 
  arrange(-median) %>% 
  top_n(20, median) %>% 
  mutate(make = fct_shuffle(make), make_id =  as.numeric(make)) #%>%
  # dplyr::select(-median) #%>% 
  #gather(median, -make, -make_id)

df_cars_top

lines <-
  df_cars_top %>% 
  group_by(make_id) %>% 
  summarize(val = unique(make_id) + 0.5) %>% 
  add_row(make_id = 0, val = 0.5)

lines

```



### Plot
#### tbd

```{r, message=FALSE, warning=FALSE, echo=TRUE, fig.align='center', out.width="100%"}

set.seed(2019)
car <- "archetypes/mpg-by-car/car.png"

v1 <- 
  ggplot(df_cars_top, 
         aes(make_id, median, group = make_id)) +
    ## lower tire track
    geom_segment(aes(x = make_id - 0.15, xend = make_id - 0.15, 
                     y = 0, yend = median),
                 size = 1.7) +
    ## upper tire track
    geom_segment(aes(x = make_id + 0.15, xend = make_id + 0.15, 
                     y = 0, yend = median),
                 size = 1.7) +
    ## car
    geom_image(aes(make_id, median + 1.5, image = car), size = 0.05, asp = 0.7) +
    ## guard stripes 
    geom_vline(data = lines,
               aes(xintercept = val),
               color = "white",
               linetype = "dashed",
               size = 0.3) +
    ## labels manufacturer
    geom_text(aes(make_id, -16, label = make),
              color = "grey80",
              hjust = 0,
              family = "Montserrat",
              size = 5,
              fontface = "bold") +
    scale_x_continuous(expand = c(0.01, 0.01)) +
    scale_y_continuous(limits = c(-17, 102), 
                       expand = c(0.001, 0.001),
                       breaks = seq(0, 100, by = 10),
                       labels = c("0 miles", as.character(seq(10, 100, by = 10)))) + 
    coord_flip() + 
    theme_bw() +
    theme(axis.ticks.x = element_blank(),
          axis.text.x = element_text(size = 16),
          axis.ticks.y = element_blank(),
          axis.text.y = element_blank(),
          plot.title = element_text(size = 32),
          plot.subtitle = element_text(size = 18,
                                       lineheight = 1.2),
          plot.caption = element_text(size = 16,
                                      color = "grey80"),
          panel.border = element_blank(),
          panel.grid.major.x = element_line(color = "grey10", 
                                            size = 0.2),
          plot.margin = margin(12, 18, 12, 12)) +
      labs(x = NULL, y = NULL,
           title = "How far can you go with 1 gallon of gas?",
           subtitle = "Top 20 most energy efficient brands in city driving. Estimates are based on median MPG and MPGe of all models since 1984.\n\n",
           caption = "\n\nVisualization by Cédric Scherer  |  Data: EPA  |  Icon: mynamepong via flaticon.com")

 girafe(ggobj = v1, width_svg = 16, height_svg = 12,
        options = list(opts_sizing(rescale = TRUE, width = 1)))

```


# References
## The citations and data sources used for this case

source: <a href="https://www.statista.com/chart/6483/the-worlds-aircraft-carrier-fleets/" target="_blank">China Commissions Its Second Aircraft Carrier Article</a>

<pre>
@misc{niallmccarthy_2019_infographic,
  author = {Niall McCarthy},
  month = {12},
  publisher = {Statista},
  title = {Infographic: China Commissions Its Second Aircraft Carrier},
  url = {https://www.statista.com/chart/6483/the-worlds-aircraft-carrier-fleets/},
  urldate = {2021-07-19},
  year = {2019},
  organization = {Statista Infographics}
}
</pre>

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

