---
pagetitle: "South Sudan Events"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include = FALSE, results = "hide"}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(sf)
library(geojsonio)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# South Sudan Events
## hexbin

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Randy Fath on Unsplash"}

masthead <- "assets/randy-fath-nsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Dinka tribe, South Sudan</div>

> The journey of my people from conflict to peace, independence and freedom was costly,\
  and characterized by economic and political marginalization, a prolonged war, humanitarian disasters,\
  the loss of millions of lives and untold human suffering...\
--- South Sudanese President Salva Kiir, speech to the United Nations General Assembly, 2014\

***

### Map Sources
#### geojson state, country, and abeyi boundaries

```{r, message = FALSE, warning = FALSE, echo = FALSE, results = "hide", class.source='fold-show'}

# Load map sources
# Shape files and data
# ++++++++++++++++++++
# state_boundaries
# county
# abeyi
# ++++++++++++++++++++

# Borders
state_boundaries <- st_read("archetypes/south-sudan/maps/ss-state.geojson")
county <- st_read("archetypes/south-sudan/maps/ss-county.geojson")
abeyi <- st_read("archetypes/south-sudan/maps/ss-abeyi.geojson")

head(as.data.frame(state_boundaries))
head(as.data.frame(county))
head(as.data.frame(abeyi))

```


### Ingest the data
#### conflict data


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

conflict_data = read.csv("archetypes/south-sudan/conflict-data-ssd.csv", header = TRUE, stringsAsFactors = FALSE)
conflict_data

iati_activities = read.csv("archetypes/south-sudan/iati-activities.csv", header = TRUE, stringsAsFactors = FALSE)
# iati_activities

qc_conflict = read.csv("archetypes/south-sudan/qc-conflict-data-ssd.csv", header = TRUE, stringsAsFactors = FALSE)
# qc_conflict

```


### Plot
#### as points and no binning


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

# theme parameters
theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  # panel.background = element_blank(),
  panel.background = element_rect(fill = "#ffffff"),
  panel.border = element_blank(),
  # plot.background = element_blank(),
  plot.background = element_rect(fill = "#ffffff")
)

transparent_fill <- rgb(0, 0, 0, max = 255, alpha = 0, names = "transparent")

# In order of layer placement top -> down
v1 = ggplot() + 
  geom_point(data=conflict_data, aes(x=longitude, y=latitude), color="orange", size=3) +
  geom_sf(data = state_boundaries, color="#333333", fill = transparent_fill, size=1.0) +
  geom_sf(data = county, color="#333333", fill = transparent_fill, size=0.5) +
  geom_sf(data = abeyi, color="#333333", fill = transparent_fill, size=0.5, linetype = "dashed") +
  scale_fill_gradient(low="orange", high="red",trans="log10") +
  scale_x_continuous() +
  scale_y_continuous() +
  coord_sf() +
  theme_bw() +
  labs(x = NULL, # Longitude
       y = NULL, # Latitude
       title = NULL, 
       subtitle = NULL) +
  theme_opts

girafe( ggobj = v1, width_svg = 16, height_svg = 12, options = list( opts_sizing(rescale = TRUE, width = 0.9) ))

```



### Plot
#### as hex geom, 40 bins


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}


transparent_fill <- rgb(0, 0, 0, max = 255, alpha = 0, names = "transparent")

# In order of layer placement top -> down
v2 = ggplot() + 
  geom_hex(data=conflict_data, aes(x=longitude, y=latitude), color="#ffffff", size=0.5, bins=40) +
  geom_sf(data = state_boundaries, color="#333333", fill = transparent_fill, size=1.0) +
  geom_sf(data = county, color="#333333", fill = transparent_fill, size=0.5) +
  geom_sf(data = abeyi, color="#333333", fill = transparent_fill, size=0.5, linetype = "dashed") +
  scale_fill_gradient(low="orange", high="red",trans="log10") +
  scale_x_continuous() +
  scale_y_continuous() +
  coord_sf() +
  theme_bw() +
  labs(x = NULL, # Longitude
       y = NULL, # Latitude
       title = NULL, 
       subtitle = NULL) +
  theme_opts

girafe( ggobj = v2, width_svg = 16, height_svg = 12, options = list( opts_sizing(rescale = TRUE, width = 0.9) ))

```


### Plot
#### bin2d geom, 25 bins


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v3 = ggplot() + 
  geom_bin2d(data=conflict_data, aes(x=longitude, y=latitude), color="#ffffff", size=0.5, bins=25) +
  geom_sf(data = state_boundaries, color="#333333", fill = transparent_fill, size=1.0) +
  geom_sf(data = county, color="#333333", fill = transparent_fill, size=0.5) +
  geom_sf(data = abeyi, color="#333333", fill = transparent_fill, size=0.5, linetype = "dashed") +
  scale_fill_gradient(low="orange", high="red",trans="log10") +
  scale_x_continuous() +
  scale_y_continuous() +
  coord_sf() +
  theme_bw() +
  labs(x = NULL, # Longitude
       y = NULL, # Latitude
       title = NULL, 
       subtitle = NULL) +
  theme_opts

girafe( ggobj = v3, width_svg = 16, height_svg = 12, options = list( opts_sizing(rescale = TRUE, width = 0.9) ))

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "assets/ssd-hexbin-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "assets/ssd-hexbin-sm.svg", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative Inspiration: TBD
* Data Source: TBD


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
