---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    #self_contained: false
    #lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(htmltools) # needed to include html snippets
library(tidyverse)

library(knitcitations)
library(bibtex)

```

<div class="activity">
WRANGLERS  
</div>

# Link analysis
## I want to fix irregularities in my dataset

> Don't call the world dirty because you forgot to clean your glasses...\
--- Aaron Hill\

Link analysis is a visual method extending the patterns of social network analysis and graph theory. Link Analysis has found wide-spread application in law enforcement for its utility to discover insight about the nature of relationships between entities. This chapter describes the link analysis techniques that can be applied to the results of the models of information activity, specifically where populating the data model, transforms, and mining (associations) has yielded relational structured data.

Link Analysis patterns are closely related to social network methods of analysis where a set of entities and the set of relationships between them are examined. It employs graph layout patterns to assist in the exploration process and enhances layout views with additional visual cues. These enhancements are typically configuring the visual properties for node and edge rendering described earlier.

Substance

The basic goal of link analysis is to examine networks of actors and the analysis of relational configurations or “actor constellations” (Scharpf 1997). Using the link analysis approach, An example may be examining the relations among countries in cases of trade, the networks of organizations, or the associations of individuals.

1. Finding Relevant Actors and Finding Meaningful Relationships
An essential, initial activity in preparing data for link analysis is to identify relevant entities and actors in the
transactional data. Applying domain specifi c knowledge is very important for this task. In order to support effective link analysis, linkages between entities should represent meaningful relationships as defined by the domain.

Representation Structures

Since the structure of a given network is analyzed through specifi c measures of various structural properties, a visualization should make these properties visible.
• Connectedness Perspective
• Profile Perspective
• Partitioning Perspective

The first of the two main categories comprises those measures which are solely dependent on the presence or absence of links in the network. They are called the syntactical attributes of the network because they are completely determined by the underlying network structure no matter what the network actually describes. On the other hand there are properties which do not depend on the relationships constituting the network. These are called the semantic attributes because they relate elements of the abstract graph to their real counterparts. Layout and attribute properties such as size, shape, color, etc. According to the respective classes of properties we subdivide the design specification into layout specification (positional properties) and rendering specification (retinal properties)

Connectedness Perspective

On the one hand, there are structural methods aiming at a detailed description of whether and how the different actors in the network are connected to each other via direct and or indirect links of communication, support, or other flows of policy resources. Layout Considerations A straightforward example are ego-centered networks, where it is reasonable to fi x the position of ego to lie in the center of the drawing. Another example is a hierarchy, where subordinates be placed beneath their super-ordinates.

Profile Perspective

The other type of structural analysis is less interested whether actors are directly or indirectly connected, but more into the similarity or dissimilarity of profiles of relations in which an actor is involved. Actors with an identical or nearly identical profile then are said to have structural equivalent network positions. Assigning Node Attributes Based on our simple data structure, our node table provides interesting attributes which may be useful to highlight in our representation. We can assign a variety of visual properties to our nodes based on a data value. For example, we can color, size or shape these objects in proportion to a specific attribute. Assigning Edge Attributes Our edge table provides additional opportunity to represent an element of interest. Again the options for styling our edge properties include setting color or size.


***



# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

# cleanbib()
# read.bibtex(file = "./citations.bib")

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

