---
pagetitle: "Euro Debt Crisis"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE, dev='svg')
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggraph)
library(igraph)
library(graphlayouts)
library(tidygraph)
library(ggforce)
library(ggsankey)
library(ggalluvial)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
GRAPHS
</div>

# Euro Debt Crisis
## sankey

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Marjan Blan on Unsplash"}

# masthead <- "assets/marjan-blan-unsplash.jpg"
# knitr::include_graphics(masthead, dpi=72)

```

> We are defined not by our borders but by our bonds...\
--- Barack Obama\

***

### Ingest
#### creditor, debtor, and amount

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read.csv("archetypes/euro-debt-crisis/euro-debt-crisis.csv", header = TRUE, stringsAsFactors = FALSE)
df

```


### View
#### geom_alluvium


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}

theme_opts <- theme(
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  plot.background = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  legend.position = "none",
  legend.title = element_blank()
)

v1 <- ggplot(data = df,
       aes(axis1 = creditor, axis2 = debtor,
           y = amount)) +
  geom_alluvium(aes(fill = amount)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("creditor", "debtor"), expand = c(.2, .05)) +
  ggtitle("passengers on the maiden voyage of the Titanic",
          "stratified by demographics and survival") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 14,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


### View
#### geom_sankey


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}

df_long <- df %>%
  make_long(creditor, debtor, amount)
#df_long <- filter(df_long, nchar(as.character(next_x)) > 0)
df_long

v2 <- ggplot(df_long, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node))) +
  geom_sankey()

girafe(ggobj = v2, width_svg = 16, height_svg = 14,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


### View
#### geom_parallel_sets


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.align='center', out.width="100%"}

data <- gather_set_data(df, 1:3)
data <- filter(data, x != "amount")
data

v3 <- ggplot(data, aes(x, id = id, split = y, value = amount)) +
  geom_parallel_sets(aes(fill = creditor), alpha = 0.3, axis.width = 0.1) +
  geom_parallel_sets_axes(expand = c(0, 0), axis.width = 0.05, fill = "white", color = "black", alpha = 0.8) +
  geom_parallel_sets_labels(colour = 'black') +
  theme_bw() +
  theme_opts

girafe(ggobj = v3, width_svg = 16, height_svg = 14,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


### Prepare data [Wrangle]
#### Format the data into a graph data frame 


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}



```


### Plot
#### nicely


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}



```


### References
#### citations for narrative and data sources

* Narrative, Visualign, Number of neighbors for world countries, https://visualign.org/2011/10/06/number-of-neighbors-for-world-countries/
* Data: https://docs.google.com/spreadsheets/d/1agWAs620UntEQGY0yXUo5_C6zZesLEjBj1TVd3tTEDc/edit#gid=0


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


