---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE, dev='svg')
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(ggraph)
library(igraph)
library(graphlayouts)
library(tidygraph)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
GRAPHS
</div>

# Country Borders
## Node-links - Association

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Marjan Blan on Unsplash"}

masthead <- "assets/marjan-blan-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> We are defined not by our borders but by our bonds...\
--- Barack Obama\

***

### Ingest
#### border graph

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_path <- "archetypes/country-borders/country-borders.csv"
df <- read.csv(df_path, header = TRUE, stringsAsFactors = FALSE)
df

```


### Prepare data [Wrangle]
#### Filtering only a few countries of our interest


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_wrangle <- df %>% rename(to='target', from='source')

# enrich with UN region name
df_wrangle$from_region <- countrycode(df_wrangle$from, origin='country.name', destination='un.region.name')
df_wrangle$to_region <- countrycode(df_wrangle$to, origin='country.name', destination='un.region.name')

df_wrangle <- df_wrangle %>% filter(from_region == 'Africa' & to_region == 'Africa' )

df_wrangle

```


### Prepare data [Wrangle]
#### Format the data into a graph data frame 


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Convert data to graph data frame
# directed FALSE means no flow. It's just an association
g <- graph.data.frame(df_wrangle, directed = FALSE)
g

```


### Prepare data [Wrangle]
#### Associating different attributes for your Nodes 

Creating numerical fields for the Nodes set in order to attribute the nodes size and/or color  

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}
## Creating centrality numerical field for the Nodes

# centrality_alpha()
# centrality_authority() 
# centrality_betweenness() 
# centrality_power() 
# centrality_closeness() 
# centrality_eigen() 
# centrality_hub() 
# centrality_pagerank() 
# centrality_subgraph() 
# centrality_degree() 
# centrality_edge_betweenness() 
# centrality_manual() 
# centrality_closeness_harmonic() 
# centrality_closeness_residual() 
# centrality_closeness_generalised() 
# centrality_communicability() 
# centrality_communicability_odd() 
# centrality_communicability_even() 
# centrality_subgraph_odd() 
# centrality_subgraph_even() 
# centrality_katz() 
# centrality_betweenness_network() 
# centrality_betweenness_current() 
# centrality_betweenness_communicability() 
# centrality_betweenness_rsp_simple() 
# centrality_betweenness_rsp_net() 
# centrality_information() 
# centrality_decay() 
# centrality_random_walk() 
# centrality_expected()

cg <- g %>% 
    as_tbl_graph() %>% 
    activate(nodes) %>% 
  # associating random numerical value to nodes to differentiate their colors and sizes
    mutate(centrality  = centrality_betweenness())



```


### Prepare data [Wrangle]
#### Associating different attributes for your Nodes


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

## Creating group numerical field for the Nodes

# group_components() 
# group_edge_betweenness() 
# group_fast_greedy() 
# group_infomap() 
# group_label_prop() 
# group_leading_eigen() 
# group_louvain() 
# group_optimal() 
# group_spinglass() 
# group_walktrap() 
# group_biconnected_component()

cg <- cg %>% 
  activate(nodes) %>%
  # use functions to compute numerical values to attribute the edge width and/or color
  mutate(group = group_louvain())

cg

```


## Associating different attributes for the Edges between Nodes 
### Creating new numerical fields (smaller values) in order to attribute the edge width and/or color  


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

cg <- cg %>% 
    activate(edges) %>% 
  # computing random number (n) which are between 0 and 1 to attribute the edge width and/or color
    #mutate(edge_weights = runif(n()))
  ## computes numbers between 0 and 1 according to distance in km
  mutate(edge_weights = log10(km)/50)

cg


```


## Layout & Aesthetic Parameters
### Choose the types of Edges you would like to display


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Layouts can be computationally intensive
# Un-comment only for use

# igraph
# dh <- create_layout(cg, layout = 'dh')
# fr <- create_layout(cg, layout = 'fr')
# gem <- create_layout(cg, layout = 'gem')
# lgl <- create_layout(cg, layout = 'lgl')
# sugiyama <- create_layout(cg, layout = 'sugiyama')
# star <- create_layout(cg, layout = 'star')
# kk <- create_layout(cg, layout = 'kk', maxiter = 100)
# drl <- create_layout(cg, layout = 'drl')
# linear_straight <- create_layout(cg, layout = 'linear')
# linear_circular <- create_layout(cg, layout = 'linear' , circular = TRUE)

# ggraph
# arc <- create_layout(cg, layout = 'linear')
# arc_circular <- create_layout(cg, layout = 'linear', circular = TRUE)
# stress <- create_layout(cg, layout = 'stress')
# sparse_stress <- create_layout(cg, layout = 'sparse_stress')
# backbone <- create_layout(cg, layout = 'backbone')
# pmds <- create_layout(cg, layout = 'pmds')
# eigen <- create_layout(cg, layout = 'eigen')
# centrality <- create_layout(cg, layout = 'centrality')
# focus <- create_layout(cg, layout = 'focus')
# dendrogram <- create_layout(cg, layout = 'dendrogram')
# unrooted <- create_layout(cg, layout = 'unrooted')
# matrix <- create_layout(cg, layout = 'matrix')
# hive <- create_layout(cg, layout = 'hive')
# fabric <- create_layout(cg, layout = 'fabric')

# graphlayouts
nicely <- create_layout(cg, layout = "nicely")
# stress <- create_layout(cg, layout = "stress")
# radial <- create_layout(cg, layout = "focus", focus = 1)

```


## Layout & Aesthetic Parameters
### Choose the types of Edges you would like to display


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Edge Types
# geom_edge_arc
# geom_edge_arc0
# geom_edge_arc2
# geom_edge_density
# geom_edge_diagonal
# geom_edge_diagonal0
# geom_edge_diagonal2
# geom_edge_elbow
# geom_edge_elbow0
# geom_edge_elbow2
# geom_edge_fan
# geom_edge_fan0
# geom_edge_fan2
# geom_edge_hive
# geom_edge_hive0
# geom_edge_hive2
# geom_edge_link
# geom_edge_link0
# geom_edge_link2
# geom_edge_loop
# geom_edge_loop0

```



### Plot
#### nicely

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    # plot.margin = unit(c(1.5,1,1,1), "in"),
    legend.position='none'
)

v1 <- ggraph(nicely) + 
  #geom_edge_link(aes(colour = factor(km), edge_width = edge_weights)) + 
  geom_edge_link(aes(colour = factor(km))) +
  geom_node_point(aes(color = group, size = centrality)) +
  geom_node_text(aes(label = name)) +
  scale_color_gradient(low = "green", high = "blue", na.value = NA) +
  scale_size(range = c(1,6)) +
  theme_graph()+
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)


```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/country-borders-fs.svg", plot = v1, width=720/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/country-borders-sm.svg", plot = v1, width=2.25, height=2.25)

```



### References
#### citations for narrative and data sources

* Narrative, Visualign, Number of neighbors for world countries, https://visualign.org/2011/10/06/number-of-neighbors-for-world-countries/
* Data: https://docs.google.com/spreadsheets/d/1agWAs620UntEQGY0yXUo5_C6zZesLEjBj1TVd3tTEDc/edit#gid=0

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "" # mostly used in wranglers and analytics
keywords <- 'country borders'
commands <- 'graph_from_data_frame create_layout'
sources <- 'Economist Nextstrain'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


