---
pagetitle: "Vietnam Organic Market"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

# Load needed libraries
library(tidyverse)
library(reshape2)
library(ggiraph)

```

<div class="activity">
CHARTS
</div>

# Vietnam Organic Market
## Bar Horizontal Grouped


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by René DeAnda on Unsplash"}

masthead <- "assets/rene-deanda-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> When eating fruit, remember who planted the tree; when drinking clear water, remember who dug the well...\
--- Vietnamese Proverb\

***

Vietnam imports a diverse number of organic food and beverage products to meet consumer demand for items that cannot be grown or produced locally, a majority of which are fresh fruits and vegetables and processed products.  A recent report of the USDA Foreign Agriculture Service analyzed export trends and foresee Vietnam as a potential growth market for imported organic food and beverage products.  Let's take a closer look at the and use a horizontal grouped bar chart to visualize the results.

### Ingest
#### U.S. Organic Agricultural Exports to Vietnam in 2015-2020

List of Products

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

products <- read.csv("archetypes/organic-exports/usda-gats-product-group-organics.csv", header = TRUE, stringsAsFactors = FALSE)
products

```

Exports to Vietnam

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
df <- read.csv("archetypes/organic-exports/usda-gats-organics-vietnam-data.csv", header = TRUE, stringsAsFactors = FALSE)

df$X2017 <- as.integer(df$X2017)
df$X2019 <- as.integer(df$X2019)
df$X2020 <- as.integer(df$X2020)

df

```

### Wrangle
#### convert from wide to long form

The year columns become a factored column that we can use for grouping or as a visual variable.

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Convert wide to long
df_long <- melt(df, id.vars=c("Partner", "HS.Code", "Product"))
df_long

# Note: value is in thousands of dollars

```


### Plot
#### group by product


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 1920/72, fig.height = 1080/72, out.width = "100%"}

# Theme parameters
theme_opts <- theme(
  legend.position="top",
  legend.title = element_blank(),
  text = element_text(size=16),                       # Set font size for plot text (axes labels, legend labels, plot title, etc.)
  axis.title = element_blank(),                       # Remove x and y axes titles
  axis.ticks.y = element_blank(),
  axis.ticks.x = element_blank(),
  panel.background = element_blank(),
  plot.title = element_text(size=18),                 # Increase font size of plot title text
  plot.background = element_blank()
)

# Make the plot
v1 <- ggplot(df_long, aes(x = value, y = Product, fill = variable)) +
  geom_bar(stat = "identity", position = position_dodge(0.7), width = 0.8) +
  scale_x_continuous() +
  theme_minimal() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
      options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```


### Plot
#### removing zero values

Let's remove the zero values and see how it effects the chart.

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Remove zero values
df_long <- filter(df_long, value > 0)
df_long

```

Notice the difference?

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 1920/72, fig.height = 1080/72, out.width = "100%"}

# Theme parameters
theme_opts <- theme(
  legend.position="top",
  legend.title = element_blank(),
  text = element_text(size=16),                       # Set font size for plot text (axes labels, legend labels, plot title, etc.)
  axis.title = element_blank(),                       # Remove x and y axes titles
  axis.ticks.y = element_blank(),
  axis.ticks.x = element_blank(),
  panel.background = element_blank(),
  plot.title = element_text(size=18),                 # Increase font size of plot title text
  plot.background = element_blank()
)

# Make the plot
v2 <- ggplot(df_long, aes(x = value, y = Product, fill = variable)) +
  geom_bar(stat = "identity", position = position_dodge(0.7), width = 0.8) +
  scale_x_continuous() +
  theme_minimal() +
  theme_opts

girafe(ggobj = v2, width_svg = 1280/72, height_svg = 720/72,
      options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```


### Plot
#### group by year

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 1920/72, fig.height = 1080/72, out.width = "100%"}

# Make the plot
v3 <- ggplot(df_long, aes(x = value, y = variable, fill = Product)) +
  geom_bar(stat = "identity", position = position_dodge(0.7), width = 0.8) +
  theme_minimal() +
  theme_opts

girafe(ggobj = v3, width_svg = 1280/72, height_svg = 720/72,
      options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```

Comparison against a stacked bar

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 1920/72, fig.height = 1080/72, out.width = "100%"}

# Make the plot
v4 <- ggplot(df_long, aes(x = value, y = variable, fill = Product)) +
  geom_bar(stat = "identity", position = "stack", width = 0.5) +
  theme_minimal() +
  theme_opts

girafe(ggobj = v4, width_svg = 1280/72, height_svg = 720/72,
      options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source = 'fold-hide'}

# eval = FALSE as default; set to TRUE for production outputs

# full version
ggsave(filename = "assets/vietnam-organic-market-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "assets/vietnam-organic-market-sm.png", plot = v1, width=4, height=2.25)

```


### References
#### The citations and data sources used for this case

* Narrative sources: Vietnam: Vietnam Organic Market, [GO](https://www.fas.usda.gov/data/vietnam-vietnam-organic-market){target="_blank"}
* Data sources: USDA, Foreign Agricultural Service, Global Agriculture Trade System (gats), [GO](https://apps.fas.usda.gov/gats/ExpressQuery1.aspx){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
