---
pagetitle: "Diamonds"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Diamonds
## Sort

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Edgar Soto on Unsplash"}

masthead <- "assets/edgar-soto-gb0BZGae1Nk-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> The focus now is on citizen activism, where citizens express themselves in a peaceful and nonviolent way....\
--- Promise Mkwananzi\

***

### Load data


```{r load raw data,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df<-read.csv('./archetypes/diamonds/diamonds.csv', header = TRUE, stringsAsFactors = FALSE)
set.seed(123)
index <- sample(1:nrow(df), 100)
df_1<-df[index,]%>%
  select(carat, cut, color,clarity,price)
row.names(df_1)<-NULL


```



```{r Styling Data Set, echo=FALSE}
#NOT TO BE USED AS SOLUTION


df_tmp <- df_1%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)
df_tmp
#NOT TO BE USED AS SOLUTION 

```

Sort a dataset from a given reference with set order

Here is a reference list for "clarity" based on the <a href = "https://en.wikipedia.org/wiki/Diamond_clarity" target="_blank"> modern GIA grading system </a>.

```{r, message=FALSE, echo=FALSE}

reference<-c('IF','VVS1','VVS2','VS1','VS2','SI1','SI2','I1')

reference

```

Sort the order following the reference list.

```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 


df_2<-df_1%>% arrange(factor(clarity, levels = reference))


```


```{r Styling Data Set1, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_2%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(4, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)
df_tmp
#NOT TO BE USED AS SOLUTION 

```

### Sort a dataset by column ascending

Sort a number column "carat".

```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_3<-df_1%>%arrange(carat)

```

```{r Styling Data Set2, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_3%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(1, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)
df_tmp
#NOT TO BE USED AS SOLUTION 

```

Sort a string column "cut".

```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_4 <- df_1 %>% arrange(cut)

```


```{r Styling Data Set3, echo=FALSE}

#NOT TO BE USED AS SOLUTION

df_tmp <- df_4%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(2, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)
df_tmp

#NOT TO BE USED AS SOLUTION 

```


### Sort a dataset by column descending

Sort a number column "price".

```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_5<-df_1%>%arrange(desc(price))


```

```{r Styling Data Set4, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_5%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(5, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)
df_tmp
#NOT TO BE USED AS SOLUTION 

```


Sort a string column "color".

```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_6<-df_1%>%arrange(desc(color))


```

```{r Styling Data Set5, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_6%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(3, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)
df_tmp
#NOT TO BE USED AS SOLUTION 

```

## Sort by several columns

Let's sort by ascending "price" and descending "carat".

```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 
df_7<-df_1%>%arrange(price,desc(carat))


```

```{r Styling Data Set6, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df_7%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
column_spec(c(1,5), bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)
df_tmp
#NOT TO BE USED AS SOLUTION 

```



```{r draw-plot, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width= 1920/72, fig.height = 1080/72, out.width = "100%"}
v1 <- ggplot( data=df, aes(carat, price, colour=clarity)) +
    geom_point(alpha = 0.5, size = .75, position="jitter") +
    scale_colour_brewer(
        guide = guide_legend(title = NULL, reverse=T,
            override.aes = list(alpha = 1))) +
    theme_minimal()


girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72, options =
list(opts_sizing(rescale = TRUE, width = 1.0)))
```



### References
#### citations for narrative and data sources

* Narrative sources: Diamond Clarity, [GO](https://en.wikipedia.org/wiki/Diamond_clarity){target="_blank"}

#### The data source was built in R. Use function data() in the console to view available datasets.


<pre>
@misc{wikipedia_2021_diamond,
  author = {Wikipedia},
  month = {04},
  title = {Diamond clarity},
  url = {https://en.wikipedia.org/wiki/Diamond_clarity},
  urldate = {2021-06-05},
  year = {2021},
  organization = {Wikipedia}
}
</pre>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
