---
pagetitle: "Food Consumption by CO2 Emissions"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(forcats)
library(ggridges)
library(ggiraph)
library(wesanderson)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# Food Consumption by CO2 Emissions
## Ridgeline Plot


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Alejandro Rugama on Unsplash"}

masthead <- "assets/alejandro-rugama-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> What you do makes a difference, and you have to decide what kind of difference you want to make...\
--- Dr Jane Goodall

***

### Ingest
#### country, food_category, consumption, co2_emmission

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load data

food_consumption = read.csv("archetypes/food_consumption-by-co2-emissions/food_consumption-by-co2-emissions.csv", header = TRUE, stringsAsFactors = TRUE)
food_consumption

```


### Wrangle
#### filter and order


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

food_consumption <- food_consumption %>% filter(co2_emmission>=10)

food_consumption <- food_consumption %>% mutate(food_category = fct_reorder(food_category,co2_emmission))

food_consumption

```


### Plot
#### standard ridgeline

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 1920/72, fig.height = 1080/72, out.width = "100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    legend.position='none'
)

pal <- wes_palette("Zissou1", 10, type = "continuous")

v1 = ggplot(food_consumption, aes(x=co2_emmission, y=food_category, fill=food_category)) +
    geom_density_ridges() +
    scale_x_continuous(trans="log10") +
    scale_fill_manual(values = pal) +
    scale_color_manual(values = pal) +
    xlab("CO2 Emissions") +
    ylab("") +
    theme_bw() +
    theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
      options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```

### Plot
#### with density points and quantile lines

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 1920/72, fig.height = 1080/72, out.width = "100%"}

v2 = ggplot(food_consumption, aes(x=co2_emmission, y=food_category, fill=food_category)) +
    stat_density_ridges( quantile_lines = TRUE,
          jittered_points = TRUE,
          position = position_points_jitter(width = 0.05, height = 0),
          point_shape = '|', point_size = 3, point_alpha = 1, alpha = 0.7) +
    scale_x_continuous(trans="log10") +
    scale_fill_manual(values = pal) +
    scale_color_manual(values = pal) +
    xlab("CO2 Emissions") +
    ylab("") +
    theme_bw() +
    theme_opts

girafe(ggobj = v2, width_svg = 1280/72, height_svg = 720/72,
      options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/food_consumption-by-co2-emissions-fs.svg", plot = v1, width=720/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/food_consumption-by-co2-emissions-sm.svg", plot = v1, width=2.25, height=2.25)

```


### References
#### citations for narrative and data sources

Data Source: [GO](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-02-18/readme.md){target="_blank"}

<pre>
@misc{mock_2020_rfordatasciencetidytuesday,
  author = {Mock , Thomas },
  month = {02},
  title = {rfordatascience/tidytuesday},
  url = {https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-02-18/readme.md},
  urldate = {2021-07-19},
  year = {2020},
  organization = {GitHub}
}

@misc{ritchie_2020_you,
  author = {Ritchie, Hannah},
  month = {01},
  title = {You want to reduce the carbon footprint of your food? Focus on what you eat, not whether your food is local},
  url = {https://ourworldindata.org/food-choice-vs-eating-local},
  year = {2020},
  organization = {Our World in Data}
}
</pre>

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


