---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(DiagrammeR)

library(knitcitations)
library(bibtex)

```

<div class="activity">
DIAGRAMS
</div>

# Gantt diagram
## I want to fix irregularities in my dataset

> Don't call the world dirty because you forgot to clean your glasses...\
--- Aaron Hill\



***

# Section
## Subsection

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

mermaid("
gantt
    title A Gantt Diagram
    dateFormat  YYYY-MM-DD
    section Section
    A task           :a1, 2014-01-01, 30d
    Another task     :after a1  , 20d
    section Another
    Task in sec      :2014-01-12  , 12d
    another task      : 24d
")

```


# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}




```


# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```



# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```



# Section
## Subsection


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}



```


# Section
## Subsection

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}



```


# Section
## Subsection

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}



```


# Section
## Subsection

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}



```


# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

# cleanbib()
# read.bibtex(file = "./citations.bib")

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

