---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    #self_contained: false
    #lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)

library(knitcitations)
library(bibtex)

```

<div class="activity">
INGEST  
</div>

# Case
## Child Labor, average-working-hours-of-children

> All the problems of the world - child labor, corruption - are symptoms of a spiritual disease: lack of compassion...\
--- Bill Vaughan\

***

# Accessing a comma-separated-values file (.csv)

```{r, echo=TRUE, message=FALSE}

df <- read.csv('archetypes/child-labor/average-working-hours-of-children.csv')
df

```

## Fixing encoding issue

```{r, echo=TRUE, message=FALSE}

df1 <- read.csv('archetypes/child-labor/average-working-hours-of-children.csv', encoding = "UTF-8")
df1

```


# References
## The citations and data sources used for this case

The data files used as examples here were obtained from the [Child Labor](https://ourworldindata.org/child-labor) article published by Our World in Data.

```{r generateBibliography, echo=FALSE, message=FALSE, warning=FALSE}

cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "citations/average-working-hours-of-children.bib")

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

