---
pagetitle: "Cannabis legalisation"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(countrycode)
library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Cannabis legalisation
## Choropleth Map

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Ryan Lange on Unsplash"}

masthead <- "assets/ryan-lange-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Legalize marijuana and take all that money and invest it in teachers and in education...\
--- Carlos Santana\

***

### Ingest
#### find unique values of the "Recreational" column

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read.csv("archetypes/cannabis-legalisation/cannabis-legal-status.csv", header = TRUE)
df

# unique(df$Recreational)

```


### Wrangle
#### enrich with ISO3C

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_wrangle <- df
df_wrangle$ISO3 <- countrycode(df_wrangle$Country_Territory, origin = 'country.name', destination = 'iso3c') 
df_wrangle

```


### World map
#### merge attributes by ISO3C


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# natural earth base map
ne_world <- ne_countries(scale = "small", returnclass = "sf")
# removes Antarctica
ne_world <- filter(ne_world, iso_a3 != "ATA") 
# combine data with map based on ISO3 codes
ne_world_df <- merge(ne_world, df_wrangle, by.x = "iso_a3", by.y = "ISO3", all = TRUE)

```


### Plot
#### fill by legal status


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', out.width="100%"}

# theme parameters
theme_opts <- theme(
  text = element_text(family = "inconsolata", size = 16), 
  plot.title = element_text(color = "black", size = 16, face = "bold"),
  plot.subtitle = element_text(color = "black", size = 12),
  plot.caption = element_text(color = "#555555", size = 11),
  plot.background = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  legend.position = "bottom",
  legend.title = element_blank(),
)

# color palette to use
status_palette <- c(
  "Illegal" = "#D8D9CF",
  "Decriminalized" = "#9AC4B8",
  "Legal" = "#335855",
  "Unknown" = "#CCCCCC"
)

v1 <- ggplot(data = ne_world_df) +
  # map feature styling
  geom_sf(aes(fill=Recreational), color="#FFFFFF", stroke=0.5) +
  scale_fill_manual(values = status_palette) + 
  coord_sf() +
  theme_bw() +
  labs(x="", # Longitude
       y="", # Latitude
       title = "Choropleth Map", 
       subtitle="Legality of cannabis") +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/cannabis-legalisation-fs.svg", plot = v1, width=16, height=9)

```


### References
#### citations for narrative and data sources

* Narrative and Data: Wikipedia, Legality of cannabis, [GO](https://en.wikipedia.org/wiki/Legality_of_cannabis){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```



