---
pagetitle: "The Happy Planet Index 2020"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(wesanderson)
library(ggiraph)
library(xlsx)
library(countrycode)
library(janitor)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# The Happy Planet Index 2020
## Choropleth Map

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Sippakorn Yamkasikorn on Unsplash"}

masthead <- "assets/sippakorn-yamkasikorn-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Happiness is a journey, not a destination...\
--- Alfred D. Souza\

***

Some suggested revisions:

* Convert excel to csv and remove BOM
* Use janitor to clean column names (janitor::clean_names)
* Generate a quantile or similar statistic of the Rank to apply the palette (scale_file_manual)
* Match the palette as shown in the graphic (see image in archetypes)



### Ingest


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Data source must have an ISO3 field
df <- read.xlsx("archetypes/happy-planet-index/happy-planet-index-2020.xlsx", "1. All countries", rowIndex = 9:161)
df

```


### Wrangle
#### select columns and remove NAs

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Only select columns :Country, ISO and HPI for the map
df_wrangle <-df[,c(2,3,10)]
df_wrangle$HPI<-as.numeric(df$HPI)
na.omit(df_wrangle)


```


### World map
#### from natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# natural earth base map
ne_world <- ne_countries(scale = "small", returnclass = "sf")
# removes Antarctica
ne_world <- filter(ne_world, iso_a3 != "ATA") 

```


### Wrangle
#### merge data and map geometry


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# combine data with map based on ISO3 codes
ne_world_df <- merge(ne_world, df_wrangle, by.x = "iso_a3", by.y = "ISO", all = TRUE)

```



### Plot
#### The Happy Planet Index 2020


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide',  out.width="100%"}

# theme parameters
theme_opts <- theme(
  text = element_text(family = "inconsolata"), 
  plot.title = element_text(color = "black", size = 14, face = "bold"),
  plot.subtitle = element_text(color = "black", size = 12),
  plot.caption = element_text(color = "#555555", size = 8),
  plot.background = element_blank(),
  legend.position = "bottom",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank()
)

# color palette matching publication
pal <- c(
  "#388E3C",
  "#00C853",
  "#9CCC65",
  "#FFEB3B",
  "#FBC02D",
  "#FF8F00",
  "#FF7043",
  "#F44336",
  "#C62828"
)

v1 <- ggplot(data = ne_world_df) +
  # map feature styling
  geom_sf(aes(fill=HPI), color="#FFFFFF", stroke=0.5) +
  scale_fill_gradientn(colours = rev(pal)) + 
  coord_sf() +
  theme_bw() +
  labs(x="", # Longitude
       y="", # Latitude
       title = "Choropleth Map", 
       subtitle="The Happy Planet Index 2020") +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "outputs/hpi-data-2020-fs.svg", plot = v2, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "outputs/hpi-data-2020-sm.svg", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Data sources: The Data Source,  [GO](https://happyplanetindex.org/countries/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```



