---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: hide
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(tidyr)
library(scales)

# needed to include bib references
library(knitcitations)
library(bibtex)

```

<div class="activity">
CHARTS
</div>

# Bar Horizontal Segmented

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Marcelo Silva on Unsplash"}

masthead <- "assets/marcelo-silva-uKxGOwwALuU-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Being a single parent is twice the work, but also twice the hugs...\
--- Unknown\

***

# Real-life case: Lone-parent Households

# Load the data
## Lone-parent households by age and sex of parent, age of child and region, latest available year

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE}

# Load data
df <- read_csv("archetypes/figure-2-11.csv", col_names=TRUE)

# Transpose columns
long <- gather(df, type, Percentage, "Lone father (all ages)":"Lone mother 60+ and all children 18 and over", factor_key=FALSE)

# Format x-axis labels
long$Regionwrap = str_wrap(long$Region, width = 17)

# Order by category
long$type <- factor(long$type, levels=c("Lone mother 0-17 and at least one child below 18",
                                        "Lone mother 18-24 and at least one child below 18",
                                        "Lone mother 25-34 and at least one child below 18",
                                        "Lone mother 35-59 and at least one child below 18",
                                        "Lone mother 60+ and at least one child below 18",
                                        "Lone mother 25-34 and all children 18 and over",
                                        "Lone mother 35-59 and all children 18 and over",
                                        "Lone mother 60+ and all children 18 and over",
                                        "Lone father (all ages)"))

long

```

# Plot the chart
## One-parent households: mostly lone mothers - Figure 2.11

```{r draw-plot, message=FALSE, warning=FALSE, echo=TRUE, fig.width=10, fig.height=6}

# Define palette
segment_palette <- c("Lone mother 0-17 and at least one child below 18" = "#6b9e7e",
                "Lone mother 18-24 and at least one child below 18" = "#88b88a",
                "Lone mother 25-34 and at least one child below 18" = "#a6609c",
                "Lone mother 35-59 and at least one child below 18" = "#692c7d",
                "Lone mother 60+ and at least one child below 18" = "#acc8ed",
                "Lone mother 25-34 and all children 18 and over" = "#678bb3",
                "Lone mother 35-59 and all children 18 and over" = "#406993",
                "Lone mother 60+ and all children 18 and over" = "#bec068",
                "Lone father (all ages)" = "#2b4662")

# Make the plot
v1<-ggplot(long, aes(y = Percentage, x = Regionwrap)) + 
  geom_col(aes(fill = type), position = "fill", width = 0.55) +
  scale_y_continuous(labels = percent_format(accuracy=1), breaks=seq(0,1,0.1)) +
  scale_fill_manual(values = segment_palette) +
  scale_x_discrete(limits=c("Sub-Saharan\nAfrica",
                            "Central and\nSouthern Asia",
                            "Northern Africa\nand Western Asia",
                            "Latin America and\nthe Caribbean",
                            "Europe and\nNorthern America",
                            "World")) +
  labs(
    title = "Figure 2.11: Lone-parent households by age and sex of parent, age of child and region, latest available year",
    caption = "Source: UN Women Progress of the World's Women 2019-2020 - Families in a Changing World") +
  theme( panel.background = element_rect(fill = "white"), 
         panel.grid.major.x = element_line(color="gray", size=0.1), 
         axis.title.y = element_blank(), 
         axis.ticks = element_blank(), 
         legend.position = "bottom", 
         legend.title = element_blank()) +
  guides(fill = guide_legend(ncol=2)) +
  geom_text(aes(fill = type, label = Percentage), position = position_fill(vjust = 0.5), check_overlap = TRUE, color="white", size = 3) +
  coord_flip()
 
v1

```

# Exercises and practice
## Knime and R practice solutions


# References
## The citations and data sources used for this case

Source: <a href="https://www.unwomen.org/en/digital-library/progress-of-the-worlds-women">UN Women Progress of the world’s women 2019-2020 Report</a>

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "citations/figure-2-11.bib")

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

