---
pagetitle: "Animal Bites"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext

```

<div class="activity">
WRANGLERS  
</div>


# Animal Bites
## Profiling

```{r, out.width="60%", fig.align="center", fig.cap= "Photo by Janko Ferlič on Unsplash"}

masthead <- "assets/janko-ferlic-MBYNW2987qc-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Snake on a Tree</div>


> If you pick up a starving dog and make him prosperous he will not bite you.\
This is the principal difference between a dog and man...\
--- Mark Twain\

***

### Load the data

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "animal-bites/animal-bites.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE)

df

```

Based on an initial view of the data, we can see basic table structure and the columns defined.  The column definitions were provided by the source as follows:

* __bite_date__: The date the bite occurred
* __SpeciesIDDesc__: The species of animal that did the biting
* __BreedIDDesc__: Breed (if known)
* __GenderIDDesc__: Gender (of the animal)
* __color__: color of the animal
* __vaccination_yrs__: how many years had passed since the last vaccination
* __vaccination_date__: the date of the last vaccination
* __victim_zip__: the zipcode of the victim
* __AdvIssuedYNDesc__: whether advice was issued
* __WhereBittenIDDesc__: Where on the body the victim was bitten
* __quarantine_date__: whether the animal was quarantined
* __DispositionIDDesc__: whether the animal was released from quarantine
* __head_sent_date__: the date the animal’s head was sent to the lab
* __release_date__: the date the animal was released
* __ResultsIDDesc__: results from lab tests (for rabies)

The column definitions give a hint for the data we can expect, but let's use profiling method to explore the features and characteristics.


### Value Frequency
#### absolute and relative frequency

<kbd>mutate</kbd>
<kbd>rename</kbd>

```{r message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# Display frequency of the values of a column
f_frequency <- function(df_frequency,column) {
  
  df_tmp = table(column)
  as.data.frame(df_tmp) %>% 
    rename(Frequency_column=column ,Freq_absolute=Freq)  %>%
    mutate(Freq_relative=paste0(round(100*Freq_absolute/sum(Freq_absolute),digits=2),"%"))
  
}

# Call the function with your values to the parameters
f_frequency (df,df$bite_date)

```

### References
#### citations for narrative and data sources

* Narrative and Data source: This case is based on a dataset of animal bite incidents reported to and investigated by Louisville Metro Department of Public Health and Wellness , [GO](https://www.kaggle.com/willcanniford/animal-bites-analysis){target="_blank"}

<!-- or -->

<pre>
@misc{canniford_2020_animal,
  author = {Canniford, Will},
  title = {Animal bites analysis},
  url = {https://www.kaggle.com/willcanniford/animal-bites-analysis},
  urldate = {2021-05-18},
  year = {2020},
  organization = {kaggle.com}
}
</pre>

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
