---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# Profiling
## Discover characteristics of your dataset: dimensions, structure and row values

```{r, out.width="20%", fig.align="center"}

masthead <- "assets/noun_profile_169052.svg"
knitr::include_graphics(masthead, dpi=72)

```


This type of profiling is a __critical__ __step__ in the wrangling process. Data profiling is the process of __examining__ __data__ to discover and understand its features. Profiling methods help to describe the unique features of the source and will reveal information about the structure, content, and potential relationships the data may have with other sources.

Typical objectives

* __Structure__ : data types, column definitions, length.
* __Completeness__ : the presence of missing, null, or erroneous values.
* __Uniqueness__ : the frequency of a value relative to the number of records.
* __Value__ __Validity__ : values correspond to the meaning of the feature, e.g. age = -1?
* __Distribution__ : descriptive statistics like min, max, variance, count and sum.
* __Pattern__ __and__ __Format__ : content / temp
* __Gap__ __Analysis__ (e.g. in date ranges, missing observations)
* __Validation__ __with__ __joining__ __sources__ : temp

_nota bene_ : profile methods do not change the source data; they are intended to identify the areas that will need treatment using other wrangler tasks such as clean, formatting, imputation, validation, etc.
