---
pagetitle: "Women in space"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE, encoding = "utf-8")
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Women in space
## Profiling

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Greg Rakozy on Unsplash"}

masthead <- "assets/greg-rakozy-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Weightlessness is a great equalizer...\
--- Sally Ride\

***

### Ingest data 
#### series, values, and dates

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "women-in-space/astronaut-data.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE)

df

```
### Distinct Values
#### Retrieving unique records of female astronauts using <kbd>distinct()</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Female astronauts
hrs_mission <- df %>% 
  filter(sex == "female") %>% 
  distinct(name, total_hrs_sum)

hrs_mission

```

#### Retrieving unique records from the table for the year of mission by using <kbd>distinct()</kbd>

```{r message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

#Astronauts name with the year of mission in ascending order
distinct_df <- distinct(df, name, year_of_mission) %>% arrange( year_of_mission, name)
distinct_df

```
### References
#### citations for narrative and data sources

* Data sources: M. Stavnichuk & T. Corlett, [GO](https://doi.org/10.1016/j.lssr.2020.06.003){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
