---
pagetitle: "Which Countries are the Happiest?"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(readxl)
library(ggiraph)

library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Which Countries are the Happiest?
## Profiling

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Alex Alvarez on Unsplash"}

masthead <- "assets/happypeople.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">World Happiness Report</div>

> The World Happiness Report has proven to be an indispensable tool for policymakers \
looking to better understand what makes people happy...\
--- Jeffrey Sachs

***

### Ingest

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

#Load
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "happiness-report/happiness-report-2020.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE)

df

```

### Dimensions
#### <kbd>number of columns and rows</kbd>

```{r message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

dim(df)

```

The output tells us that the data contains 1704 rows, and 26 columns.


### Positive, Negative and Zero Values
#### <kbd>Check for all the numerical columns</kbd>

```{r message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df1 <- df[,3:ncol(df)]

nRows <- dim(df1)[1]

calcStats <- function(x) {
  temp <- na.omit(df[, x])
  pos <- sum(temp > 0)
  is_zero <- sum(temp = 0)
  neg <-  sum(temp < 0)
  c("number of positives" = pos, "negatives" = neg, "zero" = is_zero)
}
  
result <- as.data.frame(Map(calcStats, colnames(df1)))
result

```
### References
#### citations for narrative and data sources:

* Narrative and Data sources: The 7th World Happiness Report, [GO](https://worldhappiness.report/ed/2019/){target="_blank"}  

<!-- or -->

<pre>
@misc{helliwell_2019_world,
  author = {  Helliwell,  John F. Helliwell and Layard, Richard  and Sachs, Jeffrey D. },
  title = {World Happiness Report 2019},
  url = {https://worldhappiness.report/ed/2019/},
  urldate = {2021-05-18},
  year = {2019},
  organization = {Worldhappiness.report}
}
</pre>



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

