---
pagetitle: "Countries by Share of Earth Surface"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(ggiraph)
library(ggrepel)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Countries by Share of Earth Surface
## Donut Chart

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Brett Zeck on Unsplash"}

masthead <- "assets/brett-zeck-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Bourscheid castle in the north of Luxembourg</div>

> The earth is what we all have in common...\
--- Wendell Berry\

***


### Ingest the data
#### Country's size and their percentages 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load csv data file
df <- read.csv("archetypes/countries-by-share-of-earths-surface/countries-by-share-of-earths-surface.csv", header = TRUE, stringsAsFactors = FALSE)
df


```


### Wrangle the data
#### We'll convert the data in numeric and then some simple indexing to create an 'Other' row since the dataset is large. We will also have to create coordinates to where our labels will be place.


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

colnames(df) <- c("Country", "Total", "Percentage" )
df$Total <- parse_number(df$Total)
df$Percentage <- parse_number(df$Percentage)
df <- df[1:13,]

df2 <- df %>%  ## for labelling purposes
  mutate(csum = rev(cumsum(rev(Percentage))), 
         pos = Percentage/2 + lead(csum, 1),
         pos = if_else(is.na(pos), Percentage/2, pos))
  

```


### Plot
#### Donut Chart


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black",  size = 36, face = 'bold', hjust = 0.5 ),
    plot.subtitle = element_text(color = "black", size = 20, hjust = 0.5, margin=margin(0,0,40,0)),
    plot.caption = element_text(color = "#555555", size = 10),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    
    # panel.grid.minor = element_blank(),
    # panel.grid.major = element_blank(),
    legend.position='none'
  )

# Plot
v1 <- ggplot(df, aes(x = 2 , y = Percentage, fill = fct_inorder(Country))) +
  geom_col(width = 1, position = "stack") +
  coord_polar(theta = "y") +
  scale_fill_brewer(palette = "Set3") +
  geom_label_repel(data = df2,
                   aes(y = pos, label = paste0(Country, " ", Percentage, "%")),
                   size = 4.5, nudge_x = 1, show.legend = FALSE) +
  guides(fill = guide_legend(title = "Group")) +
  labs(title="Share of earth surface for top 13 countries", subtitle = "Percentage relative to global share")+
  xlim(0.5, 2.5)+
  theme_void() + theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}
# Save plot
# as vector or raster image

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "assets/size-of-countries-sm.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "assets/size-of-countries-fs.png", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative Inspiration: The Economist, Ideas Factories, Global innovation and GDP
* Data Source: Global Innovation Index (GII) 2021,[GO](https://www.globalinnovationindex.org/analysis-indicator){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```



