---
pagetitle: "Better Life Index"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(maps)
library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Better Life Index
## Bubble Map


```{r, out.width="60%", fig.align="center", fig.cap="Photo by  Jeremy Bishop l on Unsplash"}

masthead <- "assets/jeremy-bishop-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> To have a better life we must keep choosing how we are living...\
--- Albert Einstein\

***

### Ingest
#### Both better life index file and country centroids file as coordinates reference

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
df <- read_csv("archetypes/better-life-index/data/better-life-index.csv")
df_centroids<-read_csv("archetypes/better-life-index/data/country-centroids.csv")
df
df_centroids
```

### Wrangle
#### Filter Life Satisfaction as the indicator, select necessary columns, merge with the coordinates and remove NAs

```{r}

df_wrangle<-df%>%filter(Inequality=='Total'& Indicator %in% c('Life satisfaction'))%>%select(LOCATION,Country, Value)

df_combined<-merge(df_centroids,df_wrangle,by.x='iso3c',by.y='LOCATION', all = TRUE)

na.omit(df_combined)


```

### World map
#### merge attributes by ISO3C


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# natural earth base map
ne_world <- ne_countries(scale = "medium", returnclass = "sf")
# removes Antarctica
ne_world <- filter(ne_world, iso_a3 != "ATA") 
# combine data with map based on ISO3 codes
ne_world_df <- merge(ne_world, df_wrangle, by.x = "iso_a3", by.y = "LOCATION", all = TRUE)


```


### Plot
#### Bubble map


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide',  out.width="100%"}

# theme parameters
theme_opts <- theme(
  legend.position = 'none',
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.background = element_blank(),
)


v1 <- ggplot(data = ne_world_df) +
  # map feature styling
  geom_sf(fill="#cbd5e2", color="gray", stroke=1) +
  # bubble parameters
  geom_point_interactive(data=df_combined, aes(x=longitude,y=latitude,size=Value,stroke=1,color='#6497bf',
    tooltip = paste0(Country,": ",Value), data_id = iso3c),alpha=.5) +
  # size scaling applied to bubbles
  scale_size_continuous(range=c(5,15)) +
  theme_bw() +
  labs(x="Longitude",
       y="Latitude",
       title = "Bubble Map", 
       subtitle="Better Life Index") +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 7.5,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
ggsave(filename = "outputs/better-life-index-fs.svg", plot = v2, width=16, height=7.5)

```


### References
#### citations for narrative and data sources

* Narrative and Data: OECD Better Life Index, [GO](https://stats.oecd.org/Index.aspx?DataSetCode=BLI){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


