---
pagetitle: "Which Electric Vehicle to Choose"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(ggiraph)
library(ggvoronoi)
library(scales)
library(ggrepel)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# Which Electric Vehicle to Choose
## Scatter Voronoi


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Michael Marais on Unsplash"}

masthead <- "assets/michael-marais-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Economic growth doesn't mean anything if it leaves people out...\
--- Jack Kemp


***

### Load the data [Ingest]

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
df <- read.csv("./archetypes/Cheapestelectriccars-EVDatabase.csv", header = TRUE, stringsAsFactors = FALSE)
df

```

### Prepare the data [Wrangle]

While creating a heatmap, it might make better sense to bin the continuous data into levels and represent each level as a discrete colour. The cut() function in R allows to break and label a continuous variable

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df$Acceleration <- parse_number(df$Acceleration)
df$TopSpeed <- parse_number(df$TopSpeed)
df$Range <- parse_number(df$Range)
df$Price.UK <- parse_number(df$Price.UK)

df$Name <- sub("(\\w+\\s+\\w+).*", "\\1", df$Name)

df <- df %>%  mutate(zero2sixty=cut(Acceleration, breaks=c(0,4,6,8,10,12),
                      labels=c('3-4','4-6','6-8','8-10','12+'))) %>%
  mutate(zero2sixty = as.factor(zero2sixty))

```

### Plot 
#### Top Speed and Price


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}


theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.title = element_text(color = "green", size = 14, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 8),
    axis.text = element_text(size=7.5),
    panel.border = element_blank(),
    panel.background = element_blank(),
    legend.title = element_text(color = "black", size = 8, face = "bold"), # remove legend title
    legend.text = element_text(color = "black", size = 8),
    legend.position='right'
)


v1 <- ggplot(data = df, aes(y= TopSpeed,
                      x= rescale(Price.UK, to=c(135,250)),
                      label = Name))+
  stat_voronoi(geom="path", colour = 'green') +
  geom_point(aes(color=zero2sixty)) +
  geom_text_repel(size=4, aes(color=zero2sixty)) +
  scale_x_continuous(breaks=c(140, 160, 200, 240),
                  labels=c(10000, 20000,30000, 64111)) +
      labs(y="Top Speed",
           x = "Price",
       title = "Which EV to Choose?",
       subtitle = "Pinpoint your desired Top Speed and Price",
       caption = "refer to data frame for full car name")+
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```
### Plot
#### Range and Price


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v2 <- ggplot(data = df, aes(y= Range,
                      x= rescale(Price.UK, to=c(200,640)),
                      label = Name))+
  stat_voronoi(geom="path", colour = 'green') +
  geom_point(aes(color=zero2sixty)) +
  geom_text_repel(size=4, aes(color=zero2sixty))+
  scale_x_continuous(breaks=c(200, 300, 400, 500, 600),
                  labels=c(30000, 45000,65000, 85000, 105000)) +
   labs(y="Range",
        x = "Price",
       title = "Which EV to Choose?",
       subtitle = "Pinpoint your desired Range and Price",
       caption = "refer to data frame for full car name") +
  theme_opts

girafe(ggobj = v2, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "assets/electric-voronoi.svg", plot = v1, width=16, height=9)

# without annotations
#ggsave(filename = "assets/economic-growth-happiness-sm.svg", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative sources: EV Database, [GO](https://ev-database.org){target="_blank"}
* Data sources: Kaggle, [GO](https://www.kaggle.com/kkhandekar/cheapest-electric-cars){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

