---
pagetitle: "Temperature Changes in Kuwait"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(dplyr)
library(ggiraph)
library(wesanderson)

library(DiagrammeR)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
TEMPORALS  
</div>

# Temperature Changes in Kuwait
## Heatmap


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Chi Girls on Unsplash"}

masthead <- "assets/chi-girls-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">A sunrise through a rain storm at the beach.</div>

> Forgiveness is an act of the will, and the will can function regardless of the temperature of the heart.....\
--- Corrie Ten Boom\

***


### Ingest

Loading the temperature-changes-around-the-world 

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read.csv("archetypes/temperature-changes-around-the-world/tas_1901_2020.csv", header = TRUE, stringsAsFactors = TRUE)
df

```


### Wranglers
#### Rename Columns


```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df1 <- df %>% rename("Temp_Celsius"="Temperature....Celsius.")
df1 <- df1 %>% rename("Month"="Statistics")
head(df1)

```


### Wranglers
#### Format String


```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# replace space with no character
df1$ISO3 <- gsub(" ","",df1$ISO3)
df1$Country <- gsub(" ","",df1$Country)

# replace "Average" with no character
df1$Month <- gsub(" Average","",df1$Month)

# replace space with no character
df1$Month <- gsub(" ","",df1$Month)

#transforming from factor to double
df1$Temp_Celsius <- as.numeric(as.character(df1$Temp_Celsius))

head(df1)

```



### Wranglers
#### Filter 

Kuwait records __ISO3__ == KWT and Year from 2015 and beyond

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df2 <- df1 %>% filter(ISO3 == "KWT" & Year >= 2015)
head(df2)

```


### Wranglers
#### Select

Select only __Temperature__, __Year__ and __Month__

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df2$Month <- factor(df2$Month, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug","Sep","Oct","Nov","Dec"))
df3 <- df2 %>% select(Year,Month,Temp_Celsius)
df3

```


### Temporal Heatmap
#### Average Temperature Monthly per Year


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    legend.position = 'bottom'
)

pal <- wes_palette("Zissou1", 10, type = "continuous")


v1 <- ggplot(df3)+
      geom_tile(aes(x = Month, y = Year, fill = Temp_Celsius), color = "white", size = 1) +
      scale_y_continuous(breaks=c(2015,2016,2017,2018,2019,2020)) +
      scale_fill_gradientn(colours = pal) + 
      labs(title = "Temperature Changes in Kuwait - 2015-2020",
        subtitle = "Average in Celsius",
        caption = "worldbank")+
      theme_bw() +
      theme_opts
 
girafe(ggobj = v1, width_svg = 16, height_svg = 9,
      options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```


### Temporal Heatmap
#### Interactivity


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v2 <- ggplot(df3)+
      geom_tile_interactive(aes(x = Month, y = Year, fill = Temp_Celsius), color = "white", size = 1,
                            tooltip = paste0(df3$Year,"\n",df3$Month,"\n", df3$Temp_Celsius,"C")) +
      scale_y_continuous(breaks=c(2015,2016,2017,2018,2019,2020)) +
      scale_fill_gradientn(colours = pal) + 
      labs(title = "Temperature Changes in Kuwait - 2015-2020",
        subtitle = "Average in Celsius",
        caption = "worldbank")+
      theme_bw() +
      theme_opts
 
girafe(ggobj = v2, width_svg = 16, height_svg = 9,
      options = list(opts_sizing(rescale = TRUE, width = 0.8)))

```


### References
#### citations for narrative and data sources

* Narrative and Data sources: Worldbank Climate Knowledge Portal, [GO](https://climateknowledgeportal.worldbank.org/download-data){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

