---
pagetitle: "Water Access Points"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(geosphere)
library(tmap)
library(tmaptools)
library(patchwork)
library(cowplot)
library(colorspace)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggvoronoi)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Water Access Points
## Voronoi

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Jeff Ackley on Unsplash"}

masthead <- "assets/jeff-ackley-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Water is life, and clean water means health...\
--- Audrey Hepburn\

***

The voronoi map shows water points monitored over time by governments and development partners. The data is collected by the __Water Point Data Exchange (WPDx)__ which aims to unlock the potential of water point data to improve decision-making and increase rural water access. Voronoi maps are based on the minimal distance needed to reach a landmark by using tessellation techniques that partition a plane into regions closest to these points. The darker the color of the region, the closer it is to the country's capital city.

### Ingest
#### coordinates and features of water points


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df <- read.csv("archetypes/water-access-points/water-access-points.csv", header = TRUE, stringsAsFactors = FALSE)
head(df, n=10)

```


### Ingest
#### country captials with coordinates


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

country_capitals <- read.csv("archetypes/water-access-points/country-capitals.csv", header = TRUE, stringsAsFactors = FALSE)
country_capitals <- filter(country_capitals, ContinentName == "Africa")
head(country_capitals, n = 10)

```


### Wrangle
#### clean names, enrich with capital city coordinates


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- df %>%
  filter(country_name %in% unique(country_capitals$CountryName)) %>%
  mutate(
    country_name = case_when(
      country_name == "Congo - Kinshasa" ~ "Democratic Republic of the Congo",
      country_name == "Congo - Brazzaville" ~ "Republic of Congo", # Republic of the Congo
      #country_name == "Swaziland" ~ "Eswatini",
      #country_name == "Tanzania" ~ "United Republic of Tanzania",
      TRUE ~ country_name
    ))

df_wrangle <- merge(df, country_capitals, by.x = "country_name", by.y = "CountryName")
df_wrangle <- df_wrangle %>% select(row_id, country_name, lat_deg, lon_deg, water_source, water_tech, CapitalName, CapitalLatitude, CapitalLongitude, CountryCode)

df_wrangle <- df_wrangle %>%
  mutate(
    country_name = case_when(
      #country_name == "Swaziland" ~ "Eswatini",
      country_name == "Tanzania" ~ "United Republic of Tanzania",
      TRUE ~ country_name
    ))

head(df_wrangle, n=10)


```


### Analytics
#### calculate geospatial distance (in meters) to capital city

* distHaversine()
* distMeeus()
* distRhumb()
* distVincentyEllipsoid()
* distVincentySphere()


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

df_wrangle <- 
    df_wrangle %>% 
    mutate(lon_deg = if_else(lon_deg > 180, lon_deg - 360, lon_deg))

df_analytics <- df_wrangle %>%
  rowwise() %>%
  mutate(lat_deg = round(lat_deg, digits = 2),  lon_deg = round(lon_deg, digits = 2)) %>%
  mutate( dist_to_capital = distm ( x = c(lon_deg, lat_deg), y = c(CapitalLongitude, CapitalLatitude), fun = distHaversine))

df_analytics <- df_analytics %>% distinct(lon_deg, lat_deg, .keep_all = TRUE)

head(df_analytics, n=10)

```


### Voronoi function
#### generated by country


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

theme_opts <- theme(
  text = element_text(family = "inconsolata", size = 12), 
  plot.title = element_text(color = "black", size = 16, face = "bold", hjust = 0.5),
  plot.subtitle = element_text(color = "black", size = 12, hjust = 0.5),
  plot.caption = element_text(color = "#555555", size = 11),
  plot.margin = margin(.25, .25, .25, .25, "cm"),
  plot.background = element_blank(),
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  axis.text.x = element_blank(),
  axis.text.y = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  legend.position = 'none'
)

draw_voronoi <- function(country) {
  
  # map for specified country
  map_sp <- ne_countries(scale = "small", country = country, returnclass = "sp")
  # for scale limits
  bounding_box <- bb(map_sp, projection=4326)
  
  # filter data for specified country and limit coordinates to bounding box
  df_country <- filter(df_analytics, country_name == country)
  df_country <- filter(df_country, lon_deg >= bounding_box$xmin & lon_deg <= bounding_box$xmax)
  df_country <- filter(df_country, lat_deg >= bounding_box$ymin & lat_deg <= bounding_box$ymax)
  
  v <-  df_country %>% 
    ggplot(aes(x = lon_deg, y = lat_deg)) +
    # country borders
    geom_polygon(data = map_sp, aes(long, lat), color = "grey20", fill = "#ffffff", size = 13.5) +
    geom_polygon(data = map_sp, aes(long, lat), color = "white", fill = "#ffffff", size = 10) +
    # alternative to country borders
    # geom_voronoi(fill = "white", color = "grey25", size = 13.5, outline = map_sp) +
    # geom_voronoi(fill = "white", color = "white", size = 10, outline = map_sp) +
    # color by distance, outline using map
    geom_voronoi(aes(fill = dist_to_capital, color = dist_to_capital), size = 0.3, outline = map_sp) +
    # contour of water points
    geom_density_2d(color = "white") +
    # all water points
    # geom_point(color = "white", alpha = 0.5, size = 0.5) +
    # show capital city location
    geom_point(data = head(df_country, n=1), aes(x = CapitalLongitude, y = CapitalLatitude), shape = 21, fill = "white", color = "black", size = 6) +
    geom_point(data = head(df_country, n=1), aes(x = CapitalLongitude, y = CapitalLatitude), size = 3) +
    scale_x_continuous(limits = c(bounding_box$xmin, bounding_box$xmax), expand = c(0.05, 0.05)) +
    scale_y_continuous(limits = c(bounding_box$ymin, bounding_box$ymax), expand = c(0.05, 0.05)) +
    scale_fill_gradient(low = "yellow", high = "red", na.value = NA) +
    # lightened to see voronoi borders
    scale_color_gradient(low = lighten("yellow", 0.25), high = lighten("red", 0.25), na.value = NA) +
    coord_map(clip = "off") +
    # labs(title = country, subtitle = "voronoi of water points, color by distance to capital city") +
    theme_void() +
    theme_opts
  v
}

```


### Plot
#### Uganda


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

# list of countries to select from
# africa <- unique(df_analytics$country_name)
africa <- c(
  "Algeria",
  "Angola",
  "Burkina Faso",
  "Burundi",
  "Central African Republic",
  "Chad",
  "Egypt",
  "Ethiopia",
  "Ghana",
  "Kenya",
  "Liberia",
  "Madagascar",
  "Mali",
  "Mauritania",
  "Mozambique",
  "Namibia",
  "Niger",
  "Nigeria",
  "Rwanda",
  "Sierra Leone",
  "South Africa",
  "South Sudan",
  "Sudan",
  "Swaziland",
  "United Republic of Tanzania",
  "Uganda",
  "Zambia",
  "Zimbabwe"
)

uganda <- draw_voronoi("Uganda")

girafe(ggobj = uganda, width_svg = 16, height_svg = 16,
       options = list(opts_sizing(rescale = TRUE, width = 0.5))
)

```



### References
#### citations for narrative and data sources

* Narrative: inspired by visualization created by Cédric Scherer
* Data Source: Water Point Data Exchange (WPDx), [GO](https://www.waterpointdata.org/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


