---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(ggplot2)
library(ggthemes)
library(rnaturalearth)
library(rgdal)
library(sf)
library(wbstats)
# install.packages("remotes")
#library(remotes)
#install_github("rCarto/popcircle")
library(popcircle) # Not in CRAN (Comprehensive R Archive Network)
library(cartography)
library(ggiraph)

# install.packages(c("ggthemes", "rnaturalearth", "rgdal", "sf", "wbstats", "cartography"))

```

<div class="activity">
MAPS  
</div>

# Geo Circle Packing
## Geographical Maps  +  Circle Packing (visualization where area of circles represents the numerical data)
## Case: Population


> Who runs in circles never gets far...\
--- Thornton Burgess\

***

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Get countries
ctry <- ne_countries(scale = "small", returnclass = "sf") # "sf" = simplefeatures (one of the standard in r for mapping)
ctry <- st_transform(ctry, 3857)

# Only keep the largest polygons of multipart polygons for a few countries
# (e.g. display only continental US)
frag_ctry <- c("US", "RU", "FR", "IN", "ES", "NL", "CL", "NZ", "ZA")
largest_ring = function(x) {
  x$ids <- 1:nrow(x)
  pols = st_cast(x, "POLYGON", warn = FALSE)
  spl = split(x = pols, f = pols$ids)
  do.call(rbind, (lapply(spl, function(y) y[which.max(st_area(y)),])))
}
st_geometry(ctry[ctry$iso_a2 %in% frag_ctry,]) <-
  st_geometry(largest_ring(ctry[ctry$iso_a2 %in% frag_ctry,]))


```

# Section
## Subsection

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

## POPULATION
# Get and merge data
data_pop <- wb(indicator = "SP.POP.TOTL", startdate = 2017, enddate = 2017)
ctry_pop <- merge(ctry[,"iso_a2"], data_pop, by.x = "iso_a2", by.y = "iso2c" )

data_pop
ctry_pop

# Computes circles and polygons
res_pop <- popcircle(x = ctry_pop, var = "value")
circles_pop <- res_pop$circles
shapes_pop <- res_pop$shapes

circles_pop$lab <- paste0(circles_pop$country, '\n', round(circles_pop$value/1000000))

```

## Question: Which countries have the highest populations? What do these countries look like?

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width=12, fig.height=6, out.width = "100%"}

# theme parameters
theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.background = element_blank(),
)

circles_pop_sf = st_as_sf(circles_pop)
shapes_pop_sf = st_as_sf(shapes_pop)

v1 <- ggplot() +
  geom_sf(data = circles_pop_sf, aes(fill = value), color = "#ffffff", stroke = 0.5 ) +
  geom_sf(data = shapes_pop_sf, fill = "#ffffff", color = "#ffffff", stroke = 0.25 ) +
  geom_sf_text(data = circles_pop_sf, aes( label = ifelse((value>125000000),iso3c, "")), size=3, color = 'black') +
  scale_fill_gradient2_tableau() +
  theme_bw() +
  labs(title = "Population, Million Inhabitants", 
       subtitle="T. Giraud, 2019 - World Development Indicators, 2017") +
  theme_opts

girafe(ggobj = v1, width_svg = 13, height_svg = 7,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# ggsave(filename = "assets/pop-circles-population.svg", plot = v1, width=12, height=6)

```


# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case

<a href="https://github.com/rCarto/popcircle">Source</a>

```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

# cleanbib()
# read.bibtex(file = "./citations.bib")

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


