---
pagetitle: "Where does your medicine come from?"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(rnaturalearth)
library(rgdal)
library(sf)
# install.packages("remotes")
# library(remotes)
# install_github("rCarto/popcircle")
library(popcircle) # Not in CRAN (Comprehensive R Archive Network)
library(cartography)
library(ggthemes)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Where does your medicine come from?
## Geo Circle Packing

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Benjamin Lehman on Unsplash"}

masthead <- "assets/benjamin-lehman-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Always laugh when you can. It is cheap medicine....\
--- Lord Byron\

***

Geo Circle Packing is a visualization where area of circles represents a numerical data value and within each circle, a representation of the associated geographical geometry.

### Ingest
#### exporter, year, usd value


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read.csv("archetypes/where-does-your-medicine-come-from/data/drug_medicine_exports.csv", header = TRUE)
df

```


### Wrangler
#### profile & filter


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# filter for latest year
# distinct(df,year) %>% arrange(desc(year))

df_1 <- df %>% filter(year=="2017")
df_1

```


### Wrangler
#### clean (remove missing values)


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_2 <- df_1[!is.na(df_1$exports_usd),]
df_2 

```


### Wrangler
#### arrange by exports


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_3 <- df_2 %>% arrange(desc(exports_usd))
df_3 

```


### Base map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# Get countries, simplified resolution
ctry <- ne_countries(scale = "small", returnclass = "sf")

ctry <- st_transform(ctry, 3857)

# Only keep the largest polygons of multipart polygons for a few countries
frag_ctry <- c("CH", "FR", "GB", "US", "IE", "CA", "JP")
largest_ring = function(x) {
  x$ids <- 1:nrow(x)
  pols = st_cast(x, "POLYGON", warn = FALSE)
  spl = split(x = pols, f = pols$ids)
  do.call(rbind, (lapply(spl, function(y) y[which.max(st_area(y)),])))
}

st_geometry(ctry[ctry$iso_a2 %in% frag_ctry,]) <-
st_geometry(largest_ring(ctry[ctry$iso_a2 %in% frag_ctry,]))

```


### Wrangle
#### merge data and circle geometry


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# merge data
ctry_med <- merge(ctry[,"name_sort"], df_3, by.x = "name_sort", by.y = "exporter" )
ctry_med

# Computes circles and polygons
res_med <- popcircle(x = ctry_med, var = "exports_usd")
circles_med <- res_med$circles
circles_med$lab <- paste0(circles_med$name_sort, '\n', round(circles_med$exports_usd/100000000))
circles_med_sf = st_as_sf(circles_med)

shapes_med <- res_med$shapes
shapes_med_sf = st_as_sf(shapes_med)

```


### Plot
#### Which countries have the highest medicine exportation value (in USD)?


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

theme_opts <- theme(
  text = element_text(family = "inconsolata", size = 16), 
  plot.title = element_text(color = "black", size = 16, face = "bold"),
  plot.subtitle = element_text(color = "black", size = 12),
  plot.caption = element_text(color = "#555555", size = 11),
  plot.background = element_blank(),
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank()
)

v1 <- ggplot() +
  geom_sf(data = circles_med_sf, aes(fill = exports_usd), color = "#ffffff", stroke = 0.5 ) +
  geom_sf(data = shapes_med_sf, fill = "#ffffff", color = "#ffffff", stroke = 0.25 ) +
  geom_sf_text(data = circles_med_sf, aes( label = ifelse((exports_usd>1200000000),name_sort, "")), size=3, color = 'black', family = "inconsolata") +
  scale_fill_gradient2_tableau() +
  theme_bw() +
  labs(title = "Medicine Exportation Value", 
       subtitle="in 2017") +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 14,
       options = list(opts_sizing(rescale = TRUE, width = 0.75)))

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source = 'fold-hide'}

# eval = FALSE as default; set to TRUE for production outputs
ggsave(filename = "outputs/where-does-your-medicine-come-from-fs.svg", plot = v1, width=16, height=14)

```


### References
#### citations for narrative and data sources

* Narrative sources: Makeover Monday, [GO](https://data.world/makeovermonday/2018w8-where-does-your-medicine-come-from){target="_blank"}
* Data sources: ITC, TradeMap, [GO](https://www.trademap.org/Country_SelProduct_TS.aspx?nvpm=1%7c%7c%7c%7c%7cTOTAL%7c%7c%7c2%7c1%7c1%7c2%7c2%7c1%7c2%7c1%7c%7c1){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
