---
pagetitle: "Capital cities would you live there"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(ggtext)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS
</div>

# Capital cities: would you live there?
## Concatenate


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Alisa Matthews on Unsplash"}

masthead <- "assets/alisa-matthews-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Houston, TX, USA</div>

> This City is what it is because our citizens are what they are...\
--- Plato\

***

# Load data
## city, country, group, measure, and population


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "capital-cities/capital-cities-would-you-live-there.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE)
df

```

### Concatenate Rows
#### Combine records of the same structure

Sometimes we may need to combine two tables that we know contain the same information, basically the two tables get stacked.  


```{r, message=FALSE, echo=TRUE}

df_part1 <- df[1:100,]
df_part2 <- df[101:189,]

```

Let's assume we need to combined the following two tables. The first table contains 5 rows:

```{r, message=FALSE, echo=FALSE}

df_part1

```
The second table contains 6 rows:

```{r, message=FALSE, echo=FALSE}

df_part2

```

Notice that both tables include the same information (same number of columns, and column names).

We can now Concatenate the two tables

```{r, echo=TRUE, message=FALSE, warning=FALSE}

df_concat <- bind_rows(df_part1, df_part2)

```

The output table looks like this:

```{r, message=FALSE, echo=FALSE}

df_concat

```

As expected, we got the full dataset back.

### References
#### citations for narrative and data sources

* Narrative and Data Source: TBD


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


