---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Enrich
## a dataset with additional features or record insertion

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Ravi Roshan on Unsplash"}

masthead <- "archetypes/join-venn.png"
knitr::include_graphics(masthead, dpi=72)

```

* __constant__ __value__ : add a column with the same value in each cell to your table
* __concat__ __rows__ : concatenation combines rows from sources with identical properties
* __cross__ __join__ : will create a combination of every row from the two tables
* __inner__ __join__ : only matching rows will show up in the output table.
* __left__ __outer__ __join__ : will fill up the columns that come from the bottom table with missing values if no matching row exists in the bottom table.
* __right__ __outer__ __join__ : will fill up the columns from the top table with missing values if no matching row in the top table exists.
* __full__ __outer__ __join__ : will fill up columns from both the top and bottom table with missing values if a row cannot be joined.




```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "enrich anti-join concantenate inner-join left-join outer-join right-join" # mostly used in wranglers and analytics
keywords <- ''
commands <- ''
sources <- ''

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

