---
pagetitle: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# Enrich
## a dataset with additional features or record insertion

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Ravi Roshan on Unsplash"}

masthead <- "archetypes/join-venn.png"
knitr::include_graphics(masthead, dpi=72)

```

* __constant__ __value__ : add a column with the same value in each cell to your table
* __concat__ __rows__ : concatenation combines rows from sources with identical properties
* __cross__ __join__ : will create a combination of every row from the two tables
* __inner__ __join__ : only matching rows will show up in the output table.
* __left__ __outer__ __join__ : will fill up the columns that come from the bottom table with missing values if no matching row exists in the bottom table.
* __right__ __outer__ __join__ : will fill up the columns from the top table with missing values if no matching row in the top table exists.
* __full__ __outer__ __join__ : will fill up columns from both the top and bottom table with missing values if a row cannot be joined.
