---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.


library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()


```

<div class="activity">
WRANGLERS 
</div>

# Store in a File

```{r, out.width="20%", fig.align="center", fig.cap="Photo by Real Estate Line Icons Collection"}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "./assets/preserve_icon.jpg"
knitr::include_graphics(masthead, dpi=72)

```




After all data evaluation, preparation, reduction, extension, rearrangement and/or restructure tasks are applied on your data source as shown in this Wranglers session, one final method is essential to ensure all those changes are stored. 

If your main end-result is to obtain a new data set to be used as a data source for future analysis and visualization or the new data set is in fact the final report to be presented, the amended data is an important output which shall be saved as new data file.

Furthermore, if from your data source, you were able to plot a graph, a map or any visual that was later saved as an image, this image can also be saved into a data file. 

In this sub-section, the presented solutions are as follows:

* __write to csv file__: save an amended data source into a new data file
* __save an image__: save a newly plotted image from a data source

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "save-last-image save-image write-csv" # mostly used in wranglers and analytics
keywords <- ''
commands <- ''
sources <- ''

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

