---
pagetitle: "Capital cities would you live there"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# Capital cities: would you live there?
## Marimekko


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Fikri Rasyid on Unsplash"}

masthead <- "assets/fikri-rasyid-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Bandung City, Indonesia, Becak; Indonesia’s traditional rickshaw cycle</div>

> This City is what it is because our citizens are what they are...\
--- Plato\

***

# Load data
## city, country, group, measure, and population


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df = read.csv("archetypes/capital-cities/capital-cities-would-you-live-there.csv", header = TRUE)
df

```


### Analytics
#### calculate top, max, min, and labels


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

#df_top <- df %>% slice_max(Population, n = 15)
#df_top

df_top <- sample_n(df, 15)

df_top$xmax <- cumsum(df_top$Population)
df_top$xmin <- df_top$xmax - df_top$Population
df_top$xlabel <- (df_top$xmax + df_top$xmin)/2
df_top$label <- paste(as.character(round(df_top$Measure, digits=0)),"%")

df_top

```


### Plot
#### geom rect, text, and hline


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "95%"}

theme_opts <- theme(
  text = element_text(family = "inconsolata", size = 16), 
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.title = element_text(color = "black", size = 16, face = "bold"),
  plot.subtitle = element_text(color = "black", size = 12),
  plot.caption = element_text(color = "#555555", size = 10),
  plot.background = element_blank(),
  plot.margin = unit(c(0, 0, 1.25, 0), "in")
)

group_palette <- c(
  "0. Exceeded" = "#455A64",
  "1. Within" = "#FB8C00"
)

v1 <-ggplot(df_top) +
    geom_rect(aes(ymin = 0, ymax = Measure, xmin = xmin, xmax = xmax, fill = Group), color = "white", alpha = 0.5) + 
    geom_text(aes(x = xlabel, y = Measure, label = label, vjust = -1), position = "identity", color = "black", size = 3 ) +
    geom_text(aes(x = xlabel, y = 2, label = Population, vjust = 0), position = "identity", color = "black", size = 3 ) +
    geom_text(aes(x = xlabel, y = 0, label = City), hjust = "right", vjust = 1.5, position = "identity", color = "black", size = 3.5, angle = 45 ) +
    geom_hline(yintercept = 10) +
    scale_fill_manual(values = group_palette) +
    coord_cartesian(clip="off") +
    theme_bw() +
    theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source = 'fold-hide'}

# eval = FALSE as default; set to TRUE for production outputs

# full version
ggsave(filename = "assets/capital-cities-would-you-live-there-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "assets/capital-cities-would-you-live-there-sm.png", plot = v1, width=4, height=2.25)

```


### References
#### citations for narrative and data sources

* Narrative and Data Source: The Economist, Which countries dominate the world’s dinner tables? [GO](https://www.economist.com/graphic-detail/2019/08/23/which-countries-dominate-the-worlds-dinner-tables){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


