---
pagetitle: "Airline passenger traffic"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# Airline passenger traffic
## Marimekko

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Tomas Williams on Unsplash"}

masthead <- "assets/tomas-williams-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Sometimes, the world from above seems too beautiful, too wonderful, too distant for human eyes to see....\
--- Charles A. Lindbergh  

***

### Load the data
#### Projected growth in airline passenger traffic by region

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Create dataset
df = read.csv("archetypes/airline-passenger-traffic/projected-growth-in-airline-passenger-traffic-by-region.csv", header = TRUE)

# Prepare the data
df$xmax <- cumsum(df$RPK)
df$xmin <- df$xmax - df$RPK
df$xlabel <- (df$xmax + df$xmin)/2
df$label <- paste(as.character(df$Growth),"%")
data<-df %>% rename(Regions=Region)
data

```

### Plot the chart
#### Projected growth in airline passenger traffic by region

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "85%"}

theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background=element_rect(fill="white", colour="white"),
  panel.border = element_blank(),
  plot.background = element_blank(),
  plot.margin = unit(c(0, 0, 1.25, 0), "in")
)

v1 <- ggplot(data) +
    geom_rect(aes(ymin = 0, ymax = Growth, xmin = xmin, xmax = xmax, fill = Regions), color = "white", alpha = 0.5 ) + 
    geom_text(aes(x = xlabel, y = Growth, label = label, vjust = -1), position = "identity", color = "black", size = 3 ) +
    geom_text(aes(x = xlabel, y = 0.2, label = format(RPK, big.mark = ",", scientific = FALSE), vjust = 0), position = "identity", color = "black", size = 3 ) +
    geom_text(aes(x = 9500, y = 0.2, label = "Estimated\nRPK (B)\nin 2035"), vjust = 0.4) +
    geom_text(aes(x = xlabel, y = 0, label = Regions), hjust = "right", vjust = 1.5, position = "identity", color = "black", size = 3.5, angle = 45 ) +
    geom_hline(yintercept = 4.8, linetype = "dashed") + geom_text(aes(0, 4.8, label = "World Traffic\nGrowth 4.8%")) +
    geom_hline(yintercept = 2.9, linetype = "dashed") + geom_text(aes(0, 2.9, label = "World GDP\nGrowth 2.9%")) +
    coord_cartesian(clip="off") +
    theme(plot.title = element_text(size = rel(1.5)), panel.background = element_rect(fill = "white", colour = "grey50")) +
    theme_opts + 
    labs(title = "Projected Annual Growth in Revenue Passenger Kilometers (RPK) 2015-2035 (top 10 regional flows)")

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source = 'fold-hide'}

# eval = FALSE as default; set to TRUE for production outputs

# full version
ggsave(filename = "assets/percentage-of-females-married-by-18-fs.svg", plot = v1, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "assets/percentage-of-females-married-by-18-sm.png", plot = v1, width=4, height=2.25)

```

### References
#### citations for narrative and data sources

The citations and data sources used for this case is available at the source: <a href="https://www.boeing.com/resources/boeingdotcom/commercial/about-our-market/assets/downloads/cmo_print_2016_final_updated.pdf" target="_blank" rel="noopener noreferrer">Projected growth in airline passenger traffic by region</a>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

