---
pagetitle: "Canadian windmills"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggrepel)
library(extrafont)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Canadian Wind Turbines
## Point Symbol Map

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Keshav Rajasekar on Unsplash"}

masthead <- "assets/keshav-rajasekar-rq7VubCPFdY-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> The answer my friend is blowin' in the wind...\
--- Bob Dylan\

***

### Ingest

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Data source must have an ISO3 field
df <- read_csv("archetypes/canadian-windmills/wind_turbine.csv")
df

```

### Wrangle

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_wrangled <- df %>%
  # group the data by province/territory to calculate summary statistics
  group_by(province_territory) %>%
  # now summarize the data for count and mean of variables
  summarise(count=n(), # count the number of windmills in each province
            meandiam=mean(rotor_diameter_m), # mean of their diameters
            meanlat=mean(latitude), # mean of their latitudes
            meanlong=mean(longitude))

df_wrangled

```

### Map of Canada

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', out.width="100%"}

# Filter and keep only map of Canada
# using ggplot2 built-in maps
canada_map <- map_data("world") %>% 
  filter(region=="Canada")


map <- ggplot() +
       geom_polygon(data=canada_map,
               aes(x=long, y=lat, group=group), fill="grey90", color="white") +
       theme_void()

girafe(ggobj = map, width_svg = 16, height_svg = 12,
       options = list(opts_sizing(rescale = TRUE, width = 0.5))
)

```

### Plot
#### fill by "water source" status

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', out.width="100%"}

v1 <- ggplot(df_wrangled) +
  # add a map of Canada
  geom_polygon(data=canada_map,
               aes(x=long, y=lat, group=group), fill="grey90", color="white") +
  # add a point and star at each mean windmill location
  geom_point(aes(x=meanlong, y=meanlat, color=count), size=4, shape=20) +
  geom_point(aes(x=meanlong, y=meanlat, size=meandiam, color=count), shape=8) +
  # add labels for the points
  geom_text_repel(aes(x=meanlong, y=meanlat, color=count,
                      label=str_wrap(province_territory, 14)), # wrap the labels so they fit better
                  nudge_y=1.5, family="Amaranth", segment.alpha=0) +
  # change the color scheme
  scale_color_gradient(low="red3",high="black") +
  # add overall theme and fix the coordinates so the map doesn't warp
  theme_void() + 
  coord_fixed(1.3) +
  # edit the theme and legend position
  theme(text=element_text(family="Amaranth"),
        legend.position=c(0.9,0.7), 
        legend.box="horizontal", 
        legend.direction = "vertical") +
  # add title to the top left of the plot
  geom_text(aes(x=-110, y=78, label="Canadian Windmills by Province/Territory"),
            size=7, fontface="bold", family="Amaranth") +
  # add subtitle under the title
  geom_text(aes(x=-110, y=76, 
                label="Each point represents the mean location, size, and diameter of the windmills in the territory."),
            size=4, family="Amaranth", color="red4") +
  # add caption on bottom left inset
  geom_text(aes(x=-125, y=43, 
                label="data from open.canada.ca | plot by @rjstevick for #TidyTuesday"),
            size=3, family="Amaranth", color="grey60") +
  # add those labels
  labs(color="Number of \nWindmills", 
       size="Mean diameter \nof Windmills (m)")


girafe(ggobj = v1, width_svg = 16, height_svg = 12,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
ggsave(filename = "assets/canadian-windmills-fs.svg", plot = v1, width=16, height=12)

```


### References
#### citations for narrative and data sources

* Narrative sources: This is a reproduction of an original plot by Rebecca Stevick for #TidyTuesday, [GO](https://github.com/rjstevick){target="_blank"}
* Data sources: TidyTuesday 2020 week 44 - Canadian Wind Turbines, [GO](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-10-27){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

