---
pagetitle: "Filter Overview"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS

# Filter
## by position
## by value: [not] equal, less/greater [equal] than, [not] between, regex

```{r, out.width="20%", fig.align="center", fig.cap="Photo by ArtWorkLeaf, ID"}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "assets/4-wranglers-3-reduce.svg"
knitr::include_graphics(masthead, dpi=72)

```

Whether you would like to filter out sensitive information, focus on only desirable information to simplify your data analysis or specify the required data to be visualized, you may use this task to reduce your data.

In other words, filtering the data is essential to get a sample of what is most relevant and meaningful to what is needed for your work as a data scientist. You may have one or more criteria at different times to obtain a sample of your data.

The methods of filtering are used in reference to variables(columns) and records(rows)
in different approaches:

* By __position__ of __rows__ and/or __columns__ 
* By __value__ to be compared with a __row_value__ within a __column__ 
  + Where __column__ [not] equal __value__ 
  + Where __column__ [not] between __value_1 and value_2__
  + Where __column__ greater/less than [equal] __value__
  + Where __column__ Regular Expression __value__
