---
pagetitle: "Base Vector Map of Kuwait"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(Rcpp)
library(tidyverse)
library(sf)
library(geojsonio)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS 
</div>

# Base Vector Map of Kuwait
## Vector Map


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Abdelrahman Wael on Unsplash"}

masthead <- "assets/abdelrahman-wael-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Al Shaheed Park, Kuwait City, Kuwait</div>

> We believe that Kuwait is for all its citizens and not for one party or sect,\
  all live on its earth and ally themselves to its identity...\
--- His Highness Sheikh Sabah Al Ahmad Al Jaber Al Sabar\

***

### Ingest
#### border geometry for admin levels

Administrative boundaries at __adm0__ and __adm1__ levels

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load map sources
# ++++++++++++++++++++
# using the same map sources up to adm1 which refers to Governorates in Kuwait
adm0 <- st_read("archetypes/kuwait/kuwait-adm0.geojson")
adm1 <- st_read("archetypes/kuwait/kuwait-adm1.geojson")

head(as.data.frame(adm0))
head(as.data.frame(adm1))

```

### Plot
#### __adm0__ borders


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  # panel.background = element_blank(),
  panel.background = element_rect(fill = "#ffffff"),
  panel.border = element_blank(),
  # plot.background = element_blank(),
  plot.background = element_rect(fill = "#ffffff")
)

transparent_fill <- rgb(0, 0, 0, max = 255, alpha = 0, names = "transparent")

# In order of layer placement top -> down
# using adm0 map sources which contains info of area of the country
v1 <- ggplot() +
  geom_sf(data = adm0, color="#333333", fill = transparent_fill, size=1.0) +
  scale_x_continuous() +
  scale_y_continuous() +
  coord_sf() +
  theme_bw() +
  labs(x = NULL, # Longitude
      y = NULL, # Latitude
      title = NULL, 
      subtitle = NULL) +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 14,
       options = list(opts_sizing(rescale = TRUE, width = 0.6)))

```


#### __adm0__, and __adm1__ borders


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

v2 <-  v1 + geom_sf(data = adm1, color="#333333", fill = transparent_fill, size=0.5)

girafe(ggobj = v2, width_svg = 16, height_svg = 14,
       options = list(opts_sizing(rescale = TRUE, width = 0.6)))

```



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source = 'fold-hide'}

# eval = FALSE as default; set to TRUE for production outputs
ggsave(filename = "outputs/kuwait-base-vector-map-fs.svg", plot = v2, width=16, height=14)

```


### References
#### citations for narrative and data sources

* Narrative and Data sources: HDX, [GO](https://data.humdata.org/search?groups=kwt&res_format=GeoJSON&res_format=SHP&q=&ext_page_size=25){target=blank}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```



