---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: ["../../../z-assemblers/assets/styles/content/kamino.css", "../../../z-assemblers/assets/icons/line-awesome/css/line-awesome.css"]
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    #self_contained: false
    #lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(sf)
library(geojsonio)
library(ggplot2)
library(ggiraph)

```

<div class="activity">
MAPS  
</div>

# Vector Map
## Using UN sources

> A map says to you. Read me carefully, follow me closely, doubt me not...\
I am the earth in the palm of your hand...\
--- Beryl Markham\

***

# Load sources
## Regions, continents, admin levels, infrastructure, living places

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# REGIONS

#esri_world_regions <- topojson_read("archetypes/regions/esri_world_regions.topojson")
#ne_110m_geography_regions <- topojson_read("archetypes/regions/ne_110m_geography_regions.topojson")

# CONTINTENTS

#africa <- topojson_read("archetypes/continents/africa.topojson")
#asia <- topojson_read("archetypes/continents/asia.topojson")
#europe <- topojson_read("archetypes/continents/europe.topojson")
#north_america <- topojson_read("archetypes/continents/north-america.topojson")
#oceania <- topojson_read("archetypes/continents/oceania.topojson")
#south_america <- topojson_read("archetypes/continents/south-america.topojson")

# BASE MAP
# Simplification levels: 09, 07, 05, 03, 01, 009, 008, 007, 005, 001
land <- topojson_read("archetypes/un-default/BNDA50-LAND-no-ATA-03.topojson")
borders <- topojson_read("archetypes/un-default/BNDL50-BORDERS-no-ATA-03.topojson")
type_3 <- topojson_read("archetypes/un-default/BNDL50-BORDERS-TYPE-3.topojson")
type_4 <- topojson_read("archetypes/un-default/BNDL50-BORDERS-TYPE-4.topojson")

# ADMIN LEVEL 1

#admin <- topojson_read("archetypes/admin/ne_10m_admin_1.topojson")

# INFRASTRUCTURE

#ne_10m_railroads <- topojson_read("archetypes/poi/ne_10m_railroads.topojson")
#ne_10m_roads <- topojson_read("archetypes/poi/ne_10m_roads.topojson")

# LIVING PLACES

ne_10m_urban_areas <- topojson_read("archetypes/poi/ne_10m_urban_areas.topojson")

```

# Plot
## Layer by layer

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width=12, fig.height=6, out.width = "100%"}

# theme parameters
theme_opts <- theme(
  legend.position = "none",
  legend.title = element_blank(),
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  axis.title = element_blank(),
  panel.grid = element_blank(),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_blank(),
  plot.background = element_blank(),
)

# In order of layer placement top -> down
v1 = ggplot() +
  geom_sf(data = land, color="#AAAAAA", fill="#FFFFFF", size=0.5) +
  # geom_sf(data = borders, color="#CCCCCC") +
  geom_sf(data = type_3, color="red", size=0.5) +
  geom_sf(data = type_4, color="blue", size=0.5) +
  # REGIONS
  # geom_sf(data = esri_world_regions, color="blue") +
  # geom_sf(data = ne_110m_geography_regions, color="green") +
  # CONTINENTS
  # geom_sf(data = africa, color="orange", fill="#FFFFFF") +
  # geom_sf(data = asia, color="red", fill="#FFFFFF") +
  # geom_sf(data = europe, color="green", fill="#FFFFFF") +
  # geom_sf(data = north_america, color="blue", fill="#FFFFFF") +
  # geom_sf(data = oceania, color="purple", fill="#FFFFFF") +
  # geom_sf(data = south_america, color="pink", fill="#FFFFFF") +
  # ADMIN
  # geom_sf(data = admin, color="#cccccb", size=0.5) +
  # POI
  # geom_sf(data = ne_10m_railroads, color="#cccccb", size=0.5) +
  # geom_sf(data = ne_10m_roads, color="#cccccb", size=0.5) +
  geom_sf(data = ne_10m_urban_areas, color="#aaaaaa", fill="#aaaaaa", size=0.5) +
  scale_x_continuous() +
  scale_y_continuous() +
  coord_sf() +
  theme_bw() +
  labs(x="", # Longitude
       y="", # Latitude
       title = "Topojson Vector Map", 
       subtitle="Land and Borders") +
  theme_opts

# v1

girafe( ggobj = v1, width_svg = 12, height_svg = 6,
  options = list( opts_sizing(rescale = TRUE) )
)

```


## Save output to file


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

ggsave(filename = "assets/world-topojson.svg", plot = v1, width=12, height=6)

```


# Exercises and practice
## Knime and R practice solutions



# References
## The citations and data sources used for this case


```{r generateBibliography, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

# cleanbib()
# read.bibtex(file = "./citations.bib")

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```


