---
pagetitle: "Volcanos"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(colorspace)
library(rnaturalearth)
library(sf)
library(cowplot)
library(patchwork)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
MAPS  
</div>

# Volcanos
## zone dispersion map


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Iswanto Arif on Unsplash"}

masthead <- "assets/iswanto-arif-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> This ground is hot enough to cook the Sunday roast!\
--- John Seach (Volcanologist) just before his boots melted on the hot ground. Lopevi Volcano 2000.\


***

### Ingest
#### volcanos


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_volcanos <- read.csv("archetypes/volcanos/volcanos.csv", header = TRUE)
head(df_volcanos, n=10)

```


### Ingest
#### eruptions


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_eruptions <- read.csv("archetypes/volcanos/eruptions.csv", header = TRUE)
head(df_eruptions, n=10)

```


### Wrangle
#### filter for distinct


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

df_eruptions <-
  df_eruptions %>%
  filter(volcano_number %in% unique(df_volcanos$volcano_number))

```


### Base Map
#### natural earth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

# PLOT NATURAL EARTH BORDERS
ne_world <- ne_countries(scale = "small", returnclass = "sf")

```


### Plates and Ring of Fire Maps
#### geojson


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

plates <- st_read("archetypes/volcanos/PB2002_plates.geojson")
rof <- st_read("archetypes/volcanos/ring-of-fire.geojson")

```


### Wrangle
#### wrap dateline for ring of fire geometry


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-show'}

rof_dt <- rof %>% 
  st_cast("MULTILINESTRING") %>% 
  st_cast("LINESTRING") %>% 
  st_wrap_dateline(options = c("WRAPDATELINE=YES", "DATELINEOFFSET=180")) %>% 
  st_union() %>% 
  st_cast("POLYGON")

```


### View
#### longitudinal density of volcanos


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.title = element_text(color = "black", size = 14, face = "bold", family = "inconsolata", hjust = 0.5),
    plot.subtitle = element_text(color = "black", size = 12, family = "inconsolata", hjust = 0.5),
    plot.caption = element_text(color = "#555555", size = 8, family = "inconsolata"),    
    plot.margin = margin(10, 10, 10, 10),
    plot.background = element_rect(fill = "#ffffff", color = "#111111"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background=element_rect(fill="#ffffff", colour=NA),
    panel.border = element_blank(),
    axis.text = element_blank(),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    legend.position = "none"
)

v <- ggplot(data = df_volcanos, aes(longitude)) +
    geom_density(
      color = colorspace::darken("#546E7A", .2),
      fill = "#546E7A",
      alpha = .6, size = .3,  bw = .5
    ) +
    ggforce::geom_mark_circle(
      aes(
        x = 140,
        y = .019,
        label = "Highest number of volcanos   "
      ),
      color = "transparent",
      label.fill = "transparent",
      label.colour = colorspace::darken("#546E7A", .25),
      label.family = "inconsolata",
      label.fontsize = 9,
      label.buffer = unit(9, "mm"),
      con.colour = colorspace::darken("#546E7A", .25),
      con.size = .4,
      con.cap = unit(.1, "mm"),
      expand = unit(1, "mm")
    ) +
    scale_x_continuous( expand = c(0, 0), limits = c(-180, 180)) +
    scale_y_continuous( expand = c(0, 0), limits = c(NA, 0.031) ) +
    theme_bw() +
    theme_opts

girafe(ggobj = v, width_svg = 16, height_svg = 3,
       options = list(opts_sizing(rescale = TRUE, width = 0.65)))

```


### View
#### longitudinal density of eruptions


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

e <-
  df_eruptions %>%
  ggplot(aes(longitude)) +
    geom_density(
      color = colorspace::darken("#cf1020", .2),
      fill = "#cf1020",
      alpha = .6, size = .3, bw = .5
    ) +
    ggforce::geom_mark_circle(
      aes(
        x = 138.8,
        y = .029,
        label = "Highest number of eruptions   "
      ),
      color = "transparent",
      label.fill = "transparent",
      label.colour = colorspace::darken("#cf1020", .25),
      label.family = "inconsolata",
      label.fontsize = 9,
      label.margin = margin(50, 2, 2, 2, "mm"),
      con.colour = colorspace::darken("#cf1020", .25),
      con.size = .4,
      con.cap = unit(.3, "mm"),
      expand = unit(1, "mm")
    ) +
    scale_x_continuous( expand = c(0, 0), limits = c(-180, 180) ) +
    scale_y_reverse( expand = c(0, 0), limits = c(.037, NA) ) +
    theme_bw() +
    theme_opts

girafe(ggobj = e, width_svg = 16, height_svg = 3,
       options = list(opts_sizing(rescale = TRUE, width = 0.65)))

```


### View
#### plotting world borders, plates, ring of fire, and points


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

transparent_fill <- rgb(0, 0, 0, max = 255, alpha = 0, names = "transparent")

m <-
  ggplot(ne_world) +
    geom_sf( color = "#e5e5e5", fill = "#fefefe" ) +
    geom_sf(data = rof_dt, color="transparent", fill = "red", size=1.0, alpha = 0.2) +
    geom_sf(data = plates, color="#aaaaaa", fill = transparent_fill, size=1.0) +
    geom_point(data = df_eruptions, aes(x = longitude, y = latitude), shape = 21, fill = "white", color = "red", size = 5.0) +
    geom_point(data = df_volcanos, aes(x = longitude, y = latitude), size = 1.0, color = "#546E7A") +
    scale_x_continuous(expand = c(0, 0)) +
    scale_y_continuous(expand = c(0, 0)) +
    coord_sf(xlim  = c(-180, 180) ) +
    labs(
      caption = NULL
    ) +
    theme_bw() +
    theme_opts

girafe(ggobj = m, width_svg = 16, height_svg = 8,
       options = list(opts_sizing(rescale = TRUE, width = 0.65)))

```


### View
#### as a plot grid with aligned longitude axis


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', out.width="100%"}

girafe( ggobj = plot_grid(v, m, e, ncol = 1, align = "v", axis = "b", rel_heights = c(1, 2.75, 1)), 
        width_svg = 16, height_svg = 14,
        options = list(opts_sizing(rescale = TRUE, width = 0.65)))

```



### References
#### citations for narrative and data sources


* Data by The Smithsonian Institution
* Visualization inspired by the work of Cédric Scherer


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
