---
pagetitle: "Bulging waistlines"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Bulging waistlines
## Mean

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Towfiqu Barbhuiya on Unsplash"}

masthead <- "assets/towfiqu-barbhuiya-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> I'm in good shape.  That shape is round...\
--- Jarod Kintz\

***

### Ingest

country, year, bmi

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}
#Load Data1
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"

url_file1 <- "bulging-waistlines/mean-body-mass-index-bmi-in-adult-males.csv"
url1 <- paste0(url_root, url_file1)
df_males <- read.csv(url1, header = TRUE, stringsAsFactors = TRUE)
df_males

#Load Data2
url_file2 <- "bulging-waistlines/mean-body-mass-index-bmi-in-adult-women.csv"
url2 <- paste0(url_root, url_file2)
df_females <- read.csv(url2, header = TRUE, stringsAsFactors = TRUE)
df_females


```

The mean is the average or a calculated central value of a set of numbers and is used to measure the central tendency of the data. Central tendency is the statistical measure that recognizes the entire set of data or distribution through a single value. It provides an exact description of the whole data. In statistics, the mean can also be defined as the sum of all observations to the total number of observations.

### Wrangle

calculating mean for female BMI by using <kbd>mean()</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# calculate the mean for female BMI
df_wrangle <- mean(df_females$Mean.BMI..female.)
df_wrangle

```
calculating mean for male BMI by using <kbd>mean()</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# calculate the mean for Male BMI
df_wrangle <- mean(df_males$Mean.BMI..male.)
df_wrangle

```
### References
#### citations for narrative and data sources

* Narrative source: The Economist, [GO](https://www.economist.com/graphic-detail/2019/10/28/china-worries-about-its-bulging-waistlines){target="_blank"} 
* Data Source: Our World in Data, [GO](https://ourworldindata.org/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

