---
pagetitle: "Welcome to Earth!"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS 
</div>


# Welcome to Earth! 
## Imputing

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Albert Anthony on Unsplash"}

masthead <- "assets/albert-antony-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> No unidentified objects in the popular sense have been seen from the International Space Station...\
--- NASA\


***

### Ingest
#### date and count

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

#Load Data
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "welcome-to-earth/national-ufo-reporting-database-aggregated.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE)
df

```

Median is one of the three measures of central tendency. When describing a set of data, the central position of the data set is identified. Median splits the data into two halves. If the number of elements in the data set is odd then the center element is median and if it is even then the median would be the average of two central elements.

The median formula of a given set of numbers, say having 'n' __odd number__ of observations, can be expressed as:

* Median = [(n + 1)/2]th term

The median formula of a given set of numbers say having 'n' __even number__ of observations, can be expressed as:

* Median = [(n/2)th term + ((n/2) + 1)th term]/2


### Wrangle
#### calculating median for odd number of observations by using <kbd>median()</kbd>


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

#Apply median for the month January where n is odd
df_jan <- filter(df, df$Month == 'January')
df_wrangle <- median(df_jan$Count)
df_wrangle

```

#### calculating median for even number of observations by using <kbd>median()</kbd>

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

#Apply median for the whole dataset where n is even
df_wrangle <- median(df$Count)
df_wrangle

```

### References
#### citations for narrative and data sources

* Narrative and Data Sources: The National UFO Reporting Center Online Database, [GO](http://www.nuforc.org/webreports.html){target="_blank"}

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
