---
pagetitle: "Family Policy Scores by Country"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# Family Policy Scores by Country
## Bar Horizontal Ordered


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Nathan Dumlao on Unsplash"}

masthead <- "assets/nathan-dumlao-Wr3comVZJxU-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Don't call the world dirty because you forgot to clean your glasses...\
--- Aaron Hill\



***

### Ingest

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
df = read.csv("archetypes/family-policy-scores-by-country/family-policy-scores-by-country.csv", header = TRUE, stringsAsFactors = TRUE)
df


```

### Plot the chart 
#### Chart will plot as the original index in the dataframe 

```{r draw-plot, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 1080/72, fig.height = 1920/72, out.width="100%"}

theme_opts <- theme(
    plot.margin = margin(.25, 1, .25, .25, "cm"),
    plot.background = element_blank(),
    panel.background = element_blank(),
    legend.position = "none",
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    axis.ticks.y=element_blank(),
    axis.ticks.x=element_blank(),
    axis.text.x=element_blank(),
    strip.placement = "outside",                      # Place facet labels outside x axis labels.
    strip.background = element_rect(fill = "white"),  # Make facet label background white.
    axis.title = element_blank()                     # Remove x and y axis titles.
)

# Make the plot
v1 <- ggplot(df, aes(x=Family.Integration.Policy.Average.Scores, y=Country)) + 
  geom_bar(stat="identity", fill="#88b88a") +
  # scale_y_discrete(limits=c("Almond milk", "Oat milk", "Soy milk", "Rice milk","Cow's milk")) +
  #scale_fill_manual(values=c("Carbon Emissions (kg CO2eq)" = "#364e5d", "Land Use (m2)" = "#597e4e", "Water Use (L)" = "#587f89")) +
  #scale_color_manual(values=c("white" = "#ffffff", "black" = "#000000")) +
  coord_cartesian(clip="off") +
  labs(title = "FAMILY INTEGRATION POLICY AVERAGE SCORES BY COUNTRY, 2014") +
  theme_opts

# Print the plot
girafe(ggobj = v1, width_svg = 720/72, height_svg = 1280/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


### Rank From Highest to Lowest
#### As it is a horizontal Bar Chart, we reorder the y-axis.
#### Note: In the case of vertical Bar Charts, we will reorder the x-axis.

```{r drawa, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width=10.5, fig.height=10.5, out.width="100%"}

# Make the plot
v2 <- ggplot(df, aes(x=Family.Integration.Policy.Average.Scores, y=reorder(Country,Family.Integration.Policy.Average.Scores))) + 
  geom_bar(stat="identity", fill="#88b88a") +
  # scale_y_discrete(limits=c("Almond milk", "Oat milk", "Soy milk", "Rice milk","Cow's milk")) +
  #scale_fill_manual(values=c("Carbon Emissions (kg CO2eq)" = "#364e5d", "Land Use (m2)" = "#597e4e", "Water Use (L)" = "#587f89")) +
  #scale_color_manual(values=c("white" = "#ffffff", "black" = "#000000")) +
  coord_cartesian(clip="off") +
  labs(title = "FAMILY INTEGRATION POLICY AVERAGE SCORES BY COUNTRY, 2014") +
  theme_opts

# Print the plot
girafe(ggobj = v2, width_svg = 720/72, height_svg = 1280/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


### Rank from Lowest to Highest
#### The only change is putting a "-" sign infront of the axis we're reordering.



```{r drawb, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width=10.5, fig.height=10.5, out.width="100%"}


# Make the plot
v3 <- ggplot(df, aes(x=Family.Integration.Policy.Average.Scores, y=reorder(Country,-Family.Integration.Policy.Average.Scores))) + 
  geom_bar(stat="identity", fill="#88b88a") +
  # scale_y_discrete(limits=c("Almond milk", "Oat milk", "Soy milk", "Rice milk","Cow's milk")) +
  #scale_fill_manual(values=c("Carbon Emissions (kg CO2eq)" = "#364e5d", "Land Use (m2)" = "#597e4e", "Water Use (L)" = "#587f89")) +
  #scale_color_manual(values=c("white" = "#ffffff", "black" = "#000000")) +
  coord_cartesian(clip="off") +
  labs(title = "FAMILY INTEGRATION POLICY AVERAGE SCORES BY COUNTRY, 2014") +
  theme_opts

# Print the plot
girafe(ggobj = v3, width_svg = 720/72, height_svg = 1280/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```



```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width=10.5, fig.height=10.5, out.width="100%",  fig.show='hide'}

# As reusable function

make_hbar <- function(df, x_field, y_field, fill_str, title_str) {

x_var <- c(x_field)
y_var <- c(y_field)

ggplot(df, aes(x=get(x_var), y=get(y_var))) + 
  geom_bar(stat="identity", fill=fill_str) +
  coord_cartesian(clip="off") +
  labs(title = title_str) +
  theme_opts

}

```


### References

* Narrative and Data Source, United Nations [GO](https://www.un.org/en/development/desa/population/publications/policy/international-migration-policies-report-2013.asp){target="_blank"}



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

