---
pagetitle: "Road deaths by country"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
ANALYTICS  
</div>

# Road deaths by country
## Linear Regression

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Yannis H on Unsplash"}

masthead <- "assets/yannis-h-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Some car accidents are caused by the ignorance or disbelief of the fact\
  that a driver’s eyes and mind can be thousands of kilometres apart...\
--- Mokokoma Mokhonoana\

***


### Ingest the data
#### gdp and road traffic accidents

GDP

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

url_root <- "archetypes/"

url_file1 <- "gdp.csv"
url1 <- paste0(url_root, url_file1)

df_gdp <- read.csv(url1, header = TRUE, stringsAsFactors = FALSE, encoding = "UTF-8")
df_gdp

```


Road deaths


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

url_file2 <- "road-deaths.csv"
url2 <- paste0(url_root, url_file2)

df_rd <- read.csv(url2, header = TRUE, stringsAsFactors = FALSE, encoding = "UTF-8")
df_rd



```


### Wrangle the data
#### bracket removal, merge, rename, and filter


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_rd_wrangle <- df_rd %>% mutate(road_deaths = as.integer(str_replace(est_road_traffic_death_rate_per_100k_population_both_sexes, "\\[.+?\\]", "")))
df_rd_wrangle <- df_rd_wrangle %>% filter(year == 2017)
df_rd_wrangle <- df_rd_wrangle %>% select(c(country, road_deaths))
df_rd_wrangle$iso3 <- countrycode(df_rd_wrangle$country, origin='country.name', destination='iso3c')
# df_rd_wrangle

df_combined <- merge(df_rd_wrangle, df_gdp, by.x='iso3', by.y='Country_Code')
df_combined$region <- countrycode(df_combined$iso3, origin='iso3c', destination='un.region.name')
df_combined <- df_combined %>% select(c(iso3, country, road_deaths, X2017, region))
df_combined <- df_combined[complete.cases(df_combined), ]
# df_combined

df_final <- df_combined %>% rename(gdp = X2017)
df_final <- df_final %>% rename_with(toupper)
df_final <- df_final %>% filter(ROAD_DEATHS > 0)
df_final

```
#### Visualizing the possible relationship

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.grid.major = element_blank(),
    legend.position='top'
  )

region_palette <- c(
  "Africa" = "#F57C00",
  "Americas" = "#00ACC1",
  "Asia" = "#90A4AE",
  "Europe" = "#E53935",
  "Oceania" = "#8BC34A"
)

g1 <- ggplot(df_final, aes(x = GDP, y = ROAD_DEATHS)) + 
  geom_point(aes( fill = REGION, color = REGION), size = 4, shape = 21) +
  # geom_text_repel(aes(label = COUNTRY)) + 
  scale_color_manual(values = region_palette) +
  scale_fill_manual(values = region_palette) +
  labs( title = "Driving lessons",
        subtitle = NULL,
        #caption = "Source: World Bank, IHME",
        x = "GDP per capita, PPP (constant 2017 international $)",
        y = "Est road traffic death rate per 100k population both sexes, 2017") +
  theme_bw() +
  theme_opts

girafe(ggobj = g1, width_svg = 16, height_svg = 12,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```

### Linear Regression Plot
<kbd>
geom_smooth
</kbd>

We plot the relationship between the estimated road traffic death per 100k people and GDP per capita in 2017 using a linear regression model. With the linear model, we observed a negative relation between the two variables. The GDP per capita is inversely proportional to the road traffic death rate. In other words, the higher is the GDP per capita, the lower is the road traffic rate per 100k population.

#### Fitting the model

We now run a linear regression using function <kbd>lm</kbd>

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# lm required parameters
# lm(formula, data)

simple_fit = lm(ROAD_DEATHS~GDP, data = df_final) #Create the linear regression
summary(simple_fit) #Review the results

```
#### Visualizing the model results

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

g2 <- g1 + 
  geom_abline(intercept = simple_fit$coefficients[1], 
              slope = simple_fit$coefficients[2], color = "#33abdd", size = 2, linetype = 'dashed') +
  theme_opts

girafe(ggobj = g2, width_svg = 16, height_svg = 12,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```

### Wrangle
#### create a label subset


```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

label_list <- c(
  "Burundi",
  "Liberia",
  "Haiti",
  "India",
  "Dominican Republic",
  "Thailand",
  "China",
  "Saudi Arabia",
  "Oman",
  "United States of America",
  "Sweden",
  "Ireland",
  "Singapore",
  "Qatar"
)

df_labels <- filter(df_final, COUNTRY %in% label_list)
df_labels

```


### Plot with annotations
#### adding labels and annotations


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

v2 <- g2 +
  geom_text_repel(data=df_labels, aes(label = COUNTRY), box.padding = 0.75, min.segment.length = 0.0, nudge_y = 0.75, point.padding = 0.5, family = "inconsolata") + 
  geom_hline(yintercept = mean(df_final$ROAD_DEATHS), linetype = 'dashed', size = 1.5, color = '#E53935')

girafe(ggobj = v2, width_svg = 16, height_svg = 12,
       options = list(opts_sizing(rescale = TRUE, width = 0.75)))

```


### References
#### citations for narrative and data sources

* Narrative Inspiration: The Economist, Driving lession
* Data Source: World Health Organization, [GO](https://apps.who.int/gho/data/node.main.A997){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

