---
pagetitle: "Better Life Index"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(countrycode)
library(janitor)
library(tidyverse)
library(factoextra)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Better Life Index
## Biplots

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Nilay Sozbir  on Unsplash"}

masthead <- "assets/nilay-sozbir-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Karaköy , Istanbul, Turkey</div>


> We have always held to the hope, the belief,\
  the conviction that there is a better life, a better world, beyond the horizon...\
--- Franklin D. Roosevelt\

***

### Ingest
#### countries, indicators, and measures

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read.csv('archetypes/better-life-index/better-life-index.csv', encoding = "UTF-8")
df

```


### Wrangle
#### filter indicators, transform long to wide, clean

* Educational attainment
* Student skills
* Years in education


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Apply filter (or not)
df_filter <- filter(df, Indicator %in% c("Educational attainment", "Student skills", "Years in education"))

# Create a unique indicator name
df_filter <- df_filter %>% mutate(
  Indicator_Long = paste0(Indicator, "-", Inequality, "-", Unit)
)

# Select relevant fields
df_select <- df_filter %>% select(Country, Indicator_Long, Value )

# Convert from long to wide
df_wide <- spread(df_select, Indicator_Long, Value)

# The pca function can only take numeric values,
# so we convert Country column to be rownames
df_wide <- column_to_rownames(df_wide, var = "Country")

# Use only complete cases
df_wide <- df_wide[complete.cases(df_wide), ]
df_wrangle <- df_wide %>% janitor::clean_names()
df_wrangle



```


### Wrangle
#### filter to create groups for men, women, total, and combined

Men measures:  

* educational_attainment_men_percentage  
* student_skills_men_average_score  
* years_in_education_men_years  

Women measures:  

* educational_attainment_women_percentage  
* student_skills_women_average_score  
* years_in_education_women_years  

Total measures:  

* educational_attainment_total_percentage  
* student_skills_total_average_score  
* years_in_education_total_years  


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_men <- df_wrangle %>% select(educational_attainment_men_percentage, student_skills_men_average_score, years_in_education_men_years)

df_women <- df_wrangle %>% select(educational_attainment_women_percentage, student_skills_women_average_score, years_in_education_women_years )

df_total <- df_wrangle %>% select(educational_attainment_total_percentage, student_skills_total_average_score, years_in_education_total_years )

df_men_and_women <- df_wrangle %>% select(educational_attainment_men_percentage, 
                                          student_skills_men_average_score, 
                                          years_in_education_men_years,
                                          educational_attainment_women_percentage, 
                                          student_skills_women_average_score, 
                                          years_in_education_women_years)

```


### Analytics
#### fit a principal components model


```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# fit a principal components model
df_pca_men <- prcomp(x = df_men, 
              center = TRUE, 
              scale = TRUE)
# df_pca_men

df_pca_women <- prcomp(x = df_women, 
              center = TRUE, 
              scale = TRUE)
# df_pca_women

df_pca_total <- prcomp(x = df_total, 
              center = TRUE, 
              scale = TRUE)
# df_pca_total

df_pca_men_and_women <- prcomp(x = df_men_and_women, 
              center = TRUE, 
              scale = TRUE)
df_pca_men_and_women

```

# Plot

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

# fviz_pca function produces a ggplot2 graph.
v1 <- fviz_pca(df_pca_men,  repel = TRUE,  labelsize = 3) + 
  theme_bw() +
  labs(title = "Better Life Index, Education, Men")

# Draw plot
girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```
 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

# fviz_pca function produces a ggplot2 graph.
v2 <- fviz_pca(df_pca_women,  repel = TRUE,  labelsize = 3) + 
  theme_bw() +
  labs(title = "Better Life Index, Education, Women")

# Draw plot
girafe(ggobj = v2, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

# fviz_pca function produces a ggplot2 graph.
v3 <- fviz_pca(df_pca_total,  repel = TRUE,  labelsize = 3) + 
  theme_bw() +
  labs(title = "Better Life Index, Education, Total")

# Draw plot
girafe(ggobj = v3, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

# fviz_pca function produces a ggplot2 graph.
v4 <- fviz_pca(df_pca_men_and_women,  repel = TRUE,  labelsize = 3) + 
  theme_bw() +
  labs(title = "Better Life Index, Education, Men & Women")

# Draw plot
girafe(ggobj = v4, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "assets/better-life-index-fs.svg", plot = v3, width=1280/72, height=720/72)

# thumbnail version without annotations
ggsave(filename = "assets/better-life-index-sm.png", plot = v3, width=4, height=2.25)

```



# References
## The citations and data sources used for this case

* Narrative and Data Source, [OECD](https://www.oecdbetterlifeindex.org/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```