---
pagetitle: "Human Development Index"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(countrycode)
library(tidyverse)
library(factoextra)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS  
</div>

# Human Development Index
## Biplots


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Yogendra Singh on Unsplash"}

masthead <- "assets/yogendra-singh-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> You cannot predict the outcome of human development.\
  All you can do is like a farmer create the conditions under which it will begin to flourish...\
--- Ken Robinson\

***

### Ingest
#### country, rank, and measures


```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "hdi/hdi-2020.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, encoding = "UTF-8")
df


```


### Wrangle
#### row names, numeric, and select


```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df$REGION <- countrycode(df$Country, origin = 'country.name', destination = 'region') 

df_wrangle <- df

# The pca function can only take numeric values,
# so we convert Country column to be rownames
df_wrangle <- column_to_rownames(df_wrangle, var = "Country")

# Convert string to numeric
df_wrangle$Gross.national.income..GNI..per.capita <- parse_number(df_wrangle$Gross.national.income..GNI..per.capita)

# Remove HDI ranks to use key indicators only
df_wrangle <- df_wrangle %>% select(Life.expectancy.at.birth, Expected.years.of.schooling, Mean.years.of.schooling, Gross.national.income..GNI..per.capita, )
df_wrangle

```


### Analytics
#### fit a principal components model


```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# fit a principal components model
df_pca <- prcomp(x = df_wrangle, 
              center = TRUE, 
              scale = TRUE)
df_pca

# review computed results
# var <- get_pca_var(df_pca)
# var

# head(var$coord)
# head(var$cor)
# head(var$cos2)
# head(var$contrib)

# ind <- get_pca_ind(df_pca)
# ind

# head(ind$coord)
# head(ind$cos2)
# head(ind$contrib)

```

### Plot
#### standard output

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# fviz_pca function produces a ggplot2 graph.
v1 <- fviz_pca(df_pca,  repel = TRUE,  labelsize = 3) + 
  theme_bw() +
  labs(title = "HDI Biplot")

# Draw plot
girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))


```
 
 
### Plot
#### with visual variable mapping and theme
 
```{r, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, class.source='fold-hide'}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.grid.major = element_blank(),
    legend.title = element_blank(),
    legend.position='bottom'
)

region_palette <- c(
  "East Asia & Pacific" = "#FF3AAF",
  "Europe & Central Asia" = "#FFD24F",
  "Latin America & Caribbean" = "#3BD04F",
  "North America" = "#6E9EA6",
  "South Asia" = "#36D9E1",
  "Sub-Saharan Africa" = "#FF8D2F"
)

# fviz_pca function produces a ggplot2 graph.
v2 <- fviz_pca(df_pca,
               repel = TRUE,  
               col.var = "black",
               labelsize = 3, family = "inconsolata",
               pointshape = 21, 
               fill.ind = df$REGION, palette = region_palette, 
               col.ind = "black"
               ) + 
  labs(title = "Human Development Index", subtitle = "principal components model") +
  theme_bw() +
  theme_opts

# Draw plot
girafe(ggobj = v2, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```

### References
#### The citations and data sources used for this case

* Narrative and Data Source, [UNDP](http://hdr.undp.org/en/composite/HDI){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```