---
pagetitle: "Azerbaijan Anonymous"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggtext)
library(emojifont)
library(ggraph)
library(igraph)
library(tidygraph)
library(graphlayouts)
library(DiagrammeR)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
 GRAPHS  
</div>

# Azerbaijan Anonymous
## Link analysis 

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Orkhan-Farmanli on Unsplash"}

masthead <- "assets/orkhan-farmanli-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Searches in media databases (both English and Russian language) provide virtually no relevant results...\
--- Global Witness\

***



### Ingest
#### edges and nodes


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Tree data
df_edges_path <- "archetypes/azerbaijan-anonymous/azerbaijan-anonymous-edges.csv"
df_edges <- read.csv(df_edges_path, header = TRUE, stringsAsFactors = FALSE)
df_edges

df_nodes_path <- "archetypes/azerbaijan-anonymous/azerbaijan-anonymous-nodes.csv"
df_nodes <- read.csv(df_nodes_path, header = TRUE, stringsAsFactors = FALSE)
df_nodes

```


### Wrangle
#### create graph structure


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# transform to graph data structure
df_graph <- graph_from_data_frame( df_edges, vertices = df_nodes, directed = TRUE )
#df_graph_directed <- graph_from_data_frame( df_tree, directed = TRUE )
#df_graph_undirected <- graph_from_data_frame( df_tree, directed = FALSE )

# to view results as data frame
df_graph_view <-  get.data.frame(df_graph, what= "both" ) # as.data.frame(get.edgelist(df_graph))
# df_graph_view

```


### Analytics
#### compute layouts


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}


# igraph layouts

# bipartite <- create_layout(df_graph, layout = 'igraph', algorithm = 'bipartite')
circle <- create_layout(df_graph, layout = 'igraph', algorithm = 'circle')
dh <- create_layout(df_graph, layout = 'igraph', algorithm = 'dh')
drl <- create_layout(df_graph, layout = 'igraph', algorithm = 'drl')
fr <- create_layout(df_graph, layout = 'igraph', algorithm = 'fr')
gem <- create_layout(df_graph, layout = 'igraph', algorithm = 'gem')
graphopt <- create_layout(df_graph, layout = 'igraph', algorithm = 'graphopt')
grid <- create_layout(df_graph, layout = 'igraph', algorithm = 'grid')
kk <- create_layout(df_graph, layout = 'igraph', algorithm = 'kk')

lgl <- create_layout(df_graph, layout = 'igraph', algorithm = 'lgl')
mds <- create_layout(df_graph, layout = 'igraph', algorithm = 'mds')
nicely <- create_layout(df_graph, layout = 'igraph', algorithm = 'nicely')
sphere <- create_layout(df_graph, layout = 'igraph', algorithm = 'sphere')
star <- create_layout(df_graph, layout = 'igraph', algorithm = 'star')
sugiyama <- create_layout(df_graph, layout = 'igraph', algorithm = 'sugiyama')

# ggraph layouts

#backbone <- create_layout(df_graph_undirected, layout = 'backbone')

#centrality_bc <- betweenness(df_graph_directed)
#centrality_cc <- closeness(df_graph_directed)
#centrality <- create_layout(df_graph_undirected, layout = 'centrality', centrality = centrality_bc)

# circlepack <- create_layout(df_graph_directed, layout = 'circlepack')
# dendrogram <- create_layout(df_graph, layout = 'dendrogram')
# eigen <- create_layout(df_graph, layout = 'eigen', type = "laplacian", eigenvector = "smallest")

focus <- create_layout(df_graph, layout = 'focus', focus = V(df_graph)['Anar Aliyev'])

# hive <- create_layout(df_graph, layout = 'hive', axis = friends, sort.by = degree)

#linear <- create_layout(df_graph, layout = 'linear')
#matrix <- create_layout(df_graph, layout = 'matrix')
#partition <- create_layout(df_graph_directed, layout = 'partition')

# pmds_pivots <- 4
# pmds <- create_layout(df_graph, layout = 'pmds', pivots = pmds_pivots)

stress <- create_layout(df_graph, layout = 'stress')
# stress <- layout_rotate(stress, 90)

#sunburst <- create_layout(df_graph_directed, layout = 'partition', circular = TRUE)
#treemap <- create_layout(df_graph_directed, layout = 'treemap')

# df_unrooted <- df_graph_undirected %>%  activate(edges) %>%  mutate(length = runif(n()))
# unrooted <- create_layout(df_graph_undirected, layout = 'unrooted' )

# mlc <- layout_as_multilevel(df_graph,type = "all", alpha = 25, beta = 45)
# ml <- create_layout(df_graph, layout = mlc)

```


### Plot
#### dendrogram


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.margin = unit(c(1,1,1,1), "in"),
    legend.position='none'
)

node_palette <- c('Joint ventures with Socar' = '#B71C1C',
                  'Contract holder with Socar' = '#009688',
                  'Other companies' = '#0288D1',
                  'Focus' = '#111111')

edge_line_map <- c('Shareholding' = 'solid',
                   'Directorship' = 'dashed',
                   'Other' = 'dotted')

#search_emoji('office')
#emoji(search_emoji('office'))

v1 <- ggraph(stress) + 
  # draw_circle(use = "focus", max.circle = 5) +
  geom_edge_link(aes(linetype = edge_type)) + 
  # geom_edge_bend(aes(linetype = edge_type), strength=1.0) + 
  # geom_edge_diagonal(aes(linetype = edge_type)) + 
  geom_node_point(aes(color=type), shape=21, fill='white', size=12) +
  # geom_textbox(aes(x = x, y = y, label=label, fill=type), halign = 0.5, hjust = 0.5, vjust = 0.5, nudge_y = 0.1, color='#ffffff', size = 4, family = "inconsolata") +
  geom_text(aes(x = x, y = y, label=emoji(symbol), color=type), fill='black', family="EmojiOne", size=6, vjust = 0.5, nudge_y=0.06) +
  scale_color_manual(values = node_palette) +
  scale_fill_manual(values = node_palette) +
  scale_edge_linetype_manual(values = edge_line_map) +
  coord_fixed(clip = 'off') + 
  theme_void() +
  theme_opts

#v1

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 1280/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

# pg <- ggplot_build(v1)
# pg$data[[2]]
# pg$data[[3]]

```



```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

graph <- create_graph()

graph <- graph %>%
  add_nodes_from_table(
    table = df_nodes,
    label_col = label,
    type_col = type)

graph <- graph %>%
    add_edges_from_table(
      table = df_edges,
      from_col = from,
      to_col = to,
      from_to_map = node) # rel_col = edge_type

# graph attributes
graph <- add_global_graph_attrs(
    graph = graph,
    attr = c("layout", "fontname", "width"),
    value = c("twopi", "inconsolata", 0.1),
    attr_type = c("graph", "node", "node"))

# graph %>% get_global_graph_attr_info()

# nicely, circle, tree, kk, and fr or from graph spec
# render_graph(graph, layout = 'kk', as_svg = FALSE)

dot <- generate_dot(graph)
# dot

grViz(dot)

# export_csv(
#   graph,
#   ndf_name = "nodes.csv",
#   edf_name = "edges.csv",
#   output_path = getwd(),
#   colnames_type = NULL
# )

```


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

visnetwork(graph)

```



### References
#### citations for narrative and data sources

* Narrative: Global Witness, Azerbaijan Anonymous  


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

