---
pagetitle: "Illegal fishing operators"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggraph)
library(igraph)
library(tidygraph)
library(graphlayouts)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
 GRAPHS  
</div>

# Illegal fishing operators
## Link analysis 

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Snehal Krishna on Unsplash"}

masthead <- "assets/snehal-krishna-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> The only ones to profit from illegal, unreported and unregulated fishing\
  are the owners of the fishing fleets who remain hidden behind veils of corporate secrecy...\
--- Achim Steiner\

***

### Ingest
#### nodes and edges


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_edge1_path <- "archetypes/illegal-fishing-operators/illegal-fishing-operators-e1.csv"
df_edge1 <- read.csv(df_edge1_path, header = TRUE, stringsAsFactors = FALSE)
head(df_edge1, n=10)

df_node1_path <- "archetypes/illegal-fishing-operators/illegal-fishing-operators-n1.csv"
df_node1 <- read.csv(df_node1_path, header = TRUE, stringsAsFactors = FALSE)
head(df_node1, n=10)

df_edge2_path <- "archetypes/illegal-fishing-operators/illegal-fishing-operators-e2.csv"
df_edge2 <- read.csv(df_edge2_path, header = TRUE, stringsAsFactors = FALSE)
head(df_edge2, n=10)

df_node2_path <- "archetypes/illegal-fishing-operators/illegal-fishing-operators-n2.csv"
df_node2 <- read.csv(df_node2_path, header = TRUE, stringsAsFactors = FALSE)
head(df_node2, n=10)

```


### Wrangle
#### create graph structure


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

# transform to graph data structure
df_graph_1 <- graph_from_data_frame( df_edge1, vertices = df_node1 )
df_graph_2 <- graph_from_data_frame( df_edge2, vertices = df_node2 )

# to view results as data frame
df_graph_1_view <-  get.data.frame(df_graph_1, what= "both" ) # as.data.frame(get.edgelist(df_graph))
df_graph_2_view <-  get.data.frame(df_graph_2, what= "both" ) # as.data.frame(get.edgelist(df_graph))
# df_graph_1_view

```


### Analytics
#### compute layouts


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}


# igraph layouts

# bipartite <- create_layout(df_graph, layout = 'igraph', algorithm = 'bipartite')
#circle <- create_layout(df_graph, layout = 'igraph', algorithm = 'circle')
dh <- create_layout(df_graph_2, layout = 'igraph', algorithm = 'dh')
drl <- create_layout(df_graph_2, layout = 'igraph', algorithm = 'drl')
fr <- create_layout(df_graph_2, layout = 'igraph', algorithm = 'fr')
gem <- create_layout(df_graph_2, layout = 'igraph', algorithm = 'gem')
graphopt <- create_layout(df_graph_2, layout = 'igraph', algorithm = 'graphopt')
grid <- create_layout(df_graph_2, layout = 'igraph', algorithm = 'grid')
# kk <- create_layout(df_graph_2, layout = 'igraph', algorithm = 'kk')
#lgl <- create_layout(df_graph, layout = 'igraph', algorithm = 'lgl')
#mds <- create_layout(df_graph, layout = 'igraph', algorithm = 'mds')
#nicely <- create_layout(df_graph, layout = 'igraph', algorithm = 'nicely')
#sphere <- create_layout(df_graph, layout = 'igraph', algorithm = 'sphere')
#star <- create_layout(df_graph, layout = 'igraph', algorithm = 'star')

sugiyama_1 <- create_layout(df_graph_1, layout = 'igraph', algorithm = 'sugiyama')
sugiyama_2 <- create_layout(df_graph_2, layout = 'igraph', algorithm = 'sugiyama')

# ggraph layouts

#backbone <- create_layout(df_graph_undirected, layout = 'backbone')

#centrality_bc <- betweenness(df_graph_directed)
#centrality_cc <- closeness(df_graph_directed)
#centrality <- create_layout(df_graph_undirected, layout = 'centrality', centrality = centrality_bc)

#circlepack <- create_layout(df_graph_directed, layout = 'circlepack')
#dendrogram <- create_layout(df_graph_directed, layout = 'dendrogram')
#eigen <- create_layout(df_graph, layout = 'eigen', type = "laplacian", eigenvector = "smallest")

#focus <- create_layout(df_graph_directed, layout = 'focus', focus = 1)

# hive <- create_layout(df_graph, layout = 'hive', axis = friends, sort.by = degree)

#linear <- create_layout(df_graph, layout = 'linear')
#matrix <- create_layout(df_graph, layout = 'matrix')
#partition <- create_layout(df_graph_directed, layout = 'partition')

#pmds_pivots <- 3
#pmds <- create_layout(df_graph, layout = 'pmds', pivots = pmds_pivots)

stress <- create_layout(df_graph_2, layout = 'stress')
#sunburst <- create_layout(df_graph_directed, layout = 'partition', circular = TRUE)
#treemap <- create_layout(df_graph_directed, layout = 'treemap')

# df_unrooted <- df_graph_undirected %>%  activate(edges) %>%  mutate(length = runif(n()))
# unrooted <- create_layout(df_graph_2, layout = 'unrooted' )

```


### Plot
#### Overview of the ownership structure


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.margin = unit(c(1.5,1,1,1), "in"),
    legend.position='none'
  )

v1 <- ggraph(sugiyama_1) + 
  # geom_edge_elbow(aes(label = LABEL), angle_calc = 'along', label_dodge = unit(2.5, 'mm')) + 
  # geom_edge_bend(aes(label = LABEL)) +
  geom_edge_diagonal() +
  geom_node_point(size=4) +
  geom_node_label( aes(label=label), repel = FALSE, vjust = 0.0, nudge_y = 0.05, size = 6, family = "inconsolata") +
  # coord_fixed(clip = 'off') + 
  theme_void() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

# pg <- ggplot_build(v1)
# pg$data[[2]]
# pg$data[[3]]

```


#### Joint venture agreement structure


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

v2 <- ggraph(dh) + 
  geom_edge_link() +
  geom_node_point(size=4) +
  geom_node_label( aes(label=label), repel = FALSE, vjust = 0.0, nudge_y = 0.1, size = 4, family = "inconsolata") +
  # coord_fixed(clip = 'off') + 
  theme_void() +
  theme_opts

girafe(ggobj = v2, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### References
#### citations for narrative and data sources

* Narrative: C4ADS, The exploitation of company structures by illegal fishing operators

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

