---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide',
   dev = "svg")
options(scipen=999)  # turn-off scientific notation like 1e+48

# load twitter library - the rtweet library is recommended now over twitteR
library(rtweet)
# plotting and pipes - tidyverse!
library(dplyr)
# text mining library
library(tidytext)
# plotting packages
library(igraph)
library(ggraph)
library(ggiraph)
library(wordcloud)
library(tidyverse)
library(textstem)
library(quanteda)
library(openNLP)
library(NLP)
library(rJava)
```

ANALYTICS

# TEXT ANALYTICS
## Twitter hashtag covid 19

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Jeremy Bezanger on Unsplash"}

masthead <- "assets/jeremy-bezanger-Jm1YUfYjpHI-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> This pandemic has magnified every existing inequality in our society – like systemic racism, gender inequality, and poverty...\
--- Melinda Gates\

***

### Ingest tweets

Search for up to 10,000 tweets containing #covid19, excluding re-tweets:
A browser window will pop up to request for authorization

* Note that this function can only be used if you own a twitter account and have access to a twitter api. For this reason, the code will be commented out using (#). Erase the (#) if you would like to run the code


```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'}

#covid_tweets <- search_tweets(q = "#covid19", n = 10000,
                                     #lang = "en",
                                     #include_rts = FALSE)

#head(covid_tweets)

```



### References
#### citations for narrative and data sources


* Reference [GO](https://cran.r-project.org/web/packages/rtweet/vignettes/intro.html){target="_blank"}

