---
pagetitle: "Mental Health Survey"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(DBI)
library(RSQLite)

library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


<div class="activity">
INGEST  
</div>

# Mental Health Survey
## Ingest a SQLite database

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Dan Meyers on Unsplash"}

masthead <- "assets/dan-meyers-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Mental health affects every aspect of your life. It's not just this neat little issue you can put into a box....\
--- Shannon Purser\

***


### Accessing the database
#### db_connection

In order to explore the data within the Mental Health database, we can first open a db connection and list all its tables. 

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

db <- dbDriver("SQLite")
conn <- dbConnect(db,'archetypes/mental-health/mental_health.sqlite')
df <- as.data.frame(dbListTables(conn))

```


```{r, echo=FALSE}
#NOT TO BE USED AS SOLUTION
df_tmp <- df

df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = TRUE, bootstrap_options = c("striped", "hover"))
#NOT TO BE USED AS SOLUTION 

```

Now that we know this database presents the tables __Answer__, __Question__ and __Survey__, we can access each one of them separately.

Since this is a survey, we will read __Question__ table first. Then, __Answer__ and __Survey__ tables will follow.

### Explore
#### Question table

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df1 <- dbReadTable(conn, 'Question')

```

```{r, echo=FALSE}

#NOT TO BE USED AS SOLUTION
df_tmp <- df1[1:100,]

df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = TRUE, bootstrap_options = c("striped", "hover"))%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)
#NOT TO BE USED AS SOLUTION 

```


### Explore
#### Answer table


```{r, echo=TRUE, message=FALSE, warning=FALSE,class.source='fold-hide'}

df2 <- dbReadTable(conn, 'Answer')

```


```{r, echo=FALSE}

#NOT TO BE USED AS SOLUTION
df_tmp <- df2[c(1:"22000"), ]

df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = TRUE, bootstrap_options = c("striped", "hover"))%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)
#NOT TO BE USED AS SOLUTION 

```

### Explore
#### Survey table

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df3 <- dbReadTable(conn, 'Survey')

```


```{r, echo=FALSE}

# NOT TO BE USED AS SOLUTION
df_tmp <- df3[1:5,]

df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = TRUE, bootstrap_options = c("striped", "hover"))
# NOT TO BE USED AS SOLUTION 

```


### Close
#### the database connection.


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

dbDisconnect(conn)

```


### References
#### citations for narrative and data sources


* Data: Open Sourcing Mental Illness Ltd., OSMI Mental Health in Tech, https://osmihelp.org/research

<pre>
@misc{osmi_research,
  author = {OSMI},
  title = {Research :: Open Sourcing Mental Illness - Changing how we talk about mental health in the tech community - Stronger Than Fear},
  url = {https://osmihelp.org/research},
  urldate = {2021-02-24},
  organization = {osmihelp.org}
}
</pre>


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

