---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

INGEST  


# Ingest database

```{r, out.width="40%", fig.align="center", fig.cap="Photo by iconixar"}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "assets/sql.png"
knitr::include_graphics(masthead, dpi=72)
```

You can think of a traditional database as an electronic filing system where data is organized by one or more tables which are connected/related to one another via specfic keys. Each table is much like a regular data file structured by fields (columns) and records (rows).

* Table Employee

```
{  "Id", "Name", "Phone", "Dept_Id" }
```
* Table Department

```
{  "Dept_Id", "Title", "Location", "City" }
```

* __Relationship Employee and Department__ : Every employee in __Employee table__ works in a department whose information is shown in the __Department table__.