---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(DBI)
library(RSQLite)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


<div class="activity">
INGEST  
</div>

# World PM25 Levels
## ingest a SQLite database

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Dominik Dancs on Unsplash"}

masthead <- "assets/dominik-dancs-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> There's so much pollution in the air now that if it weren't for our lungs there'd be no place to put it all...\
--- Robert Orben\

***


### Accessing the database
#### via db_connection


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

db <- dbDriver("SQLite")
conn <- dbConnect(db,'archetypes/world-pm25/world-pm25.db')

df <- as.data.frame(dbListTables(conn))
df

```


### Explore
#### the pm25 table


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

df_table <- dbReadTable(conn, 'pm25')
df_table

```


### Close
#### the database connection.


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

dbDisconnect(conn)

```


### References
#### citations for narrative and data sources

* Data Source:
  * World Health Organization, 
  * SDG Indicator 11.6.2 Concentrations of fine particulate matter (PM2.5)
  * https://www.who.int/data/gho/data/indicators/indicator-details/GHO/concentrations-of-fine-particulate-matter-(pm2-5)


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "database sqlite" # mostly used in wranglers and analytics
keywords <- 'concentration particulate matter PM2.5'
commands <- 'dbConnect dbReadTable'
sources <- 'World Health Organization'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

