---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(DBI)
library(RSQLite)

library(sqldf)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


INGEST  


# World PM25 Levels
## ingest a SQLite database

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Dominik Dancs on Unsplash"}

masthead <- "assets/dominik-dancs-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> There's so much pollution in the air now that if it weren't for our lungs there'd be no place to put it all...\
--- Robert Orben\

***


### Accessing the database
#### via db_connection


```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}


db <- dbDriver("SQLite")

conn <- dbConnect(db,'archetypes/world-pm25/world-pm25.db')

df <- as.data.frame(dbListTables(conn))
df




```


### Explore
#### the pm25 table


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_table <- dbReadTable(conn, 'pm25')
df_table

```


### Close
#### the database connection.


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-show'}

dbDisconnect(conn)

```


### References
#### citations for narrative and data sources

* Data Source:
  * World Health Organization, 
  * SDG Indicator 11.6.2 Concentrations of fine particulate matter (PM2.5)
  * [GO](https://www.who.int/data/gho/data/indicators/indicator-details/GHO/concentrations-of-fine-particulate-matter-(pm2-5)){target="_blank"}
