---
pagetitle: "China's Energy Transition"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(ggplot2)
library(treemapify)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
TREES  
</div>

# China's Energy Transition
## The Treemap


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by National Cancer Institute on Unsplash"}

masthead <- "assets/national-cancer-institute-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Without hair, a queen is still a queen...\
--- Prajakta Mhadnak\

Global Burden of Disease Study, 2019

***

### Ingest the data
#### disease by cause and death


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

# Load data
df <- read.csv("./archetypes/global-burden-of-disease/IHME-GBD_2019_DATA-GLOBAL-ALL-CAUSES.csv", header = TRUE, stringsAsFactors = TRUE)  # read text file 
df


```

### Wrangle the data
#### Create hierarchy

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}


```


### Analyze the data
#### Create a quartile column to use for color mapping


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}



```


### The Layout
#### squarified with size and fill


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

# Layouts
# squarified" (the default), "scol", "srow" or "fixed"
# Simple
v1 <- ggplot(df_analysis, aes(area = val, fill = quartile)) +
  geom_treemap(color = "#ffffff") +
  scale_fill_brewer(palette = "Spectral") +
  theme_minimal() +
  theme(legend.position = "bottom")

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```



### References
#### citations for narrative and data sources

* Narrative and Data Sources:


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
