---
pagetitle: "The Top 1 Percent"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(tidyverse)
library(ggplot2)
library(treemapify)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
TREES  
</div>

# The Top 1 Percent
## The Treemap


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Mike Kononov on Unsplash"}

masthead <- "assets/mike-kononov-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Success doesn’t count unless you earn it fair and square...\
--- Michelle Obama\

This example is based on The New York Times graphics article _The Top 1 Percent: What Jobs Do They Have?_.  The use of a treemap layout conveys the many dimensions of the data, representing the taxonomy structure of occupations and industries, combined with size and color for measured and computed values.

***

### Ingest the data
#### occupations, industries, and number of people in the top 1 percent


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
df = read.csv("./archetypes/the-top-1-percent/nyt-the-top-1-percent.csv", header = TRUE, stringsAsFactors = TRUE)  # read text file 
df

```


### Analyze the data
#### Create a quartile column to use for color mapping

The within function is used for calculating new columns. The quantile function calculates the quartiles where 0:4/4 evaluates to c(0, 0.25, 0.50, 0.75, 1). Finally the cut function splits the data into the calculated quartiles. Casting the result to integers returns groups labeled as 1,2,3,4. The column is converted to a factor for use with a discrete color scale.
<p></p>

```{r}

df_analysis <- within(df, quartile <- factor(as.integer(cut(size, quantile(size, probs=0:4/4), include.lowest=TRUE))))
df_analysis

```


### The Layout
#### squarified with size, fill, and labels


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

# Layouts
# squarified" (the default), "scol", "srow" or "fixed"
v1 <- ggplot(df_analysis, aes(area = size, fill = quartile, label = label)) +
  geom_treemap(color = "#ffffff") +
  geom_treemap_text(fontface = "italic", colour = "white", place = "centre", grow = TRUE) +
  scale_fill_brewer(palette = "Oranges") +
  theme_minimal() +
  theme(legend.position = "bottom")

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


#### with subgroups


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

# Sub-grouping
v2 <- ggplot(df_analysis, aes(area = size, fill = quartile, label = label,
                subgroup = pname)) +
  geom_treemap(color = "#ffffff") +
  geom_treemap_subgroup_border(colour = "white") +
  geom_treemap_subgroup_text(place = "centre", grow = T, alpha = 0.5, colour =
                               "black", fontface = "italic", min.size = 0) +
  geom_treemap_text(colour = "white", place = "topleft", reflow = T) +
  scale_fill_brewer(palette = "Oranges") +
  theme_minimal() +
  theme(legend.position = "bottom")

# v3

girafe(ggobj = v2, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


#### as facets


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

filtered_data <- filter(df_analysis, pname != "all")

# Sub-grouping
v3 <- ggplot(filtered_data, 
             aes(area = size, fill = quartile, label = label)) +
  geom_treemap(color = '#ffffff') +
  facet_wrap( ~pname) +
  scale_fill_brewer(palette = "Oranges") +
  # geom_treemap_text(colour = "white", place = "topleft", reflow = T) +
  theme_minimal()+
  theme(legend.position = "bottom")

girafe(ggobj = v3, width_svg = 1280/72, height_svg = 1280/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### References
#### citations for narrative and data sources

* Narrative and Data Sources:The New York Times, The Top 1 Percent: What Jobs Do They Have?, 
* https://archive.nytimes.com/www.nytimes.com/packages/html/newsgraphics/2012/0115-one-percent-occupations/?ref=business  


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
