---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    df_print: paged
    mathjax: NULL
    code_folding: show
    self_contained: true
    css: ./style.css
    # lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(googlesheets4)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Roboto Mono", "roboto_mono")
# turn on showtext
showtext_auto()

```


# Kamino Project
## content status & project management

***

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# read only, authentication not needed with shared link
gs4_deauth()
path <- "https://docs.google.com/spreadsheets/d/150N38yVYhbGq6NzScBvXQkLCVr9owAmCafzOy2r3gV4/edit?usp=sharing"

```

## Activities {.tabset}

### Plan & Process
#### goals and objectives of analysis

* why
* systems
* models
* collections
* methods

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_plan <- read_sheet(path, sheet = 1)
df_plan

```

### Ingest
#### acquire data sources

* tabular
* relational
* unstructured
* pdf
* web
* social media

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_ingest <- read_sheet(path, sheet = 2)
df_ingest

```

### Wranglers
#### transform data for optimal use

* evaluate
* prepare
* reduce
* extend
* arrange
* structure
* domain
* preserve

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_wranglers <- read_sheet(path, sheet = 3)
df_wranglers

```

### Analytics
#### reveal insights

* calculate
* discover
* time-Series
* measure
* geospatial
* graph
* text-analytics

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_analytics <- read_sheet(path, sheet = 4)
df_analytics

```

### Views
#### design principles for visualization

* design
* perception
* acuity
* form
* layouts

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_views <- read_sheet(path, sheet = 5)
df_views

```

### Charts
#### design a quantitative view

* correlation
* deviation
* distribution
* magnitude
* part-to-whole
* ranking
* multiples

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_charts <- read_sheet(path, sheet = 6)
df_charts

```

### Diagrams
#### design a schematic view

* concept
* event
* logic
* structure
* system
* organization

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_diagrams <- read_sheet(path, sheet = 7)
df_diagrams

```

### Graphs
#### design a relational view

* characteristics
* operations
* link analysis
* social network analysis
* association
* flow

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_graphs <- read_sheet(path, sheet = 8)
df_graphs

```

### Maps
#### design a geospatial view

* map making
* area
* point
* abstract
* path
* space and time
* perspective


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_maps <- read_sheet(path, sheet = 9)
df_maps

```

### Semiographics
#### design a symbolic view

* meaning
* representation

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_semiographics <- read_sheet(path, sheet = 10)
df_semiographics

```

### Tables
#### design a tabular view

* chart table
* periodic table
* symbol table

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_tables <- read_sheet(path, sheet = 11)
df_tables

```

### Temporals
#### design an event view

* observables
* change
* flow
* resemblance
* finance
* chronology
* duration

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_temporals <- read_sheet(path, sheet = 12)
df_temporals

```

### Trees
#### design a hierarchical view

* space-filling
* node-link

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_trees <- read_sheet(path, sheet = 13)
df_trees

```

### Storytelling
#### design a presentation

* purpose
* design
* structure
* creation
* production

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_storytelling <- read_sheet(path, sheet = 14)
df_storytelling

```

### Summit
#### best practices and standards

* impact
* literacy
* professional standards

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_summit <- read_sheet(path, sheet = 15)
df_summit

```

### Case Studies
#### applying lifecycle to cases

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_case_studies <- read_sheet(path, sheet = 16)
df_case_studies

```

### Concatenate catalog

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_catalog <- rbind(df_plan, df_ingest, df_wranglers, df_analytics, df_views, df_charts, df_diagrams, df_graphs, df_maps, df_semiographics, df_tables, df_temporals, df_trees, df_storytelling, df_summit)

df_catalog <- df_catalog %>% mutate(ACTIVITY = factor(ACTIVITY, 
                                                         levels = c("2-plan", 
                                                                    "3-ingest", 
                                                                    "4-wranglers", 
                                                                    "5-analytics", 
                                                                    "6-views", 
                                                                    "7-charts", 
                                                                    "8-diagrams", 
                                                                    "9-graphs", 
                                                                    "10-maps", 
                                                                    "11-semiographics", 
                                                                    "12-tables",
                                                                    "13-temporals",
                                                                    "14-trees",
                                                                    "15-storytelling",
                                                                    "16-summit")), 
                                    SUBACTIVITY = factor(SUBACTIVITY),
                                    TASK = factor(TASK),
                                    STATUS = factor(STATUS),
                                    TEAM = factor(TEAM))

df_catalog

```

## Generate Search Index Output

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

kamino_content_index <- df_catalog
kamino_content_index <- filter(kamino_content_index, STATUS == "Published")
<<<<<<< HEAD
kamino_content_index <- kamino_content_index %>% mutate(
  id = row_number(), 
  ACTIVITY = paste0(ACTIVITY_SORT, "-", ACTIVITY),
  SUBACTIVITY = paste0(SUBACTIVITY_SORT, "-", SUBACTIVITY),
  TASK = paste0(TASK_SORT, "-", TASK),
  TITLE = ARCHETYPE)

=======
kamino_content_index <- kamino_content_index %>% mutate(id = row_number(), TITLE = ARCHETYPE)
>>>>>>> parent of bb67a36 (initial maps commit)
kamino_content_index <- kamino_content_index %>% select(id, ACTIVITY, SUBACTIVITY, TASK, TITLE, ARCHETYPE, METHODS, KEYWORDS, SYNTAX, SOURCES) 

kamino_content_index <- kamino_content_index %>% mutate(URL = paste0("content/", ACTIVITY, "/", SUBACTIVITY, "/", TASK, "/", TITLE, ".html"), ICON = paste0("assets/symbols/", ACTIVITY, "/", TASK, ".svg"))

kamino_content_index$LAST_UPDATE <- Sys.Date()

kamino_content_index

write.csv(kamino_content_index,"../../packages/web/models/kamino-content-index.csv", row.names = FALSE)

```


## Summary Content Views {.tabset}

### Summary Content Views
#### by activity 

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

theme_opts <- theme(
    text = element_text(family = "roboto_mono", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    # axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.grid.major = element_blank(),
    legend.position='none'
)

activity_palette <- c("2-plan" = "#B71C1C", 
                      "3-ingest" = "#880E4F", 
                      "4-wranglers" = "#4A148C", 
                      "5-analytics" = "#311B92", 
                      "6-views" = "#1A237E", 
                      "7-charts" = "#0D47A1", 
                      "8-diagrams" = "#01579B", 
                      "9-graphs" = "#006064", 
                      "10-maps" = "#004D40", 
                      "11-semiographics" = "#1B5E20", 
                      "12-tables" = "#33691E",
                      "13-temporals" = "#9E9D24",
                      "14-trees" = "#F57F17",
                      "15-storytelling" = "#FF6F00",
                      "16-summit" = "#E65100"
)

```


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_activity_summary <- df_catalog %>% group_by(ACTIVITY) %>% count()
df_activity_summary

```


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

v_activity_summary <- ggplot(df_activity_summary, aes(x = n, y = ACTIVITY, fill = ACTIVITY)) + 
  geom_bar(stat = "identity") +
  scale_y_discrete(limits = rev) +
  scale_fill_manual(values = activity_palette) +
  labs( title = "Kamino Activity Summary",
        subtitle = "Content View",
        caption = NULL,
        x = "count of articles",
        y = NULL) +
  theme_bw() +
  theme_opts

girafe(ggobj = v_activity_summary, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```


### Summary Content Views
#### by sub-activity 

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_sub_activity_summary <- df_catalog %>% group_by(ACTIVITY, SUB_ACTIVITY) %>% count()
df_sub_activity_summary

```


### Summary Content Views
#### by task 

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_task_summary <- df_catalog %>% group_by(ACTIVITY, SUB_ACTIVITY, TASK) %>% count()
df_task_summary

```


### Summary Status Views
#### by activity

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_activity_status_summary <- df_catalog %>% group_by(ACTIVITY, STATUS) %>% count()
df_activity_status_summary

```


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

v_activity_status_summary <- ggplot(df_activity_status_summary, aes(x=n, y=ACTIVITY, fill=STATUS)) + 
  geom_bar(position="stack", stat="identity") +
  scale_y_discrete(limits = rev) +
  # scale_fill_manual(values = activity_palette) +
  labs( title = "Kamino Activity Summary",
        subtitle = "Status View",
        caption = NULL,
        x = "count of articles by status",
        y = NULL) +
  theme_bw() +
  theme_opts

girafe(ggobj = v_activity_status_summary, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```


## Summary Status Views {.tabset}

### Summary Status Views
#### by sub-activity

```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_subactivity_status_summary <- df_catalog %>% group_by(ACTIVITY, SUB_ACTIVITY, STATUS) %>% count()
df_subactivity_status_summary

```


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

v_subactivity_status_summary <- ggplot(df_subactivity_status_summary, aes(x=n, y=SUB_ACTIVITY, fill=STATUS)) + 
  geom_bar(position="stack", stat="identity") +
  scale_y_discrete(limits = rev) +
  facet_grid(rows = vars(ACTIVITY), scales = "free_y", space = "free") +
  labs( title = "Kamino Activity Summary",
        subtitle = "Status View",
        caption = NULL,
        x = "count of articles by status",
        y = NULL) +
  theme_bw() +
  theme_opts

girafe(ggobj = v_subactivity_status_summary, width_svg = 1280/72, height_svg = 1280/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.75))
)

```


## Summary Team Views {.tabset}

### Activity

### Sub-Activity

