---
pagetitle: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) # turn-off scientific notation like 1e+48

library(tidyverse)

# needed to include bib references
library(knitcitations)
library(bibtex)

```


# Bar Horizontal Stacked
## Real-life case: Progress of The World's Women 2019-2020 Report - With whom do women and girls live?

> Don't call the world dirty because you forgot to clean your glasses...\
--- Aaron Hill\



***

# Load the data
## Global variations in household structure

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
df = read.csv("../archetypes/figure-2-10.csv", header = TRUE, stringsAsFactors = TRUE)
#df

# Transform wide to long
long <- df %>% gather(Type, Value, -c(ï..Region))

# Keep the rest except 'Total' column
new_long<-long %>% filter(Type!='Total')%>% rename(Region=ï..Region)

new_long

```

# Plot the chart
## Couples with children households as a proportion of all households, by age of children and region, latest available year - Figure 2.10

```{r draw-plot, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show', fig.width=10.5, fig.height=3}

gg<-ggplot(new_long, aes(x=Value, y=Region))+ 
  geom_col(aes(fill=Type), position="stack")+
  ggtitle("Percentage of all households")+
  theme(panel.background = element_rect(fill = "white"), axis.title.x=element_blank(), axis.title.y=element_blank(), 
        axis.ticks.y=element_blank(), axis.ticks.x=element_blank(), axis.text.x=element_blank(), legend.position="top")+
  geom_text(aes(label=Value, hjust="right"), color="white")

gg

```

# References
## The citations and data sources used for this case

Source: <a href="https://www.unwomen.org/-/media/headquarters/attachments/sections/library/publications/2019/progress-of-the-worlds-women-2019-2020-en.pdf?la=en&vs=3512">Progress of The World's Women 2019-2020 Report - Figure 2.10</a>
