---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)
library(officer)
library(textreadr)
library(janitor)
library(ggtext)
library(readr)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

INGEST  

# Great Apes
## ingesting multiple word documents

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Kelly Sikkema on Unsplash"}

masthead <- "assets/kelly-sikkema-r077pfFsdaU-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

>When it comes to global warming, coal is the gorilla in the room.\
---Jeff Goodell\



The following code read the documents from a folder then binds them into one output in R
```{r load-data, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}


url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "great-apes"
url <- paste0(url_root, url_file)


(f <- file.path(url, c("K0581915.doc",
    "K0582038.doc", "K0651932.doc", "K0651934.doc")))

word_documents <- lapply(f, read_doc)
word_documents


```

### References
#### citations for narrative and data sources

* Narrative and Data Source: United Nations, UNESCO| Council of the Great Apes Survival Project [GO](https://atom.archives.unesco.org/zd6rl){target="_blank"}
