---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)
library(officer)
library(textreadr)
library(janitor)
library(ggtext)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

INGEST  

# Illegal Logging
## ingest a word document

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Ivar Utinans on Unsplash"}

masthead <- "assets/ivars-utinans-vkQgb1lZZPQ-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

>Forests are the world's air-conditioning system – the lungs of the planet – and we are on the verge of switching it off \
--- Prince Charles of Wales\


***

### Ingest
#### ingest a word document into r

```{r load-data, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}


url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "illegal-logging/G0422822.doc"
url <- paste0(url_root, url_file)


word <- read_doc(url)
word

```


### References
#### citations for narrative and data sources

* Narrative and Data Source: United Nations, Economic Commission for Europe | Timber Committee [GO](https://unece.org/fileadmin/DAM/timber/docs/sem/2004-1/sem-2004-1.htm){target="_blank"}
