---
pagetitle: "Illegal Logging"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(officer)
library(textreadr)

library(janitor)
library(ggtext)

library(knitcitations)
library(bibtex)


library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


<div class="activity">
INGEST  
</div>

# Illegal Logging
## ingest a word document

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Ivar Utinans on Unsplash"}

masthead <- "assets/ivars-utinans-vkQgb1lZZPQ-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

>Forests are the world's air-conditioning system – the lungs of the planet – and we are on the verge of switching it off \
--- Prince Charles of Wales\


***

### Ingest
#### ingest a word document into r

```{r load-data, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}


url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "illegal-logging/G0422822.doc"
url <- paste0(url_root, url_file)


word <- read_doc(url)
word

```


### References
#### citations for narrative and data sources

* Narrative and Data Source: United Nations, Economic Commission for Europe | Timber Committee



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```



