---
title: "Wild Life Trafficking"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)

library(textreadr)

library(ggtext)

library(readr)


library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


<div class="activity">
INGEST  
</div>

# Illicit Trafficking in Wildlife
## ingesting a select lines of a word document while keeping format


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Dylan Mullins on Unsplash"}

masthead <- "assets/dylan-mullins-ztTPVfsrb9Y-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

>The more we exploit nature, The more our options are reduced, until we have only one: to fight for survival.\
---Mo Udall\


The following code skips the first 476 lines to the conclusion section of the document
```{r load-data, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}


url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "illicit-trafficking-in-wildlife/K1401058.doc"
url <- paste0(url_root, url_file)

skip_lines <- read_doc(url, skip = 476)

skip_lines


```




Now we will skip lines while keeping the word format of the document in tact
```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}


skip_lines_w_format <- read_doc(url, skip = 536, format = TRUE)

skip_lines_w_format
```



### References
#### citations for narrative and data sources

* Narrative and Data Source:United Nations Environment Assembly of the United Nations Environment Programme [GO](https://digitallibrary.un.org/record/3943298){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```



