---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)
library(textreadr)
library(ggtext)
library(readr)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

INGEST  

# Illicit Trafficking in Wildlife
## ingesting a select lines of a word document while keeping format


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Dylan Mullins on Unsplash"}

masthead <- "assets/dylan-mullins-ztTPVfsrb9Y-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

>The more we exploit nature, The more our options are reduced, until we have only one: to fight for survival.\
---Mo Udall\


The following code skips the first 476 lines to the conclusion section of the document
```{r load-data, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}


url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "illicit-trafficking-in-wildlife/K1401058.doc"
url <- paste0(url_root, url_file)

skip_lines <- read_doc(url, skip = 476)

skip_lines


```




Now we will skip lines while keeping the word format of the document in tact
```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}


skip_lines_w_format <- read_doc(url, skip = 536, format = TRUE)

skip_lines_w_format
```

### References
#### citations for narrative and data sources

* Narrative and Data Source:United Nations Environment Assembly of the United Nations Environment Programme [GO](https://digitallibrary.un.org/record/3943298){target="_blank"}
