---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

# Ingest an unstructured document

```{r, out.width="40%", fig.align="center", fig.cap="Photo by Soni Sokell, ID"}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "assets/document.svg"
knitr::include_graphics(masthead, dpi=72)
```



This task refers to the ingest of an _unstructured document_. An unstructured document Unstructured documents are documents that can be free-form and don’t have a set structure but are still able to be scanned, captured, and imported.

Some examples are:

* Contracts
* Letters
* Articles
* Memos


### References
#### citations for narrative and data sources

* Narrative and Data Source: OPTIFORM, [GO](https://www.optiform.com/news/structured-unstructured-documents/#:~:text=Unstructured%20documents%20are%20just%20that,Articles){target="_blank"} 
