---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(knitcitations)
library(bibtex)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

# Ingest an unstructured document

```{r, out.width="40%", fig.align="center", fig.cap="Photo by Soni Sokell, ID"}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "assets/document.svg"
knitr::include_graphics(masthead, dpi=72)
```



This task refers to the ingest of an _unstructured document_. An unstructured document Unstructured documents are documents that can be free-form and don’t have a set structure but are still able to be scanned, captured, and imported.

Some examples are:

* Contracts
* Letters
* Articles
* Memos


### References
#### citations for narrative and data sources

* Narrative and Data Source: OPTIFORM, [GO](https://www.optiform.com/news/structured-unstructured-documents/#:~:text=Unstructured%20documents%20are%20just%20that,Articles){target="_blank"} 



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "DOC DOCX"
keywords <- 'free-form scanned created unstructured'
commands <- 'read_doc'
sources <- ''

# CREATE METADATA
#source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```

```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```




