---
pagetitle: "Gender Pay Gap"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggrepel)
library(ggiraph)


library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# Gender Pay Gap
## the dumbbell chart

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Tommy Lisbin on Unsplash"}

masthead <- "assets/tommy-lisbin-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> As a single mum you’ll discover inner strengths and capabilities you never knew you had...\
--- Emma-Louise Smith 

***

### Ingest
#### Occupation, Type, Women_average_annual_salary, Men_average_annual_salary, Pay_gap, Pay_gap_as_a_percentage

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df = read.csv("archetypes/gender-pay-gap/uk-gender-pay-gap.csv", header = TRUE, stringsAsFactors = FALSE) # read text file
df

```

### Wrangle
#### factor category for facet


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df_wrangle <- df
df_wrangle$Type <- as.factor(df_wrangle$Type)

head(df_wrangle)

```



### View, chart
#### segment and points 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    plot.title = element_text(color = "black", size = 14, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10, hjust = 1.0, vjust = 1.0),
    axis.title.x = element_blank(),
    # axis.title.y = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 12, hjust = 1.0, vjust = 0.5),
    panel.border = element_blank(),
    panel.background = element_blank(),
    #panel.grid.minor = element_blank(), # remove minor gridlines
    panel.grid.major.x = element_blank(), # remove x (vertical) gridlines
    panel.grid.minor.x = element_blank(), # remove x (vertical) gridlines
    legend.title = element_blank(), # remove legend title
    legend.text = element_text(color = "black", size = 10),
    legend.position='bottom',
    plot.margin = unit(c(0.5, 0.25, 0.5, 0.5), "in")
  )

offset <- 500

v1<-ggplot(df_wrangle) +  
  geom_segment( aes(x = Women_average_annual_salary, xend = Men_average_annual_salary, y = Occupation, yend = Occupation), lineend = "butt", linejoin = "round", size=1.0, color="black" ) +
  geom_point( aes(x = Women_average_annual_salary, y = Occupation), shape = 21, size = 3, fill = "#5AC085", color = "#5AC085", alpha = 0.9) +
  geom_text( aes(x = Women_average_annual_salary - (ifelse(Pay_gap > 0, offset, -offset)), y = Occupation, label=Women_average_annual_salary), 
             size=4, color="black", 
             hjust = ifelse(df_wrangle$Pay_gap > 0, 1.0, 0.0), 
             vjust = 0.5, family = "inconsolata" ) +
  geom_point( aes(x = Men_average_annual_salary, y = Occupation), shape = 21, size = 3, fill = "#474B52", color = "#474B52", alpha = 0.9) +
  geom_text( aes(x = Men_average_annual_salary + (ifelse(Pay_gap > 0, offset, -offset)), y = Occupation, label=Men_average_annual_salary), 
             size=4, color="black", 
             hjust = ifelse(df_wrangle$Pay_gap > 0, 0.0, 1.0), 
             vjust = 0.5, family = "inconsolata" ) + 
  scale_x_continuous() +
  coord_cartesian(clip = "off") +
  facet_wrap(~Type, scales = "free", ncol = 1) +
  labs(title = "GENDER PAY GAP",
       subtitle = "UK, by salary and job category",
       caption = "Source: UK Office for National Statistics",
       x = NULL,
       y = NULL) +
  theme_minimal() + 
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 1080/72,
       options = list(opts_sizing(rescale = TRUE, width = 0.95)))

```




```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-show'}

# eval = FALSE as default; run manually as chunk

# full version
ggsave(filename = "assets/gender-pay-gap-fs.svg", plot = v1, width=720/72, height=1080/72)

# thumbnail version without annotations
ggsave(filename = "outputs/gender-pay-gap-sm.svg", plot = v1, width=2.25, height=2.25)

```

# References
## The citations and data sources used for this case

* Narrative and Data: Information is Beautiful, UK Gender Pay Gap, 2021, 
[GO](https://informationisbeautiful.net/visualizations/gender-pay-gap/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}
# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())
```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

