---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(countrycode)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


WRANGLERS  


# Big Mac by Country
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Amirali Mirhashemian on Unsplash"}

masthead <- "assets/amirali-mirhashemian-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">A Good-Looking Burger</div>


> About once every three and a half weeks, I need a Big Mac, but after that I'm fine...\
--- Sara Cox\

***

### Load the data


```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "big-mac-by-country/big-mac-by-country.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE)
df<-df[1:12,]
df

```

### Wrangle


ISO_Alpha3

<a href="https://cran.r-project.org/web/packages/countrycode/countrycode.pdf" target="_blank" rel="noopener noreferrer">library(countrycode)</a> is a very useful package when we deal with country data. This package includes a set of functions that we can apply to convert, guess and/or validate country code.

For example, the second column in the dataset we loaded, called "iso_a3", seems to contain ISO-3 characters. Using the package, we can confirm that these code are all valid. If some of them are not valid, it will return NA.

Let's enter "iso3c" as origin first (meaning we guess it is ISO-3). For each cell, it will return the country name if the code is recognized. To do this, we use the function <kbd>countrycode()</kbd>

```{r is.country, echo=TRUE, message=FALSE}

results <- countrycode(df$iso_a3, origin = 'iso3c', destination = 'country.name')
results

```

Notice that the tenth entry is NA, meaning the code was not recognized as a valid ISO3 code. 

### References
#### citations for narrative and data sources

* Narrative sources: The Economist, The Big Mac Index, [GO](https://www.economist.com/big-mac-index){target="_blank"}
* Data sources: TidyTuesday, [GO](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-12-22){target="_blank"}
