---
pagetitle: "Big Mac by Country"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Big Mac by Country
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Amirali Mirhashemian on Unsplash"}

masthead <- "assets/amirali-mirhashemian-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Burger</div>


> About once every three and a half weeks, I need a Big Mac, but after that I'm fine...\
--- Sara Cox\

***

### Ingest Data


```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "big-mac-by-country/big-mac-by-country.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE)
df<-df[1:12,]
df

```

### ISO_Alpha3

library(countrycode) is a very useful package when we deal with country data,   <a href="https://cran.r-project.org/web/packages/countrycode/countrycode.pdf" target="_blank" rel="noopener noreferrer">[country code library]</a>

This package includes a set of functions that we can apply to convert, guess and/or validate country code.

For example, the second column in the dataset we loaded, called "iso_a3", seems to contain ISO-3 characters. Using the package, we can confirm that these code are all valid. If some of them are not valid, it will return NA.

Let's enter "iso3c" as origin first (meaning we guess it is ISO-3). For each cell, it will return the country name if the code is recognized.

```{r is.country, echo=TRUE, message=FALSE}

results <- countrycode(df$iso_a3, origin = 'iso3c', destination = 'country.name')
results

```

Notice that the tenth entry is NA, meaning the code was not recognized as a valid ISO3 code. 

### References
#### citations for narrative and data sources

* Data sources: TidyTuesday, [GO](https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-12-22/big-mac.csv){target="_blank"}

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
