---
pagetitle: "Biocapacity by Country"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# BioCapacity by Country
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Cedric VT on Unsplash"}

masthead <- "assets/cedric-vt-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Fields and forest just before sunset, with a cloudy sky</div>


> We do not inherit the Earth from our ancestors; we borrow it from our children...\
--- Native American Proverb\

***

### Load the data


```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "global-ecological-footprint/biocapacity-gha.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE, nrows=20)
df

```


### Wrangle 

ISO_Alpha2

ISO 3166-1 alpha-2 codes are standardized two-letter country codes. We can validate ISO2 codes by using library(countrycode). Let's enter "iso2c" as origin first (meaning we guess it is ISO-A2). For each cell, it will return the country name if the code is recognized. To do this, we use the function <kbd>countrycode()</kbd>

```{r is.alpha, echo=TRUE, message=FALSE}
results <- countrycode(df$isoa2, origin = 'iso2c', destination = 'country.name')
df2 <- data.frame(df$isoa2, results)
df2

```


Our package successfully converted all our iso2c codes from the ingested data into Country Names. This means that our column follows the iso2c code.

### References
#### citations for narrative and data sources

* Narrative and Data sources: Global Footprint Network, [GO](https://www.footprintnetwork.org/resources/data/){target="_blank"}  



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
