---
pagetitle: "Broadway Grosses"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Broadway Grosses
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Kyle Head on Unsplash"}

masthead <- "assets/kyle-head-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Broadway Play</div>


> They say the neon lights are bright on Broadway. They say there’s always magic in the air...\
--- The Drifters\

***




```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "broadway/grosses.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE, nrows=20)
df

```


### Is alpha

Checking if the cells in the first column contain letters, and only letters (a-zA-Z). We can use the function <kbd>grepl()</kbd>

```{r is.alpha, echo=TRUE, message=FALSE}

a <- df$show

df_1 <- grepl("^[a-zA-Z ]*$", a, perl = T)
df_1

```


As you can see, only cell 18 contains letters, the other cells contain numbers or other characters.

<!-- FOR DISPLAY ONLY -->

```{r, echo=FALSE}
# NOT TO BE USED AS SOLUTION
list <- list(a, df_1)
df_tmp<-as.data.frame(do.call(cbind, list))%>%rename(Broad_Way_Show=V1,is_alpha=V2)


df_tmp <-df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
row_spec(c(1,3, 14, 15,20), bold = T, color = "white", background = "#76b5c5")%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)
df_tmp

#NOT TO BE USED AS SOLUTION 

```


As you can see, some rows contain other characters than just alphabets.

### References
#### citations for narrative and data sources

* Narrative and Data sources: This case is based on a dataset by Tidy Tuesday, [GO](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-04-28/readme.md") 



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
