---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# Broadway Grosses
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Kyle Head on Unsplash"}

masthead <- "assets/kyle-head-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Broadway Play</div>


> They say the neon lights are bright on Broadway. They say there’s always magic in the air...\
--- The Drifters\

***

### Load the data


```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "broadway/grosses.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE, nrows=20)
df

```


### Wrangle 

Is alpha

Checking if the cells in the first column contain letters, and only letters (a-zA-Z). We can use the function <kbd>grepl()</kbd>

```{r is.alpha, echo=TRUE, message=FALSE}

a <- df$show

df_1 <- grepl("^[a-zA-Z ]*$", a, perl = T)
df_1

```


As you can see, only cell 18 contains letters, the other cells contain numbers or other characters.


As you can see, some rows contain other characters than just alphabets.

### References
#### citations for narrative and data sources

* Narrative and Data sources: This case is based on a dataset by Tidy Tuesday, [GO](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-04-28){target="_blank"}  

