---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# Car Makes and Models
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Alex Suprun on Unsplash"}

masthead <- "assets/alex-suprun-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Vintage Cars</div>


> If I had asked people what they wanted, they would have said faster horses...\
--- Henry Ford\

***

### Load the data


```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "car-prices/CarPrice_Assignment.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE)
df

```


### Wrangle 

Is In List

We will check if a list contains a particular element or a multitude of elements. Here, we ingested a list of automobiles and their features. We'll see if a particular car is in that list. We can use the operator <kbd>%in%</kbd>

```{r, echo=TRUE, message=FALSE}

"bmw x5" %in% df$CarName

```

We can see that the string 'bmw x5' is in our ingested dataset. We can also create a list of cars to check if they are in the dataset.


```{r, echo=TRUE, message=FALSE}

a <- c("nissan sentra", "honda civic", 'toyota corolla', 'hyundai elantra')
a

a %in% df$CarName

```

### References
#### citations for narrative and data sources

* Narrative and Data sources: This case is based on a dataset by Kaggle, [GO](https://www.kaggle.com/goyalshalini93/car-data){target="_blank"}  
