---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# Hexadecimal Colors
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Mario Gogh on Unsplash"}

masthead <- "assets/mario-gogh-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Color Pallete</div>


> Color! What a deep and mysterious language, the language of dreams...\
--- Paul Gauguin\

***


### Load the data

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "colors/colors.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE, nrows=25)
colnames(df) <- c('Color_code', 'Color_Name', 'Hex_code', 'R', 'G', 'B')
df

```


### Wrangle


Is Hex Color

Hexadecimal Color Code starts with a # followed by six or three letters or digits.For example: #fff, #FFF, #000, #111111, #F000F0, #00FF00, #0000FF, #FFFFFF are all valid Hexadecimal color codes.

To validate, we can use the function <kbd>grepl()</kbd>

```{r is.alpha, echo=TRUE, message=FALSE}
a <- df$Hex_code

df_1 <- grepl("^#([A-Fa-f0-9]{6}|[A-Fa-f0-9]{3})$", a, perl = T)
df_1

```


As you can see, every cell in column "Hex_code" are valid Hexadecimal Codes.


### References
#### citations for narrative and data sources

* Data sources: The complete list of colors and Hexadecimal Color Codes can be found on Wikipedia, [GO](https://en.wikipedia.org/wiki/List_of_colors:_A%E2%80%93F){target="_blank"}
