---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# Meteorite Landings
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Vincentiu Solomon on Unsplash"}

masthead <- "assets/vincentiu-solomon-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Meteor</div>


> If the Earth gets hit by an asteroid, it's game over. It's control-alt-delete for civilization...\
--- Bill Nye\

***

### Load the data


```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "meteorite-landings/meteorite-landings.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE, nrows = 25)
df

```

### Wrangle

Is Alphanumeric

Checking if the cells in the fourth column (Meteorite Classification) contain only letters or numbers. To do this we use regular expression with the function <kbd>grepl()</kbd>

```{r is.alphanumeric, echo=TRUE, message=FALSE}

a <- df$recclass
df_2 <- grepl("^[0-9A-Za-z ]+$", a, perl = T)
df_2

```

As you can see, cells that contain punctuation will output as FALSE.


### References
#### citations for narrative and data sources

* Data sources: This case is based on a dataset by Nasa on Kaggle, [GO](https://www.kaggle.com/nasa/meteorite-landings){target="_blank"}

