---
pagetitle: "Meteorite Landings"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Meteorite Landings
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Vincentiu Solomon on Unsplash"}

masthead <- "assets/vincentiu-solomon-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Meteor</div>


> If the Earth gets hit by an asteroid, it's game over. It's control-alt-delete for civilization...\
--- Bill Nye\

***

### Load the data


```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "meteorite-landings/meteorite-landings.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE, nrows = 25)
df

```

### Wrangle

Is Alphanumeric

Checking if the cells in the fourth column (Meteorite Classification) contain only letters or numbers. To do this we use regular expression with the function <kbd>grepl()</kbd>

```{r is.alphanumeric, echo=TRUE, message=FALSE}

a <- df$recclass
df_2 <- grepl("^[0-9A-Za-z ]+$", a, perl = T)
df_2

```

As you can see, cells that contain punctuation will output as FALSE.

<!-- FOR DISPLAY ONLY -->

```{r, echo=FALSE}

# NOT TO BE USED AS SOLUTION
list <- list(a, df_2)
df_tmp<-as.data.frame(do.call(cbind, list))%>%rename(CMeteorite_Classification=V1,is_alpha=V2)


df_tmp <-df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = "striped")%>%
row_spec(c(7, 11, 17,18,21,23), bold = T, color = "white", background = "#76b5c5")%>%
scroll_box(height = "350px", width = NULL, extra_css = NULL, fixed_thead = TRUE)
df_tmp

#NOT TO BE USED AS SOLUTION 

```

### References
#### citations for narrative and data sources

* Data sources: This case is based on a dataset by Nasa on Kaggle, [GO](https://www.kaggle.com/nasa/meteorite-landings){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
