---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r , include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# Three Star Michelin Restaurants
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Rod Long on Unsplash"}

masthead <- "assets/rod-long-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Broadway Play</div>


> There’s always something that could be done better...\
--- Joël Robuchon (Michelin Chef)\

***

### Load the data

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "michelin-three-stars/three-stars-michelin-restaurants.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE, nrows=25)
df

```


### Wrangle

Is LatLong

Check if the string is a valid latitude-longitude coordinate. The latitude of the location ranges from -90.0 to 90.0. The longitude of the location ranges from -180.0 to 180.0.

Let's check if "latitude" column fit the requirement. 

```{r , echo=TRUE, message=FALSE}

df$latitude<90.0 & df$latitude>-90.0

```

As you can see, the column fits the latitude requirement. 

Now, let's check if "longitude" column fit the requirement. 

```{r , echo=TRUE, message=FALSE}

df$longitude < 180.0 & df$longitude > -180.0

```

### References
#### citations for narrative and data sources

* Data sources: This dataset on Michelin Star Restaurants can be found on Kaggle,
[GO](https://www.kaggle.com/jackywang529/michelin-restaurants){target="_blank"}
