---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(showtext)
library(stringr)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# New York Restaurant Inspection
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Gerrie Van Der Walt on Unsplash"}

masthead <- "assets/gerrie-van-der-walt-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Burger</div>


> I'm plagued with indecision in my life. I can't figure out what to order in a restaurant...\
--- Chuck Close\

***

### Load the data


```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}
url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "new-york-restaurant-inspection/New_York_City_Restaurant_Inspection.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE, nrows=30)
df

```

### Wrangle

Is Length

String Length validation is especially useful to make sure the number of characters entered into a field can be restricted. It can be used to make sure the number of characters are the same throughout the column.

For example, United States phone numbers must be 10 digits. We can use this information to validate that all the cells in the column 'Phone' are 10 digits.

We'll validate both Phone Number(10 digits) and Postal Code (5 digits) by using <kbd>nchar()</kbd>


```{r, echo=TRUE, message=FALSE}

nchar(df$ZIPCODE)== 5
nchar(df$PHONE)==10

```

We can also utilize <kbd>str_length()</kbd> from the stringr library

```{r, echo=TRUE, message=FALSE}

str_length(df$ZIPCODE)== 5
str_length(df$PHONE)==10

```



### References
#### citations for narrative and data sources

* Data sources: Kaggle, [GO](https://www.kaggle.com/new-york-city/nyc-inspections/version/1){target="_blank"}
