---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Validate
## Verify the conformity and quality of source Data Set

```{r, out.width="60%", fig.align="center", fig.cap="Photo by "}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
#masthead <- "assets/asses_name.png"
#knitr::include_graphics(masthead, dpi=72)

```

__Data Validation__ is the process of ensuring that the data conforms to the requirements of the use cases. Typical examples include ensuring that the column __First Name__ only contain alphabets, column __Age__ contains only whole numbers, and the column __Date__ is set up in a Date Format (MM/DD/YY). The goal of Data Validation is to ensure that data is consistent, accurate and complete.  


These are the key areas we'll focus on addressing:

* __Data-Type Check__ : verify that the characters in the dataset conform to the expected characters or datatypes
* __Range and Constraint Validation__ : check the consistency with a maximum/minimum range or evaluate a sequence of characters
* __Code Check__ : verify that data conforms to an external rule or organizational rule (eg. Country Codes of a Region)

Data validation determines the formal aspects and rules of the data, however does not necessarily ensure the accuracy of the data. Errors such as misspellings and inaccurate information can still occur. Therefore, data validation is an important aspect of data science before other processes are operated upon the data. 

These are some sample functions that we'll be utilizing:

* __Is Alpha__ : check that the cells contains letter and letters only
* __Is Integer__ : check if the cells are whole numbers or with the __integer__ datatype
* __Country Code__ : Validate Country Names and Country Codes using global standards

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "Validate change-date country-code is-alpha is-alphanumeric is-date is-decimal is-divisible is-empty is-integer is-length is-logical is-longitude is-numeric" # mostly used in wranglers and analytics
keywords <- ''
commands <- ''
sources <- ''

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

