---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# The Price of a Pangolin
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Louis Mornaud on Unsplash"}

masthead <- "assets/louis-mornaud-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">The Pangolin is the most illegally trafficked animal in the world.</div>


> We have to stop the blood flow. We have to be relentless in our pursuit for justice; in our pursuit for humanity. Nature is the mother of us all, and within all of us is the spirit of an eco warrior. The war on poaching is a war on greed, but what stands to be lost is priceless...\
--- National Green Party\

***

### Load the data


```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "price-of-pangolin/pangolin_scales.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE)
df

```

Pangolins are believed to be the world's most trafficked mammal, accounting for as much as 20% of all illegal wildlife trade. According to the International Union for Conservation of Nature (IUCN), more than a million pangolins were poached in the decade prior to 2014.

The animals are trafficked mainly for their scales, which are believed to treat a variety of health conditions in traditional Chinese medicine, and as a luxury food in Vietnam and China. In Africa, pangolins are sold as a form of bushmeat, for ritual or spiritual purposes, and use in traditional African medicine. Many times the animal is trafficked just for clothing and fashion. (Source: Wikipedia)

### Wrangle 

Is Currency

We can use regular expression to match if our cells are in the correct format. A currency might start with the $ sign and might have commas and decimals. Here we have the decimal and commas as optional. We can use the function <kbd>grepl()</kbd>

```{r , echo=TRUE, message=FALSE}

a <- gsub(" ", "", df$Price_per_kg)

df_1 <- grepl("(?=.*?\\d)^\\$?(([1-9]\\d{0,2}(,\\d{3})*)|\\d+)?(\\.\\d{1,2})?$", a, perl = T)
df_1

```

We can also validate with other rules such as the commas and decimals being mandatory. Here, we will make decimals required and commas optional.


```{r , echo=TRUE, message=FALSE}

df_2 <- grepl("^\\$?(([1-9]\\d{0,2}(,\\d{3})*)|0)?\\.\\d{1,2}$", a, perl = T)
df_2

```
As you can see, our Price column does not follow the decimal format. We can use additional currency formatters if we wish to do so.


### References
#### citations for narrative and data sources

* Narratives: Additional Narratives on Illegal Pangolin Trade and Pangolin Conservation,
[GO](https://www.savepangolins.org/){target="_blank"}  
* Data sources: This case is based on a dataset by The Pangolin Report, [GO](https://www.pangolinreports.com/){target="_blank"}  
