---
pagetitle: "Toronto Stolen Bikes"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: vendor
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Torento Stolen Bikes
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Nasa on Unsplash"}

masthead <- "assets/robert-bye-tG36rvCeqng-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Satellite in Orbit</div>


> Nothing compares to the simple pleasure of a bike ride....\
--- John F. Kennedy, late former American president\

***

### Load the data

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "toronto-stolen-bikes/toronto-stolen-bikes.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE, nrows=25)
df

```


### Wrangle

Is is_ISO8601

ISO 8601 is an international standard covering the worldwide exchange and communication of date- and time-related data in the format yyyy-mm-dd or yyyy-mm-dd hh:mm:ss. To validate this we input the column into a try-catch with the function <kbd>as.Date()</kbd> 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

d <- try(as.Date(df$DATE, format="%Y-%m-%d"))
if("try-error" %in% class(d) || is.na(d)) {
  print("The list is NOT in an ISO8601 format")
}else print("The list is in an ISO8601 format")

```

Let's try with the column 'Year'.

```{r , message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

d <- try(as.Date(df$Year, format="%Y-%m-%d"))
if("try-error" %in% class(d) || is.na(d)) {
  print("The list is NOT in an ISO8601 format")
}else print("The list is in an ISO8601 format")

```


### References
#### citations for narrative and data sources

* Narrative and Data sources: Toronto Bike Thefts - Toronto Police, [GO](https://data.torontopolice.on.ca/datasets/bicycle-thefts){target="_blank"}

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
