---
title: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(tidyverse)
library(kableExtra)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# UCS Satellites
## Validate

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Nasa on Unsplash"}

masthead <- "assets/photo-satellite.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Satellite in Orbit</div>


> If I had a spreadsheet on my computer, it looked like I was busy...\
--- Nate Silver\

***

### Load the data

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "ucs-satellite-database/ucs-satellite-database-original.csv"
url <- paste0(url_root, url_file)
df <- read.csv(url, header = TRUE, nrows=25)
df

```


### Wrangle

Is empty

Checking if the column "Detailed.Purpose" column has any cells with length zero. To do this, we use function <kbd>nchar()</kbd> 

```{r is.empty, echo=TRUE, message=FALSE}

df_2 <- nchar(df$Detailed_Purpose)==0
df_2

```

```{r, echo=FALSE}

list <- data.frame(Detailed_Purpose = df$Detailed_Purpose, is.empty = df_2)
list

```

As you can see, there are many empty rows.



### References
#### citations for narrative and data sources

* Narrative and Data sources: This case is based on a dataset that comes from the following report by Union of Concerned Scientists, [GO](https://www.ucsusa.org/resources/satellite-database){target="_blank"} 
