---
pagetitle: "Missing Migrants"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(ggthemes)
library(ggiraph)

library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()


```

<div class="activity">
WRANGLERS  
</div>

# Missing Migrants
## Group by Columns

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Nikko Macaspac on Unsplash"}

masthead <- "assets/nikko-macaspac-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Man is not the sum of what he has already, but rather the sum of what he does not yet have, of what he could have....\
--- Jean-Paul Sartre  

***

### Load Data

We will group this data into different parts, and apply function/s to each of them, such as sum, mean, median, max and min. Since we have some missing valueS, let's also replace "NA" data with 0 first (we will revisit this pattern later in the course).


```{r load raw data,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df <- read_csv('./archetypes/missing-migrants/MissingMigrants-Global-2020-10-18T06-37-33.csv')

df <- df %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0))

df

```


### Group one variable with one calculation

First, lets create a simle Group by on "Reported Year" and calculate the sum of the "Total Dead and Missing" persons.

```{r, message=FALSE, echo=TRUE, warning=FALSE}

df_1 <- df %>% 
  group_by(`Reported Year`) %>% 
  summarise(sum_number=sum(`Total Dead and Missing`))

df_1

```


### Group more than one variable with one calculation

Let's now group by "Reported Year" and "Reported Month", calculating the sum of the "Total Dead and Missing".


```{r method: group more, message=FALSE, echo=TRUE,warning=FALSE}

df_2 <- df %>% 
  group_by(`Reported Year`, `Reported Month`) %>% 
  summarise(sum_number=sum(`Total Dead and Missing`))

df_2

```


Notice that the data is presented vertically, with only 3 columns, and each row representing one observation (here the sum for a specific year and month. This is called the "Long data format". This is the best format to run the chart below.


### Time to plot

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide',out.width = "100%"}

df_2$`Reported Month` <- factor(df_2$`Reported Month`, levels=c('Jan','Feb','Mar','Apr','May','Jun','Jul','Aug','Sep','Oct','Nov','Dec'))
df_2$`Reported Year` <- factor(df_2$`Reported Year`, levels=c('2014','2015','2016','2017','2018','2019','2020'))
year_palette <- c("2014" = "#E9EAF6", "2015" = "#C5C8E0", "2016" = "#959DCA", "2017" = "#4764A8", "2018" = "#6F7DB6",
                  "2019" = "#33B5B3", "2020" = "#C5C8E0")


v1 <- ggplot(df_2,aes(x=`Reported Month`, y=sum_number, fill=`Reported Year`)) +
  geom_hline(yintercept = 0, size=0.1, color = "grey") +
  geom_hline(yintercept = 500, size=0.1, color = "grey") +
  geom_hline(yintercept = 1000, size=0.1, color = "grey") +
  geom_hline(yintercept = 1500, size=0.1, color = "grey") +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_manual(values=year_palette, name = "YEAR") +
  geom_text(aes(label = sum_number), hjust=-0.1, size = 3, angle=90,
            position = position_dodge(0.9)) +
  theme_tufte(base_size = 15) +
  theme(
    panel.background = element_blank(),
    plot.title = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.ticks = element_blank()
    #plot.margin = unit(c(1, 5, 1, 1), "lines")
  ) + 
  theme(legend.position="top") + 
  guides(colour = guide_legend(nrow = 1))


girafe(ggobj = v1, width_svg = 16, height_svg = 9, options =
list(opts_sizing(rescale = TRUE, width = 1.0)))

```

### References
#### citations for narrative and data sources

* Narrative and data sources: Missing Migrants, [GO](https://missingmigrants.iom.int/){target="_blank"}

<pre>
@misc{missingmigrants_2001_missing,
  author = {MissingMigrants},
  month = {06},
  title = {Missing Migrants Project},
  url = {https://missingmigrants.iom.int/},
  urldate = {2021-06-08},
  year = {2001},
  organization = {Iom.int}
}
</pre>



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

