---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Group
## Aggregate individual observations into groups

```{r, out.width="20%", fig.align="center", fig.cap="Photo by Creative Commons"}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "assets/4-wranglers-4-extend.svg"
knitr::include_graphics(masthead, dpi=72)
```

Group Methods  

* Group __one_variable__ with __one_calculation__
* Group __multiple_variables__ with __one_calculation__
* Group __multiple_variables__ with __multiple_calculations__

Common aggregations functions:  

* __Count__: quatity of records per group
* __Sum__: Summation of a value per group
* __Min__, __Max__, find the minimum or maximum value per group
* Measure of __central tendency__: mean, median, mode per group

Other useful methods:

* __Pivot__, turning “Long data format” to "Wide data format"
* __Unpivot__, turning "Wide data format" to “Long data format”

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "group-by group-by-summarise pivot unpivot" # mostly used in wranglers and analytics
keywords <- ''
commands <- ''
sources <- ''

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

