---
pagetitle: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  

# Group
## Aggregate individual observations into groups

```{r, out.width="20%", fig.align="center", fig.cap="Photo by Creative Commons"}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "assets/4-wranglers-4-extend.svg"
knitr::include_graphics(masthead, dpi=72)
```

Group Methods  

* Group __one_variable__ with __one_calculation__
* Group __multiple_variables__ with __one_calculation__
* Group __multiple_variables__ with __multiple_calculations__

Common aggregations functions:  

* __Count__: quatity of records per group
* __Sum__: Summation of a value per group
* __Min__, __Max__, find the minimum or maximum value per group
* Measure of __central tendency__: mean, median, mode per group

Other useful methods:

* __Pivot__, turning “Long data format” to "Wide data format"
* __Unpivot__, turning "Wide data format" to “Long data format”
