---
pagetitle: "Welcome to Earth!"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(ggthemes)
library(ggiraph)
library(dplyr)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>


# Welcome to Earth! 
## Pivot

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Albert Anthony on Unsplash"}

masthead <- "assets/albert-antony-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> No unidentified objects in the popular sense have been seen from the International Space Station...\
--- NASA\


***

### Ingest
#### date and count

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "welcome-to-earth/national-ufo-reporting-database-aggregated.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE)
head(df, n=10)

```


### Wrangle
#### convert to date type


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_wrangle <- df
df_wrangle$Date <- as.Date(df_wrangle$Date, "%m-%d-%Y")
df_wrangle$Year <- format(as.Date(df_wrangle$Date, format="%d/%m/%Y"), "%Y")
df_wrangle

```
### Group more than one variable with one calculation

Let's now group by "Year" and "Month", calculating the sum of the "Count".


```{r method: group more, message=FALSE, echo=TRUE,warning=FALSE}

df_2 <- df_wrangle %>% 
  group_by(`Year`, `Month`) %>% 
  summarise(sum_number=sum(`Count`))

df_2

```

### Pivot

The above "Long data format" may be good for running a chart, but it is not the most human-friendly presentation. Let's see how we can transform this.


```{r method: one cal, message=FALSE, echo=TRUE,warning=FALSE}

df_3 <- df_2 %>% 
  pivot_wider(names_from = `Month`, values_from = sum_number) %>% 
  relocate(`Year`,January, February, March, April, May, June, July, August, September, October, November, December)

df_3

```


### References
#### citations for narrative and data sources

* Narrative and Data Sources: The National UFO Reporting Center Online Database, [GO](http://www.nuforc.org/webreports.html){target="_blank"}

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
