---
pagetitle: "Welcome to Earth!"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

library(tidyverse)
library(ggplot2)
library(gridExtra)
library(ggthemes)
library(ggiraph)
library(dplyr)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS  


# Welcome to Earth! 
## Pivot

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Albert Anthony on Unsplash"}

masthead <- "assets/albert-antony-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> No unidentified objects in the popular sense have been seen from the International Space Station...\
--- NASA\


***

### Ingest
#### date and count

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

url_root <- "https://raw.githubusercontent.com/UN-AVT/kamino-source/main/sources/0-shared/data/"
url_file <- "welcome-to-earth/national-ufo-reporting-database-aggregated.csv"
url <- paste0(url_root, url_file)

df <- read.csv(url, header = TRUE)
head(df, n=10)

```


### Wrangle
#### convert to date type


```{r, echo=TRUE, message=FALSE, warning=FALSE, class.source='fold-hide'}

df_wrangle <- df
df_wrangle$Date <- as.Date(df_wrangle$Date, "%m-%d-%Y")
df_wrangle$Year <- format(as.Date(df_wrangle$Date, format="%d/%m/%Y"), "%Y")
df_wrangle

```
### Group more than one variable with one calculation

Let's now group by "Year" and "Month", calculating the sum of the "Count".


```{r method: group more, message=FALSE, echo=TRUE,warning=FALSE}

df_2 <- df_wrangle %>% 
  group_by(`Year`, `Month`) %>% 
  summarise(sum_number=sum(`Count`))

df_2

```

### Pivot

The above "Long data format" may be good for running a chart, but it is not the most human-friendly presentation. Let's see how we can transform this.


```{r method: one cal, message=FALSE, echo=TRUE,warning=FALSE}

df_3 <- df_2 %>% 
  pivot_wider(names_from = `Month`, values_from = sum_number) %>% 
  relocate(`Year`,January, February, March, April, May, June, July, August, September, October, November, December)

df_3

```


### References
#### citations for narrative and data sources

* Narrative and Data Sources: The National UFO Reporting Center Online Database, [GO](http://www.nuforc.org/webreports.html){target="_blank"}
