---
pagetitle: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---


```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

WRANGLERS


# Find String
## Find Datapoints that starts with, ends with, or contains a particular string.


```{r, out.width="20%", fig.align="center", fig.cap="Photo by ArtWorkLeaf, ID"}

# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "assets/4-wranglers-3-reduce.svg"
knitr::include_graphics(masthead, dpi=72)

```

While working on datasets it can be important to segment or filter data points that contains a particular character, alphabet or number. It can be anything from single text characters like the alphabet (A-Z), strings of alphabets("ame"), numeral digits (0-9), or punctuation (. ! ? ; :) from a string-type data. We can find strings in different positions and patterns whether it is at the start or the end. 

Finding strings can help us subset and work on a group of data points. For example, we can find names that starts with "C" and view the data associated with it. We can also operate on strings that we find, for example, we can find strings that contains "centimeters" and abbreviate it to "cm". 
