---
pagetitle: "World University Rankings"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---


```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(magick)
library(tidyverse)
library(ggiraph)
library(knitr)
library(kableExtra)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```


WRANGLERS  


# World University Rankings
## Find String

```{r, out.width="60%", fig.align="center", fig.cap="Photo by Pang Yuhao on Unsplash"}

masthead <- "assets/pang-yuhao-_kd5cxwZOK4-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">World Happiness Report</div>


> All truths are easy to understand once they are discovered; the point is to discover them.....\
--- Galileo Galilei\

***

### Load data




```{r Load raw data, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}


df<-read.csv('./archetypes/times-higher-education-world-university-ranking.csv')

df
```


### Exact String

#### Let's find the exact word <span style="color: #fc7f03;font-weight:bold">USA</span> in the <span style="color: #FE9A2E;font-weight:bold">country</span> field. 

```{r method: exact string, echo=TRUE, message=FALSE}
df_1 <- df %>% filter(str_detect(country, "USA"))

```



### Ends with
#### Or let's find all rows where <span style="color: #FE9A2E;font-weight:bold">country</span> ends with <span style="font-weight:bold">a</span>. 

```{r method: ends with, echo=TRUE, message=FALSE}
df_2<-df%>%filter(str_detect(country, "a$"))

```


### Starts with
#### Let's find all the rows where column <span style="color: #0000FF;font-weight:bold">institution</span> starts with <span style="font-weight:bold">A</span>. 

```{r method: starts with, echo=TRUE, message=FALSE}

df_3 <- df %>% filter(str_detect(institution, "^A"))

```


### Contains

#### Let's find all the rows where column <span style="color: #0000FF;font-weight:bold">institution</span> contains the word <span style="font-weight:bold">Technology</span>. 

```{r method: contains,  echo=TRUE, message=FALSE}
df_4<-df%>%filter(str_detect(institution, "Technology"))

```


### Contains digits

#### Let's find all the rows where column <span style="color: #0000FF;font-weight:bold">institution</span> contains any <span style="font-weight:bold">digits</span>. 

```{r method: contains digit,  echo=TRUE, message=FALSE}
df_5<-df%>%filter(str_detect(institution, "\\d"))

```

### Contains Either/Or

#### Let's find all the rows where column <span style="color: #0000FF;font-weight:bold">institution</span> contains the words <span style="font-weight:bold">University</span> OR <span style="font-weight:bold">College</span>. 

```{r method: contains either or,  echo=TRUE, message=FALSE}
df_6<-df%>%filter(str_detect(institution, "University|College"))

```


### Does NOT Contain

#### Let's find all the rows where column <span style="color: #0000FF;font-weight:bold">institution</span> does __NOT__ contain the word  <span style="font-weight:bold">University</span>. 

```{r method: does NOT contain,  echo=TRUE, message=FALSE}

df_7 <- df %>% filter(!str_detect(institution, "University"))

```

### References
#### The citations and data sources used for this case 

THE (Times Higher Education), https://www.timeshighereducation.com/content/world-university-rankings
