---
pagetitle: "Global wealth report"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(countrycode)
library(ggraph)
library(igraph)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
TREES  
</div>

# Global wealth report
## Circle packing


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Aleksey Malinovski on Unsplash"}

masthead <- "assets/aleksey-malinovski-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Everyone wants to ride with you in the limo,\
  but what you want is someone who will take the bus with you when the limo breaks down...\
--- Oprah Winfrey\

***

Published by the Credit Suisse Research Institute, the Global wealth report analyzes the household wealth of 5.2 billion people across the globe.

### Ingest the data
#### country, region, wealth


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_file_path <- "archetypes/global-wealth-report/global-wealth-report.csv"
df = read.csv(df_file_path, header = TRUE, stringsAsFactors = FALSE, encoding = "UTF-8")
df


```


### Wrangle the data
#### Create node and edge tables


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_wrangle <- df
df_wrangle$un_region <- countrycode(df_wrangle$country, origin='country.name', destination='un.region.name')
df_wrangle <- filter(df_wrangle, wealth_b > 0 )
df_wrangle <- filter(df_wrangle, nchar(un_region) > 0 )
df_wrangle

# Unique edges
df_edges <- aggregate(x = df_wrangle$wealth_b,
          by = list(df_wrangle$country, df_wrangle$un_region),
          FUN = sum)
colnames(df_edges) <- c("TO","FROM", "SIZE")
df_edges <- df_edges %>% select(FROM, TO)

# Root nodes
df_nodes_1 <- aggregate(x = df_wrangle$wealth_b,
          by = list(df_wrangle$un_region),
          FUN = sum)
colnames(df_nodes_1) <- c("NODE", "SIZE")
df_nodes_1$COLOR <- df_nodes_1$NODE

df_nodes_2 <- aggregate(x = df_wrangle$wealth_b,
          by = list(df_wrangle$country, df_wrangle$un_region),
          FUN = sum)

colnames(df_nodes_2) <- c("NODE", "COLOR", "SIZE")

# Combine
df_nodes <- rbind(df_nodes_1, df_nodes_2)

# Transform to graph data structure
df_graph <- graph_from_data_frame( df_edges, vertices = df_nodes )

```


#### edge table


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_edges

```

<p></p>
#### node table


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_nodes

```


### Plot
#### circle pack layout with size, color, and labels (at root level)


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    legend.position='none'
  )

region_pal <- c("Africa" = "#E57373", 
               "Americas" = "#80CBC4", 
               "Asia" = "#FDD835", 
               "Europe" = "#66BB6A",
               "Oceania" = "#FFB300")

n <- 10
top_x <- head(arrange(df_nodes_2, desc(SIZE)), n = n)
top <- top_x$SIZE[[1]]
bottom <- top_x$SIZE[[n]]

v1 <- ggraph(df_graph, layout = 'circlepack', weight = SIZE) + 
  geom_node_circle(aes(fill = COLOR)) + 
  scale_fill_manual(values = region_pal) +
  geom_node_text( aes(label=name, filter=SIZE >= bottom & SIZE <= top), size = 4, color = "#ffffff", family = "inconsolata", face="bold") +
  geom_node_label( aes(label=name, filter=depth==0), size = 6, family = "inconsolata") +
  coord_fixed() + 
  theme_void() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### References
#### citations for narrative and data sources

* Narrative source: How Much, All the World’s Wealth in One Visual, https://howmuch.net/articles/distribution-worlds-wealth-2019
* Narrative source: MakeOverMonday, https://data.world/makeovermonday/2020w7-world-wealth
* Data sources: Credit Suisse, Global Wealth Report, https://www.credit-suisse.com/about-us/en/reports-research/global-wealth-report.html


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

