---
pagetitle: "Vaccines in the pipeline"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
library(stringr)
library(ggraph)
library(igraph)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
TREES  
</div>

# Vaccines in the pipeline
## Circle packing


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by CDC on Unsplash"}

masthead <- "assets/cdc-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text">Swine Flu vaccination administered by way of a jet injector known as a “Ped-O-Jet®”, 1976</div>

> Science is telling us that we can do phenomenal things if we put our minds and our resources to it...\
--- Anthony Fauci\

***

To facilitate the creation and dissemination of new vaccines, the WHO maintains a list of vaccines in the “pipeline” for clinical trials. The sources on information for these trials are clinicaltrials.gov and who.int/ictrp, which includes clinical trial registries from 17 countries. Some information is also obtained through contact with investigators, sponsors, and funders of vaccine trials.

### Ingest the data
#### disease, phases, and sample size enrollment


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_file_path <- "archetypes/vaccines-in-the-pipeline/new-vaccines-in-the-pipeline.csv"
df = read.csv(df_file_path, header = TRUE, stringsAsFactors = FALSE)
df


```


### Wrangle the data
#### Create node and edge tables


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Complete cases
df_wrangle <- df %>% mutate(ID = row_number(), Size = as.numeric(Sample.Size..Enrollment))
df_wrangle <- filter(df_wrangle, Size > 0 )
df_wrangle <- filter(df_wrangle, nchar(Registry.ID) > 0 )

# Unique edges
df_edges <- aggregate(x = df_wrangle$Size,
          by = list(df_wrangle$Disease, df_wrangle$Registry.ID),
          FUN = sum)

# Standard edge table structure
colnames(df_edges) <- c("FROM","TO", "SIZE")

# Root nodes
df_nodes_1 <- aggregate(x = df_wrangle$Size,
          by = list(df_wrangle$Disease),
          FUN = sum)

colnames(df_nodes_1) <- c("NODE","SIZE")
df_nodes_1$COLOR <- "0"

# Leaf nodes
df_nodes_2 <- df_wrangle %>% select(Registry.ID, PNUM, Size)
colnames(df_nodes_2) <- c("NODE", "COLOR", "SIZE")

# Combine
df_nodes <- rbind(df_nodes_1, df_nodes_2)

# Complete cases
df_nodes <- filter(df_nodes, SIZE > 0 )


# Transform to graph data structure
df_graph <- graph_from_data_frame( df_edges, vertices = df_nodes )

```


#### edge table


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_edges

```

<p></p>
#### node table


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

df_nodes

```


### Plot
#### circle pack layout with size, color, and labels (at root level)


```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source ='fold-hide', fig.width=1920/72, fig.height=1080/72, out.width="100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata"), 
    legend.position='none'
  )

phase_pal <- c("0" = "#FFFFFF", "1" = "#6A1B9A", "1.5" = "#7B1FA2", "2" = "#8E24AA",
               "2.5" = "#9C27B0", "3" = "#AB47BC", "3.5" = "#BA68C8", "4" = "#CE93D8")

v1 <- ggraph(df_graph, layout = 'circlepack', weight = SIZE) + 
  geom_node_circle(aes(fill = COLOR)) + 
  scale_fill_manual(values = phase_pal) +
  geom_node_label( aes(label=name, filter=depth==0), size = 6, family = "inconsolata") +
  coord_fixed() + 
  theme_void() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
       options = list(opts_sizing(rescale = TRUE, width = 1.0))
)

```


### References
#### citations for narrative and data sources

* Narrative sources
* Data sources: WHO vaccine pipeline tracker, World Health Organization, http://www.who.int/immunization/research/vaccine_pipeline_tracker_spreadsheet/en/


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

