---
pagetitle: "Kamino"
output:
  bookdown::gitbook: default
documentclass: book
date: "`r Sys.Date()`"
---

```{r, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```
<div class="activity">
CHARTS  
</div>

# Scatter Contour
## Story-Telling with Scatter Contour

```{r, out.height="50%", out.width="50%", fig.align="center", fig.cap=""}
#masthead <- ""
#knitr::include_graphics(masthead, dpi=72)
```

Scatter plots' primary uses are to observe and show relationships between two numeric variables. A contour plot is appropriate if you want to see how some value Z changes as a function of two inputs, X and Y: z = f(x, y). Scatter-Contour provides a better visualization result as the contour which commonly show altitude (like height of a geographical features), can also be used to show density, brightness, or electric potential. Inclusion of contour are particularly helpful when you need to identify combinations of X and Y that produce beneficial or required values of Z. The contour lines and bands make it easy to find combinations that yield the values you need.

Contour plots are helpful to assess the following features of the dataset:

* __Explore the relationship between three variables on a single chart__
* __View combinations of X and Y that produce desirable outcome values__

Types of Contour plot:

* __Rectangular Contour__ : Projection of 2-D plot in 2-D rectangular canvas.
* __Polar Contour__ : They are circular and plotted by using the polar coordinates r and theta.
* __Ternary Contour __ : They are triangular and show a relationship between three explanatory variables and a response variable. Most commonly, the third explanatory variable is a height value for an XYZ value in ternary space.
