---
pagetitle: "Graphs Overview"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48


```

<div class="activity">
GRAPHS
</div>

# Clean data
## I want to fix irregularities in my dataset

> Don't call the world dirty because you forgot to clean your glasses...\
--- Aaron Hill\

***

The objective of this chapter is to describe representation patterns for highlighting relational phenomena. Relational views bring salience to associations, social structures, organization, and networks. The methods presented in this Chapter are intended for expressing connections, linkages and other structures.

Analysis of Linkages, Relations and Structures
Substance

Relational representations are based on the exploration and discovery of associations between entities. This method of analysis provides visibility of the relationships and associations between objects of diff erent types that are not apparent from raw data. These methods have long standing history for applications to social sciences and have developed through the contributions of multiple disciplines such as mathematics, graph theory, biology, physics, and other sciences. The common goal of these approaches is to provide visibility to structures that may be present as hidden patterns or links among seemingly unrelated items.

The mapping of social structures as “networks” means choosing nodes and links as the basic units of analysis. For example, in the analysis of policy networks or policy processes the nodes mostly represent political actors who are very often corporate actors (organizations), but may also be events or issues in a policy process. Links (edges) may represent diff erent types of relations, such as links of communication, participation, resource exchange, social and political support, infl uence reputation, status relations, etc. You will fi nd many practical uses for employing relational representation patterns to describe “small worlds”, organizational structures, communication networks, groups such as political parties, organizations, nation-states.

Representation Structures

These are the main points to understand as we discuss relation patterns. Many of the approaches demonstrated are generated by computer applications. It is important to understand that these options are available and may prove to be of valuable use to creating relational representations.

* Graph Layout Patterns
* Link and Network Analysis
* Flow and Diagram Layout Patterns

the plane can be used merely as a substrate to keep the visual identities of the nodes distinct.

Working with Network and Relational Data

Applying the layout patterns mentioned in this chapter requires specifi c data structure. The structure is most often found in one of three forms: an adjacency matrix, node and edge Lists, and various graph XML formats. Node and Edge Lists are sources provided in two parts, fi rst with the identifi cation of nodes, and second with the defi nition of relations. Remembering that nodes are the objects and edges are relations, a typical data set will contain records describing each.

Table 1: Node List
NodeID Label Attribute A Attribute B Measure A Measure B
n1
n2
n3
n4
n5

Table 2: Edge List
From To Weight
n1 n2
n1 n3
n2 n4
n3 n5

In Matrix an adjacency matrix also called sociomatrix or incidence matrix. A graph can be represented by an adjacency matrix, where each value in row i and column j corresponds to the link from node i to node j. Given this representation, an obvious visualization then is: show the matrix! Using color or saturation instead of text allows patterns to be perceived rapidly. The seriation problem applies just as much to the matrix view as to the arc diagram, so the order of rows and columns is important: here we use a community-detection algorithm to order and color the display.

While path following is harder in a matrix view than in a node-link diagram, matrices have a number of compensating advantages. As networks get large and highly connected, node-link diagrams often devolve into giant hairballs of line crossings. In matrix views, however, line crossings are impossible, and with an eff ective sorting one quickly can spot clusters and bridges. Allowing interactive grouping and reordering of the matrix facilitates deeper exploration of network structure.

Graph Formats Several graph specifi c formats are supported by special purpose graphing software. GraphML is a popular XML-format to describe the structural propoerties of a graph. The format would be structured as such:

<pre>
<graph id=”Graph” edgedefault=”undirected”>
<node id=”node0”/>
<node id=”node1”/>
<edge id=”edge1” source=”n0” target=”n1”/>
</graph>
</pre>

Graph Drawing Patterns

A relational graph is based on a mathematical algorithm for drawing nodes and edges in a calculated structure. A layout pattern refl ects the drawn structure of a relational graph. A “graph” refers to a collection
of nodes and a collection of edges that connect pairs of nodes. To better understand the basis for relational analysis and the methods of graph theory, fi ve basic points should be understood:

1. A node is a single graphed object or item;
2. An edge is a link between two nodes;
3. Relations between nodes may be directed or undirected;
4. Graphs may be connected or disconnected;
5. The distance between interrelated nodes is often termed degrees of separation; e.g. a nodeedge-node relation represents one degree of separation.

Graph Layouts (Layout by Structure)

Graph layout patterns are a suite of methods to provide “smart” and automatic organization of relational data structures into visual constructs. In the same way that charts are rendered from quantitative data, a graph layout provides a drawing method to relational data. These layouts are computed from specialized algorithm and mathematical models designed to render order and various aesthetic properties. Visualizing graphs and hierarchies has been a major research topic within the data visualization community since its conception in the early 1990s. The most commonly applied layout patterns are as tree and network. Each of these patterns provide computation methods for the rendering of relational data. The selection of a layout will be based on certain aesthetic properties such as:

* minimized number of edge crossings
* evenly distributed edge length
* evenly distributed node positions
* sufficient node-edge distances
* sufficient angular resolution between edges

The most commonly used aesthetic objectives are to expose symmetries and to maximize space usage. With this criteria in mind, we’ll explore the common layout structures.

### References
#### citations for narrative and data sources

Source: 



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

