---
pagetitle: "Maternal Mortality - Africa"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(tidyverse)
require(ggrepel)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
TEMPORALS
</div>

# Maternal Mortality - Africa
## Slope Plot


```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Barbara Verge on Unsplash"}

masthead <- "assets/barbara-verge-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```


> Mother is the name for God in the lips and hearts of little children....\
--- William Makepeace Thackeray\

***

### Ingest
#### country, year, maternal mortality ratio

```{r,  message=FALSE, warning=FALSE, echo=TRUE, class.source='fold-hide'}

df <- read.csv("archetypes/maternal-mortality/maternal-mortality.csv", header = TRUE, stringsAsFactors = FALSE)
head(df, n=10)

```


### Wrangle
#### Filter

*  __Year__ of <mark> 2000 </mark>, <mark> 2005 </mark>, <mark> 2010 </mark> and <mark> 2015 </mark>
* A few African countries under __Entity__  column

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Filter for year and continent
maternal_mortality_df <- df %>%
  filter(Year %in% c(2000, 2005, 2010, 2015) &
           Continent %in% c("Africa", "World"))

entity_list <- c("Angola", "Algeria","Cameroon", "Ethiopia", "Ghana", "Kenya" , "Rwanda", "Senegal", "Somalia", "South Sudan", "Sudan", "Tunisia", "Uganda", "Zimbabwe", "World")

maternal_mortality_df <- maternal_mortality_df %>%
  filter(Entity %in% entity_list)

head(maternal_mortality_df, n=10)

```


### Wrangle
#### Factor

Create ordered factor for __Year__

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

maternal_mortality_df$Year <- factor(maternal_mortality_df$Year, ordered = TRUE, levels = c("2000", "2005", "2010", "2015"))
head(maternal_mortality_df, n=10)

```


### Slope Plot
#### <kbd> geom_line() </kbd> and <kbd> geom_point() </kbd> 

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', out.width = "100%"}

color_palette <- c("Angola" = "#cccccb", 
                   "Algeria" = "#cccccb",
                   "Cameroon" = "#cccccb", 
                   "Ethiopia" = "#cccccb",
                   "Ghana" = "#cccccb",
                   "Kenya" = "#cccccb",
                   "Rwanda" = "#cccccb",
                   "Senegal" = "#cccccb",
                   "Somalia" = "#cccccb",
                   "South Sudan" = "#cccccb",
                   "Sudan" = "#cccccb",
                   "Tunisia" = "#cccccb",
                   "Uganda" = "#d8472b",
                   "Zimbabwe" = "#cccccb",
                   "World" = "#7dbfe6")

slope_specs <- list(  
  # move the x axis labels up top
  scale_x_discrete(position = "top"),
  theme_bw(),
  # Format tweaks
  # Remove the legend
  theme(legend.position = "none"),
  # Remove the panel border
  theme(panel.border     = element_blank()),
  # Remove just about everything from the y axis
  theme(axis.title.y     = element_blank()),
  theme(axis.text.y      = element_blank()),
  theme(panel.grid.major.y = element_blank()),
  theme(panel.grid.minor.y = element_blank()),
  # Remove a few things from the x axis and increase font size
  theme(axis.title.x     = element_blank()),
  theme(panel.grid.major.x = element_blank()),
  theme(axis.text.x.top      = element_text(size=12)),
  # Remove x & y tick marks
  theme(axis.ticks       = element_blank()),
  # Format title & subtitle
  theme(plot.title       = element_text(size=14, face = "bold")),
  theme(plot.subtitle    = element_text())
)

v1 <- ggplot(data = maternal_mortality_df, aes(x = Year, y = Maternal_Mortality_Ratio, group = Entity)) +
  geom_line(aes(color = Entity), size = 0.5, alpha = 1) +
  geom_text_repel(data = maternal_mortality_df %>% filter(Year == "2000"), 
                  aes(label = paste0(Entity)) , 
                  force = 1,
                  hjust = "left", 
                  fontface = "bold", 
                  size = 2.5, 
                  nudge_x = -.5, 
                  direction = "y",
                  segment.color = "gray") +
  geom_text_repel(data = maternal_mortality_df %>% filter(Year == "2015"), 
                  aes(label = paste0(Entity)), 
                  force = 1,
                  hjust = "right", 
                  fontface = "bold", 
                  size = 2.5, 
                  nudge_x = .5, 
                  direction = "y",
                  segment.color = "gray") +
  geom_point(aes(fill = Entity), shape = 21, color="white", size = 2, stroke = 0.75, alpha = 1) +
  # geom_text(aes(label = Maternal_Mortality_Ratio), color="black", size = 2.5, alpha = 1) +
  geom_text_repel(aes(label = Maternal_Mortality_Ratio), color="black", size = 2.5, alpha = 1,
                  force = 1,
                  hjust = "center", 
                  #fontface = "bold", 
                  size = 2.0, 
                  # nudge_x = 0, 
                  direction = "y",
                  segment.color = "gray") +
  scale_fill_manual(values = color_palette) +
  scale_color_manual(values = color_palette) +
  slope_specs +
  labs(
    title = "Maternal Mortality by Country",
    subtitle = "Africa, Maternal deaths per 100,000 live births.",
    caption = "source: Our World in Data"
  )

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
      options = list(opts_sizing(rescale = TRUE, width = 1.0)))


```


### References
#### citations for narrative and data sources

* Narrative and Data sources: Maternal Mortality - Our World in Data, [GO](https://ourworldindata.org/grapher/maternal-mortality-slope-chart?time=1990..latest&country=ARG~BOL~BRA~ECU~GUY~URY~VEN~PRY~PER~SUR~CHL~CO){target="_blank"}



```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```



```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
