---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(htmltools) # needed to include html snippets
library(tidyverse)

library(purrr)
library(kableExtra)

library(knitcitations)
library(bibtex)
library(ggiraph)
library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
WRANGLERS  
</div>

# Google Trending Searches on "Data Science"
## Format Date


```{r, out.width="60%", fig.align="center", fig.cap="Photo by Luke Chesser on Unsplash"}

masthead <- "assets/trend-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

<div class="figure-text"> Trends Visualization</div>

> To be a consistent winner means preparing not just one day, one month or even one year - but for a lifetime...\
--- Bill Rodgers\

***

### Load data


```{r load-data, echo=TRUE, message=FALSE, warning=FALSE,class.source = 'fold-hide'} 

df <- read.csv('archetypes/google-trend-on-data-science.csv')

```

<!-- FOR DISPLAY ONLY -->

```{r Styling Data Set, echo=FALSE}

#NOT TO BE USED AS SOLUTION
df_tmp <- df

df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = c("striped", "hover"))%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)

#NOT TO BE USED AS SOLUTION

```


### Convert character format into date format 

#### Let's focus on the <span style="color: #8000FF;font-weight:bold">Time</span> column. 

#### If only the __date__ (not the time) portion of the data is needed, then use as.Date to convert the characters into date format.

```{r convert date, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_1 <- df
df_1$date <- as.Date(df$Time)

```

<!-- FOR DISPLAY ONLY -->

```{r Styling Data Set1, echo=FALSE}

#NOT TO BE USED AS SOLUTION

df_tmp <- df_1

names(df_tmp)[3] <- cell_spec(names(df_tmp)[3], color = "#8000FF")
      
df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = c("striped", "hover"))%>%
column_spec(3, bold = TRUE, color = "#000000", background = "#E3CEF6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)

#NOT TO BE USED AS SOLUTION 

```

#### On the other hand, if __time__ is important to us, then add the time into the date format as <span style="font-weight:bold">%Y-%m-%dT%H:%M:%S</span>. You may set the default system time zone to convert the date and time. In our case, it only records in hours.

```{r method: convert time, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_2 <- df
df_2$Time <-as.POSIXct(df_2$Time, format = "%Y-%m-%dT%H",tz=Sys.timezone())

```

<!-- FOR DISPLAY ONLY -->

```{r Styling Data Set2, echo=FALSE}

#NOT TO BE USED AS SOLUTION

df_tmp <- df_2

names(df_tmp)[1] <- cell_spec(names(df_tmp)[1], color = "#8000FF")
      
df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = c("striped", "hover"))%>%
column_spec(1, bold = TRUE, color = "#000000", background = "#E3CEF6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)

#NOT TO BE USED AS SOLUTION

```



### Quarter

#### Use this method to create a <span style="color: #2E2EFE;font-weight:bold">Quarter</span> column which categorizes each record into each quarter as per <span style="color: #8000FF;font-weight:bold">Time</span>.

```{r method: qtr,  message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_3 <- df
df_3$Quarter <-quarters(df_2$Time)

```

<!-- FOR DISPLAY ONLY -->

```{r Styling Data Set3, echo=FALSE}

#NOT TO BE USED AS SOLUTION

df_tmp <- df_3
names(df_tmp)[1] <- cell_spec(names(df_tmp)[1], color = "#8000FF")
names(df_tmp)[3] <- cell_spec(names(df_tmp)[3], color = "#2E2EFE")

df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = c("striped", "hover"))%>%
column_spec(3, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)

#NOT TO BE USED AS SOLUTION 

```

### Year

#### Use this method to create a <span style="color: #2E2EFE;font-weight:bold">Year</span> column which captures the year of <span style="color: #8000FF;font-weight:bold">Time</span>.


```{r method: yr, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_4 <- df_2
df_4$Year <- format(df_2$Time,format="%Y")

```

<!-- FOR DISPLAY ONLY -->

```{r Styling Data Set4, echo=FALSE}

#NOT TO BE USED AS SOLUTION

df_tmp <- df_4

names(df_tmp)[1] <- cell_spec(names(df_tmp)[1], color = "#8000FF")
names(df_tmp)[3] <- cell_spec(names(df_tmp)[3], color = "#2E2EFE")

df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = c("striped", "hover"))%>%
column_spec(3, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)

#NOT TO BE USED AS SOLUTION 

```


### Year_Month

#### Use this method to create a <span style="color: #2E2EFE;font-weight:bold">Year_Month</span> column which captures only the combination year and month of <span style="color: #8000FF;font-weight:bold">Time</span>.

```{r method: ym, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_5 <- df_2
df_5$Year_Month <-format(df_2$Time,format="%Y-%m")

```

<!-- FOR DISPLAY ONLY -->

```{r Styling Data Set5, echo=FALSE}

#NOT TO BE USED AS SOLUTION

df_tmp <- df_5

names(df_tmp)[1] <- cell_spec(names(df_tmp)[1], color = "#8000FF")
names(df_tmp)[3] <- cell_spec(names(df_tmp)[3], color = "#2E2EFE")

df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = c("striped", "hover"))%>%
column_spec(3, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)

#NOT TO BE USED AS SOLUTION 

```



### Month
#### Use this method to create a <span style="color: #2E2EFE;font-weight:bold">Month</span> column (Numeric or Abbreviation format) which captures only the month of <span style="color: #8000FF;font-weight:bold">Time</span>.


```{r method: m, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_6 <- df_2
df_6$Month_Num <-format(df_2$Time,format="%m")
df_6$Month_ABR <-format(df_2$Time,format="%b")

```

<!-- FOR DISPLAY ONLY -->

```{r Styling Data Set6, echo=FALSE}

#NOT TO BE USED AS SOLUTION

df_tmp <- df_6

names(df_tmp)[1] <- cell_spec(names(df_tmp)[1], color = "#8000FF")
names(df_tmp)[3] <- cell_spec(names(df_tmp)[3], color = "#2E2EFE")
names(df_tmp)[4] <- cell_spec(names(df_tmp)[4], color = "#2E2EFE")

df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = c("striped", "hover"))%>%
column_spec(3:4, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)

#NOT TO BE USED AS SOLUTION 

```


### Month_Day
#### Likewise, use this method to create a <span style="color: #2E2EFE;font-weight:bold">Month_Day</span> column (Numeric or Name format) which captures the month-and-day (or day-and-month) combination of <span style="color: #8000FF;font-weight:bold">Time</span>.


```{r method: md, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-show'} 

df_7 <- df_2
df_7$MM_DD_Num <- format(df_2$Time,format="%m-%d")
df_7$DD_MM_Name <- format(df_2$Time,format="%d %B")

```

<!-- FOR DISPLAY ONLY -->

```{r Styling Data Set7, echo=FALSE}

#NOT TO BE USED AS SOLUTION

df_tmp <- df_7

names(df_tmp)[1] <- cell_spec(names(df_tmp)[1], color = "#8000FF")
names(df_tmp)[3] <- cell_spec(names(df_tmp)[3], color = "#2E2EFE")
names(df_tmp)[4] <- cell_spec(names(df_tmp)[4], color = "#2E2EFE")

df_tmp%>%
kable(escape = FALSE)%>%
kable_styling(position = "center", full_width = FALSE, bootstrap_options = c("striped", "hover"))%>%
column_spec(3:4, bold = TRUE, color = "#000000", background = "#CEE3F6")%>%
scroll_box(height = "350px", width = "NULL", extra_css = NULL, fixed_thead = TRUE)

#NOT TO BE USED AS SOLUTION

```


### Plot an example
```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width= 1920/72, fig.height = 1080/72, out.width = "100%"}
df <- read.csv('archetypes/historical-trend-on-data-science.csv')
df_1 <- add_column(df,date=paste0(df$Month,'-01'))
df_1$quarter<-quarters(as.Date(df_1$date))
df_1$year<-format(as.Date(df_1$date),format="%Y")

df_2 <- df_1 %>% group_by(quarter,year) %>% summarise(sum_number=sum(data.science...Worldwide.))%>% filter(between(year, as.numeric("2013"), as.numeric("2020")))
rownames(df_2) <- NULL
df_3 <- df_1 %>% group_by(year) %>% summarise(sum_number=sum(data.science...Worldwide.))%>%filter(year!=2021)
rownames(df_3) <- NULL
v1<-ggplot(data=df_3, aes(x=year, y=sum_number, group=1))+
  geom_line(color='#2E2EFE',size=1.5,alpha=0.3)+
  geom_point(color='#2E2EFE',size=1.8)+
  theme_minimal()+labs(
    x='Year',
    y='Search Frequency'
  )
v2<-ggplot(data=df_2, aes(x=quarter, y=sum_number, group=year)) +
  geom_step(aes(color=year))+
  geom_point(aes(color=year))+
  theme_minimal()+labs(
    x='Quarter',
    y='Search Frequency'
  )

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72, options =
list(opts_sizing(rescale = TRUE, width = 1.0)))

girafe(ggobj = v2, width_svg = 1280/72, height_svg = 720/72, options =
list(opts_sizing(rescale = TRUE, width = 1.0)))
```

### As reusable solution
```{r eval=FALSE, echo=TRUE, message=FALSE, include=TRUE}

####################################################################################
# Required libraries
# Not Required
####################################################################################


####################################################################################
# Convert Character Format to Date Format
f_chardate <- function(df_chardate) {
  as.Date(df_chardate)
}

# Call the function with your values to the parameters
df$Time2 <- f_chardate(df$Time)
####################################################################################

 
####################################################################################
# Convert to Date-Time Format
f_dateTime <- function(df_dateTime) {
  as.POSIXct(df_dateTime, format = "%Y-%m-%dT%H",tz=Sys.timezone())
}

# Call the function with your values to the parameters
df$Time2 <- f_dateTime(df$Time)
####################################################################################


####################################################################################
# Crete Quarter Column from Date Data
f_quarter <- function(df_quarter) {
  temp <<- as.Date(df_quarter) #if not in Date Format
  quarters(temp)
}

# Call the function with your values to the parameters
df$Time2 <- f_quarter(df$Time)
####################################################################################


####################################################################################
# Extract Year from Date Data
f_year <- function(df_year) {
  temp <<- as.Date(df_year) #if not in Date Format
  format(temp,format="%Y")
}

# Call the function with your values to the parameters
df$Time2 <-f_year(df$Time)
####################################################################################


####################################################################################
# Extract Year-Month from Date Data
f_yearMonth <- function(df_yearMonth) {
  temp <<- as.Date(df_yearMonth) #if not in Date Format
  format(temp,format="%Y-%m")
}

# Call the function with your values to the parameters
df$Time2 <- f_yearMonth(df$Time)
####################################################################################



####################################################################################
# Extract Month (numerical) from Date Data
f_monthNum <- function(df_monthNum) {
  temp <<- as.Date(df_monthNum) #if not in Date Format
  format(temp,format="%m")
}

# Call the function with your values to the parameters
df$Time2 <- f_monthNum(df$Time)
####################################################################################


####################################################################################
# Extract Month (Alphabetical) from Date Data
f_monthAlpha <- function(df_monthAlpha) {
  temp <- as.Date(df_monthAlpha) #if not in Date Format
  format(temp,format="%b")
}

# Call the function with your values to the parameters
df$Month <- f_monthAlpha(df$Time)
####################################################################################


####################################################################################
# Extract Month-Day (Alphabetical) from Date Data
f_monthDay <- function(df_monthDay) {
  temp <<- as.Date(df_monthDay) #if not in Date Format
  format(temp,format="%d %B")
}

# Call the function with your values to the parameters
df$Time2 <- f_monthDay(df$Time)
####################################################################################



####################################################################################
# Extract Several Date Formats by substituting "type"
f_dateType <- function(df_dateType, type) {
  temp <<- as.Date(df_dateType) #if not in Date Format
  format(temp,format=type)
}

# Call the function with your values to the parameters
df$Time2 <- f_dateType(df$Time, "%d %B")
####################################################################################
```



# References
## The citations and data sources used for this case

The data source was from <a href="https://trends.google.com/trends/trendingsearches/daily?geo=US" target="_blank">Google Trending Searches on "Data Science"</a>.

```{r generateBibliography, echo=FALSE, message=FALSE, warning=FALSE}

cleanbib()
options("citation_format" = "pandoc")
read.bibtex(file = "./citations/google-trend-on-data-science.bib")

```

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "Format-Date character-to-date date-month-alphabetical date-month-numerical date-quarters date-year date-day-month date-to-datetime date-year-month date-extract-all" # mostly used in wranglers and analytics
keywords <- 'google data-science'
commands <- 'as.Daate as.POSIXct quarters format mutate'
sources <- 'Google'

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

