---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()


```

<div class="activity">
WRANGLERS 
</div>

# Format Date
## Convert to Date, Quarter, Year, Month and Combinations {#when-to-use}

```{r, out.width="20%", fig.align="center"}

masthead <- "assets/noun_code formatting_2665697.svg"
knitr::include_graphics(masthead, dpi=72)

```

Formatting date might be a crucial task when dealing with time series data sets or any data set where date and time are important portions of the data to be analyzed. Having your dates in the proper format allows R to know that the data points are dates, and as such knows what calculations can or can not be performed on them. It is also the foundation for our data window and date math courses in the __Analytics section__. Dates can be imported from various formats such as character, numeric, and POSIXlt.

These are the key solutions when Formatting Date:

* __Convert Other DataTypes into Date Format__
* __Extract Specific Month/Year/Day from Dates__
* __Categorize Time Data into Different Quarters__

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "Format-Date character-to-date date-month-alphabetical date-month-numerical date-quarters date-year date-day-month date-to-datetime date-year-month date-extract-all" # mostly used in wranglers and analytics
keywords <- ''
commands <- ''
sources <- ''

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

