---
pagetitle: "Welcome to Earth!"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.

library(ggplot2)
library(gridExtra)
library(ggthemes)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
TEMPORAL  
</div>


# Welcome to Earth! 
## Area

```{r, out.width = "60%", fig.align = 'center', fig.cap="Photo by Albert Anthony on Unsplash"}

masthead <- "assets/albert-antony-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> No unidentified objects in the popular sense have been seen from the International Space Station...\
--- NASA\


***

## Load data [Ingest]

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load csv data file
df = read.csv("archetypes/welcome-to-earth/national-ufo-reporting-database-aggregated.csv", header = TRUE, stringsAsFactors = FALSE)
df

```


## Prepare data [Wrangle]


```{r echo=TRUE, message=FALSE, warning=FALSE, class.source = 'fold-hide'}

# Convert to date
df$Date <- as.Date(df$Date, "%m-%d-%Y")
df

```


## Plot [ Views / Temporals ]

```{r echo=TRUE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, , fig.align='center', class.source='fold-hide', out.width="100%"}

theme_opts <- theme(
    plot.title = element_text(color = "black", size = 12, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 8),
    plot.caption = element_text(color = "#555555", size = 8),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    # axis.text.x = element_text(vjust = 12),
    panel.border = element_blank(),
    panel.background = element_blank(),
    panel.grid.minor = element_blank(), # remove minor gridlines
    panel.grid.major.x = element_blank(), # remove x (vertical) gridlines
    legend.title = element_blank(), # remove legend title
    legend.text = element_text(color = "black", size = 8),
    legend.position='top'
  )


# Plot
v1 <- ggplot(df, aes(x=Date, y=Count)) + 
  geom_area(color = "#458cb6", fill= "#a1b5d2", alpha=1.0 , size=0.5) +
   #geom_hline(yintercept = c(seq(0, 100, 10)), color="#ffffff", size=0.25, alpha=0.2) + # gridlines in the forefront
  scale_x_date(date_labels = "%b") +
  scale_y_continuous(breaks=seq(0, 2500, 500)) +
  labs( title = "Welcome to Earth!",
        subtitle = "United States, cumulative daily reported UFO sightings, 2020",
        caption = "The Economist, The National UFO Reporting Center Online Database") +
  theme_bw() +
  theme_opts

girafe(ggobj = v1, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.9)))

```

## Plot with annotations [ Views / Temporals ]

```{r echo=TRUE, fig.height=6, fig.width=12, message=FALSE, warning=FALSE, , fig.align='center', class.source='fold-hide', out.width="100%"}

v2 <- v1 + annotate("text", x = as.Date("1-1-2020", "%m-%d-%Y"), y = 600, 
             label = "  January 1st", 
             hjust = "left", vjust = 0, color = "#458cb6", size = 4, fontface = 2) +
    annotate("text", x = as.Date("7-4-2020", "%m-%d-%Y"), y = max(df$Count), 
             label = "  July 4th", 
             hjust = "left", vjust = 1, color = "#458cb6", size = 4, fontface = 2)

girafe(ggobj = v2, width_svg = 16, height_svg = 9,
       options = list(opts_sizing(rescale = TRUE, width = 0.9)))
  
```



```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Save plot to svg file
# ggsave(filename = "assets/economist-welcome-to-earth.svg", plot = v2, width=12, height=6)

```


# References
## The citations and data sources used for this case

* Narrative and Data Sources: The National UFO Reporting Center Online Database, [GO](http://www.nuforc.org/webreports.html){target="_blank"}

```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```

```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```
