---
pagetitle: "Global homicide rates"
output:
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    code_folding: show
    include:
      in_header: ["../../../z-assemblers/fragments/google-analytics.html", "../../../z-assemblers/fragments/header.html"]
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen = 999) ## To disable scientific notation

# Clear environment and memory
rm(list = ls(all.names = TRUE)) # will clear all objects including hidden objects.
gc() #free up memory and report the memory usage.

# Load needed libraries
library(tidyverse)
library(ggiraph)

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()

```

<div class="activity">
CHARTS
</div>

# Global Homicide Rates
## Bar Vertical Negative 

```{r, out.width="60%", fig.align="center", fig.cap="Photo from Wikipedia based on original oil painting by Jerry Barrett"}

masthead <- "assets/lacie-slezak-gHwOUe9OLwE-unsplash.jpg"
knitr::include_graphics(masthead, dpi=72)

```

> Murder is always a mistake, One should never do anything that one cannot talk about after dinner...\
--- Oscar Wilde\

***

### Load the data
#### Homicides are falling around the world, 1995-2015

```{r load-data, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide'}

# Load data
df <- read_csv("archetypes/global-homicide-rates/homicides-falling.csv", col_names=TRUE)
df

```

### Plot
#### Eastern Europe in particular has seen steep drops, by as much as 75%

```{r, message=FALSE, warning=FALSE, echo=TRUE, class.source = 'fold-hide', fig.width = 1920/72, fig.height = 1080/72, out.width = "100%"}

theme_opts <- theme(
    text = element_text(family = "inconsolata", size = 16), 
    plot.title = element_text(color = "black", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "black", size = 12),
    plot.caption = element_text(color = "#555555", size = 10),
    axis.text.x = element_text(angle=90, hjust=1, vjust=0.2),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.background = element_rect(fill = alpha("#1db4b3", 0.4))
)

v1 <- ggplot(df, aes(x=country, y=change)) +
  geom_bar(stat="identity", width=0.6, fill="white", alpha=0.8) +
  geom_point(shape=25, fill="white", color="white", alpha=0.7, size=2.1) +
  geom_text(aes(y = (change - 0.05), label = paste(change * 100, "%")), hjust = 0.0, angle=90, size=3, family = "inconsolata") +
  labs(title="Homicides Are Falling Around the World",
       subtitle="% decrease 1995-2015",
       caption="Source: World Bank",
       x = NULL, y = NULL) +
  theme_minimal() +
  theme_opts

girafe(ggobj = v1, width_svg = 1280/72, height_svg = 720/72,
      options = list(opts_sizing(rescale = TRUE, width = 1.0)))

```

### References
#### The citations and data sources used for this case

* Narrative sources: Homicides Are Falling Around the World, [GO](https://informationisbeautiful.net/beautifulnews/695-homicides-falling/){target="_blank"}


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk
# PUSH TO PRODUCTION
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())

```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

