---
pagetitle: "Kamino"
output: 
  html_document:
    theme: lumen
    css: "../../../z-assemblers/assets/styles/content.css"
    df_print: paged
    mathjax: NULL
    #code_folding: show
    include:
      in_header: "../../../z-assemblers/fragments/header.html"
      after_body: "../../../z-assemblers/fragments/footer.html"
    self_contained: false
    lib_dir: "vendor"
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo=FALSE)
options(scipen=999)  # turn-off scientific notation like 1e+48

# Clear environment and memory
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage.

library(showtext)
## Loading Google fonts (https://fonts.google.com/)
font_add_google("Inconsolata", "inconsolata")
# turn on showtext
showtext_auto()
```

<div class="activity">
WRANGLERS
</div>

# Find String
## Find Datapoints that starts with, ends with, or contains a particular string.


```{r, out.width="20%", fig.align="center", fig.cap="Photo by ArtWorkLeaf, ID"}
# image of an icon to represent the activity or any method (visit for icon https://thenounproject.com/search/?q=attribute&i=4326168)
masthead <- "assets/4-wranglers-3-reduce.svg"
knitr::include_graphics(masthead, dpi=72)

```

While working on datasets it can be important to segment or filter data points that contains a particular character, alphabet or number. It can be anything from single text characters like the alphabet (A-Z), strings of alphabets("ame"), numeral digits (0-9), or punctuation (. ! ? ; :) from a string-type data. We can find strings in different positions and patterns whether it is at the start or the end. 

Finding strings can help us subset and work on a group of data points. For example, we can find names that starts with "C" and view the data associated with it. We can also operate on strings that we find, for example, we can find strings that contains "centimeters" and abbreviate it to "cm". 


```{r, echo=FALSE, eval=FALSE, message=FALSE, warning=FALSE, class.source='fold-hide'}

# eval = FALSE as default; run manually as chunk

# ENTER METADATA
# Use space to separate keywords or "-" for phrases
methods <- "contains-digits ends-with exact-string not-contain starts-with" # mostly used in wranglers and analytics
keywords <- ''
commands <- ''
sources <- ''

# CREATE METADATA
source("../../../z-scripts/create_metadata.R", local = knitr::knit_global())

# RUN PRODUCTION OUTPUTS
source("../../../z-scripts/create_production_output.R", local = knitr::knit_global())


```


```{js, message=FALSE, warning=FALSE, echo=FALSE}

// Must be included to position footer
$(function() {
  $('.main-container').after($('.footer'));
})

```

